### 2024-07-15 ProxySelection.Rmd
Proxy selection methods include: Bross formula, hybrid bross & lasso, pure lasso, elastic net, xgboost, GA,  SVM,  Boruta, stepwise (forward, backward and both direction)

---
title: "Step1_LoadData"
author: "Yang Lei"
date: "2024-07-11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Codechuck 0. Loading data -- Generating Recurrence Covariates**

_Step 0: Analytic data, Step 1: Proxy sources, Step 2: Emperical, Step 3: Recurrence_
```{r loading-data, warning=FALSE}
# ------------------- Select proxy based on the results from out2
# ------------------- change the code after Step 3: Recurrence
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)

load("data/analytic3cycles.RData")

analytic <- data.complete
idx <- analytic$id
outcome <- as.numeric(analytic$diabetes == "Yes") 
exposure <- as.numeric(analytic$obese == "Yes")

domain <- "dx"
analytic.dfx <- as.data.frame(cbind(idx, exposure, outcome, domain))
dat.proxy.long <- subset(dat.proxy.long, 
                         icd10 != "E66") # Overweight and obesity
dat.proxy.long <- subset(dat.proxy.long, 
                         icd10 != "O24") # Gestational diabetes mellitus
dat.proxy.long <- subset(dat.proxy.long, 
                         icd10 != "E10") # Type 1 diabetes mellitus
dat.proxy.long <- subset(dat.proxy.long, 
                         icd10 != "E11") # Type 2 diabetes mellitus
proxy.var.long <- dat.proxy.long
proxy.var.long$idx <- proxy.var.long$id
proxy.var.long$id <- NULL
dfx <- merge(analytic.dfx, proxy.var.long, by = "idx")
# ------------------- now the proxy data was combined to the A and Y

# basetable <- dfx %>% select(idx, exposure, outcome) %>% distinct()
basetable <- dfx[, c(1:3)] %>% distinct()
patientIds <- basetable$idx
length(patientIds)
# ------------------- number of observations

save(dfx, patientIds, basetable, file = "data/dfx.RData")
load(file = "data/dfx.RData")

require(autoCovariateSelection)
step1 <- get_candidate_covariates(df = dfx,  
                                  domainVarname = "domain",
                                  eventCodeVarname = "icd10", 
                                  patientIdVarname = "idx",
                                  patientIdVector = patientIds,
                                  n = 200, 
                                  min_num_patients = 20)
out1 <- step1$covars_data
# ------------------- top 200 prevalent icd10 with min 20 patients

step2 <- get_recurrence_covariates(df = out1, 
                                   patientIdVarname = "idx",
                                   eventCodeVarname = "icd10", 
                                   patientIdVector = patientIds)
out2 <- step2$recurrence_data

exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
```

**Method 1: Bross Formula**
```{r, warning=FALSE}
out3 <- get_prioritised_covariates(df = out2,
                                   patientIdVarname = "idx", 
                                   exposureVector = basetable$exposure,
                                   outcomeVector = basetable$outcome,
                                   patientIdVector = patientIds, 
                                   k = 100)
hdps.dim <- out3$autoselected_covariate_df

load("data/analytic3cycles.RData")
hdps.dim$id <- hdps.dim$idx
hdps.dim$idx <- NULL
hdps.data <- merge(data.complete[,c("id",
                                    outcome, 
                                    exposure, 
                                    investigator.specified.covariates)], 
                   hdps.dim, by = "id")

hdps.data$exposure <- as.numeric(I(hdps.data$obese=='Yes'))
hdps.data$outcome <- as.numeric(I(hdps.data$diabetes=='Yes'))

proxy.list.sel <- names(out3$autoselected_covariate_df[,-1])
proxyform <- paste0(proxy.list.sel, collapse = "+")
covform <- paste0(investigator.specified.covariates, collapse = "+")
rhsformula <- paste0(c(covform, proxyform), collapse = "+")
ps.formula <- as.formula(paste0("exposure", "~", rhsformula))

require(WeightIt)
W.out <- weightit(ps.formula, 
                  data = hdps.data, 
                  estimand = "ATE",
                  method = "ps")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
fit <- glm(out.formula,
           data = hdps.data,
           weights = W.out$weights,
           family= binomial(link = "logit"))
fit.summary <- summary(fit)$coef["exposure",
                                 c("Estimate", 
                                   "Std. Error", 
                                   "Pr(>|z|)")]
fit.ci <- confint(fit, level = 0.95)["exposure", ]
fit.summary_with_ci <- c(fit.summary, fit.ci)
fit.summary_with_ci

fs.bross <- proxy.list.sel
sum_ci.bross <- c(exp(fit.summary_with_ci[1]), fit.summary_with_ci)
names(sum_ci.bross) <- c("Odds Ratio",
                          "Estimate",
                          "Std. Error",
                          "Pr(>|z|)",
                          "2.5 %",
                          "97.5 %")

print("No need to print the number of proxy variables selected, as it is set to be 100.")

print("The Odds Ratio by Bross Formula")
round(sum_ci.bross, 3)
```

**Method 2: Hybrid Bross Formula & Lasso**
```{r, warning=FALSE}
set.seed(42)
proxy.list <- names(out3$autoselected_covariate_df[,-1])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
lasso.fit<-glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 1, 
                             nfolds = 5)
coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.hybrid <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.hybrid)
fs.hybrid <- proxy.list.sel.hybrid

proxyform <- paste0(proxy.list.sel.hybrid, collapse = "+")
rhsformula <- paste0(c(covform, proxyform), collapse = "+")
ps.formula <- as.formula(paste0("exposure", "~", rhsformula))

W.out <- weightit(ps.formula, 
                  data = hdps.data, 
                  estimand = "ATE",
                  method = "ps")

out.formula <- as.formula(paste0("outcome", "~", "exposure"))
fit <- glm(out.formula,
           data = hdps.data,
           weights = W.out$weights,
           family= binomial(link = "logit"))
fit.summary <- summary(fit)$coef["exposure",
                                 c("Estimate", 
                                   "Std. Error", 
                                   "Pr(>|z|)")]
fit.ci <- confint(fit, level = 0.95)["exposure", ]
fit.summary_with_ci.h <- c(fit.summary, fit.ci)
sum_ci.hybrid <- c(exp(fit.summary_with_ci.h[1]), fit.summary_with_ci.h)

paste("The number of proxy variables selected:", length(proxy.list.sel.hybrid))
print("All proxy variables selected are in common as they are all selected from 
      the proxy variable list by the bross formula")

print("The Odds Ratio by Bross Formula & Lasso")
round(sum_ci.hybrid, 3)
```

_Before implementing other methods, drop the information from method 1 (Bross formula). Continue with the results from Step 3: Recurrence (table `out2`)._
```{r, warning=FALSE}
hdps.dim <- out2

load("data/analytic3cycles.RData")
hdps.dim$id <- hdps.dim$idx
hdps.dim$idx <- NULL
hdps.data <- merge(data.complete[,c("id",
                                    outcome, 
                                    exposure, 
                                    investigator.specified.covariates)], 
                   hdps.dim, by = "id")

hdps.data$exposure <- as.numeric(I(hdps.data$obese=='Yes'))
hdps.data$outcome <- as.numeric(I(hdps.data$diabetes=='Yes'))

proxy.list.sel <- names(out2[,-1])
proxyform <- paste0(proxy.list.sel, collapse = "+")
covform <- paste0(investigator.specified.covariates, collapse = "+")
rhsformula <- paste0(c(covform, proxyform), collapse = "+")
ps.formula <- as.formula(paste0("exposure", "~", rhsformula))

proxy.list <- names(out2[,-1])    # length(proxy.list) :  142
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )

```

**Method 3: Pure Lasso**
```{r, warning=FALSE}
set.seed(42) # different seed -> different length for the selected proxy list
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
lasso.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                               x = covar.mat, 
                               type.measure='mse',
                               family="binomial",
                               alpha = 1, 
                               nfolds = 5)
coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.ml <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.ml)
fs.lasso <- proxy.list.sel.ml
proxy.lasso <- paste0(fs.lasso, collapse = "+")
form.lasso <- paste0(c(covform, proxy.lasso), collapse = "+")
formula.lasso <- as.formula(paste0("exposure", "~", form.lasso))

require(WeightIt)
W.out.lasso <- weightit(formula.lasso, 
                        data = hdps.data, 
                        estimand = "ATE",
                        method = "ps")

hdps.data$ps.l <- W.out.lasso$ps
hdps.data$w.l <- W.out.lasso$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
out.formula
fit.lasso <- glm(out.formula,
                 data = hdps.data,
                 weights = W.out.lasso$weights,
                 family= binomial(link = "logit"))
summary.lasso <- summary(fit.lasso)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci.lasso <- confint(fit.lasso, level = 0.95)["exposure", ]
sum_ci.lasso <- c(exp(summary.lasso[1]), summary.lasso, ci.lasso)
names(sum_ci.lasso) <- c("Odds Ratio",
                         "Estimate",
                         "Std. Error",
                         "Pr(>|z|)",
                         "2.5 %",
                         "97.5 %")

# Q1: How many proxy variables are in common?
# length(fs.lasso)  # 60 features selected by lasso
# length(fs.lasso[fs.lasso %in% fs.bross])  # 47 of 60 also selected by bross
print("How many proxy variables are in common?")
paste("There are", length(fs.lasso), "features selected by lasso")
paste(length(fs.lasso[fs.lasso %in% fs.bross]), "of the", length(fs.lasso), 
      "are also selected by the bross formula method")
# See which variables are not in common:
# fs.lasso[!(fs.lasso %in% fs.bross)]

# Q2: Odds ratio
print("The Odds Ratio by Method Pure Lasso")
sum_ci.lasso
```

**Method 4: Elastic Net**
```{r, warning=FALSE}
set.seed(42)
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
elas.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 0.5, 
                             nfolds = 5)
coef.fit<-coef(elas.fit, s='lambda.min', exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.elastic <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.elastic)
fs.elastic <- proxy.list.sel.elastic

proxy.elastic <- paste0(fs.elastic, collapse = "+")
form.elastic <- paste0(c(covform, proxy.elastic), collapse = "+")
formula.elastic <- as.formula(paste0("exposure", "~", form.elastic))

require(WeightIt)
W.out.elastic <- weightit(formula.elastic, 
                       data = hdps.data, 
                       estimand = "ATE",
                       method = "ps")

hdps.data$ps.e <- W.out.elastic$ps
hdps.data$w.e <- W.out.elastic$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
out.formula
fit.elastic <- glm(out.formula,
                data = hdps.data,
                weights = W.out.elastic$weights,
                family= binomial(link = "logit"))
summary.elastic <- summary(fit.elastic)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci.elastic <- confint(fit.elastic, level = 0.95)["exposure", ]
sum_ci.elastic <- c(exp(summary.elastic[1]), summary.elastic, ci.elastic)
names(sum_ci.elastic) <- c("Odds Ratio",
                         "Estimate",
                         "Std. Error",
                         "Pr(>|z|)",
                         "2.5 %",
                         "97.5 %")

# Q1: How many proxy variables are in common (Elastic Net vs Bross Formula)?
# length(fs.elastic)  # 69 features selected by elastic net
# length(fs.elastic[fs.elastic %in% fs.bross])  # 54 of 69 also selected by bross formula
print("How many proxy variables are in common?")
paste("There are", length(fs.elastic), "features selected by elas")
paste(length(fs.elastic[fs.elastic %in% fs.bross]), "of the", length(fs.elastic), 
      "are also selected by the bross formula method")
# See which variables are not in common:
# fs.elastic[!(fs.elastic %in% fs.bross)]

# Q2: Odds ratio
print("The Odds Ratio by Elastic Net")
sum_ci.elastic
```

**Method 5: XGBoost**
```{r, warning=FALSE}
xgb_fit <- xgboost(data = covar.mat, label = hdps.data$outcome, 
                    max.depth = 20, eta = 1, nthread = 2, nrounds = 5, 
                    objective = "binary:logistic")

xgb_imp <- xgb.importance(model = xgb_fit)
xgb.plot.importance(importance_matrix = xgb_imp)
fs.xgboost <- xgb_imp$Feature
fs.xgboost <- proxy.list[proxy.list %in% fs.xgboost]
proxy.xgboost <- paste0(fs.xgboost, collapse = "+")
form.xgboost <- paste0(c(covform, proxy.xgboost), collapse = "+")
formula.xgboost <- as.formula(paste0("exposure", "~", form.xgboost))

require(WeightIt)
W.out.xgboost <- weightit(formula.xgboost, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

hdps.data$ps.xgboost <- W.out.xgboost$ps
hdps.data$w.xgboost <- W.out.xgboost$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
out.formula
fit.xgboost <- glm(out.formula,
                   data = hdps.data,
                   weights = W.out.xgboost$weights,
                   family= binomial(link = "logit"))
summary.xgboost <- summary(fit.xgboost)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci.xgboost <- confint(fit.xgboost, level = 0.95)["exposure", ]
sum_ci.xgboost <- c(exp(summary.xgboost[1]), summary.xgboost, ci.xgboost)
names(sum_ci.xgboost) <- c("Odds Ratio",
                           "Estimate",
                           "Std. Error",
                           "Pr(>|z|)",
                           "2.5 %",
                           "97.5 %")

# Q1: How many proxy variables are in common?
# length(fs.xgboost) 
# length(fs.xgboost[fs.xgboost %in% fs.bross])
print("How many proxy variables are in common?")
paste("There are", length(fs.xgboost), "features selected by xgboost")
paste(length(fs.xgboost[fs.xgboost %in% fs.bross]), "of the", length(fs.xgboost), 
      "are also selected by the bross formula method")
# See which variables are not in common:
# fs.xgboost[!(fs.xgboost %in% fs.bross)]

# Q2: Odds ratio
print("The Odds Ratio by XGBoost")
sum_ci.xgboost
```

**Method 6: GA**

_GA (Genetic Algorithm) has no specific internal model building mechanism and would wrap around whatever model the user specifies_
```{r, warning=FALSE}
gaOpt <- function(vars, IV.train, DV.train) {
	varNames <- colnames(IV.train) #getting names of all variables
	selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
	gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars

	gaDat <- cbind(gaSolutionData,DV.train) # combining selected variables with outcome variable
	gaMod <- glm(DV.train ~ ., family = "binomial", data = gaDat) #build model
	gaProb <- predict(gaMod, IV.train, type = "response") # get probabilities
	gaPred <- ifelse(gaProb >= .8, 1, 0) # get predicted 0s and 1s

	ari <- adjustedRandIndex(gaPred, DV.train)
	return(ari)
}

ga.solution <- ga(fitness = function(vars)
 gaOpt(vars=vars, 
       IV.train=data.frame(covar.mat),
       DV.train=hdps.data$outcome),
 type = "binary", 
 nBits = ncol(covar.mat),
 names = colnames(covar.mat), 
 seed = 42,
 run=5)

allVarNames <- colnames(covar.mat)
sel.variables.GA <- allVarNames[ga.solution@solution[1,]==1]
fs.GA <- proxy.list[proxy.list %in% sel.variables.GA]
proxy.GA <- paste0(fs.GA, collapse = "+")
form.GA <- paste0(c(covform, proxy.GA), collapse = "+")
formula.GA <- as.formula(paste0("exposure", "~", form.GA))

require(WeightIt)
W.out.GA <- weightit(formula.GA, 
                         data = hdps.data, 
                         estimand = "ATE",
                         method = "ps")

hdps.data$ps.ga <- W.out.GA$ps
hdps.data$w.ga <- W.out.GA$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
out.formula
fit.GA <- glm(out.formula,
                  data = hdps.data,
                  weights = W.out.GA$weights,
                  family= binomial(link = "logit"))
summary.GA <- summary(fit.GA)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci.GA <- confint(fit.GA, level = 0.95)["exposure", ]
sum_ci.GA <- c(exp(summary.GA[1]), summary.GA, ci.GA)
names(sum_ci.GA) <- c("Odds Ratio",
                          "Estimate",
                          "Std. Error",
                          "Pr(>|z|)",
                          "2.5 %",
                          "97.5 %")

# Q1: How many proxy variables are in common (GA vs Bross Formula)?
# length(fs.GA)  # 64 features selected by GA
# length(fs.GA[fs.GA %in% fs.bross])  # 44 of 64 also selected by bross formula
print("How many proxy variables are in common?")
paste("There are", length(fs.GA), "features selected by GA")
paste(length(fs.GA[fs.GA %in% fs.bross]), "of the", length(fs.GA), 
      "are also selected by the bross formula method")
# See which variables are not in common:
# fs.GA[!(fs.GA %in% fs.bross)]

# Q2: Odds ratio
print("The Odds Ratio by GA:")
sum_ci.GA
```

**Method 7: Elastic SCAD SVM**

_Elastic SCAD SVM uses an approach like LASSO and Elastic Net in that it selects variables via the addition of a penalty._

_(Long Running Time)_
```{r, results='hide'}
svmTrainOutcome <- hdps.data$outcome
svmTrainOutcome[svmTrainOutcome == 0] <- -1
svmTrainPreds <- data.frame(covar.mat)

bounds <- t(data.frame(log2lambda1=c(-10, 10), log2lambda2=c(-10,10)))
colnames(bounds)<-c("lower", "upper")
svm.model <- svmfs(x=covar.mat,
				   y = svmTrainOutcome,
				   fs.method = "scad+L2",
				   bounds=bounds,
				   grid.search = "interval",
				   inner.val.method = "cv",
				   show = "none",
				   parms.coding = "none",
				   seed=42)
```

```{r, warning=FALSE}
fs.svm <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
fs.svm <- proxy.list[proxy.list %in% fs.svm]
proxy.svm <- paste0(fs.svm, collapse = "+")
form.svm <- paste0(c(covform, proxy.svm), collapse = "+")
formula.svm <- as.formula(paste0("exposure", "~", form.svm))

require(WeightIt)
W.out.svm <- weightit(formula.svm, 
                        data = hdps.data, 
                        estimand = "ATE",
                        method = "ps")

hdps.data$ps.svm <- W.out.svm$ps
hdps.data$w.svm <- W.out.svm$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
out.formula
fit.svm <- glm(out.formula,
                 data = hdps.data,
                 weights = W.out.svm$weights,
                 family= binomial(link = "logit"))
summary.svm <- summary(fit.svm)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci.svm <- confint(fit.svm, level = 0.95)["exposure", ]
sum_ci.svm <- c(exp(summary.svm[1]), summary.svm, ci.svm)
names(sum_ci.svm) <- c("Odds Ratio",
                         "Estimate",
                         "Std. Error",
                         "Pr(>|z|)",
                         "2.5 %",
                         "97.5 %")

# Q1: How many proxy variables are in common?
# length(fs.svm) 
# length(fs.svm[fs.svm %in% fs.bross])
print("How many proxy variables are in common?")
paste("There are", length(fs.svm), "features selected by svm")
paste(length(fs.svm[fs.svm %in% fs.bross]), "of the", length(fs.svm), 
      "are also selected by the bross formula method")
# See which variables are not in common:
# fs.svm[!(fs.svm %in% fs.bross)]

# Q2: Odds ratio
print("The Odds Ratio by Elastic SCAD SVM")
sum_ci.svm
```

**Method 8: Boruta Selection**

_Boruta Selection would give the feature importance ranking based on the Random Forests algorithm which are able to capture some non-linear trends but not easy to interpret._

_(Long Running Time)_
```{r, warning=FALSE}
set.seed(42)
boruta_output <- Boruta(Y.form, data = hdps.data, doTrace = 1)
sel.variables.bor <- names(boruta_output$finalDecision)[which(boruta_output$finalDecision != "Rejected")]
fs.boruta <- proxy.list[proxy.list %in% sel.variables.bor]
proxy.boruta <- paste0(fs.boruta, collapse = "+")
form.boruta <- paste0(c(covform, proxy.boruta), collapse = "+")
formula.boruta <- as.formula(paste0("exposure", "~", form.boruta))

require(WeightIt)
W.out.boruta <- weightit(formula.boruta, 
                         data = hdps.data, 
                         estimand = "ATE",
                         method = "ps")

hdps.data$ps.b <- W.out.boruta$ps
hdps.data$w.b <- W.out.boruta$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
out.formula
fit.boruta <- glm(out.formula,
                  data = hdps.data,
                  weights = W.out.boruta$weights,
                  family= binomial(link = "logit"))
summary.boruta <- summary(fit.boruta)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci.boruta <- confint(fit.boruta, level = 0.95)["exposure", ]
sum_ci.boruta <- c(exp(summary.boruta[1]), summary.boruta, ci.boruta)
names(sum_ci.boruta) <- c("Odds Ratio",
                          "Estimate",
                          "Std. Error",
                          "Pr(>|z|)",
                          "2.5 %",
                          "97.5 %")

# Q1: How many proxy variables are in common (Boruta vs Bross Formula)?
# length(fs.boruta)  # 28 features selected by boruta selection
# length(fs.boruta[fs.boruta %in% fs.bross])  # 24 of 28 also selected by bross formula
print("How many proxy variables are in common?")
paste("There are", length(fs.boruta), "features selected by boruta")
paste(length(fs.boruta[fs.boruta %in% fs.bross]), "of the", length(fs.boruta), 
      "are also selected by the bross formula method")
# See which variables are not in common:
# fs.boruta[!(fs.boruta %in% fs.bross)]

# Q2: Odds ratio
print("The Odds Ratio by Boruta Selection")
sum_ci.boruta
```

**Method 9.1: Stepwise Regression (Forward)**
```{r}
set.seed(42)

initial_formula <- as.formula(paste0("outcome~exposure+",
                                     covform,
                                     collapse = "+"))
full_formula <- as.formula(paste0("outcome~exposure+",
                                  rhsformula,
                                  collapse = "+"))

initial_model <- glm(initial_formula, data = hdps.data, family = binomial)
full_model <- glm(full_formula, data = hdps.data, family = binomial)
stepwise_forward <- stepAIC(initial_model, 
                            scope = list(lower = initial_model, 
                                         upper = full_model), 
                            direction = "forward")

fs.forward <- all.vars(formula(stepwise_forward))[-1]
fs.forward <- proxy.list[proxy.list %in% fs.forward]
proxy.forward <- paste0(fs.forward, collapse = "+")
form.forward <- paste0(c(covform, proxy.forward), collapse = "+")
formula.forward <- as.formula(paste0("exposure", "~", form.forward))

require(WeightIt)
W.out.forward <- weightit(formula.forward, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

hdps.data$ps.forward <- W.out.forward$ps
hdps.data$w.forward <- W.out.forward$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
out.formula
fit.forward <- glm(out.formula,
                   data = hdps.data,
                   weights = W.out.forward$weights,
                   family= binomial(link = "logit"))
summary.forward <- summary(fit.forward)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci.forward <- confint(fit.forward, level = 0.95)["exposure", ]
sum_ci.forward <- c(exp(summary.forward[1]), summary.forward, ci.forward)
names(sum_ci.forward) <- c("Odds Ratio",
                           "Estimate",
                           "Std. Error",
                           "Pr(>|z|)",
                           "2.5 %",
                           "97.5 %")

# Q1: How many proxy variables are in common?
# length(fs.forward) 
# length(fs.forward[fs.forward %in% fs.bross])
print("How many proxy variables are in common?")
paste("There are", length(fs.forward), "features selected by forward")
paste(length(fs.forward[fs.forward %in% fs.bross]), "of the", length(fs.forward), 
      "are also selected by the bross formula method")
# See which variables are not in common:
# fs.forward[!(fs.forward %in% fs.bross)]

# Q2: Odds ratio
print("The Odds Ratio by Stepwise Forward Selection")
sum_ci.forward
```

**Method 9.2: Stepwise Regression (Backward)**
```{r}
stepwise_backward <- stepAIC(full_model, direction = "backward")
fs.backward <- proxy.list[proxy.list %in% fs.backward]
fs.backward <- fs.backward[fs.backward != "exposure"]
proxy.backward <- paste0(fs.backward, collapse = "+")
form.backward <- paste0(c(covform, proxy.backward), collapse = "+")
formula.backward <- as.formula(paste0("exposure", "~", form.backward))

require(WeightIt)
W.out.backward <- weightit(formula.backward, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

hdps.data$ps.backward <- W.out.backward$ps
hdps.data$w.backward <- W.out.backward$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
out.formula
fit.backward <- glm(out.formula,
                   data = hdps.data,
                   weights = W.out.backward$weights,
                   family= binomial(link = "logit"))
summary.backward <- summary(fit.backward)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci.backward <- confint(fit.backward, level = 0.95)["exposure", ]
sum_ci.backward <- c(exp(summary.backward[1]), summary.backward, ci.backward)
names(sum_ci.backward) <- c("Odds Ratio",
                           "Estimate",
                           "Std. Error",
                           "Pr(>|z|)",
                           "2.5 %",
                           "97.5 %")

# Q1: How many proxy variables are in common?
# length(fs.backward) 
# length(fs.backward[fs.backward %in% fs.bross])
print("How many proxy variables are in common?")
paste("There are", length(fs.backward), "features selected by backward")
paste(length(fs.backward[fs.backward %in% fs.bross]), "of the", length(fs.backward), 
      "are also selected by the bross formula method")
# See which variables are not in common:
# fs.backward[!(fs.backward %in% fs.bross)]

# Q2: Odds ratio
print("The Odds Ratio by Stepwise Backward Selection")
sum_ci.backward
```

**Method 9.3: Stepwise Regression (Both)**
```{r}
stepwise_both <- stepAIC(initial_model, 
                            scope = list(lower = initial_model, 
                                         upper = full_model), 
                            direction = "both")
fs.both <- all.vars(formula(stepwise_both))[-1]
fs.both <- proxy.list[proxy.list %in% fs.both]
proxy.both <- paste0(fs.both, collapse = "+")
form.both <- paste0(c(covform, proxy.both), collapse = "+")
formula.both <- as.formula(paste0("exposure", "~", form.both))

require(WeightIt)
W.out.both <- weightit(formula.both, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

hdps.data$ps.both <- W.out.both$ps
hdps.data$w.both <- W.out.both$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
out.formula
fit.both <- glm(out.formula,
                   data = hdps.data,
                   weights = W.out.both$weights,
                   family= binomial(link = "logit"))
summary.both <- summary(fit.both)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci.both <- confint(fit.both, level = 0.95)["exposure", ]
sum_ci.both <- c(exp(summary.both[1]), summary.both, ci.both)
names(sum_ci.both) <- c("Odds Ratio",
                           "Estimate",
                           "Std. Error",
                           "Pr(>|z|)",
                           "2.5 %",
                           "97.5 %")

# Q1: How many proxy variables are in common?
# length(fs.both) 
# length(fs.both[fs.both %in% fs.bross])
print("How many proxy variables are in common?")
paste("There are", length(fs.both), "features selected by both")
paste(length(fs.both[fs.both %in% fs.bross]), "of the", length(fs.both), 
      "are also selected by the bross formula method")
# See which variables are not in common:
# fs.both[!(fs.both %in% fs.bross)]

# Q2: Odds ratio
print("The Odds Ratio by Stepwise Both Selection")
sum_ci.both
```

Comparing the Results:
```{r}
sum_ci.all <- rbind(sum_ci.bross, sum_ci.hybrid, sum_ci.lasso, sum_ci.elastic, 
                    sum_ci.xgboost, sum_ci.GA, sum_ci.svm, sum_ci.boruta,
                    sum_ci.forward, sum_ci.backward, sum_ci.both)

OR.data <- data.frame(method = c("bross", "hybrid", "lasso", "elastic", 
                                 "xgboost", "GA", "SVM", "boruta", 
                                 "forward", "backward", "both"),
                      OR = exp(sum_ci.all[,2]),
                      lower = exp(sum_ci.all[,5]),
                      upper = exp(sum_ci.all[,6]))

OR.data$method <- factor(OR.data$method, 
                         levels = c("both", "backward", "forward",
                                    "boruta", "SVM", "GA", "xgboost", 
                                    "elastic", "lasso", "hybrid", "bross"))

OR.ci_plot <- ggplot(OR.data, aes(y = method, x = OR)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) + 
  labs(title = "Odds Ratios with 95% Confidence Intervals",
       x = "Odds Ratio",
       y = "Method")

fs.all <- data.frame(numFeature = c(length(fs.bross), 
                                    length(fs.hybrid),
                                    length(fs.lasso), 
                                    length(fs.elastic), 
                                    length(fs.xgboost),
                                    length(fs.GA),
                                    length(fs.svm),
                                    length(fs.boruta),
                                    length(fs.forward),
                                    length(fs.backward),
                                    length(fs.both)),
                     numInCommon = c(NA,
                                     length(fs.hybrid[fs.hybrid %in% fs.bross]),
                                     length(fs.lasso[fs.lasso %in% fs.bross]),
                                     length(fs.elastic[fs.elastic %in% fs.bross]),
                                     length(fs.xgboost[fs.xgboost %in% fs.bross]),
                                     length(fs.GA[fs.GA %in% fs.bross]),
                                     length(fs.svm[fs.svm %in% fs.bross]),
                                     length(fs.boruta[fs.boruta %in% fs.bross]),
                                     length(fs.forward[fs.forward %in% fs.bross]),
                                     length(fs.backward[fs.backward %in% fs.bross]),
                                     length(fs.both[fs.both %in% fs.bross])))
rownames(fs.all) <-  c("bross", "hybrid", "lasso", "elastic", 
                       "xgb", "GA", "SVM", "boruta",
                       "forward", "backward", "both")

fs.all$pctCommon <- fs.all$numInCommon / fs.all$numFeature

fs.commonOneToOne <- data.frame(ini = rep(NA, 11))

for (i in 1:11) {
  col_name <- OR.data$method[i]
  if (col_name == "SVM") {
    col_name <- "svm"
  }
  na.i <- 1
  na <- c()
  while (na.i < i) {
    na <- c(na, NA)
    na.i <- na.i + 1
  }
  num_common <- c(length(fs.bross[fs.bross %in% get(paste0("fs.",col_name))]),
                  length(fs.hybrid[fs.hybrid %in% get(paste0("fs.",col_name))]),
                  length(fs.lasso[fs.lasso %in% get(paste0("fs.",col_name))]),
                  length(fs.elastic[fs.elastic %in% get(paste0("fs.",col_name))]),
                  length(fs.xgboost[fs.xgboost %in% get(paste0("fs.",col_name))]),
                  length(fs.GA[fs.GA %in% get(paste0("fs.",col_name))]),
                  length(fs.svm[fs.svm %in% get(paste0("fs.",col_name))]),
                  length(fs.boruta[fs.boruta %in% get(paste0("fs.",col_name))]),
                  length(fs.forward[fs.forward %in% get(paste0("fs.",col_name))]),
                  length(fs.backward[fs.backward %in% get(paste0("fs.",col_name))]),
                  length(fs.both[fs.both %in% get(paste0("fs.",col_name))]))
  fs.commonOneToOne[i] <- c(na, num_common[i:11])
}

colnames(fs.commonOneToOne) <- rownames(fs.all)
rownames(fs.commonOneToOne) <- rownames(fs.all)
```

Print the comparing plot & table:
```{r}
print("Comparison of odds ratios and the confidence intervals by different proxy selection methods:")
OR.ci_plot
```

```{r}
print("Comparison of the number & percentage of proxy variables selected by different methods in common with that by the bross formula:")
fs.all
```

```{r}
print("One-to-one comparison of the number of proxy variables selected by different methods")
fs.commonOneToOne
```

### 2024-07-15 ProxySelection.Rmd
results

@@
 knitr::opts_chunk$set(echo = TRUE)
-```
-
-**Codechuck 0. Loading data -- Generating Recurrence Covariates**
-
-_Step 0: Analytic data, Step 1: Proxy sources, Step 2: Emperical, Step 3: Recurrence_
-```{r loading-data, warning=FALSE}
-# ------------------- Select proxy based on the results from out2
-# ------------------- change the code after Step 3: Recurrence
 require(autoCovariateSelection)
@@
 library(caret)
+require(autoCovariateSelection)
+```
 
+**Codechuck 0. Loading data -- Generating Recurrence Covariates**
+
+_Step 0: Analytic data, Step 1: Proxy sources, Step 2: Emperical, Step 3: Recurrence_
+```{r loading-data, warning=FALSE, cache=TRUE}
+# ------------------- Select proxy based on the results from out2
+# ------------------- change the code after Step 3: Recurrence
 load("data/analytic3cycles.RData")
@@
 
-require(autoCovariateSelection)
 step1 <- get_candidate_covariates(df = dfx,  
@@
 **Method 1: Bross Formula**
-```{r, warning=FALSE}
+```{r, warning=FALSE, cache=TRUE}
 out3 <- get_prioritised_covariates(df = out2,
@@
 
-require(WeightIt)
 W.out <- weightit(ps.formula, 
@@
 **Method 2: Hybrid Bross Formula & Lasso**
-```{r, warning=FALSE}
+```{r, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 _Before implementing other methods, drop the information from method 1 (Bross formula). Continue with the results from Step 3: Recurrence (table `out2`)._
-```{r, warning=FALSE}
+```{r, warning=FALSE, cache=TRUE}
 hdps.dim <- out2
@@
 **Method 3: Pure Lasso**
-```{r, warning=FALSE}
+```{r, warning=FALSE, cache=TRUE}
 set.seed(42) # different seed -> different length for the selected proxy list
@@
 
-require(WeightIt)
 W.out.lasso <- weightit(formula.lasso, 
@@
 **Method 4: Elastic Net**
-```{r, warning=FALSE}
+```{r, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-require(WeightIt)
 W.out.elastic <- weightit(formula.elastic, 
@@
 **Method 5: XGBoost**
-```{r, warning=FALSE}
+```{r, warning=FALSE, cache=TRUE}
 xgb_fit <- xgboost(data = covar.mat, label = hdps.data$outcome, 
@@
 
-require(WeightIt)
 W.out.xgboost <- weightit(formula.xgboost, 
@@
 _GA (Genetic Algorithm) has no specific internal model building mechanism and would wrap around whatever model the user specifies_
-```{r, warning=FALSE}
+```{r, warning=FALSE, cache=TRUE}
 gaOpt <- function(vars, IV.train, DV.train) {
@@
 
-require(WeightIt)
 W.out.GA <- weightit(formula.GA, 
@@
 _(Long Running Time)_
-```{r, results='hide'}
+```{r, warning=FALSE, cache=TRUE}
 svmTrainOutcome <- hdps.data$outcome
@@
 
-```{r, warning=FALSE}
+```{r, warning=FALSE, cache=TRUE}
 fs.svm <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
@@
 
-require(WeightIt)
 W.out.svm <- weightit(formula.svm, 
@@
 _(Long Running Time)_
-```{r, warning=FALSE}
+```{r, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-require(WeightIt)
 W.out.boruta <- weightit(formula.boruta, 
@@
 **Method 9.1: Stepwise Regression (Forward)**
-```{r}
+```{r, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-require(WeightIt)
 W.out.forward <- weightit(formula.forward, 
@@
 **Method 9.2: Stepwise Regression (Backward)**
-```{r}
+```{r, warning=FALSE, cache=TRUE}
 stepwise_backward <- stepAIC(full_model, direction = "backward")
@@
 
-require(WeightIt)
 W.out.backward <- weightit(formula.backward, 
@@
 **Method 9.3: Stepwise Regression (Both)**
-```{r}
+```{r, warning=FALSE, cache=TRUE}
 stepwise_both <- stepAIC(initial_model, 
@@
 
-require(WeightIt)
 W.out.both <- weightit(formula.both, 
@@
 Comparing the Results:
-```{r}
+```{r, warning=FALSE, cache=TRUE}
 sum_ci.all <- rbind(sum_ci.bross, sum_ci.hybrid, sum_ci.lasso, sum_ci.elastic, 

### 2024-07-16 ProxySelection.Rmd
html
prxy

@@
 date: "2024-07-11"
-output: pdf_document
+output:
+  html_document:
+    df_print: paged
 ---
@@
 **Method 1: Bross Formula**
-```{r, warning=FALSE, cache=TRUE}
+```{r bross, warning=FALSE, cache=TRUE}
+start_time <- Sys.time()
 out3 <- get_prioritised_covariates(df = out2,
@@
 round(sum_ci.bross, 3)
+end_time <- Sys.time()
+elapsed_time.bross <- as.numeric(difftime(end_time, start_time, units = "secs"))
 ```
@@
 **Method 2: Hybrid Bross Formula & Lasso**
-```{r, warning=FALSE, cache=TRUE}
+```{r hybrid, warning=FALSE, cache=TRUE}
 set.seed(42)
+start_time <- Sys.time()
 proxy.list <- names(out3$autoselected_covariate_df[,-1])
@@
 round(sum_ci.hybrid, 3)
+end_time <- Sys.time()
+elapsed_time.hybrid <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.hybrid
 ```
@@
 _Before implementing other methods, drop the information from method 1 (Bross formula). Continue with the results from Step 3: Recurrence (table `out2`)._
-```{r, warning=FALSE, cache=TRUE}
+```{r prepare, warning=FALSE, cache=TRUE}
 hdps.dim <- out2
@@
 **Method 3: Pure Lasso**
-```{r, warning=FALSE, cache=TRUE}
+```{r lasso, warning=FALSE, cache=TRUE}
 set.seed(42) # different seed -> different length for the selected proxy list
+start_time <- Sys.time()
 covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
@@
 sum_ci.lasso
+end_time <- Sys.time()
+elapsed_time.lasso <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.lasso
 ```
@@
 **Method 4: Elastic Net**
-```{r, warning=FALSE, cache=TRUE}
+```{r enet, warning=FALSE, cache=TRUE}
 set.seed(42)
+start_time <- Sys.time()
 covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
@@
 sum_ci.elastic
+end_time <- Sys.time()
+elapsed_time.enet <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.enet
 ```
@@
 **Method 5: XGBoost**
-```{r, warning=FALSE, cache=TRUE}
+```{r xgb, warning=FALSE, cache=TRUE}
+start_time <- Sys.time()
 xgb_fit <- xgboost(data = covar.mat, label = hdps.data$outcome, 
@@
 sum_ci.xgboost
+end_time <- Sys.time()
+elapsed_time.xgb <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.xgb
 ```
@@
 _GA (Genetic Algorithm) has no specific internal model building mechanism and would wrap around whatever model the user specifies_
-```{r, warning=FALSE, cache=TRUE}
+```{r ga, warning=FALSE, cache=TRUE}
+start_time <- Sys.time()
 gaOpt <- function(vars, IV.train, DV.train) {
@@
 sum_ci.GA
+end_time <- Sys.time()
+elapsed_time.ga <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.ga
 ```
@@
 _(Long Running Time)_
-```{r, warning=FALSE, cache=TRUE}
+```{r svm, warning=FALSE, cache=TRUE}
+start_time <- Sys.time()
 svmTrainOutcome <- hdps.data$outcome
@@
 sum_ci.svm
+end_time <- Sys.time()
+elapsed_time.svm <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.svm
 ```
@@
 _(Long Running Time)_
-```{r, warning=FALSE, cache=TRUE}
+```{r Boruta, warning=FALSE, cache=TRUE}
 set.seed(42)
+start_time <- Sys.time()
 boruta_output <- Boruta(Y.form, data = hdps.data, doTrace = 1)
@@
 sum_ci.boruta
+end_time <- Sys.time()
+elapsed_time.boruta <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.boruta
 ```
@@
 **Method 9.1: Stepwise Regression (Forward)**
-```{r, warning=FALSE, cache=TRUE}
+```{r fs, warning=FALSE, cache=TRUE}
 set.seed(42)
-
+start_time <- Sys.time()
 initial_formula <- as.formula(paste0("outcome~exposure+",
@@
 sum_ci.forward
+end_time <- Sys.time()
+elapsed_time.fs <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.fs
 ```
@@
 **Method 9.2: Stepwise Regression (Backward)**
-```{r, warning=FALSE, cache=TRUE}
+```{r bs, warning=FALSE, cache=TRUE}
+start_time <- Sys.time()
 stepwise_backward <- stepAIC(full_model, direction = "backward")
@@
 sum_ci.backward
+end_time <- Sys.time()
+elapsed_time.bs <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.bs
 ```
@@
 **Method 9.3: Stepwise Regression (Both)**
-```{r, warning=FALSE, cache=TRUE}
+```{r sw, warning=FALSE, cache=TRUE}
+start_time <- Sys.time()
 stepwise_both <- stepAIC(initial_model, 
@@
 sum_ci.both
+end_time <- Sys.time()
+elapsed_time.sw <- as.numeric(difftime(end_time, start_time, units = "secs"))
+elapsed_time.sw
 ```
@@
 Comparing the Results:
-```{r, warning=FALSE, cache=TRUE}
+```{r compare, warning=FALSE, cache=TRUE}
 sum_ci.all <- rbind(sum_ci.bross, sum_ci.hybrid, sum_ci.lasso, sum_ci.elastic, 
@@
 ```{r}
+elapsed_times <- list()
+elapsed_times[["bross"]] <- elapsed_time.bross
+elapsed_times[["hybrid"]] <- elapsed_time.hybrid
+elapsed_times[["lasso"]] <- elapsed_time.lasso
+elapsed_times[["enet"]] <- elapsed_time.enet
+elapsed_times[["xgb"]] <- elapsed_time.xgb
+elapsed_times[["ga"]] <- elapsed_time.ga
+elapsed_times[["svm"]] <- elapsed_time.svm
+elapsed_times[["boruta"]] <- elapsed_time.boruta
+elapsed_times[["fs"]] <- elapsed_time.fs
+elapsed_times[["bs"]] <- elapsed_time.bs
+elapsed_times[["sw"]] <- elapsed_time.sw
+print(elapsed_times)
 print("Comparison of odds ratios and the confidence intervals by different proxy selection methods:")

### 2024-07-17 ProxySelection.Rmd
preBS

@@
 require(autoCovariateSelection)
+library(randomForest)
 ```
@@
 stepwise_backward <- stepAIC(full_model, direction = "backward")
+fs.backward <- all.vars(formula(stepwise_backward))[-1]
 fs.backward <- proxy.list[proxy.list %in% fs.backward]
@@
 ```
+
+```{r rf, warning=FALSE, cache=TRUE}
+# Random Forest Feature Selection
+start_time <- Sys.time()
+rf_model <- randomForest(outcome ~ ., data = hdps.data, importance = TRUE)
+
+# Get important features
+rf_importance <- importance(rf_model)
+important_features_rf <- rownames(rf_importance)[order(rf_importance[, 1], decreasing = TRUE)]
+
+# Select features
+fs_rf <- important_features_rf[important_features_rf %in% proxy.list]
+proxy_rf <- paste0(fs_rf, collapse = "+")
+form_rf <- paste0(c(covform, proxy_rf), collapse = "+")
+formula_rf <- as.formula(paste0("exposure", "~", form_rf))
+
+W.out_rf <- weightit(formula_rf, 
+                     data = hdps.data, 
+                     estimand = "ATE",
+                     method = "ps")
+
+hdps.data$ps_rf <- W.out_rf$ps
+hdps.data$w_rf <- W.out_rf$weights
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+fit_rf <- glm(out.formula,
+              data = hdps.data,
+              weights = W.out_rf$weights,
+              family= binomial(link = "logit"))
+summary_rf <- summary(fit_rf)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
+ci_rf <- confint(fit_rf, level = 0.95)["exposure", ]
+sum_ci_rf <- c(exp(summary_rf[1]), summary_rf, ci_rf)
+names(sum_ci_rf) <- c("Odds Ratio",
+                      "Estimate",
+                      "Std. Error",
+                      "Pr(>|z|)",
+                      "2.5 %",
+                      "97.5 %")
+
+end_time <- Sys.time()
+elapsed_time_rf <- as.numeric(difftime(end_time, start_time, units = "secs"))
+
+print("How many proxy variables are in common?")
+paste("There are", length(fs_rf), "features selected by randomForest")
+paste(length(fs_rf[fs_rf %in% fs.bross]), "of the", length(fs_rf), 
+      "are also selected by the bross formula method")
+
+print("The Odds Ratio by Random Forest")
+sum_ci_rf
+print("Elapsed time for Random Forest:")
+elapsed_time_rf
+```
+
+```{r rfe, warning=FALSE, cache=TRUE}
+# RFE Feature Selection
+start_time <- Sys.time()
+control <- rfeControl(functions = rfFuncs, method = "cv", number = 10)
+results <- rfe(hdps.data[, -which(names(hdps.data) %in% c("outcome", "exposure"))], hdps.data$outcome, sizes = c(1:10), rfeControl = control)
+
+# Get important features
+important_features_rfe <- predictors(results)
+
+# Select features
+fs_rfe <- important_features_rfe[important_features_rfe %in% proxy.list]
+proxy_rfe <- paste0(fs_rfe, collapse = "+")
+form_rfe <- paste0(c(covform, proxy_rfe), collapse = "+")
+formula_rfe <- as.formula(paste0("exposure", "~", form_rfe))
+
+W.out_rfe <- weightit(formula_rfe, 
+                      data = hdps.data, 
+                      estimand = "ATE",
+                      method = "ps")
+
+hdps.data$ps_rfe <- W.out_rfe$ps
+hdps.data$w_rfe <- W.out_rfe$weights
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+fit_rfe <- glm(out.formula,
+               data = hdps.data,
+               weights = W.out_rfe$weights,
+               family= binomial(link = "logit"))
+summary_rfe <- summary(fit_rfe)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
+ci_rfe <- confint(fit_rfe, level = 0.95)["exposure", ]
+sum_ci_rfe <- c(exp(summary_rfe[1]), summary_rfe, ci_rfe)
+names(sum_ci_rfe) <- c("Odds Ratio",
+                       "Estimate",
+                       "Std. Error",
+                       "Pr(>|z|)",
+                       "2.5 %",
+                       "97.5 %")
+
+end_time <- Sys.time()
+elapsed_time_rfe <- as.numeric(difftime(end_time, start_time, units = "secs"))
+
+print("How many proxy variables are in common?")
+paste("There are", length(fs_rfe), "features selected by RFE")
+paste(length(fs_rfe[fs_rfe %in% fs.bross]), "of the", length(fs_rfe), 
+      "are also selected by the bross formula method")
+
+print("The Odds Ratio by RFE")
+sum_ci_rfe
+print("Elapsed time for RFE:")
+elapsed_time_rfe
+```

### 2024-07-18 ProxySelection.Rmd
all results

@@
 important_features_rf <- rownames(rf_importance)[order(rf_importance[, 1], decreasing = TRUE)]
-
+```
+
+```{r rf2, warning=FALSE, cache=TRUE}
 # Select features
@@
 important_features_rfe <- predictors(results)
-
+```
+
+```{r rfe2, warning=FALSE, cache=TRUE}
 # Select features
-fs_rfe <- important_features_rfe[important_features_rfe %in% proxy.list]
-proxy_rfe <- paste0(fs_rfe, collapse = "+")
-form_rfe <- paste0(c(covform, proxy_rfe), collapse = "+")
-formula_rfe <- as.formula(paste0("exposure", "~", form_rfe))
-
-W.out_rfe <- weightit(formula_rfe, 
-                      data = hdps.data, 
-                      estimand = "ATE",
-                      method = "ps")
-
-hdps.data$ps_rfe <- W.out_rfe$ps
-hdps.data$w_rfe <- W.out_rfe$weights
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-fit_rfe <- glm(out.formula,
-               data = hdps.data,
-               weights = W.out_rfe$weights,
-               family= binomial(link = "logit"))
-summary_rfe <- summary(fit_rfe)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
-ci_rfe <- confint(fit_rfe, level = 0.95)["exposure", ]
-sum_ci_rfe <- c(exp(summary_rfe[1]), summary_rfe, ci_rfe)
-names(sum_ci_rfe) <- c("Odds Ratio",
-                       "Estimate",
-                       "Std. Error",
-                       "Pr(>|z|)",
-                       "2.5 %",
-                       "97.5 %")
-
-end_time <- Sys.time()
-elapsed_time_rfe <- as.numeric(difftime(end_time, start_time, units = "secs"))
-
-print("How many proxy variables are in common?")
-paste("There are", length(fs_rfe), "features selected by RFE")
-paste(length(fs_rfe[fs_rfe %in% fs.bross]), "of the", length(fs_rfe), 
-      "are also selected by the bross formula method")
-
-print("The Odds Ratio by RFE")
-sum_ci_rfe
-print("Elapsed time for RFE:")
-elapsed_time_rfe
-```
+# fs_rfe <- important_features_rfe[important_features_rfe %in% proxy.list]
+# proxy_rfe <- paste0(fs_rfe, collapse = "+")
+# form_rfe <- paste0(c(covform, proxy_rfe), collapse = "+")
+# formula_rfe <- as.formula(paste0("exposure", "~", form_rfe))
+# 
+# W.out_rfe <- weightit(formula_rfe, 
+#                       data = hdps.data, 
+#                       estimand = "ATE",
+#                       method = "ps")
+# 
+# hdps.data$ps_rfe <- W.out_rfe$ps
+# hdps.data$w_rfe <- W.out_rfe$weights
+# out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+# fit_rfe <- glm(out.formula,
+#                data = hdps.data,
+#                weights = W.out_rfe$weights,
+#                family= binomial(link = "logit"))
+# summary_rfe <- summary(fit_rfe)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
+# ci_rfe <- confint(fit_rfe, level = 0.95)["exposure", ]
+# sum_ci_rfe <- c(exp(summary_rfe[1]), summary_rfe, ci_rfe)
+# names(sum_ci_rfe) <- c("Odds Ratio",
+#                        "Estimate",
+#                        "Std. Error",
+#                        "Pr(>|z|)",
+#                        "2.5 %",
+#                        "97.5 %")
+# 
+# end_time <- Sys.time()
+# elapsed_time_rfe <- as.numeric(difftime(end_time, start_time, units = "secs"))
+# 
+# print("How many proxy variables are in common?")
+# paste("There are", length(fs_rfe), "features selected by RFE")
+# paste(length(fs_rfe[fs_rfe %in% fs.bross]), "of the", length(fs_rfe), 
+#       "are also selected by the bross formula method")
+# 
+# print("The Odds Ratio by RFE")
+# sum_ci_rfe
+# print("Elapsed time for RFE:")
+# elapsed_time_rfe
+```

### 2024-07-31 ProxySelection.Rmd
saved workspace
Add estimated RD & the SE.
Updated / added code chunks: Chunk 4 (bross RD), Chunk 6 (hybrid RD), Chunk 9 (lasso RD), Chunk 11 (enet ED), Chunk 13 (xgb RD), Chunk 15 (ga RD), Chunk 18 (svm RD), Chunk 20 (Boruta RD), Chunk 22 (fs RD), Chunk 24 (bs RD), Chunk 26 (sw RD), Chunk 28 (rf OR-cont), Chunk 29 (rf RD), Chunk 39 (OR.ci_plot with # of proxy), Chunk 40 (summary RD all methods), Chunk 41 (print RD result table), chunk 42 (print OR.ci_plot with # of proxy)

@@
 **Method 1: Bross Formula**
-```{r bross, warning=FALSE, cache=TRUE}
+```{r bross OR, warning=FALSE, cache=TRUE}
 start_time <- Sys.time()
+
 out3 <- get_prioritised_covariates(df = out2,
@@
 
+```{r bross RD, warning=FALSE, cache=TRUE}
+# Estimating RD and SE
+hdps.dim.bross <- out3$autoselected_covariate_df
+hdps.dim.bross$id <- hdps.dim.bross$idx
+hdps.dim.bross$idx <- NULL
+hdps.data.bross <- merge(data.complete[,c("id",
+                                    outcome, 
+                                    exposure, 
+                                    investigator.specified.covariates)], 
+                         hdps.dim.bross, 
+                         by = "id")
+hdps.data.bross$exposure <- as.numeric(I(hdps.data$obese=='Yes'))
+hdps.data.bross$outcome <- as.numeric(I(hdps.data$diabetes=='Yes'))
+
+proxyform <- paste0(fs.bross, collapse = "+")
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+rhsformula <- paste0(c(covform, proxyform), collapse = "+")
+ps.formula <- as.formula(paste0("exposure", "~", rhsformula))
+out.formula <- as.formula(paste0("outcome","~", "exposure"))
+
+W.out.bross <- weightit(ps.formula, 
+                  data = hdps.data.bross, 
+                  estimand = "ATE",
+                  method = "ps")
+fit_gau.bross <- glm(out.formula,
+               data= hdps.data.bross,
+               weights= W.out.bross$weights,
+               family=gaussian(link= "identity"))
+
+summary_rd.bross  <- summary(fit_gau.bross)$coef["exposure",
+                                           c("Estimate",
+                                             "Std. Error",
+                                             "Pr(>|t|)")]
+summary_rd.bross[2]<- sqrt(sandwich::sandwich(fit_gau.bross)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.bross, "exposure", level = 0.95,  method = "hc1")
+summary_rd.bross  <- c(summary_rd.bross, conf.int)
+
+round(summary_rd.bross, 2)
+```
+
 **Method 2: Hybrid Bross Formula & Lasso**
-```{r hybrid, warning=FALSE, cache=TRUE}
+```{r hybrid OR, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
+```{r hybrid RD, warning=FALSE, cache=TRUE}
+proxyform <- paste0(fs.hybrid, collapse = "+")
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+rhsformula <- paste0(c(covform, proxyform), collapse = "+")
+ps.formula <- as.formula(paste0("exposure", "~", rhsformula))
+out.formula <- as.formula(paste0("outcome","~", "exposure"))
+
+W.out.hybrid <- weightit(ps.formula, 
+                  data = hdps.data.bross, 
+                  estimand = "ATE",
+                  method = "ps")
+fit_gau.hybrid <- glm(out.formula,
+               data= hdps.data.bross,
+               weights= W.out.hybrid$weights,
+               family=gaussian(link= "identity"))
+
+summary_rd.hybrid  <- summary(fit_gau.hybrid)$coef["exposure",
+                                           c("Estimate",
+                                             "Std. Error",
+                                             "Pr(>|t|)")]
+summary_rd.hybrid[2]<- sqrt(sandwich::sandwich(fit_gau.hybrid)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.hybrid, "exposure", level = 0.95,  method = "hc1")
+summary_rd.hybrid  <- c(summary_rd.hybrid, conf.int)
+
+round(summary_rd.hybrid, 2)
+```
+
 _Before implementing other methods, drop the information from method 1 (Bross formula). Continue with the results from Step 3: Recurrence (table `out2`)._
@@
                               covarsTfull), collapse = "+") )
-
 ```
@@
 **Method 3: Pure Lasso**
-```{r lasso, warning=FALSE, cache=TRUE}
+```{r lasso OR, warning=FALSE, cache=TRUE}
 set.seed(42) # different seed -> different length for the selected proxy list
@@
 covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
+
 lasso.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
@@
                                nfolds = 5)
+
 coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
@@
 
+```{r lasso RD, warning=FALSE, cache=TRUE}
+fit_gau.lasso <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out.lasso$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.lasso  <- summary(fit_gau.lasso)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.lasso[2]<- sqrt(sandwich::sandwich(fit_gau.lasso)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.lasso, "exposure", level = 0.95,  method = "hc1")
+summary_rd.lasso  <- c(summary_rd.lasso, conf.int)
+
+round(summary_rd.lasso, 2)
+```
+
 **Method 4: Elastic Net**
-```{r enet, warning=FALSE, cache=TRUE}
+```{r enet OR, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
+
 elas.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
@@
                              nfolds = 5)
+
 coef.fit<-coef(elas.fit, s='lambda.min', exact=TRUE)
@@
 
+```{r enet RD, warning=FALSE, cache=TRUE}
+fit_gau.elastic <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out.elastic$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.elastic  <- summary(fit_gau.elastic)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.elastic[2]<- sqrt(sandwich::sandwich(fit_gau.elastic)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.elastic, "exposure", level = 0.95,  method = "hc1")
+summary_rd.elastic  <- c(summary_rd.elastic, conf.int)
+
+round(summary_rd.elastic, 2)
+```
+
 **Method 5: XGBoost**
-```{r xgb, warning=FALSE, cache=TRUE}
+```{r xgb OR, warning=FALSE, cache=TRUE}
 start_time <- Sys.time()
+
 xgb_fit <- xgboost(data = covar.mat, label = hdps.data$outcome, 
@@
 
+```{r xgb RD, warning=FALSE, cache=TRUE}
+fit_gau.xgboost <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out.xgboost$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.xgboost  <- summary(fit_gau.xgboost)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.xgboost[2]<- sqrt(sandwich::sandwich(fit_gau.xgboost)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.xgboost, "exposure", level = 0.95,  method = "hc1")
+summary_rd.xgboost  <- c(summary_rd.xgboost, conf.int)
+
+round(summary_rd.xgboost, 2)
+```
+
 **Method 6: GA**
@@
 _GA (Genetic Algorithm) has no specific internal model building mechanism and would wrap around whatever model the user specifies_
-```{r ga, warning=FALSE, cache=TRUE}
+```{r ga OR, warning=FALSE, cache=TRUE}
 start_time <- Sys.time()
+
 gaOpt <- function(vars, IV.train, DV.train) {
@@
 
+```{r ga RD, warning=FALSE, cache=TRUE}
+fit_gau.GA <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out.GA$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.GA  <- summary(fit_gau.GA)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.GA[2]<- sqrt(sandwich::sandwich(fit_gau.GA)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.GA, "exposure", level = 0.95,  method = "hc1")
+summary_rd.GA  <- c(summary_rd.GA, conf.int)
+
+round(summary_rd.GA, 2)
+```
+
 **Method 7: Elastic SCAD SVM**
@@
 _(Long Running Time)_
-```{r svm, warning=FALSE, cache=TRUE}
+```{r svm OR, warning=FALSE, cache=TRUE}
 start_time <- Sys.time()
@@
 
-```{r, warning=FALSE, cache=TRUE}
+```{r svm OR-cont, warning=FALSE, cache=TRUE}
 fs.svm <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
@@
 
+```{r svm RD, warning=FALSE, cache=TRUE}
+fit_gau.svm <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out.svm$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.svm  <- summary(fit_gau.svm)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.svm[2]<- sqrt(sandwich::sandwich(fit_gau.svm)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.svm, "exposure", level = 0.95,  method = "hc1")
+summary_rd.svm  <- c(summary_rd.svm, conf.int)
+
+round(summary_rd.svm, 2)
+```
+
 **Method 8: Boruta Selection**
@@
 _(Long Running Time)_
-```{r Boruta, warning=FALSE, cache=TRUE}
+```{r Boruta OR, warning=FALSE, cache=TRUE}
 set.seed(42)
 start_time <- Sys.time()
+
 boruta_output <- Boruta(Y.form, data = hdps.data, doTrace = 1)
+
 sel.variables.bor <- names(boruta_output$finalDecision)[which(boruta_output$finalDecision != "Rejected")]
@@
 
+```{r Boruta RD, warning=FALSE, cache=TRUE}
+fit_gau.boruta <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out.boruta$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.boruta  <- summary(fit_gau.boruta)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.boruta[2]<- sqrt(sandwich::sandwich(fit_gau.boruta)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.boruta, "exposure", level = 0.95,  method = "hc1")
+summary_rd.boruta  <- c(summary_rd.boruta, conf.int)
+
+round(summary_rd.boruta, 2)
+```
+
 **Method 9.1: Stepwise Regression (Forward)**
-```{r fs, warning=FALSE, cache=TRUE}
+```{r fs OR, warning=FALSE, cache=TRUE}
 set.seed(42)
 start_time <- Sys.time()
+
 initial_formula <- as.formula(paste0("outcome~exposure+",
@@
 
+```{r fs RD, warning=FALSE, cache=TRUE}
+fit_gau.forward <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out.forward$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.forward  <- summary(fit_gau.forward)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.forward[2]<- sqrt(sandwich::sandwich(fit_gau.forward)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.forward, "exposure", level = 0.95,  method = "hc1")
+summary_rd.forward  <- c(summary_rd.forward, conf.int)
+
+round(summary_rd.forward, 2)
+```
+
 **Method 9.2: Stepwise Regression (Backward)**
-```{r bs, warning=FALSE, cache=TRUE}
+```{r bs OR, warning=FALSE, cache=TRUE}
 start_time <- Sys.time()
+
 stepwise_backward <- stepAIC(full_model, direction = "backward")
+
 fs.backward <- all.vars(formula(stepwise_backward))[-1]
@@
 
+```{r bs RD, warning=FALSE, cache=TRUE}
+fit_gau.backward <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out.backward$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.backward  <- summary(fit_gau.backward)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.backward[2]<- sqrt(sandwich::sandwich(fit_gau.backward)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.backward, "exposure", level = 0.95,  method = "hc1")
+summary_rd.backward  <- c(summary_rd.backward, conf.int)
+
+round(summary_rd.backward, 2)
+```
+
 **Method 9.3: Stepwise Regression (Both)**
-```{r sw, warning=FALSE, cache=TRUE}
+```{r sw OR, warning=FALSE, cache=TRUE}
 start_time <- Sys.time()
+
 stepwise_both <- stepAIC(initial_model, 
@@
                             direction = "both")
+
 fs.both <- all.vars(formula(stepwise_both))[-1]
@@
 
+```{r sw RD, warning=FALSE, cache=TRUE}
+fit_gau.both <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out.both$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.both  <- summary(fit_gau.both)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.both[2]<- sqrt(sandwich::sandwich(fit_gau.both)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.both, "exposure", level = 0.95,  method = "hc1")
+summary_rd.both  <- c(summary_rd.both, conf.int)
+
+round(summary_rd.both, 2)
+```
+
+```{r rf OR, warning=FALSE, cache=TRUE}
+# Random Forest Feature Selection
+start_time <- Sys.time()
+
+rf_model <- randomForest(outcome ~ ., data = hdps.data, importance = TRUE)
+
+# Get important features
+rf_importance <- importance(rf_model)
+important_features_rf <- rownames(rf_importance)[order(rf_importance[, 1], decreasing = TRUE)]
+```
+
+```{r rf OR-cont, warning=FALSE, cache=TRUE}
+# Select features
+fs_rf <- important_features_rf[important_features_rf %in% proxy.list][1:100]
+proxy_rf <- paste0(fs_rf, collapse = "+")
+form_rf <- paste0(c(covform, proxy_rf), collapse = "+")
+formula_rf <- as.formula(paste0("exposure", "~", form_rf))
+
+W.out_rf <- weightit(formula_rf, 
+                     data = hdps.data, 
+                     estimand = "ATE",
+                     method = "ps")
+
+hdps.data$ps_rf <- W.out_rf$ps
+hdps.data$w_rf <- W.out_rf$weights
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+fit_rf <- glm(out.formula,
+              data = hdps.data,
+              weights = W.out_rf$weights,
+              family= binomial(link = "logit"))
+summary_rf <- summary(fit_rf)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
+ci_rf <- confint(fit_rf, level = 0.95)["exposure", ]
+sum_ci_rf <- c(exp(summary_rf[1]), summary_rf, ci_rf)
+names(sum_ci_rf) <- c("Odds Ratio",
+                      "Estimate",
+                      "Std. Error",
+                      "Pr(>|z|)",
+                      "2.5 %",
+                      "97.5 %")
+
+end_time <- Sys.time()
+elapsed_time_rf <- as.numeric(difftime(end_time, start_time, units = "secs"))
+
+print("How many proxy variables are in common?")
+paste("There are", length(fs_rf), "features selected by randomForest")
+paste(length(fs_rf[fs_rf %in% fs.bross]), "of the", length(fs_rf), 
+      "are also selected by the bross formula method")
+
+print("The Odds Ratio by Random Forest")
+sum_ci_rf
+print("Elapsed time for Random Forest:")
+elapsed_time_rf
+```
+
+```{r rf RD, warning=FALSE, cache=TRUE}
+fit_gau.rf <- glm(out.formula,
+                     data = hdps.data,
+                     weights = W.out_rf$weights,
+                     family = gaussian(link= "identity"))
+
+summary_rd.rf  <- summary(fit_gau.rf)$coef["exposure",
+                                                 c("Estimate",
+                                                   "Std. Error",
+                                                   "Pr(>|t|)")]
+summary_rd.rf[2]<- sqrt(sandwich::sandwich(fit_gau.rf)[2,2])
+
+require(lmtest)
+conf.int <- confint(fit_gau.rf, "exposure", level = 0.95,  method = "hc1")
+summary_rd.rf  <- c(summary_rd.rf, conf.int)
+
+round(summary_rd.rf, 2)
+```
+
+Naming consistence:
+```{r}
+sum_ci.rf <- sum_ci_rf
+fs.rf <- fs_rf
+```
+
 Comparing the Results:
 ```{r compare, warning=FALSE, cache=TRUE}
-sum_ci.all <- rbind(sum_ci.bross, sum_ci.hybrid, sum_ci.lasso, sum_ci.elastic, 
-                    sum_ci.xgboost, sum_ci.GA, sum_ci.svm, sum_ci.boruta,
+sum_ci.all <- rbind(sum_ci.bross, sum_ci.lasso, sum_ci.hybrid, sum_ci.elastic, 
+                    sum_ci.svm, sum_ci.GA, 
+                    sum_ci.xgboost, sum_ci.rf, sum_ci.boruta,
                     sum_ci.forward, sum_ci.backward, sum_ci.both)
 
-OR.data <- data.frame(method = c("bross", "hybrid", "lasso", "elastic", 
-                                 "xgboost", "GA", "SVM", "boruta", 
+OR.data <- data.frame(method = c("bross", "lasso", "hybrid", "elastic", 
+                                 "SVM", "GA",
+                                 "xgboost", "rf", "boruta", 
                                  "forward", "backward", "both"),
@@
                          levels = c("both", "backward", "forward",
-                                    "boruta", "SVM", "GA", "xgboost", 
-                                    "elastic", "lasso", "hybrid", "bross"))
+                                    "boruta", "rf", "xgboost", 
+                                    "GA", "SVM", 
+                                    "elastic", "hybrid", "lasso", "bross"))
 
@@
 fs.all <- data.frame(numFeature = c(length(fs.bross), 
+                                    length(fs.lasso),
                                     length(fs.hybrid),
-                                    length(fs.lasso), 
                                     length(fs.elastic), 
+                                    length(fs.svm),
+                                    length(fs.GA),
                                     length(fs.xgboost),
-                                    length(fs.GA),
-                                    length(fs.svm),
+                                    length(fs.rf),
                                     length(fs.boruta),
@@
                      numInCommon = c(NA,
+                                     length(fs.lasso[fs.lasso %in% fs.bross]),
                                      length(fs.hybrid[fs.hybrid %in% fs.bross]),
-                                     length(fs.lasso[fs.lasso %in% fs.bross]),
                                      length(fs.elastic[fs.elastic %in% fs.bross]),
+                                     length(fs.svm[fs.svm %in% fs.bross]),
+                                     length(fs.GA[fs.GA %in% fs.bross]),
                                      length(fs.xgboost[fs.xgboost %in% fs.bross]),
-                                     length(fs.GA[fs.GA %in% fs.bross]),
-                                     length(fs.svm[fs.svm %in% fs.bross]),
+                                     length(fs.rf[fs.rf %in% fs.bross]),
                                      length(fs.boruta[fs.boruta %in% fs.bross]),
@@
                                      length(fs.both[fs.both %in% fs.bross])))
-rownames(fs.all) <-  c("bross", "hybrid", "lasso", "elastic", 
-                       "xgb", "GA", "SVM", "boruta",
+rownames(fs.all) <-  c("bross", "lasso", "hybrid", "elastic", 
+                       "SVM", "GA",
+                       "xgboost", "rf", "boruta", 
                        "forward", "backward", "both")
@@
 
-fs.commonOneToOne <- data.frame(ini = rep(NA, 11))
-
-for (i in 1:11) {
+fs.commonOneToOne <- data.frame(ini = rep(NA, 12))
+
+for (i in 1:12) {
   col_name <- OR.data$method[i]
@@
   num_common <- c(length(fs.bross[fs.bross %in% get(paste0("fs.",col_name))]),
+                  length(fs.lasso[fs.lasso %in% get(paste0("fs.",col_name))]),
                   length(fs.hybrid[fs.hybrid %in% get(paste0("fs.",col_name))]),
-                  length(fs.lasso[fs.lasso %in% get(paste0("fs.",col_name))]),
                   length(fs.elastic[fs.elastic %in% get(paste0("fs.",col_name))]),
+                  length(fs.svm[fs.svm %in% get(paste0("fs.",col_name))]),
+                  length(fs.GA[fs.GA %in% get(paste0("fs.",col_name))]),
                   length(fs.xgboost[fs.xgboost %in% get(paste0("fs.",col_name))]),
-                  length(fs.GA[fs.GA %in% get(paste0("fs.",col_name))]),
-                  length(fs.svm[fs.svm %in% get(paste0("fs.",col_name))]),
+                  length(fs.rf[fs.rf %in% get(paste0("fs.",col_name))]),
                   length(fs.boruta[fs.boruta %in% get(paste0("fs.",col_name))]),
@@
                   length(fs.both[fs.both %in% get(paste0("fs.",col_name))]))
-  fs.commonOneToOne[i] <- c(na, num_common[i:11])
+  fs.commonOneToOne[i] <- c(na, num_common[i:12])
 }
@@
 
-```{r rf, warning=FALSE, cache=TRUE}
-# Random Forest Feature Selection
-start_time <- Sys.time()
-rf_model <- randomForest(outcome ~ ., data = hdps.data, importance = TRUE)
-
-# Get important features
-rf_importance <- importance(rf_model)
-important_features_rf <- rownames(rf_importance)[order(rf_importance[, 1], decreasing = TRUE)]
-```
-
-```{r rf2, warning=FALSE, cache=TRUE}
-# Select features
-fs_rf <- important_features_rf[important_features_rf %in% proxy.list]
-proxy_rf <- paste0(fs_rf, collapse = "+")
-form_rf <- paste0(c(covform, proxy_rf), collapse = "+")
-formula_rf <- as.formula(paste0("exposure", "~", form_rf))
-
-W.out_rf <- weightit(formula_rf, 
-                     data = hdps.data, 
-                     estimand = "ATE",
-                     method = "ps")
-
-hdps.data$ps_rf <- W.out_rf$ps
-hdps.data$w_rf <- W.out_rf$weights
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-fit_rf <- glm(out.formula,
-              data = hdps.data,
-              weights = W.out_rf$weights,
-              family= binomial(link = "logit"))
-summary_rf <- summary(fit_rf)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
-ci_rf <- confint(fit_rf, level = 0.95)["exposure", ]
-sum_ci_rf <- c(exp(summary_rf[1]), summary_rf, ci_rf)
-names(sum_ci_rf) <- c("Odds Ratio",
-                      "Estimate",
-                      "Std. Error",
-                      "Pr(>|z|)",
-                      "2.5 %",
-                      "97.5 %")
-
-end_time <- Sys.time()
-elapsed_time_rf <- as.numeric(difftime(end_time, start_time, units = "secs"))
-
-print("How many proxy variables are in common?")
-paste("There are", length(fs_rf), "features selected by randomForest")
-paste(length(fs_rf[fs_rf %in% fs.bross]), "of the", length(fs_rf), 
-      "are also selected by the bross formula method")
-
-print("The Odds Ratio by Random Forest")
-sum_ci_rf
-print("Elapsed time for Random Forest:")
-elapsed_time_rf
-```
-
 ```{r rfe, warning=FALSE, cache=TRUE}
@@
 ```
+
+```{r}
+important_features_rfe
+```
+
+Why does this codechunk not work?
+No proxy is selected by rfe. it only selects diabetes.
+ERROR: the formula in wrong format (ending with "+")
+" e ~ a+b+c+ "
 
@@
 ```
+
+```{r save}
+# Save the entire workspace to a file named "workspace.RData"
+save.image(file = "data/workspace.RData")
+```
+
+```{r OR.ci_plot with # of proxy}
+
+OR.ci_plot_new <- ggplot(OR.data, aes(y = method, x = OR)) +
+  geom_point(size = 3) +
+  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) + 
+  geom_text(aes(label = fs.all[,1], x = OR, y = method),
+            vjust = -0.8,  # Adjust vertical position
+            hjust = -1, # Adjust horizontal position
+            size = 3, 
+            color = "dark green") +
+  labs(title = "Odds Ratios with 95% Confidence Intervals",
+       x = "Odds Ratio",
+       y = "Method")
+```
+
+RD comparison:
+```{r summary RD all methods}
+sum.rd_all <- rbind(summary_rd.bross,
+                    summary_rd.hybrid,
+                    summary_rd.lasso,
+                    summary_rd.elastic,
+                    summary_rd.svm,
+                    summary_rd.GA,
+                    summary_rd.xgboost,
+                    summary_rd.rf,
+                    summary_rd.boruta,
+                    summary_rd.forward,
+                    summary_rd.backward,
+                    summary_rd.both)
+
+rownames(sum.rd_all) <- c("bross", "hybrid", "lasso", "elastic", 
+                          "SVM", "GA",
+                          "xgboost", "rf", "boruta", 
+                          "forward", "backward", "both")
+```
+
+```{r save RD}
+# Save the entire workspace to a file named "workspaceNew.RData"
+save.image(file = "data/workspaceNew.RData")
+```
+
+```{r print RD result table}
+round(sum.rd_all, 3)
+```
+
+```{r print OR.ci_plot with # of proxy}
+OR.ci_plot_new
+```

### 2024-08-01 bross/simResults_bross.Rmd
simResults_bross

---
title: "SimResults_Bross"
author: "Yang Lei"
date: "2024-07-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
require(lmtest)
```

```{r load basic information, warning=FALSE, cache=TRUE}}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
covform <- paste0(investigator.specified.covariates, collapse = "+")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
```

```{r change a to load upto 1000 datasets, warning=FALSE, cache=TRUE}}
# change to 1000 later
a <- 8

RD_bross <- data.frame(RD = numeric(),
                       SE = numeric())

errors <- c()
```

```{r scenario: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}}
set.seed(42)

# Folder "scenario"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$id <- data$idx

  # Feature Selection Method 1: Bross Formula
  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]

  bross.list <- tryCatch({
    get_prioritised_covariates(df = proxy.df,
                               patientIdVarname = "idx", 
                               exposureVector = data$exposure,
                               outcomeVector = data$outcome,
                               patientIdVector = data$idx, 
                               k = 100)
  }, error = function(e) {
    errors <<- c(errors, i)
    "ERROR"
  })

  if (class(bross.list) == "character") {
    proxy_bross <- c(NA)
    sum.RD_bross <- c(NA, NA)

    RD_bross[i,] <- sum.RD_bross
    rownames(RD_bross)[i] <- paste0("data.", i, "_bross")

    proxy_bross.i <- paste0("proxy_bross.", i)
    assign(proxy_bross.i, proxy_bross)
    sum.RD_bross.i <- paste0("sum.RD_bross.", i)
    assign(sum.RD_bross.i, sum.RD_bross)
  } else {
    proxy.df_bross <- bross.list$autoselected_covariate_df
    hdps.data_bross <- merge(data[,c("idx",
                                     outcome, 
                                     exposure, 
                                     investigator.specified.covariates)],
                             proxy.df_bross,
                             by = "idx")
    hdps.data_bross$id <- hdps.data_bross$idx
    hdps.data_bross$idx <- NULL

    hdps.data_bross$exposure <- as.numeric(I(hdps.data_bross$obese=='Yes'))
    hdps.data_bross$outcome <- as.numeric(I(hdps.data_bross$diabetes=='Yes'))

    proxy_bross <- names(proxy.df_bross[,-1])
    proxyform <- paste0(proxy_bross, collapse = "+")
    rhsformula <- paste0(c(covform, proxyform), collapse = "+")
    ps.formula <- as.formula(paste0("exposure", "~", rhsformula))

    W.out_bross <- weightit(ps.formula,
                            data = hdps.data_bross, 
                            estimand = "ATE",
                            method = "ps")
    fit.OR_bross <- glm(out.formula,
                        data = hdps.data_bross,
                        weights = W.out_bross$weights,
                        family= binomial(link = "logit"))
    fit.RD_bross <- glm(out.formula,
                        data= hdps.data_bross,
                        weights= W.out_bross$weights,
                        family=gaussian(link= "identity"))
    sum.RD_bross <- c(summary(fit.RD_bross)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_bross)[2,2]))

    RD_bross[i,] <- sum.RD_bross
    rownames(RD_bross)[i] <- paste0("data.", i, "_bross")

    proxy_bross.i <- paste0("proxy_bross.", i)
    assign(proxy_bross.i, proxy_bross)
    sum.RD_bross.i <- paste0("sum.RD_bross.", i)
    assign(sum.RD_bross.i, sum.RD_bross)
  }
}
```

```{r scenarioER: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}}
set.seed(42)

# Folder "scenarioER"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$id <- data$idx

  # Feature Selection Method 1: Bross Formula
  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]

  bross.list <- tryCatch({
    get_prioritised_covariates(df = proxy.df,
                               patientIdVarname = "idx", 
                               exposureVector = data$exposure,
                               outcomeVector = data$outcome,
                               patientIdVector = data$idx, 
                               k = 100)
  }, error = function(e) {
    errors <<- c(errors, paste0("ER.", i))
    "ERROR"
  })

  if (class(bross.list) == "character") {
    proxy_bross <- c(NA)
    sum.RD_bross <- c(NA, NA)

    RD_bross[i+a,] <- sum.RD_bross
    rownames(RD_bross)[i+a] <- paste0("ER.data.", i, "_bross")

    proxy_bross.i <- paste0("proxy_bross.ER.", i)
    assign(proxy_bross.i, proxy_bross)
    sum.RD_bross.i <- paste0("sum.RD_bross.ER.", i)
    assign(sum.RD_bross.i, sum.RD_bross)
  } else {
    proxy.df_bross <- bross.list$autoselected_covariate_df
    hdps.data_bross <- merge(data[,c("idx",
                                     outcome, 
                                     exposure, 
                                     investigator.specified.covariates)],
                             proxy.df_bross,
                             by = "idx")
    hdps.data_bross$id <- hdps.data_bross$idx
    hdps.data_bross$idx <- NULL

    hdps.data_bross$exposure <- as.numeric(I(hdps.data_bross$obese=='Yes'))
    hdps.data_bross$outcome <- as.numeric(I(hdps.data_bross$diabetes=='Yes'))

    proxy_bross <- names(proxy.df_bross[,-1])
    proxyform <- paste0(proxy_bross, collapse = "+")
    rhsformula <- paste0(c(covform, proxyform), collapse = "+")
    ps.formula <- as.formula(paste0("exposure", "~", rhsformula))

    W.out_bross <- weightit(ps.formula,
                            data = hdps.data_bross, 
                            estimand = "ATE",
                            method = "ps")
    fit.OR_bross <- glm(out.formula,
                        data = hdps.data_bross,
                        weights = W.out_bross$weights,
                        family= binomial(link = "logit"))
    fit.RD_bross <- glm(out.formula,
                        data= hdps.data_bross,
                        weights= W.out_bross$weights,
                        family=gaussian(link= "identity"))
    sum.RD_bross <- c(summary(fit.RD_bross)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_bross)[2,2]))

    RD_bross[i+a,] <- sum.RD_bross
    rownames(RD_bross)[i+a] <- paste0("ER.data.", i, "_bross")

    proxy_bross.i <- paste0("proxy_bross.ER.", i)
    assign(proxy_bross.i, proxy_bross)
    sum.RD_bross.i <- paste0("sum.RD_bross.ER.", i)
    assign(sum.RD_bross.i, sum.RD_bross)
  }
}
```

```{r scenarioOR: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}}
set.seed(42)

# Folder "scenarioOR"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$id <- data$idx

  # Feature Selection Method 1: Bross Formula
  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]

  bross.list <- tryCatch({
    get_prioritised_covariates(df = proxy.df,
                               patientIdVarname = "idx", 
                               exposureVector = data$exposure,
                               outcomeVector = data$outcome,
                               patientIdVector = data$idx, 
                               k = 100)
  }, error = function(e) {
    errors <<- c(errors, paste0("OR.", i))
    "ERROR"
  })

  if (class(bross.list) == "character") {
    proxy_bross <- c(NA)
    sum.RD_bross <- c(NA, NA)

    RD_bross[i+2*a,] <- sum.RD_bross
    rownames(RD_bross)[i+2*a] <- paste0("OR.data.", i, "_bross")

    proxy_bross.i <- paste0("proxy_bross.OR.", i)
    assign(proxy_bross.i, proxy_bross)
    sum.RD_bross.i <- paste0("sum.RD_bross.OR.", i)
    assign(sum.RD_bross.i, sum.RD_bross)
  } else {
    proxy.df_bross <- bross.list$autoselected_covariate_df
    hdps.data_bross <- merge(data[,c("idx",
                                     outcome, 
                                     exposure, 
                                     investigator.specified.covariates)],
                             proxy.df_bross,
                             by = "idx")
    hdps.data_bross$id <- hdps.data_bross$idx
    hdps.data_bross$idx <- NULL

    hdps.data_bross$exposure <- as.numeric(I(hdps.data_bross$obese=='Yes'))
    hdps.data_bross$outcome <- as.numeric(I(hdps.data_bross$diabetes=='Yes'))

    proxy_bross <- names(proxy.df_bross[,-1])
    proxyform <- paste0(proxy_bross, collapse = "+")
    rhsformula <- paste0(c(covform, proxyform), collapse = "+")
    ps.formula <- as.formula(paste0("exposure", "~", rhsformula))

    W.out_bross <- weightit(ps.formula,
                            data = hdps.data_bross, 
                            estimand = "ATE",
                            method = "ps")
    fit.OR_bross <- glm(out.formula,
                        data = hdps.data_bross,
                        weights = W.out_bross$weights,
                        family= binomial(link = "logit"))
    fit.RD_bross <- glm(out.formula,
                        data= hdps.data_bross,
                        weights= W.out_bross$weights,
                        family=gaussian(link= "identity"))
    sum.RD_bross <- c(summary(fit.RD_bross)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_bross)[2,2]))

    RD_bross[i+2*a,] <- sum.RD_bross
    rownames(RD_bross)[i+2*a] <- paste0("OR.data.", i, "_bross")

    proxy_bross.i <- paste0("proxy_bross.OR.", i)
    assign(proxy_bross.i, proxy_bross)
    sum.RD_bross.i <- paste0("sum.RD_bross.OR.", i)
    assign(sum.RD_bross.i, sum.RD_bross)
  }
}
```

```{r read RD & SE results (with error rows), warning=FALSE, cache=TRUE}
RD_bross
```

```{r check index of dataset causing error, warning=FALSE, cache=TRUE}
# check index of dataset causing error
errors
```

```{r read RD & SE results (without error rows), warning=FALSE, cache=TRUE}
RD_bross_no.error <- RD_bross[complete.cases(RD_bross),]
RD_bross_no.error
```

### 2024-08-01 bross/simResults_bross.Rmd
simResults_bross not sure why it is showing an error message:  all connections are in use

@@
 
-```{r change a to load upto 1000 datasets, warning=FALSE, cache=TRUE}}
-# change to 1000 later
-a <- 8
+```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for loop
+a <- 1000
 
@@
 ```
+
+```{r check intermediate results for each data, warning=FALSE, cache=TRUE}
+# check RD & SE by bross for each data, print:
+#   sum.RD_bross.n, sum.RD_bross.ER.n, or sum.RD_bross.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+sum.RD_bross.1
+sum.RD_bross.ER.2
+
+# check proxy selected by bross for each data, print:
+#   proxy_bross.n, proxy_bross.ER.n, or proxy_bross.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+proxy_bross.1
+proxy_bross.ER.5
+```

### 2024-08-01 bross/simResults_bross.Rmd
simulation results by bross formula

@@
 ```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
-# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
 a <- 1000

### 2024-08-01 bross/simResults_bross.Rmd
simulation results by bross. add closeAllConnections() after all connection being in used

@@
                 ".rds")
-  data <- readRDS(url(url))
+  data <- tryCatch({
+    readRDS(url(url))
+  }, error = function(e) {
+    closeAllConnections()
+    readRDS(url(url))
+  })
 

### 2024-08-01 sim_lasso/simResults_lasso.Rmd
simulation results by bross & lasso. changed folder name

---
title: "SimResults_Lasso"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
require(lmtest)
```

```{r load basic information, warning=FALSE, cache=TRUE}}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
covform <- paste0(investigator.specified.covariates, collapse = "+")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))

url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_1.rds")
data <- readRDS(url(url))
proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )
```

```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_lasso <- data.frame(RD = numeric(),
                       SE = numeric())
```

```{r}
data <- tryCatch({
  readRDS(url(url))
}, error = function(e) {
  closeAllConnections()
  readRDS(url(url))
})
```

```{r scenario: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}}
set.seed(42)

# Folder "scenario"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

  lasso.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(lasso.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_lasso <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_lasso, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_lasso <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_lasso$ps
  data$w.l <- W.out_lasso$weights

  fit.OR_lasso <- glm(out.formula,
                      data = data,
                      weights = W.out_lasso$weights,
                      family= binomial(link = "logit"))
  fit.RD_lasso <- glm(out.formula,
                       data = data,
                       weights = W.out_lasso$weights,
                       family = gaussian(link= "identity"))
  sum.RD_lasso <- c(summary(fit.RD_lasso)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_lasso)[2,2]))

  RD_lasso[i,] <- sum.RD_lasso
  rownames(RD_lasso)[i] <- paste0("data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```
```{r scenarioER: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}}
set.seed(42)

# Folder "scenarioER"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

  lasso.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(lasso.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_lasso <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_lasso, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_lasso <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_lasso$ps
  data$w.l <- W.out_lasso$weights

  fit.OR_lasso <- glm(out.formula,
                      data = data,
                      weights = W.out_lasso$weights,
                      family= binomial(link = "logit"))
  fit.RD_lasso <- glm(out.formula,
                       data = data,
                       weights = W.out_lasso$weights,
                       family = gaussian(link= "identity"))
  sum.RD_lasso <- c(summary(fit.RD_lasso)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_lasso)[2,2]))

  RD_lasso[i+a,] <- sum.RD_lasso
  rownames(RD_lasso)[i+a] <- paste0("ER.data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.ER.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.ER.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```
```{r scenarioOR: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}}
set.seed(42)

# Folder "scenarioOR"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

  lasso.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(lasso.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_lasso <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_lasso, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_lasso <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_lasso$ps
  data$w.l <- W.out_lasso$weights

  fit.OR_lasso <- glm(out.formula,
                      data = data,
                      weights = W.out_lasso$weights,
                      family= binomial(link = "logit"))
  fit.RD_lasso <- glm(out.formula,
                       data = data,
                       weights = W.out_lasso$weights,
                       family = gaussian(link= "identity"))
  sum.RD_lasso <- c(summary(fit.RD_lasso)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_lasso)[2,2]))

  RD_lasso[i+2*a,] <- sum.RD_lasso
  rownames(RD_lasso)[i+2*a] <- paste0("OR.data.", i, "_lasso")

  proxy_lasso.i <- paste0("proxy_lasso.OR.", i)
  assign(proxy_lasso.i, proxy_lasso)
  sum.RD_lasso.i <- paste0("sum.RD_lasso.OR.", i)
  assign(sum.RD_lasso.i, sum.RD_lasso)
}
```

```{r read RD & SE results by lasso, warning=FALSE, cache=TRUE}
RD_lasso
```

```{r check intermediate results for each data by lasso, warning=FALSE, cache=TRUE}
# check RD & SE by lasso for each data, print:
#   sum.RD_lasso.n, sum.RD_lasso.ER.n, or sum.RD_lasso.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_lasso.1
sum.RD_lasso.ER.2

# check proxy selected by lasso for each data, print:
#   proxy_lasso.n, proxy_lasso.ER.n, or proxy_lasso.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_lasso.1
proxy_lasso.ER.3
```

### 2024-08-01 sim_1.bross/simResults_bross.Rmd
simulation results bross, lasso, enet

--- 2024-08-01 bross/simResults_bross.Rmd
@@
 
-```{r load basic information, warning=FALSE, cache=TRUE}}
+```{r load basic information, warning=FALSE, cache=TRUE}
 # global information
@@
 
-```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
+```{r initialization before for-loop, warning=FALSE, cache=TRUE}
 # 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
@@
 
-```{r scenario: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}}
+```{r scenario: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-```{r scenarioER: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}}
+```{r scenarioER: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-```{r scenarioOR: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}}
+```{r scenarioOR: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}
 set.seed(42)

### 2024-08-01 sim_3.lasso/simResults_lasso.Rmd
simulation results bross, lasso, enet

--- 2024-08-01 sim_lasso/simResults_lasso.Rmd
@@
 
-```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
+```{r initialization before for-loop, warning=FALSE, cache=TRUE}
 # 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
-a <- 1000
+a <- 5
 
@@
 
-```{r}
-data <- tryCatch({
-  readRDS(url(url))
-}, error = function(e) {
-  closeAllConnections()
-  readRDS(url(url))
-})
-```
-
-```{r scenario: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}}
+```{r scenario: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 ```
-```{r scenarioER: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}}
+
+```{r scenarioER: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 ```
-```{r scenarioOR: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}}
+
+```{r scenarioOR: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
 set.seed(42)

### 2024-08-01 sim_4.enet/SimResults_Enet.Rmd
simulation results bross, lasso, enet

--- 2024-08-01 sim_3.lasso/simResults_lasso.Rmd
@@
 ---
-title: "SimResults_Lasso"
+title: "SimResults_Enet"
 author: "Yang Lei"
@@
 # 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
-a <- 5
+a <- 1000
 
-RD_lasso <- data.frame(RD = numeric(),
+RD_enet <- data.frame(RD = numeric(),
                        SE = numeric())
@@
 
-```{r scenario: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
+```{r scenario: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-  lasso.fit <- glmnet::cv.glmnet(y = data$outcome, 
+  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                  x = covar.mat, 
@@
                                  family="binomial",
-                                 alpha = 1, 
+                                 alpha = 0.5, 
                                  nfolds = 5)
-  coef.fit <- coef(lasso.fit,s='lambda.min',exact=TRUE)
+  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
   sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
-  proxy_lasso <- proxy.list[proxy.list %in% sel.variables]
-  proxyform <- paste0(proxy_lasso, collapse = "+")
+  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
+  proxyform <- paste0(proxy_enet, collapse = "+")
   rhsform <- paste0(c(covform, proxyform), collapse = "+")
@@
 
-  W.out_lasso <- weightit(ps.formula, 
+  W.out_enet <- weightit(ps.formula, 
                           data = data, 
@@
   #
-  data$ps.l <- W.out_lasso$ps
-  data$w.l <- W.out_lasso$weights
+  data$ps.l <- W.out_enet$ps
+  data$w.l <- W.out_enet$weights
 
-  fit.OR_lasso <- glm(out.formula,
+  fit.OR_enet <- glm(out.formula,
                       data = data,
-                      weights = W.out_lasso$weights,
+                      weights = W.out_enet$weights,
                       family= binomial(link = "logit"))
-  fit.RD_lasso <- glm(out.formula,
+  fit.RD_enet <- glm(out.formula,
                        data = data,
-                       weights = W.out_lasso$weights,
+                       weights = W.out_enet$weights,
                        family = gaussian(link= "identity"))
-  sum.RD_lasso <- c(summary(fit.RD_lasso)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_lasso)[2,2]))
+  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))
 
-  RD_lasso[i,] <- sum.RD_lasso
-  rownames(RD_lasso)[i] <- paste0("data.", i, "_lasso")
+  RD_enet[i,] <- sum.RD_enet
+  rownames(RD_enet)[i] <- paste0("data.", i, "_enet")
 
-  proxy_lasso.i <- paste0("proxy_lasso.", i)
-  assign(proxy_lasso.i, proxy_lasso)
-  sum.RD_lasso.i <- paste0("sum.RD_lasso.", i)
-  assign(sum.RD_lasso.i, sum.RD_lasso)
+  proxy_enet.i <- paste0("proxy_enet.", i)
+  assign(proxy_enet.i, proxy_enet)
+  sum.RD_enet.i <- paste0("sum.RD_enet.", i)
+  assign(sum.RD_enet.i, sum.RD_enet)
 }
 ```
-
-```{r scenarioER: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
+```{r scenarioER: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
                                  nfolds = 5)
-  coef.fit <- coef(lasso.fit,s='lambda.min',exact=TRUE)
+  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
   sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
-  proxy_lasso <- proxy.list[proxy.list %in% sel.variables]
-  proxyform <- paste0(proxy_lasso, collapse = "+")
+  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
+  proxyform <- paste0(proxy_enet, collapse = "+")
   rhsform <- paste0(c(covform, proxyform), collapse = "+")
@@
   #
-  data$ps.l <- W.out_lasso$ps
-  data$w.l <- W.out_lasso$weights
+  data$ps.l <- W.out_enet$ps
+  data$w.l <- W.out_enet$weights
 
-  fit.OR_lasso <- glm(out.formula,
+  fit.OR_enet <- glm(out.formula,
                       data = data,
-                      weights = W.out_lasso$weights,
+                      weights = W.out_enet$weights,
                       family= binomial(link = "logit"))
-  fit.RD_lasso <- glm(out.formula,
+  fit.RD_enet <- glm(out.formula,
                        data = data,
-                       weights = W.out_lasso$weights,
+                       weights = W.out_enet$weights,
                        family = gaussian(link= "identity"))
-  sum.RD_lasso <- c(summary(fit.RD_lasso)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_lasso)[2,2]))
+  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))
 
-  RD_lasso[i+a,] <- sum.RD_lasso
-  rownames(RD_lasso)[i+a] <- paste0("ER.data.", i, "_lasso")
+  RD_enet[i+a,] <- sum.RD_enet
+  rownames(RD_enet)[i+a] <- paste0("ER.data.", i, "_enet")
 
-  proxy_lasso.i <- paste0("proxy_lasso.ER.", i)
-  assign(proxy_lasso.i, proxy_lasso)
-  sum.RD_lasso.i <- paste0("sum.RD_lasso.ER.", i)
-  assign(sum.RD_lasso.i, sum.RD_lasso)
+  proxy_enet.i <- paste0("proxy_enet.ER.", i)
+  assign(proxy_enet.i, proxy_enet)
+  sum.RD_enet.i <- paste0("sum.RD_enet.ER.", i)
+  assign(sum.RD_enet.i, sum.RD_enet)
 }
@@
 
-```{r scenarioOR: for-loop generating RD & SE results for lasso, warning=FALSE, cache=TRUE}
+```{r scenarioOR: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
   #
-  data$ps.l <- W.out_lasso$ps
-  data$w.l <- W.out_lasso$weights
+  data$ps.l <- W.out_enet$ps
+  data$w.l <- W.out_enet$weights
 
-  fit.OR_lasso <- glm(out.formula,
+  fit.OR_enet <- glm(out.formula,
                       data = data,
-                      weights = W.out_lasso$weights,
+                      weights = W.out_enet$weights,
                       family= binomial(link = "logit"))
-  fit.RD_lasso <- glm(out.formula,
+  fit.RD_enet <- glm(out.formula,
                        data = data,
-                       weights = W.out_lasso$weights,
+                       weights = W.out_enet$weights,
                        family = gaussian(link= "identity"))
-  sum.RD_lasso <- c(summary(fit.RD_lasso)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_lasso)[2,2]))
+  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))
 
-  RD_lasso[i+2*a,] <- sum.RD_lasso
-  rownames(RD_lasso)[i+2*a] <- paste0("OR.data.", i, "_lasso")
+  RD_enet[i+2*a,] <- sum.RD_enet
+  rownames(RD_enet)[i+2*a] <- paste0("OR.data.", i, "_enet")
 
-  proxy_lasso.i <- paste0("proxy_lasso.OR.", i)
-  assign(proxy_lasso.i, proxy_lasso)
-  sum.RD_lasso.i <- paste0("sum.RD_lasso.OR.", i)
-  assign(sum.RD_lasso.i, sum.RD_lasso)
+  proxy_enet.i <- paste0("proxy_enet.OR.", i)
+  assign(proxy_enet.i, proxy_enet)
+  sum.RD_enet.i <- paste0("sum.RD_enet.OR.", i)
+  assign(sum.RD_enet.i, sum.RD_enet)
 }
@@
 
-```{r read RD & SE results by lasso, warning=FALSE, cache=TRUE}
-RD_lasso
+```{r read RD & SE results by enet, warning=FALSE, cache=TRUE}
+RD_enet
 ```
 
-```{r check intermediate results for each data by lasso, warning=FALSE, cache=TRUE}
-# check RD & SE by lasso for each data, print:
-#   sum.RD_lasso.n, sum.RD_lasso.ER.n, or sum.RD_lasso.OR.n
+```{r check intermediate results for each data by enet, warning=FALSE, cache=TRUE}
+# check RD & SE by enet for each data, print:
+#   sum.RD_enet.n, sum.RD_enet.ER.n, or sum.RD_enet.OR.n
 #   where "n" is a number ranges from 1 to 1000
 #   e.g.
-sum.RD_lasso.1
-sum.RD_lasso.ER.2
+sum.RD_enet.1
+sum.RD_enet.ER.2
 
-# check proxy selected by lasso for each data, print:
-#   proxy_lasso.n, proxy_lasso.ER.n, or proxy_lasso.OR.n
+# check proxy selected by enet for each data, print:
+#   proxy_enet.n, proxy_enet.ER.n, or proxy_enet.OR.n
 #   where "n" is a number ranges from 1 to 1000
 #   e.g.
-proxy_lasso.1
-proxy_lasso.ER.3
+proxy_enet.1
+proxy_enet.ER.3
 ```

### 2024-08-01 sim_4.enet/simResults_enet.Rmd
simulation results by enet done

--- 2024-08-01 sim_4.enet/SimResults_Enet.Rmd
@@
 ---
-title: "SimResults_Enet"
+title: "simResults_enet"
 author: "Yang Lei"
@@
 ```
-
-```{r check intermediate results for each data by enet, warning=FALSE, cache=TRUE}
-# check RD & SE by enet for each data, print:
-#   sum.RD_enet.n, sum.RD_enet.ER.n, or sum.RD_enet.OR.n
-#   where "n" is a number ranges from 1 to 1000
-#   e.g.
-sum.RD_enet.1
-sum.RD_enet.ER.2
-
-# check proxy selected by enet for each data, print:
-#   proxy_enet.n, proxy_enet.ER.n, or proxy_enet.OR.n
-#   where "n" is a number ranges from 1 to 1000
-#   e.g.
-proxy_enet.1
-proxy_enet.ER.3
-```

### 2024-08-01 sim_4.enet/simResults_enet.Rmd
sim results by enet, svm did not run svm, long running time

--- 2024-08-01 sim_4.enet/SimResults_Enet.Rmd
@@
 ```
+
 ```{r scenarioER: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}

### 2024-08-01 sim_5.svm/simResults_svm.Rmd
sim results by enet, svm did not run svm, long running time

--- 2024-08-01 sim_4.enet/simResults_enet.Rmd
@@
 ---
-title: "simResults_enet"
+title: "simResults_svm"
 author: "Yang Lei"
@@
 
-RD_enet <- data.frame(RD = numeric(),
+RD_svm <- data.frame(RD = numeric(),
                        SE = numeric())
@@
 
-```{r scenario: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
+```{r scenario: for-loop generating RD & SE results for svm, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
-                                 x = covar.mat, 
-                                 type.measure='mse',
-                                 family="binomial",
-                                 alpha = 0.5, 
-                                 nfolds = 5)
-  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
-  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
-  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
-  proxyform <- paste0(proxy_enet, collapse = "+")
+  svmTrainOutcome <- data$outcome
+  svmTrainOutcome[svmTrainOutcome == 0] <- -1
+  svmTrainPreds <- data.frame(covar.mat)
+
+  bounds <- t(data.frame(log2lambda1=c(-10, 10), log2lambda2=c(-10,10)))
+  colnames(bounds)<-c("lower", "upper")
+  svm.model <- svmfs(x=covar.mat,
+                     y = svmTrainOutcome,
+                     fs.method = "scad+L2",
+                     bounds=bounds,
+                     grid.search = "interval",
+                     inner.val.method = "cv",
+                     show = "none",
+                     parms.coding = "none",
+                     seed=42)
+
+  sel.variables <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
+  proxy_svm <- proxy.list[proxy.list %in% sel.variables]
+  proxyform <- paste0(proxy_svm, collapse = "+")
   rhsform <- paste0(c(covform, proxyform), collapse = "+")
@@
 
-  W.out_enet <- weightit(ps.formula, 
+  W.out_svm <- weightit(ps.formula, 
                           data = data, 
@@
                           method = "ps")
-  #
-  data$ps.l <- W.out_enet$ps
-  data$w.l <- W.out_enet$weights
 
-  fit.OR_enet <- glm(out.formula,
+  data$ps.l <- W.out_svm$ps
+  data$w.l <- W.out_svm$weights
+
+  fit.OR_svm <- glm(out.formula,
                       data = data,
-                      weights = W.out_enet$weights,
+                      weights = W.out_svm$weights,
                       family= binomial(link = "logit"))
-  fit.RD_enet <- glm(out.formula,
+  fit.RD_svm <- glm(out.formula,
                        data = data,
-                       weights = W.out_enet$weights,
+                       weights = W.out_svm$weights,
                        family = gaussian(link= "identity"))
-  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))
+  sum.RD_svm <- c(summary(fit.RD_svm)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_svm)[2,2]))
 
-  RD_enet[i,] <- sum.RD_enet
-  rownames(RD_enet)[i] <- paste0("data.", i, "_enet")
+  RD_svm[i,] <- sum.RD_svm
+  rownames(RD_svm)[i] <- paste0("data.", i, "_svm")
 
-  proxy_enet.i <- paste0("proxy_enet.", i)
-  assign(proxy_enet.i, proxy_enet)
-  sum.RD_enet.i <- paste0("sum.RD_enet.", i)
-  assign(sum.RD_enet.i, sum.RD_enet)
+  proxy_svm.i <- paste0("proxy_svm.", i)
+  assign(proxy_svm.i, proxy_svm)
+  sum.RD_svm.i <- paste0("sum.RD_svm.", i)
+  assign(sum.RD_svm.i, sum.RD_svm)
 }
 ```
-```{r scenarioER: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
+
+```{r scenarioER: for-loop generating RD & SE results for svm, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
-                                 x = covar.mat, 
-                                 type.measure='mse',
-                                 family="binomial",
-                                 alpha = 1, 
-                                 nfolds = 5)
-  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
-  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
-  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
-  proxyform <- paste0(proxy_enet, collapse = "+")
+  svmTrainOutcome <- data$outcome
+  svmTrainOutcome[svmTrainOutcome == 0] <- -1
+  svmTrainPreds <- data.frame(covar.mat)
+
+  bounds <- t(data.frame(log2lambda1=c(-10, 10), log2lambda2=c(-10,10)))
+  colnames(bounds)<-c("lower", "upper")
+  svm.model <- svmfs(x=covar.mat,
+                     y = svmTrainOutcome,
+                     fs.method = "scad+L2",
+                     bounds=bounds,
+                     grid.search = "interval",
+                     inner.val.method = "cv",
+                     show = "none",
+                     parms.coding = "none",
+                     seed=42)
+
+  sel.variables <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
+  proxy_svm <- proxy.list[proxy.list %in% sel.variables]
+  proxyform <- paste0(proxy_svm, collapse = "+")
   rhsform <- paste0(c(covform, proxyform), collapse = "+")
@@
                           method = "ps")
-  #
-  data$ps.l <- W.out_enet$ps
-  data$w.l <- W.out_enet$weights
 
-  fit.OR_enet <- glm(out.formula,
+  data$ps.l <- W.out_svm$ps
+  data$w.l <- W.out_svm$weights
+
+  fit.OR_svm <- glm(out.formula,
                       data = data,
-                      weights = W.out_enet$weights,
+                      weights = W.out_svm$weights,
                       family= binomial(link = "logit"))
-  fit.RD_enet <- glm(out.formula,
+  fit.RD_svm <- glm(out.formula,
                        data = data,
-                       weights = W.out_enet$weights,
+                       weights = W.out_svm$weights,
                        family = gaussian(link= "identity"))
-  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))
+  sum.RD_svm <- c(summary(fit.RD_svm)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_svm)[2,2]))
 
-  RD_enet[i+a,] <- sum.RD_enet
-  rownames(RD_enet)[i+a] <- paste0("ER.data.", i, "_enet")
+  RD_svm[i+a,] <- sum.RD_svm
+  rownames(RD_svm)[i+a] <- paste0("ER.data.", i, "_svm")
 
-  proxy_enet.i <- paste0("proxy_enet.ER.", i)
-  assign(proxy_enet.i, proxy_enet)
-  sum.RD_enet.i <- paste0("sum.RD_enet.ER.", i)
-  assign(sum.RD_enet.i, sum.RD_enet)
+  proxy_svm.i <- paste0("proxy_svm.ER.", i)
+  assign(proxy_svm.i, proxy_svm)
+  sum.RD_svm.i <- paste0("sum.RD_svm.ER.", i)
+  assign(sum.RD_svm.i, sum.RD_svm)
 }
@@
 
-```{r scenarioOR: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
+```{r scenarioOR: for-loop generating RD & SE results for svm, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
                           method = "ps")
-  #
-  data$ps.l <- W.out_enet$ps
-  data$w.l <- W.out_enet$weights
 
-  fit.OR_enet <- glm(out.formula,
+  data$ps.l <- W.out_svm$ps
+  data$w.l <- W.out_svm$weights
+
+  fit.OR_svm <- glm(out.formula,
                       data = data,
-                      weights = W.out_enet$weights,
+                      weights = W.out_svm$weights,
                       family= binomial(link = "logit"))
-  fit.RD_enet <- glm(out.formula,
+  fit.RD_svm <- glm(out.formula,
                        data = data,
-                       weights = W.out_enet$weights,
+                       weights = W.out_svm$weights,
                        family = gaussian(link= "identity"))
-  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))
+  sum.RD_svm <- c(summary(fit.RD_svm)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_svm)[2,2]))
 
-  RD_enet[i+2*a,] <- sum.RD_enet
-  rownames(RD_enet)[i+2*a] <- paste0("OR.data.", i, "_enet")
+  RD_svm[i+2*a,] <- sum.RD_svm
+  rownames(RD_svm)[i+2*a] <- paste0("OR.data.", i, "_svm")
 
-  proxy_enet.i <- paste0("proxy_enet.OR.", i)
-  assign(proxy_enet.i, proxy_enet)
-  sum.RD_enet.i <- paste0("sum.RD_enet.OR.", i)
-  assign(sum.RD_enet.i, sum.RD_enet)
+  proxy_svm.i <- paste0("proxy_svm.OR.", i)
+  assign(proxy_svm.i, proxy_svm)
+  sum.RD_svm.i <- paste0("sum.RD_svm.OR.", i)
+  assign(sum.RD_svm.i, sum.RD_svm)
 }
@@
 
-```{r read RD & SE results by enet, warning=FALSE, cache=TRUE}
-RD_enet
+```{r read RD & SE results by svm, warning=FALSE, cache=TRUE}
+RD_svm
 ```
+
+```{r check intermediate results for each data by svm, warning=FALSE, cache=TRUE}
+# check RD & SE by svm for each data, print:
+#   sum.RD_svm.n, sum.RD_svm.ER.n, or sum.RD_svm.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+sum.RD_svm.1
+sum.RD_svm.ER.2
+
+# check proxy selected by svm for each data, print:
+#   proxy_svm.n, proxy_svm.ER.n, or proxy_svm.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+proxy_svm.1
+proxy_svm.ER.3
+```

### 2024-08-01 sim_6.ga/simResults_ga.Rmd
sim results svm, ga

---
title: "simResults_ga"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
require(lmtest)
```

```{r load basic information, warning=FALSE, cache=TRUE}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
covform <- paste0(investigator.specified.covariates, collapse = "+")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))

url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_1.rds")
data <- readRDS(url(url))
proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )

# function for GA
gaOpt <- function(vars, IV.train, DV.train) {
	varNames <- colnames(IV.train) #getting names of all variables
	selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
	gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars

	gaDat <- cbind(gaSolutionData,DV.train) # combining selected variables with outcome variable
	gaMod <- glm(DV.train ~ ., family = "binomial", data = gaDat) #build model
	gaProb <- predict(gaMod, IV.train, type = "response") # get probabilities
	gaPred <- ifelse(gaProb >= .8, 1, 0) # get predicted 0s and 1s

	ari <- adjustedRandIndex(gaPred, DV.train)
	return(ari)
}
```

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_ga <- data.frame(RD = numeric(),
                       SE = numeric())
```

```{r scenario: for-loop generating RD & SE results for ga, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenario"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

  ga.solution <- ga(fitness = function(vars)
    gaOpt(vars = vars, 
          IV.train = data.frame(covar.mat),
          DV.train = data$outcome),
    type = "binary", 
    nBits = ncol(covar.mat),
    names = colnames(covar.mat), 
    seed = 42,
    run=5)

  allVarNames <- colnames(covar.mat)
  sel.variables <- allVarNames[ga.solution@solution[1,]==1]
  proxy_ga <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_ga, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_ga <- weightit(ps.formula, 
                       data = data, 
                       estimand = "ATE",
                       method = "ps")

  data$ps.l <- W.out_ga$ps
  data$w.l <- W.out_ga$weights

  fit.OR_ga <- glm(out.formula,
                      data = data,
                      weights = W.out_ga$weights,
                      family= binomial(link = "logit"))
  fit.RD_ga <- glm(out.formula,
                       data = data,
                       weights = W.out_ga$weights,
                       family = gaussian(link= "identity"))
  sum.RD_ga <- c(summary(fit.RD_ga)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_ga)[2,2]))

  RD_ga[i,] <- sum.RD_ga
  rownames(RD_ga)[i] <- paste0("data.", i, "_ga")

  proxy_ga.i <- paste0("proxy_ga.", i)
  assign(proxy_ga.i, proxy_ga)
  sum.RD_ga.i <- paste0("sum.RD_ga.", i)
  assign(sum.RD_ga.i, sum.RD_ga)
}
```

```{r scenarioER: for-loop generating RD & SE results for ga, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioER"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

  ga.solution <- ga(fitness = function(vars)
    gaOpt(vars = vars, 
          IV.train = data.frame(covar.mat),
          DV.train = data$outcome),
    type = "binary", 
    nBits = ncol(covar.mat),
    names = colnames(covar.mat), 
    seed = 42,
    run=5)

  allVarNames <- colnames(covar.mat)
  sel.variables <- allVarNames[ga.solution@solution[1,]==1]
  proxy_ga <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_ga, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_ga <- weightit(ps.formula, 
                       data = data, 
                       estimand = "ATE",
                       method = "ps")

  data$ps.l <- W.out_ga$ps
  data$w.l <- W.out_ga$weights

  fit.OR_ga <- glm(out.formula,
                      data = data,
                      weights = W.out_ga$weights,
                      family= binomial(link = "logit"))
  fit.RD_ga <- glm(out.formula,
                       data = data,
                       weights = W.out_ga$weights,
                       family = gaussian(link= "identity"))
  sum.RD_ga <- c(summary(fit.RD_ga)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_ga)[2,2]))

  RD_ga[i+a,] <- sum.RD_ga
  rownames(RD_ga)[i+a] <- paste0("ER.data.", i, "_ga")

  proxy_ga.i <- paste0("proxy_ga.ER.", i)
  assign(proxy_ga.i, proxy_ga)
  sum.RD_ga.i <- paste0("sum.RD_ga.ER.", i)
  assign(sum.RD_ga.i, sum.RD_ga)
}
```

```{r scenarioOR: for-loop generating RD & SE results for ga, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioOR"
for (i in 1:a) {
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- tryCatch({
    readRDS(url(url))
  }, error = function(e) {
    closeAllConnections()
    readRDS(url(url))
  })

  # found some id != idx
  data$id <- data$idx
  covar.mat <- model.matrix(Y.form, data = data)[,-1]

  ga.solution <- ga(fitness = function(vars)
    gaOpt(vars = vars, 
          IV.train = data.frame(covar.mat),
          DV.train = data$outcome),
    type = "binary", 
    nBits = ncol(covar.mat),
    names = colnames(covar.mat), 
    seed = 42,
    run=5)

  allVarNames <- colnames(covar.mat)
  sel.variables <- allVarNames[ga.solution@solution[1,]==1]
  proxy_ga <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_ga, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_ga <- weightit(ps.formula, 
                       data = data, 
                       estimand = "ATE",
                       method = "ps")

  data$ps.l <- W.out_ga$ps
  data$w.l <- W.out_ga$weights

  fit.OR_ga <- glm(out.formula,
                      data = data,
                      weights = W.out_ga$weights,
                      family= binomial(link = "logit"))
  fit.RD_ga <- glm(out.formula,
                       data = data,
                       weights = W.out_ga$weights,
                       family = gaussian(link= "identity"))
  sum.RD_ga <- c(summary(fit.RD_ga)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_ga)[2,2]))

  RD_ga[i+2*a,] <- sum.RD_ga
  rownames(RD_ga)[i+2*a] <- paste0("OR.data.", i, "_ga")

  proxy_ga.i <- paste0("proxy_ga.OR.", i)
  assign(proxy_ga.i, proxy_ga)
  sum.RD_ga.i <- paste0("sum.RD_ga.OR.", i)
  assign(sum.RD_ga.i, sum.RD_ga)
}
```

```{r}
RD_ga
```

```{r check intermediate results for each data by ga, warning=FALSE, cache=TRUE}
# check RD & SE by ga for each data, print:
#   sum.RD_ga.n, sum.RD_ga.ER.n, or sum.RD_ga.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_ga.1
sum.RD_ga.ER.2

# check proxy selected by ga for each data, print:
#   proxy_ga.n, proxy_ga.ER.n, or proxy_ga.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_ga.1
proxy_ga.ER.3
```

### 2024-08-01 sim_7.xgboost/simResults_xgboost.Rmd
sim results by lasso (changed # of datasets loading), xgboost

--- 2024-08-01 sim_4.enet/simResults_enet.Rmd
@@
 ---
-title: "simResults_enet"
+title: "simResults_xgboost"
 author: "Yang Lei"
@@
 
-RD_enet <- data.frame(RD = numeric(),
-                       SE = numeric())
+RD_xgboost <- data.frame(RD = numeric(), SE = numeric())
 ```
 
-```{r scenario: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
+```{r scenario: for-loop generating RD & SE results for xgboost, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
-                                 x = covar.mat, 
-                                 type.measure='mse',
-                                 family="binomial",
-                                 alpha = 0.5, 
-                                 nfolds = 5)
-  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
-  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
-  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
-  proxyform <- paste0(proxy_enet, collapse = "+")
+  xgb.fit <- xgboost(data = covar.mat, label = data$outcome, 
+                     max.depth = 20, eta = 1, nthread = 2, nrounds = 5, 
+                     objective = "binary:logistic")
+  xgb.imp <- xgb.importance(model = xgb.fit)
+  sel.variables <- xgb.imp$Feature
+  proxy_xgboost <- proxy.list[proxy.list %in% sel.variables]
+  proxyform <- paste0(proxy_xgboost, collapse = "+")
   rhsform <- paste0(c(covform, proxyform), collapse = "+")
@@
 
-  W.out_enet <- weightit(ps.formula, 
+  W.out_xgboost <- weightit(ps.formula, 
                           data = data, 
@@
   #
-  data$ps.l <- W.out_enet$ps
-  data$w.l <- W.out_enet$weights
+  data$ps.l <- W.out_xgboost$ps
+  data$w.l <- W.out_xgboost$weights
 
-  fit.OR_enet <- glm(out.formula,
+  fit.OR_xgboost <- glm(out.formula,
                       data = data,
-                      weights = W.out_enet$weights,
+                      weights = W.out_xgboost$weights,
                       family= binomial(link = "logit"))
-  fit.RD_enet <- glm(out.formula,
+  fit.RD_xgboost <- glm(out.formula,
                        data = data,
-                       weights = W.out_enet$weights,
+                       weights = W.out_xgboost$weights,
                        family = gaussian(link= "identity"))
-  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))
+  sum.RD_xgboost <- c(summary(fit.RD_xgboost)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_xgboost)[2,2]))
 
-  RD_enet[i,] <- sum.RD_enet
-  rownames(RD_enet)[i] <- paste0("data.", i, "_enet")
+  RD_xgboost[i,] <- sum.RD_xgboost
+  rownames(RD_xgboost)[i] <- paste0("data.", i, "_xgboost")
 
-  proxy_enet.i <- paste0("proxy_enet.", i)
-  assign(proxy_enet.i, proxy_enet)
-  sum.RD_enet.i <- paste0("sum.RD_enet.", i)
-  assign(sum.RD_enet.i, sum.RD_enet)
+  proxy_xgboost.i <- paste0("proxy_xgboost.", i)
+  assign(proxy_xgboost.i, proxy_xgboost)
+  sum.RD_xgboost.i <- paste0("sum.RD_xgboost.", i)
+  assign(sum.RD_xgboost.i, sum.RD_xgboost)
 }
 ```
-```{r scenarioER: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
+
+```{r scenarioER: for-loop generating RD & SE results for xgboost, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
 
-  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
-                                 x = covar.mat, 
-                                 type.measure='mse',
-                                 family="binomial",
-                                 alpha = 1, 
-                                 nfolds = 5)
-  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
-  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
-  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
-  proxyform <- paste0(proxy_enet, collapse = "+")
+  xgb.fit <- xgboost(data = covar.mat, label = data$outcome, 
+                     max.depth = 20, eta = 1, nthread = 2, nrounds = 5, 
+                     objective = "binary:logistic")
+  xgb.imp <- xgb.importance(model = xgb.fit)
+  sel.variables <- xgb.imp$Feature
+  proxy_xgboost <- proxy.list[proxy.list %in% sel.variables]
+  proxyform <- paste0(proxy_xgboost, collapse = "+")
   rhsform <- paste0(c(covform, proxyform), collapse = "+")
@@
   #
-  data$ps.l <- W.out_enet$ps
-  data$w.l <- W.out_enet$weights
+  data$ps.l <- W.out_xgboost$ps
+  data$w.l <- W.out_xgboost$weights
 
-  fit.OR_enet <- glm(out.formula,
+  fit.OR_xgboost <- glm(out.formula,
                       data = data,
-                      weights = W.out_enet$weights,
+                      weights = W.out_xgboost$weights,
                       family= binomial(link = "logit"))
-  fit.RD_enet <- glm(out.formula,
+  fit.RD_xgboost <- glm(out.formula,
                        data = data,
-                       weights = W.out_enet$weights,
+                       weights = W.out_xgboost$weights,
                        family = gaussian(link= "identity"))
-  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))
+  sum.RD_xgboost <- c(summary(fit.RD_xgboost)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_xgboost)[2,2]))
 
-  RD_enet[i+a,] <- sum.RD_enet
-  rownames(RD_enet)[i+a] <- paste0("ER.data.", i, "_enet")
+  RD_xgboost[i+a,] <- sum.RD_xgboost
+  rownames(RD_xgboost)[i+a] <- paste0("ER.data.", i, "_xgboost")
 
-  proxy_enet.i <- paste0("proxy_enet.ER.", i)
-  assign(proxy_enet.i, proxy_enet)
-  sum.RD_enet.i <- paste0("sum.RD_enet.ER.", i)
-  assign(sum.RD_enet.i, sum.RD_enet)
+  proxy_xgboost.i <- paste0("proxy_xgboost.ER.", i)
+  assign(proxy_xgboost.i, proxy_xgboost)
+  sum.RD_xgboost.i <- paste0("sum.RD_xgboost.ER.", i)
+  assign(sum.RD_xgboost.i, sum.RD_xgboost)
 }
@@
 
-```{r scenarioOR: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
+```{r scenarioOR: for-loop generating RD & SE results for xgboost, warning=FALSE, cache=TRUE}
 set.seed(42)
@@
   #
-  data$ps.l <- W.out_enet$ps
-  data$w.l <- W.out_enet$weights
+  data$ps.l <- W.out_xgboost$ps
+  data$w.l <- W.out_xgboost$weights
 
-  fit.OR_enet <- glm(out.formula,
+  fit.OR_xgboost <- glm(out.formula,
                       data = data,
-                      weights = W.out_enet$weights,
+                      weights = W.out_xgboost$weights,
                       family= binomial(link = "logit"))
-  fit.RD_enet <- glm(out.formula,
+  fit.RD_xgboost <- glm(out.formula,
                        data = data,
-                       weights = W.out_enet$weights,
+                       weights = W.out_xgboost$weights,
                        family = gaussian(link= "identity"))
-  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))
+  sum.RD_xgboost <- c(summary(fit.RD_xgboost)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_xgboost)[2,2]))
 
-  RD_enet[i+2*a,] <- sum.RD_enet
-  rownames(RD_enet)[i+2*a] <- paste0("OR.data.", i, "_enet")
+  RD_xgboost[i+2*a,] <- sum.RD_xgboost
+  rownames(RD_xgboost)[i+2*a] <- paste0("OR.data.", i, "_xgboost")
 
-  proxy_enet.i <- paste0("proxy_enet.OR.", i)
-  assign(proxy_enet.i, proxy_enet)
-  sum.RD_enet.i <- paste0("sum.RD_enet.OR.", i)
-  assign(sum.RD_enet.i, sum.RD_enet)
+  proxy_xgboost.i <- paste0("proxy_xgboost.OR.", i)
+  assign(proxy_xgboost.i, proxy_xgboost)
+  sum.RD_xgboost.i <- paste0("sum.RD_xgboost.OR.", i)
+  assign(sum.RD_xgboost.i, sum.RD_xgboost)
 }
@@
 
-```{r read RD & SE results by enet, warning=FALSE, cache=TRUE}
-RD_enet
+```{r read RD & SE results by xgboost, warning=FALSE, cache=TRUE}
+RD_xgboost
 ```
+
+```{r check intermediate results for each data by xgboost, warning=FALSE, cache=TRUE}
+# check RD & SE by xgboost for each data, print:
+#   sum.RD_xgboost.n, sum.RD_xgboost.ER.n, or sum.RD_xgboost.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+sum.RD_xgboost.1
+sum.RD_xgboost.ER.2
+
+# check proxy selected by xgboost for each data, print:
+#   proxy_xgboost.n, proxy_xgboost.ER.n, or proxy_xgboost.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+proxy_xgboost.1
+proxy_xgboost.ER.3
+```

### 2024-08-01 sim_8.rf/simResults_rf.Rmd
sim results rf

---
title: "simResults_rf"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
require(lmtest)
```

```{r load basic information, warning=FALSE, cache=TRUE}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
covform <- paste0(investigator.specified.covariates, collapse = "+")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))

url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_1.rds")
data <- readRDS(url(url))
proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )
```

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_rf <- data.frame(RD = numeric(), SE = numeric())
```

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1

RD_rf <- data.frame(RD = numeric(),
                       SE = numeric())
```

```{r scenario: for-loop generating RD & SE results for rf, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenario"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$id <- data$idx

  rf.fit <- randomForest(outcome ~ ., data = data, importance = TRUE)
  # Get important features
  rf.imp <- importance(rf.fit)
  ranked.variables <- rownames(rf.imp)[order(rf.imp[, 1], decreasing = TRUE)]
  proxy_rf <- ranked.variables[ranked.variables %in% proxy.list][1:100]
  proxyform <- paste0(proxy_rf, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_rf <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_rf$ps
  data$w.l <- W.out_rf$weights

  fit.OR_rf <- glm(out.formula,
                      data = data,
                      weights = W.out_rf$weights,
                      family= binomial(link = "logit"))
  fit.RD_rf <- glm(out.formula,
                       data = data,
                       weights = W.out_rf$weights,
                       family = gaussian(link= "identity"))
  sum.RD_rf <- c(summary(fit.RD_rf)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_rf)[2,2]))

  RD_rf[i,] <- sum.RD_rf
  rownames(RD_rf)[i] <- paste0("data.", i, "_rf")

  proxy_rf.i <- paste0("proxy_rf.", i)
  assign(proxy_rf.i, proxy_rf)
  sum.RD_rf.i <- paste0("sum.RD_rf.", i)
  assign(sum.RD_rf.i, sum.RD_rf)
}
```

```{r scenarioER: for-loop generating RD & SE results for rf, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioER"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$id <- data$idx

  rf.fit <- randomForest(outcome ~ ., data = data, importance = TRUE)
  # Get important features
  rf.imp <- importance(rf.fit)
  ranked.variables <- rownames(rf.imp)[order(rf.imp[, 1], decreasing = TRUE)]
  proxy_rf <- ranked.variables[ranked.variables %in% proxy.list][1:100]
  proxyform <- paste0(proxy_rf, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_rf <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_rf$ps
  data$w.l <- W.out_rf$weights

  fit.OR_rf <- glm(out.formula,
                      data = data,
                      weights = W.out_rf$weights,
                      family= binomial(link = "logit"))
  fit.RD_rf <- glm(out.formula,
                       data = data,
                       weights = W.out_rf$weights,
                       family = gaussian(link= "identity"))
  sum.RD_rf <- c(summary(fit.RD_rf)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_rf)[2,2]))

  RD_rf[i+a,] <- sum.RD_rf
  rownames(RD_rf)[i+a] <- paste0("ER.data.", i, "_rf")

  proxy_rf.i <- paste0("proxy_rf.ER.", i)
  assign(proxy_rf.i, proxy_rf)
  sum.RD_rf.i <- paste0("sum.RD_rf.ER.", i)
  assign(sum.RD_rf.i, sum.RD_rf)
}
```

```{r scenarioOR: for-loop generating RD & SE results for rf, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioOR"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$id <- data$idx

  rf.fit <- randomForest(outcome ~ ., data = data, importance = TRUE)
  # Get important features
  rf.imp <- importance(rf.fit)
  ranked.variables <- rownames(rf.imp)[order(rf.imp[, 1], decreasing = TRUE)]
  proxy_rf <- ranked.variables[ranked.variables %in% proxy.list][1:100]
  proxyform <- paste0(proxy_rf, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_rf <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_rf$ps
  data$w.l <- W.out_rf$weights

  fit.OR_rf <- glm(out.formula,
                      data = data,
                      weights = W.out_rf$weights,
                      family= binomial(link = "logit"))
  fit.RD_rf <- glm(out.formula,
                       data = data,
                       weights = W.out_rf$weights,
                       family = gaussian(link= "identity"))
  sum.RD_rf <- c(summary(fit.RD_rf)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_rf)[2,2]))

  RD_rf[i+2*a,] <- sum.RD_rf
  rownames(RD_rf)[i+2*a] <- paste0("OR.data.", i, "_rf")

  proxy_rf.i <- paste0("proxy_rf.OR.", i)
  assign(proxy_rf.i, proxy_rf)
  sum.RD_rf.i <- paste0("sum.RD_rf.OR.", i)
  assign(sum.RD_rf.i, sum.RD_rf)
}
```

```{r read RD & SE results by rf, warning=FALSE, cache=TRUE}
RD_rf
```

```{r check intermediate results for each data by rf, warning=FALSE, cache=TRUE}
# check RD & SE by rf for each data, print:
#   sum.RD_rf.n, sum.RD_rf.ER.n, or sum.RD_rf.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_rf.1
sum.RD_rf.ER.2

# check proxy selected by rf for each data, print:
#   proxy_rf.n, proxy_rf.ER.n, or proxy_rf.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_rf.1
proxy_rf.ER.3
```

### 2024-08-08 sim_10.1_forward/simResults_forward.Rmd
simulation results .RMD file added & edited

---
title: "simResults_forward"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
require(lmtest)
```

```{r load basic information, warning=FALSE, cache=TRUE}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
covform <- paste0(investigator.specified.covariates, collapse = "+")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))

url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_1.rds")
data <- readRDS(url(url))
proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~exposure", 
                              covarsTfull), collapse = "+") )

initial.formula <- as.formula(paste0("outcome~exposure+",
                                     covform,
                                     collapse = "+"))
full.formula <- as.formula(paste0("outcome~exposure+",
                                  paste0(covarsTfull, collapse = "+"),
                                  collapse = "+"))
```

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_forward <- data.frame(RD = numeric(), SE = numeric())

num.proxy_forward <- c()
```

```{r scenario: for-loop generating RD & SE results for forward, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenario"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  initial.model <- glm(initial.formula, data = data, family = binomial)
  full.model <- glm(full.formula, data = data, family = binomial)
  stepwise_forward <- stepAIC(initial.model, 
                              scope = list(lower = initial.model, 
                                           upper = full.model), 
                              direction = "forward")

  sel.variables <- all.vars(formula(stepwise_forward))[-1]
  proxy_forward <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_forward, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_forward <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_forward$ps
  data$w.l <- W.out_forward$weights

  fit.OR_forward <- glm(out.formula,
                      data = data,
                      weights = W.out_forward$weights,
                      family= binomial(link = "logit"))
  fit.RD_forward <- glm(out.formula,
                       data = data,
                       weights = W.out_forward$weights,
                       family = gaussian(link= "identity"))
  sum.RD_forward <- c(summary(fit.RD_forward)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_forward)[2,2]))

  RD_forward[i,] <- sum.RD_forward
  rownames(RD_forward)[i] <- paste0("data.", i, "_forward")
  num.proxy_forward <- c(num.proxy_forward, length(proxy_forward))
  names(num.proxy_forward)[i] <- paste0("data.", i, "_forward")

  proxy_forward.i <- paste0("proxy_forward.", i)
  assign(proxy_forward.i, proxy_forward)
  num.proxy_forward.i <- paste0("num.proxy_forward.", i)
  assign(num.proxy_forward.i, length(proxy_forward))
  sum.RD_forward.i <- paste0("sum.RD_forward.", i)
  assign(sum.RD_forward.i, sum.RD_forward)
}
```

```{r scenarioER: for-loop generating RD & SE results for forward, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioER"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  initial.model <- glm(initial.formula, data = data, family = binomial)
  full.model <- glm(full.formula, data = data, family = binomial)
  stepwise_forward <- stepAIC(initial.model, 
                              scope = list(lower = initial.model, 
                                           upper = full.model), 
                              direction = "forward")

  sel.variables <- all.vars(formula(stepwise_forward))[-1]
  proxy_forward <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_forward, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_forward <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_forward$ps
  data$w.l <- W.out_forward$weights

  fit.OR_forward <- glm(out.formula,
                      data = data,
                      weights = W.out_forward$weights,
                      family= binomial(link = "logit"))
  fit.RD_forward <- glm(out.formula,
                       data = data,
                       weights = W.out_forward$weights,
                       family = gaussian(link= "identity"))
  sum.RD_forward <- c(summary(fit.RD_forward)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_forward)[2,2]))

  RD_forward[i+a,] <- sum.RD_forward
  rownames(RD_forward)[i+a] <- paste0("ER.data.", i, "_forward")
  num.proxy_forward <- c(num.proxy_forward, length(proxy_forward))
  names(num.proxy_forward)[i+a] <- paste0("ER.data.", i, "_forward")

  proxy_forward.i <- paste0("proxy_forward.ER.", i)
  assign(proxy_forward.i, proxy_forward)
  num.proxy_forward.i <- paste0("num.proxy_forward.ER.", i)
  assign(num.proxy_forward.i, length(proxy_forward))
  sum.RD_forward.i <- paste0("sum.RD_forward.ER.", i)
  assign(sum.RD_forward.i, sum.RD_forward)
}
```

```{r scenarioOR: for-loop generating RD & SE results for forward, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioOR"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  initial.model <- glm(initial.formula, data = data, family = binomial)
  full.model <- glm(full.formula, data = data, family = binomial)
  stepwise_forward <- stepAIC(initial.model, 
                              scope = list(lower = initial.model, 
                                           upper = full.model), 
                              direction = "forward")

  sel.variables <- all.vars(formula(stepwise_forward))[-1]
  proxy_forward <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_forward, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_forward <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_forward$ps
  data$w.l <- W.out_forward$weights

  fit.OR_forward <- glm(out.formula,
                      data = data,
                      weights = W.out_forward$weights,
                      family= binomial(link = "logit"))
  fit.RD_forward <- glm(out.formula,
                       data = data,
                       weights = W.out_forward$weights,
                       family = gaussian(link= "identity"))
  sum.RD_forward <- c(summary(fit.RD_forward)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_forward)[2,2]))

  RD_forward[i+2*a,] <- sum.RD_forward
  rownames(RD_forward)[i+2*a] <- paste0("OR.data.", i, "_forward")
  num.proxy_forward <- c(num.proxy_forward, length(proxy_forward))
  names(num.proxy_forward)[i+2*a] <- paste0("OR.data.", i, "_forward")

  proxy_forward.i <- paste0("proxy_forward.OR.", i)
  assign(proxy_forward.i, proxy_forward)
  num.proxy_forward.i <- paste0("num.proxy_forward.OR.", i)
  assign(num.proxy_forward.i, length(proxy_forward))
  sum.RD_forward.i <- paste0("sum.RD_forward.OR.", i)
  assign(sum.RD_forward.i, sum.RD_forward)
}
```

```{r read RD & SE results by forward, warning=FALSE, cache=TRUE}
RD_forward
```

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_forward
mean(num.proxy_forward[complete.cases(num.proxy_forward)])
```

```{r check intermediate results for each data by forward, warning=FALSE, cache=TRUE}
# check RD & SE by forward for each data, print:
#   sum.RD_forward.n, sum.RD_forward.ER.n, or sum.RD_forward.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_forward.1
sum.RD_forward.ER.2

# check proxy selected by forward for each data, print:
#   proxy_forward.n, proxy_forward.ER.n, or proxy_forward.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_forward.1
proxy_forward.ER.3

# check number of proxy selected by forward for each data, print:
#   num.proxy_forward.n, num.proxy_forward.ER.n, or num.proxy_forward.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_forward.1
num.proxy_forward.OR.3
```

### 2024-08-08 sim_10.2_backward/simResults_backward.Rmd
simulation results .RMD file added & edited

---
title: "simResults_backward"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
require(lmtest)
```

```{r load basic information, warning=FALSE, cache=TRUE}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
covform <- paste0(investigator.specified.covariates, collapse = "+")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))

url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_1.rds")
data <- readRDS(url(url))
proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~exposure", 
                              covarsTfull), collapse = "+") )

initial.formula <- as.formula(paste0("outcome~exposure+",
                                     covform,
                                     collapse = "+"))
full.formula <- as.formula(paste0("outcome~exposure+",
                                  paste0(covarsTfull, collapse = "+"),
                                  collapse = "+"))
```

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_backward <- data.frame(RD = numeric(), SE = numeric())

num.proxy_backward <- c()
```

```{r scenario: for-loop generating RD & SE results for backward, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenario"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  initial.model <- glm(initial.formula, data = data, family = binomial)
  full.model <- glm(full.formula, data = data, family = binomial)
  stepwise_backward <- stepAIC(full.model, 
                              scope = list(lower = initial.model, 
                                           upper = full.model), 
                              direction = "backward")

  sel.variables <- all.vars(formula(stepwise_backward))[-1]
  proxy_backward <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_backward, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_backward <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_backward$ps
  data$w.l <- W.out_backward$weights

  fit.OR_backward <- glm(out.formula,
                      data = data,
                      weights = W.out_backward$weights,
                      family= binomial(link = "logit"))
  fit.RD_backward <- glm(out.formula,
                       data = data,
                       weights = W.out_backward$weights,
                       family = gaussian(link= "identity"))
  sum.RD_backward <- c(summary(fit.RD_backward)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_backward)[2,2]))

  RD_backward[i,] <- sum.RD_backward
  rownames(RD_backward)[i] <- paste0("data.", i, "_backward")
  num.proxy_backward <- c(num.proxy_backward, length(proxy_backward))
  names(num.proxy_backward)[i] <- paste0("data.", i, "_backward")

  proxy_backward.i <- paste0("proxy_backward.", i)
  assign(proxy_backward.i, proxy_backward)
  num.proxy_backward.i <- paste0("num.proxy_backward.", i)
  assign(num.proxy_backward.i, length(proxy_backward))
  sum.RD_backward.i <- paste0("sum.RD_backward.", i)
  assign(sum.RD_backward.i, sum.RD_backward)
}
```

```{r scenarioER: for-loop generating RD & SE results for backward, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioER"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  initial.model <- glm(initial.formula, data = data, family = binomial)
  full.model <- glm(full.formula, data = data, family = binomial)
  stepwise_backward <- stepAIC(full.formula, 
                              scope = list(lower = initial.model, 
                                           upper = full.model), 
                              direction = "backward")

  sel.variables <- all.vars(formula(stepwise_backward))[-1]
  proxy_backward <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_backward, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_backward <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_backward$ps
  data$w.l <- W.out_backward$weights

  fit.OR_backward <- glm(out.formula,
                      data = data,
                      weights = W.out_backward$weights,
                      family= binomial(link = "logit"))
  fit.RD_backward <- glm(out.formula,
                       data = data,
                       weights = W.out_backward$weights,
                       family = gaussian(link= "identity"))
  sum.RD_backward <- c(summary(fit.RD_backward)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_backward)[2,2]))

  RD_backward[i+a,] <- sum.RD_backward
  rownames(RD_backward)[i+a] <- paste0("ER.data.", i, "_backward")
  num.proxy_backward <- c(num.proxy_backward, length(proxy_backward))
  names(num.proxy_backward)[i+a] <- paste0("ER.data.", i, "_backward")

  proxy_backward.i <- paste0("proxy_backward.ER.", i)
  assign(proxy_backward.i, proxy_backward)
  num.proxy_backward.i <- paste0("num.proxy_backward.ER.", i)
  assign(num.proxy_backward.i, length(proxy_backward))
  sum.RD_backward.i <- paste0("sum.RD_backward.ER.", i)
  assign(sum.RD_backward.i, sum.RD_backward)
}
```

```{r scenarioOR: for-loop generating RD & SE results for backward, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioOR"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  initial.model <- glm(initial.formula, data = data, family = binomial)
  full.model <- glm(full.formula, data = data, family = binomial)
  stepwise_backward <- stepAIC(full.formula, 
                              scope = list(lower = initial.model, 
                                           upper = full.model), 
                              direction = "backward")

  sel.variables <- all.vars(formula(stepwise_backward))[-1]
  proxy_backward <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_backward, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_backward <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_backward$ps
  data$w.l <- W.out_backward$weights

  fit.OR_backward <- glm(out.formula,
                      data = data,
                      weights = W.out_backward$weights,
                      family= binomial(link = "logit"))
  fit.RD_backward <- glm(out.formula,
                       data = data,
                       weights = W.out_backward$weights,
                       family = gaussian(link= "identity"))
  sum.RD_backward <- c(summary(fit.RD_backward)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_backward)[2,2]))

  RD_backward[i+2*a,] <- sum.RD_backward
  rownames(RD_backward)[i+2*a] <- paste0("OR.data.", i, "_backward")
  num.proxy_backward <- c(num.proxy_backward, length(proxy_backward))
  names(num.proxy_backward)[i+2*a] <- paste0("OR.data.", i, "_backward")

  proxy_backward.i <- paste0("proxy_backward.OR.", i)
  assign(proxy_backward.i, proxy_backward)
  num.proxy_backward.i <- paste0("num.proxy_backward.OR.", i)
  assign(num.proxy_backward.i, length(proxy_backward))
  sum.RD_backward.i <- paste0("sum.RD_backward.OR.", i)
  assign(sum.RD_backward.i, sum.RD_backward)
}
```

```{r read RD & SE results by backward, warning=FALSE, cache=TRUE}
RD_backward
```

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_backward
mean(num.proxy_backward[complete.cases(num.proxy_backward)])
```

```{r check intermediate results for each data by backward, warning=FALSE, cache=TRUE}
# check RD & SE by backward for each data, print:
#   sum.RD_backward.n, sum.RD_backward.ER.n, or sum.RD_backward.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_backward.1
sum.RD_backward.ER.2

# check proxy selected by backward for each data, print:
#   proxy_backward.n, proxy_backward.ER.n, or proxy_backward.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_backward.1
proxy_backward.ER.3

# check number of proxy selected by backward for each data, print:
#   num.proxy_backward.n, num.proxy_backward.ER.n, or num.proxy_backward.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_backward.1
num.proxy_backward.OR.3
```

### 2024-08-08 sim_10.3_both/simResults_both.Rmd
simulation results .RMD file added & edited

---
title: "simResults_both"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
require(lmtest)
```

```{r load basic information, warning=FALSE, cache=TRUE}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
covform <- paste0(investigator.specified.covariates, collapse = "+")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))

url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_1.rds")
data <- readRDS(url(url))
proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~exposure", 
                              covarsTfull), collapse = "+") )

initial.formula <- as.formula(paste0("outcome~exposure+",
                                     covform,
                                     collapse = "+"))
full.formula <- as.formula(paste0("outcome~exposure+",
                                  paste0(covarsTfull, collapse = "+"),
                                  collapse = "+"))
```

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_both <- data.frame(RD = numeric(), SE = numeric())

num.proxy_both <- c()
```

```{r scenario: for-loop generating RD & SE results for both, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenario"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  initial.model <- glm(initial.formula, data = data, family = binomial)
  full.model <- glm(full.formula, data = data, family = binomial)
  stepwise_both <- stepAIC(initial.model, 
                              scope = list(lower = initial.model, 
                                           upper = full.model), 
                              direction = "both")

  sel.variables <- all.vars(formula(stepwise_both))[-1]
  proxy_both <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_both, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_both <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_both$ps
  data$w.l <- W.out_both$weights

  fit.OR_both <- glm(out.formula,
                      data = data,
                      weights = W.out_both$weights,
                      family= binomial(link = "logit"))
  fit.RD_both <- glm(out.formula,
                       data = data,
                       weights = W.out_both$weights,
                       family = gaussian(link= "identity"))
  sum.RD_both <- c(summary(fit.RD_both)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_both)[2,2]))

  RD_both[i,] <- sum.RD_both
  rownames(RD_both)[i] <- paste0("data.", i, "_both")
  num.proxy_both <- c(num.proxy_both, length(proxy_both))
  names(num.proxy_both)[i] <- paste0("data.", i, "_both")

  proxy_both.i <- paste0("proxy_both.", i)
  assign(proxy_both.i, proxy_both)
  num.proxy_both.i <- paste0("num.proxy_both.", i)
  assign(num.proxy_both.i, length(proxy_both))
  sum.RD_both.i <- paste0("sum.RD_both.", i)
  assign(sum.RD_both.i, sum.RD_both)
}
```

```{r scenarioER: for-loop generating RD & SE results for both, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioER"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  initial.model <- glm(initial.formula, data = data, family = binomial)
  full.model <- glm(full.formula, data = data, family = binomial)
  stepwise_both <- stepAIC(initial.model, 
                              scope = list(lower = initial.model, 
                                           upper = full.model), 
                              direction = "both")

  sel.variables <- all.vars(formula(stepwise_both))[-1]
  proxy_both <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_both, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_both <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_both$ps
  data$w.l <- W.out_both$weights

  fit.OR_both <- glm(out.formula,
                      data = data,
                      weights = W.out_both$weights,
                      family= binomial(link = "logit"))
  fit.RD_both <- glm(out.formula,
                       data = data,
                       weights = W.out_both$weights,
                       family = gaussian(link= "identity"))
  sum.RD_both <- c(summary(fit.RD_both)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_both)[2,2]))

  RD_both[i+a,] <- sum.RD_both
  rownames(RD_both)[i+a] <- paste0("ER.data.", i, "_both")
  num.proxy_both <- c(num.proxy_both, length(proxy_both))
  names(num.proxy_both)[i+a] <- paste0("ER.data.", i, "_both")

  proxy_both.i <- paste0("proxy_both.ER.", i)
  assign(proxy_both.i, proxy_both)
  num.proxy_both.i <- paste0("num.proxy_both.ER.", i)
  assign(num.proxy_both.i, length(proxy_both))
  sum.RD_both.i <- paste0("sum.RD_both.ER.", i)
  assign(sum.RD_both.i, sum.RD_both)
}
```

```{r scenarioOR: for-loop generating RD & SE results for both, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioOR"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  initial.model <- glm(initial.formula, data = data, family = binomial)
  full.model <- glm(full.formula, data = data, family = binomial)
  stepwise_both <- stepAIC(initial.model, 
                              scope = list(lower = initial.model, 
                                           upper = full.model), 
                              direction = "both")

  sel.variables <- all.vars(formula(stepwise_both))[-1]
  proxy_both <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_both, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_both <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_both$ps
  data$w.l <- W.out_both$weights

  fit.OR_both <- glm(out.formula,
                      data = data,
                      weights = W.out_both$weights,
                      family= binomial(link = "logit"))
  fit.RD_both <- glm(out.formula,
                       data = data,
                       weights = W.out_both$weights,
                       family = gaussian(link= "identity"))
  sum.RD_both <- c(summary(fit.RD_both)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_both)[2,2]))

  RD_both[i+2*a,] <- sum.RD_both
  rownames(RD_both)[i+2*a] <- paste0("OR.data.", i, "_both")
  num.proxy_both <- c(num.proxy_both, length(proxy_both))
  names(num.proxy_both)[i+2*a] <- paste0("OR.data.", i, "_both")

  proxy_both.i <- paste0("proxy_both.OR.", i)
  assign(proxy_both.i, proxy_both)
  num.proxy_both.i <- paste0("num.proxy_both.OR.", i)
  assign(num.proxy_both.i, length(proxy_both))
  sum.RD_both.i <- paste0("sum.RD_both.OR.", i)
  assign(sum.RD_both.i, sum.RD_both)
}
```

```{r read RD & SE results by both, warning=FALSE, cache=TRUE}
RD_both
```

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_both
mean(num.proxy_both[complete.cases(num.proxy_both)])
```

```{r check intermediate results for each data by both, warning=FALSE, cache=TRUE}
# check RD & SE by both for each data, print:
#   sum.RD_both.n, sum.RD_both.ER.n, or sum.RD_both.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_both.1
sum.RD_both.ER.2

# check proxy selected by both for each data, print:
#   proxy_both.n, proxy_both.ER.n, or proxy_both.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_both.1
proxy_both.ER.3

# check number of proxy selected by both for each data, print:
#   num.proxy_both.n, num.proxy_both.ER.n, or num.proxy_both.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_both.1
num.proxy_both.OR.3
```

### 2024-08-08 sim_1_bross/simResults_bross.Rmd
simulation results .RMD file added & edited

--- 2024-08-01 sim_1.bross/simResults_bross.Rmd
@@
 title: "SimResults_Bross"
-author: "Yang Lei"
-date: "2024-07-31"
 output: html_document
@@
 for (i in 1:a) {
+  closeAllConnections()
   url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
@@
                 ".rds")
-  data <- tryCatch({
-    readRDS(url(url))
-  }, error = function(e) {
-    closeAllConnections()
-    readRDS(url(url))
-  })
+  data <- readRDS(url(url))
 
   # found some id != idx
-  data$id <- data$idx
+  data$idx <- data$id
 
@@
 for (i in 1:a) {
+  closeAllConnections()
   url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
@@
 for (i in 1:a) {
+  closeAllConnections()
   url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 

### 2024-08-08 sim_2_hybrid/simResults_hybrid.Rmd
simulation results .RMD file added & edited

---
title: "SimResults_Hybrid"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
require(lmtest)
```

```{r load basic information, warning=FALSE, cache=TRUE}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
covform <- paste0(investigator.specified.covariates, collapse = "+")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_1.rds")
data <- readRDS(url(url))
proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
```

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_hybrid <- data.frame(RD = numeric(), SE = numeric())

num.proxy_hybrid <- c()

errors <- c()
```

```{r scenario: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenario"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  # Feature Selection Method 1: Bross Formula
  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]

  hybrid.list <- tryCatch({
    get_prioritised_covariates(df = proxy.df,
                               patientIdVarname = "idx", 
                               exposureVector = data$exposure,
                               outcomeVector = data$outcome,
                               patientIdVector = data$idx, 
                               k = 100)
  }, error = function(e) {
    errors <<- c(errors, i)
    "ERROR"
  })

  if (class(hybrid.list) == "character") {
    proxy_hybrid <- c(NA)
    sum.RD_hybrid <- c(NA, NA)

    RD_hybrid[i,] <- sum.RD_hybrid
    rownames(RD_hybrid)[i] <- paste0("data.", i, "_hybrid")
    num.proxy_hybrid <- c(num.proxy_hybrid, NA)
    names(num.proxy_hybrid)[i] <- paste0("data.", i, "_hybrid")

    proxy_hybrid.i <- paste0("proxy_hybrid.", i)
    assign(proxy_hybrid.i, proxy_hybrid)
    num.proxy_hybrid.i <- paste0("num.proxy_hybrid.", i)
    assign(num.proxy_hybrid.i, NA)
    sum.RD_hybrid.i <- paste0("sum.RD_hybrid.", i)
    assign(sum.RD_hybrid.i, sum.RD_hybrid)
  } else {
    proxy.df_hybrid <- hybrid.list$autoselected_covariate_df
    hdps.data_hybrid <- merge(data[,c("idx",
                                     outcome, 
                                     exposure, 
                                     investigator.specified.covariates)],
                             proxy.df_hybrid,
                             by = "idx")
    hdps.data_hybrid$id <- hdps.data_hybrid$idx
    hdps.data_hybrid$idx <- NULL

    hdps.data_hybrid$exposure <- as.numeric(I(hdps.data_hybrid$obese=='Yes'))
    hdps.data_hybrid$outcome <- as.numeric(I(hdps.data_hybrid$diabetes=='Yes'))

    proxy_hybrid <- names(proxy.df_hybrid[,-1])
    covarsTfull <- c(investigator.specified.covariates, proxy_hybrid)
    Y.form <- as.formula(paste0(c("outcome~ exposure", covarsTfull), 
                            collapse = "+") )
    covar.mat <- model.matrix(Y.form, data = hdps.data_hybrid)[,-1]
    lasso.fit_hybrid <-glmnet::cv.glmnet(y = hdps.data_hybrid$outcome,
                                         x = covar.mat, 
                                         type.measure='mse',
                                         family="binomial",
                                         alpha = 1, 
                                         nfolds = 5)

    coef.fit <- coef(lasso.fit_hybrid,s='lambda.min',exact=TRUE)
    sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
    proxy_hybrid <- proxy.list[proxy.list %in% sel.variables]
    proxyform <- paste0(proxy_hybrid, collapse = "+")
    rhsform <- paste0(c(covform, proxyform), collapse = "+")
    ps.formula <- as.formula(paste0("exposure", "~", rhsform))

    W.out_hybrid <- weightit(ps.formula,
                            data = hdps.data_hybrid, 
                            estimand = "ATE",
                            method = "ps")
    fit.OR_hybrid <- glm(out.formula,
                        data = hdps.data_hybrid,
                        weights = W.out_hybrid$weights,
                        family= binomial(link = "logit"))
    fit.RD_hybrid <- glm(out.formula,
                        data= hdps.data_hybrid,
                        weights= W.out_hybrid$weights,
                        family=gaussian(link= "identity"))
    sum.RD_hybrid <- c(summary(fit.RD_hybrid)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_hybrid)[2,2]))

    RD_hybrid[i,] <- sum.RD_hybrid
    rownames(RD_hybrid)[i] <- paste0("data.", i, "_hybrid")
    num.proxy_hybrid <- c(num.proxy_hybrid, length(proxy_hybrid))
    names(num.proxy_hybrid)[i] <- paste0("data.", i, "_hybrid")

    proxy_hybrid.i <- paste0("proxy_hybrid.", i)
    assign(proxy_hybrid.i, proxy_hybrid)
    num.proxy_hybrid.i <- paste0("num.proxy_hybrid.", i)
    assign(num.proxy_hybrid.i, length(proxy_hybrid))
    sum.RD_hybrid.i <- paste0("sum.RD_hybrid.", i)
    assign(sum.RD_hybrid.i, sum.RD_hybrid)
  }
}
```

```{r scenarioER: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioER"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  # Feature Selection Method 1: Bross Formula
  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]

  hybrid.list <- tryCatch({
    get_prioritised_covariates(df = proxy.df,
                               patientIdVarname = "idx", 
                               exposureVector = data$exposure,
                               outcomeVector = data$outcome,
                               patientIdVector = data$idx, 
                               k = 100)
  }, error = function(e) {
    errors <<- c(errors, paste0("ER.", i))
    "ERROR"
  })

  if (class(hybrid.list) == "character") {
    proxy_hybrid <- c(NA)
    sum.RD_hybrid <- c(NA, NA)

    RD_hybrid[i+a,] <- sum.RD_hybrid
    rownames(RD_hybrid)[i+a] <- paste0("ER.data.", i, "_hybrid")
    num.proxy_hybrid <- c(num.proxy_hybrid, NA)
    names(num.proxy_hybrid)[i+a] <- paste0("ER.data.", i, "_hybrid")

    proxy_hybrid.i <- paste0("proxy_hybrid.ER.", i)
    assign(proxy_hybrid.i, proxy_hybrid)
    num.proxy_hybrid.i <- paste0("num.proxy_hybrid.ER.", i)
    assign(num.proxy_hybrid.i, NA)
    sum.RD_hybrid.i <- paste0("sum.RD_hybrid.ER.", i)
    assign(sum.RD_hybrid.i, sum.RD_hybrid)
  } else {
    proxy.df_hybrid <- hybrid.list$autoselected_covariate_df
    hdps.data_hybrid <- merge(data[,c("idx",
                                     outcome, 
                                     exposure, 
                                     investigator.specified.covariates)],
                             proxy.df_hybrid,
                             by = "idx")
    hdps.data_hybrid$id <- hdps.data_hybrid$idx
    hdps.data_hybrid$idx <- NULL

    hdps.data_hybrid$exposure <- as.numeric(I(hdps.data_hybrid$obese=='Yes'))
    hdps.data_hybrid$outcome <- as.numeric(I(hdps.data_hybrid$diabetes=='Yes'))

    proxy_hybrid <- names(proxy.df_hybrid[,-1])
    covarsTfull <- c(investigator.specified.covariates, proxy_hybrid)
    Y.form <- as.formula(paste0(c("outcome~ exposure", covarsTfull), 
                            collapse = "+") )
    covar.mat <- model.matrix(Y.form, data = hdps.data_hybrid)[,-1]
    lasso.fit_hybrid <-glmnet::cv.glmnet(y = hdps.data_hybrid$outcome,
                                         x = covar.mat, 
                                         type.measure='mse',
                                         family="binomial",
                                         alpha = 1, 
                                         nfolds = 5)

    coef.fit <- coef(lasso.fit_hybrid,s='lambda.min',exact=TRUE)
    sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
    proxy_hybrid <- proxy.list[proxy.list %in% sel.variables]
    proxyform <- paste0(proxy_hybrid, collapse = "+")
    rhsform <- paste0(c(covform, proxyform), collapse = "+")
    ps.formula <- as.formula(paste0("exposure", "~", rhsform))

    W.out_hybrid <- weightit(ps.formula,
                            data = hdps.data_hybrid, 
                            estimand = "ATE",
                            method = "ps")
    fit.OR_hybrid <- glm(out.formula,
                        data = hdps.data_hybrid,
                        weights = W.out_hybrid$weights,
                        family= binomial(link = "logit"))
    fit.RD_hybrid <- glm(out.formula,
                        data= hdps.data_hybrid,
                        weights= W.out_hybrid$weights,
                        family=gaussian(link= "identity"))
    sum.RD_hybrid <- c(summary(fit.RD_hybrid)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_hybrid)[2,2]))

    RD_hybrid[i+a,] <- sum.RD_hybrid
    rownames(RD_hybrid)[i+a] <- paste0("ER.data.", i, "_hybrid")
    num.proxy_hybrid <- c(num.proxy_hybrid, length(proxy_hybrid))
    names(num.proxy_hybrid)[i+a] <- paste0("ER.data.", i, "_hybrid")

    proxy_hybrid.i <- paste0("proxy_hybrid.ER.", i)
    assign(proxy_hybrid.i, proxy_hybrid)
    num.proxy_hybrid.i <- paste0("num.proxy_hybrid.ER.", i)
    assign(num.proxy_hybrid.i, length(proxy_hybrid))
    sum.RD_hybrid.i <- paste0("sum.RD_hybrid.ER.", i)
    assign(sum.RD_hybrid.i, sum.RD_hybrid)
  }
}
```

```{r scenarioOR: for-loop generating RD & SE results, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioOR"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  # Feature Selection Method 1: Bross Formula
  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]

  hybrid.list <- tryCatch({
    get_prioritised_covariates(df = proxy.df,
                               patientIdVarname = "idx", 
                               exposureVector = data$exposure,
                               outcomeVector = data$outcome,
                               patientIdVector = data$idx, 
                               k = 100)
  }, error = function(e) {
    errors <<- c(errors, paste0("OR.", i))
    "ERROR"
  })

  if (class(hybrid.list) == "character") {
    proxy_hybrid <- c(NA)
    sum.RD_hybrid <- c(NA, NA)

    RD_hybrid[i+2*a,] <- sum.RD_hybrid
    rownames(RD_hybrid)[i+2*a] <- paste0("OR.data.", i, "_hybrid")  
    num.proxy_hybrid <- c(num.proxy_hybrid, NA)
    names(num.proxy_hybrid)[i+2*a] <- paste0("OR.data.", i, "_hybrid")

    proxy_hybrid.i <- paste0("proxy_hybrid.OR.", i)
    assign(proxy_hybrid.i, proxy_hybrid)
    num.proxy_hybrid.i <- paste0("num.proxy_hybrid.OR.", i)
    assign(num.proxy_hybrid.i, NA)
    sum.RD_hybrid.i <- paste0("sum.RD_hybrid.OR.", i)
    assign(sum.RD_hybrid.i, sum.RD_hybrid)
  } else {
    proxy.df_hybrid <- hybrid.list$autoselected_covariate_df
    hdps.data_hybrid <- merge(data[,c("idx",
                                     outcome, 
                                     exposure, 
                                     investigator.specified.covariates)],
                             proxy.df_hybrid,
                             by = "idx")
    hdps.data_hybrid$id <- hdps.data_hybrid$idx
    hdps.data_hybrid$idx <- NULL

    hdps.data_hybrid$exposure <- as.numeric(I(hdps.data_hybrid$obese=='Yes'))
    hdps.data_hybrid$outcome <- as.numeric(I(hdps.data_hybrid$diabetes=='Yes'))

    proxy_hybrid <- names(proxy.df_hybrid[,-1])
    covarsTfull <- c(investigator.specified.covariates, proxy_hybrid)
    Y.form <- as.formula(paste0(c("outcome~ exposure", covarsTfull), 
                            collapse = "+") )
    covar.mat <- model.matrix(Y.form, data = hdps.data_hybrid)[,-1]
    lasso.fit_hybrid <-glmnet::cv.glmnet(y = hdps.data_hybrid$outcome,
                                         x = covar.mat, 
                                         type.measure='mse',
                                         family="binomial",
                                         alpha = 1, 
                                         nfolds = 5)

    coef.fit <- coef(lasso.fit_hybrid,s='lambda.min',exact=TRUE)
    sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
    proxy_hybrid <- proxy.list[proxy.list %in% sel.variables]
    proxyform <- paste0(proxy_hybrid, collapse = "+")
    rhsform <- paste0(c(covform, proxyform), collapse = "+")
    ps.formula <- as.formula(paste0("exposure", "~", rhsform))

    W.out_hybrid <- weightit(ps.formula,
                            data = hdps.data_hybrid, 
                            estimand = "ATE",
                            method = "ps")
    fit.OR_hybrid <- glm(out.formula,
                        data = hdps.data_hybrid,
                        weights = W.out_hybrid$weights,
                        family= binomial(link = "logit"))
    fit.RD_hybrid <- glm(out.formula,
                        data= hdps.data_hybrid,
                        weights= W.out_hybrid$weights,
                        family=gaussian(link= "identity"))
    sum.RD_hybrid <- c(summary(fit.RD_hybrid)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_hybrid)[2,2]))

    RD_hybrid[i+2*a,] <- sum.RD_hybrid
    rownames(RD_hybrid)[i+2*a] <- paste0("OR.data.", i, "_hybrid")
    num.proxy_hybrid <- c(num.proxy_hybrid, length(proxy_hybrid))
    names(num.proxy_hybrid)[i+2*a] <- paste0("OR.data.", i, "_hybrid")

    proxy_hybrid.i <- paste0("proxy_hybrid.OR.", i)
    assign(proxy_hybrid.i, proxy_hybrid)
    num.proxy_hybrid.i <- paste0("num.proxy_hybrid.OR.", i)
    assign(num.proxy_hybrid.i, length(proxy_hybrid))
    sum.RD_hybrid.i <- paste0("sum.RD_hybrid.OR.", i)
    assign(sum.RD_hybrid.i, sum.RD_hybrid)
  }
}
```

```{r read RD & SE results (with error rows), warning=FALSE, cache=TRUE}
RD_hybrid
```

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_hybrid
mean(num.proxy_hybrid[complete.cases(num.proxy_hybrid)])
```

```{r check index of dataset causing error, warning=FALSE, cache=TRUE}
# check index of dataset causing error
errors
```

```{r read RD & SE results (without error rows), warning=FALSE, cache=TRUE}
RD_hybrid_no.error <- RD_hybrid[complete.cases(RD_hybrid),]
RD_hybrid_no.error
```

```{r check intermediate results for each data, warning=FALSE, cache=TRUE}
# check RD & SE by hybrid for each data, print:
#   sum.RD_hybrid.n, sum.RD_hybrid.ER.n, or sum.RD_hybrid.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_hybrid.1
sum.RD_hybrid.ER.2

# check proxy selected by hybrid for each data, print:
#   proxy_hybrid.n, proxy_hybrid.ER.n, or proxy_hybrid.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_hybrid.1
proxy_hybrid.ER.5

# check number of proxy selected by hybrid for each data, print:
#   num.proxy_hybrid.n, num.proxy_hybrid.ER.n, or num.proxy_hybrid.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_hybrid.1
num.proxy_hybrid.OR.3
```

### 2024-08-08 sim_3_lasso/simResults_lasso.Rmd
simulation results .RMD file added & edited

--- 2024-08-01 sim_3.lasso/simResults_lasso.Rmd
@@
 ---
-title: "SimResults_Lasso"
-author: "Yang Lei"
-date: "2024-08-01"
+title: "simResults_lasso"
 output: html_document
@@
 # 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
-a <- 5
+a <- 1000
 
-RD_lasso <- data.frame(RD = numeric(),
-                       SE = numeric())
+RD_lasso <- data.frame(RD = numeric(), SE = numeric())
+
+num.proxy_lasso <- c()
 ```
@@
                 ".rds")
-  data <- tryCatch({
-    readRDS(url(url))
-  }, error = function(e) {
-    closeAllConnections()
-    readRDS(url(url))
-  })
+  data <- readRDS(url(url))
 
   # found some id != idx
-  data$id <- data$idx
+  data$idx <- data$id
   covar.mat <- model.matrix(Y.form, data = data)[,-1]
@@
   rownames(RD_lasso)[i] <- paste0("data.", i, "_lasso")
+  num.proxy_lasso <- c(num.proxy_lasso, length(proxy_lasso))
+  names(num.proxy_lasso)[i] <- paste0("data.", i, "_lasso")
 
@@
   assign(proxy_lasso.i, proxy_lasso)
+  num.proxy_lasso.i <- paste0("num.proxy_lasso.", i)
+  assign(num.proxy_lasso.i, length(proxy_lasso))
   sum.RD_lasso.i <- paste0("sum.RD_lasso.", i)
@@
   rownames(RD_lasso)[i+a] <- paste0("ER.data.", i, "_lasso")
+  num.proxy_lasso <- c(num.proxy_lasso, length(proxy_lasso))
+  names(num.proxy_lasso)[i+a] <- paste0("ER.data.", i, "_lasso")
 
@@
   assign(proxy_lasso.i, proxy_lasso)
+  num.proxy_lasso.i <- paste0("num.proxy_lasso.ER.", i)
+  assign(num.proxy_lasso.i, length(proxy_lasso))
   sum.RD_lasso.i <- paste0("sum.RD_lasso.ER.", i)
@@
   rownames(RD_lasso)[i+2*a] <- paste0("OR.data.", i, "_lasso")
+  num.proxy_lasso <- c(num.proxy_lasso, length(proxy_lasso))
+  names(num.proxy_lasso)[i+2*a] <- paste0("OR.data.", i, "_lasso")
 
@@
   assign(proxy_lasso.i, proxy_lasso)
+  num.proxy_lasso.i <- paste0("num.proxy_lasso.OR.", i)
+  assign(num.proxy_lasso.i, length(proxy_lasso))
   sum.RD_lasso.i <- paste0("sum.RD_lasso.OR.", i)
@@
 RD_lasso
+```
+
+```{r check number of proxies selected, warning=FALSE, cache=TRUE}
+num.proxy_lasso
+mean(num.proxy_lasso[complete.cases(num.proxy_lasso)])
 ```
@@
 proxy_lasso.ER.3
+
+# check number of proxy selected by lasso for each data, print:
+#   num.proxy_lasso.n, num.proxy_lasso.ER.n, or num.proxy_lasso.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+num.proxy_lasso.1
+num.proxy_lasso.OR.3
 ```

### 2024-08-08 sim_4_enet/simResults_enet.Rmd
simulation results .RMD file added & edited

--- 2024-08-01 sim_4.enet/simResults_enet.Rmd
@@
 title: "simResults_enet"
-author: "Yang Lei"
-date: "2024-08-01"
 output: html_document
@@
                        SE = numeric())
+
+num.proxy_enet <- c()
 ```
@@
   rownames(RD_enet)[i] <- paste0("data.", i, "_enet")
+  num.proxy_enet <- c(num.proxy_enet, length(proxy_enet))
+  names(num.proxy_enet)[i] <- paste0("data.", i, "_enet")
 
@@
   assign(proxy_enet.i, proxy_enet)
+  num.proxy_enet.i <- paste0("num.proxy_enet.", i)
+  assign(num.proxy_enet.i, length(proxy_enet))
   sum.RD_enet.i <- paste0("sum.RD_enet.", i)
@@
   rownames(RD_enet)[i+a] <- paste0("ER.data.", i, "_enet")
+  num.proxy_enet <- c(num.proxy_enet, length(proxy_enet))
+  names(num.proxy_enet)[i+a] <- paste0("data.", i, "_enet")
 
@@
   assign(proxy_enet.i, proxy_enet)
+  num.proxy_enet.i <- paste0("num.proxy_enet.ER.", i)
+  assign(num.proxy_enet.i, length(proxy_enet))
   sum.RD_enet.i <- paste0("sum.RD_enet.ER.", i)
@@
   rownames(RD_enet)[i+2*a] <- paste0("OR.data.", i, "_enet")
+  num.proxy_enet <- c(num.proxy_enet, length(proxy_enet))
+  names(num.proxy_enet)[i+2*a] <- paste0("data.", i, "_enet")
 
@@
   assign(proxy_enet.i, proxy_enet)  
+  num.proxy_enet.i <- paste0("num.proxy_enet.OR.", i)
+  assign(num.proxy_enet.i, length(proxy_enet))
   sum.RD_enet.i <- paste0("sum.RD_enet.OR.", i)
@@
 RD_enet
+```
+
+```{r check number of proxies selected, warning=FALSE, cache=TRUE}
+num.proxy_enet
+mean(num.proxy_enet[complete.cases(num.proxy_enet)])
 ```
@@
 proxy_enet.ER.3
+
+# check number of proxy selected by enet for each data, print:
+#   num.proxy_enet.n, num.proxy_enet.ER.n, or num.proxy_enet.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+num.proxy_enet.1
+num.proxy_enet.OR.4
 ```

### 2024-08-08 sim_5_svm/simResults_svm.Rmd
simulation results .RMD file added & edited

--- 2024-08-01 sim_5.svm/simResults_svm.Rmd
@@
 title: "simResults_svm"
-author: "Yang Lei"
-date: "2024-08-01"
 output: html_document
@@
 
-RD_svm <- data.frame(RD = numeric(),
-                       SE = numeric())
+RD_svm <- data.frame(RD = numeric(), SE = numeric())
+
+num.proxy_svm <- c()
 ```
@@
   rownames(RD_svm)[i] <- paste0("data.", i, "_svm")
+  num.proxy_svm <- c(num.proxy_svm, length(proxy_svm))
+  names(num.proxy_svm)[i] <- paste0("data.", i, "_svm")
 
@@
   assign(proxy_svm.i, proxy_svm)
+  num.proxy_svm.i <- paste0("num.proxy_svm.", i)
+  assign(num.proxy_svm.i, length(proxy_svm))
   sum.RD_svm.i <- paste0("sum.RD_svm.", i)
@@
   rownames(RD_svm)[i+a] <- paste0("ER.data.", i, "_svm")
+  num.proxy_svm <- c(num.proxy_svm, length(proxy_svm))
+  names(num.proxy_svm)[i+a] <- paste0("ER.data.", i, "_svm")
 
@@
   assign(proxy_svm.i, proxy_svm)
+  num.proxy_svm.i <- paste0("num.proxy_svm.ER.", i)
+  assign(num.proxy_svm.i, length(proxy_svm))
   sum.RD_svm.i <- paste0("sum.RD_svm.ER.", i)
@@
   rownames(RD_svm)[i+2*a] <- paste0("OR.data.", i, "_svm")
+  num.proxy_svm <- c(num.proxy_svm, length(proxy_svm))
+  names(num.proxy_svm)[i+2*a] <- paste0("OR.data.", i, "_svm")
 
@@
   assign(proxy_svm.i, proxy_svm)
+  num.proxy_svm.i <- paste0("num.proxy_svm.OR.", i)
+  assign(num.proxy_svm.i, length(proxy_svm))
   sum.RD_svm.i <- paste0("sum.RD_svm.OR.", i)
@@
 RD_svm
+```
+
+```{r check number of proxies selected, warning=FALSE, cache=TRUE}
+num.proxy_svm
+mean(num.proxy_svm[complete.cases(num.proxy_svm)])
 ```
@@
 proxy_svm.ER.3
+
+# check number of proxy selected by svm for each data, print:
+#   num.proxy_svm.n, num.proxy_svm.ER.n, or num.proxy_svm.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+num.proxy_svm.1
+num.proxy_svm.OR.3
 ```

### 2024-08-08 sim_6_ga/simResults_ga.Rmd
simulation results .RMD file added & edited

--- 2024-08-01 sim_6.ga/simResults_ga.Rmd
@@
 title: "simResults_ga"
-author: "Yang Lei"
-date: "2024-08-01"
 output: html_document
@@
 
-RD_ga <- data.frame(RD = numeric(),
-                       SE = numeric())
+RD_ga <- data.frame(RD = numeric(), SE = numeric())
+
+num.proxy_ga <- c()
 ```
@@
   rownames(RD_ga)[i] <- paste0("data.", i, "_ga")
+  num.proxy_ga <- c(num.proxy_ga, length(proxy_ga))
+  names(num.proxy_ga)[i] <- paste0("data.", i, "_ga")
 
@@
   assign(proxy_ga.i, proxy_ga)
+  num.proxy_ga.i <- paste0("num.proxy_ga.", i)
+  assign(num.proxy_ga.i, length(proxy_ga))
   sum.RD_ga.i <- paste0("sum.RD_ga.", i)
@@
   rownames(RD_ga)[i+a] <- paste0("ER.data.", i, "_ga")
+  num.proxy_ga <- c(num.proxy_ga, length(proxy_ga))
+  names(num.proxy_ga)[i+a] <- paste0("ER.data.", i, "_ga")
 
@@
   assign(proxy_ga.i, proxy_ga)
+  num.proxy_ga.i <- paste0("num.proxy_ga.ER.", i)
+  assign(num.proxy_ga.i, length(proxy_ga))
   sum.RD_ga.i <- paste0("sum.RD_ga.ER.", i)
@@
   rownames(RD_ga)[i+2*a] <- paste0("OR.data.", i, "_ga")
+  num.proxy_ga <- c(num.proxy_ga, length(proxy_ga))
+  names(num.proxy_ga)[i+2*a] <- paste0("OR.data.", i, "_ga")
 
@@
   assign(proxy_ga.i, proxy_ga)
+  num.proxy_ga.i <- paste0("num.proxy_ga.OR.", i)
+  assign(num.proxy_ga.i, length(proxy_ga))
   sum.RD_ga.i <- paste0("sum.RD_ga.OR.", i)
@@
 
-```{r}
+```{r read RD & SE results by ga, warning=FALSE, cache=TRUE}
 RD_ga
+```
+
+```{r check number of proxies selected, warning=FALSE, cache=TRUE}
+num.proxy_ga
+mean(num.proxy_ga[complete.cases(num.proxy_ga)])
 ```
@@
 proxy_ga.ER.3
+
+# check number of proxy selected by ga for each data, print:
+#   num.proxy_ga.n, num.proxy_ga.ER.n, or num.proxy_ga.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+num.proxy_ga.1
+num.proxy_ga.OR.3
 ```

### 2024-08-08 sim_7_xgboost/simResults_xgboost.Rmd
simulation results .RMD file added & edited

--- 2024-08-01 sim_7.xgboost/simResults_xgboost.Rmd
@@
 title: "simResults_xgboost"
-author: "Yang Lei"
-date: "2024-08-01"
 output: html_document
@@
 RD_xgboost <- data.frame(RD = numeric(), SE = numeric())
+
+num.proxy_xgboost <- c()
 ```
@@
   rownames(RD_xgboost)[i] <- paste0("data.", i, "_xgboost")
+  num.proxy_xgboost <- c(num.proxy_xgboost, length(proxy_xgboost))
+  names(num.proxy_xgboost)[i] <- paste0("data.", i, "_xgboost")
 
@@
   assign(proxy_xgboost.i, proxy_xgboost)
+  num.proxy_xgboost.i <- paste0("num.proxy_xgboost.", i)
+  assign(num.proxy_xgboost.i, length(proxy_xgboost))
   sum.RD_xgboost.i <- paste0("sum.RD_xgboost.", i)
@@
   rownames(RD_xgboost)[i+a] <- paste0("ER.data.", i, "_xgboost")
+  num.proxy_xgboost <- c(num.proxy_xgboost, length(proxy_xgboost))
+  names(num.proxy_xgboost)[i+a] <- paste0("ER.data.", i, "_xgboost")
 
@@
   assign(proxy_xgboost.i, proxy_xgboost)
+  num.proxy_xgboost.i <- paste0("num.proxy_xgboost.ER.", i)
+  assign(num.proxy_xgboost.i, length(proxy_xgboost))
   sum.RD_xgboost.i <- paste0("sum.RD_xgboost.ER.", i)
@@
   rownames(RD_xgboost)[i+2*a] <- paste0("OR.data.", i, "_xgboost")
+  num.proxy_xgboost <- c(num.proxy_xgboost, length(proxy_xgboost))
+  names(num.proxy_xgboost)[i+2*a] <- paste0("OR.data.", i, "_xgboost")
 
@@
   assign(proxy_xgboost.i, proxy_xgboost)
+  num.proxy_xgboost.i <- paste0("num.proxy_xgboost.OR.", i)
+  assign(num.proxy_xgboost.i, length(proxy_xgboost))
   sum.RD_xgboost.i <- paste0("sum.RD_xgboost.OR.", i)
@@
 RD_xgboost
+```
+
+```{r check number of proxies selected, warning=FALSE, cache=TRUE}
+num.proxy_xgboost
+mean(num.proxy_xgboost[complete.cases(num.proxy_xgboost)])
 ```
@@
 proxy_xgboost.ER.3
+
+# check number of proxy selected by xgboost for each data, print:
+#   num.proxy_xgboost.n, num.proxy_xgboost.ER.n, or num.proxy_xgboost.OR.n
+#   where "n" is a number ranges from 1 to 1000
+#   e.g.
+num.proxy_xgboost.1
+num.proxy_xgboost.OR.3
 ```

### 2024-08-08 sim_8_rf/simResults_rf.Rmd
simulation results .RMD file added & edited

--- 2024-08-01 sim_8.rf/simResults_rf.Rmd
@@
 title: "simResults_rf"
-author: "Yang Lei"
-date: "2024-08-01"
 output: html_document
@@
 
-```{r initialization before for-loop, warning=FALSE, cache=TRUE}
-# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
-a <- 1
-
-RD_rf <- data.frame(RD = numeric(),
-                       SE = numeric())
-```
-
 ```{r scenario: for-loop generating RD & SE results for rf, warning=FALSE, cache=TRUE}
@@
   # found some id != idx
-  data$id <- data$idx
+  data$idx <- data$id
 

### 2024-08-08 sim_9_boruta/simResults_boruta.Rmd
simulation results .RMD file added & edited

---
title: "simResults_boruta"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
require(lmtest)
```

```{r load basic information, warning=FALSE, cache=TRUE}
# global information
exposure <- "obese"
outcome <- "diabetes" 
investigator.specified.covariates <- 
  c(# Demographic
    "age.cat", "sex", "education", "race", 
    "marital", "income", "born", "year",

    # health history related variables/access
    "diabetes.family.history", "medical.access",

    # behavioral
    "smoking", "diet.healthy", "physical.activity", "sleep",

    # Laboratory 
    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
    "sodium", "potassium", "globulin", "calcium.total", 
    "systolicBP", "diastolicBP", "high.cholesterol"
  )
covform <- paste0(investigator.specified.covariates, collapse = "+")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))

url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_1.rds")
data <- readRDS(url(url))
proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )
```

```{r initialization before for-loop, warning=FALSE, cache=TRUE}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
a <- 1000

RD_boruta <- data.frame(RD = numeric(), SE = numeric())

num.proxy_boruta <- c()
```

```{r scenario: for-loop generating RD & SE results for boruta, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenario"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenario/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  boruta.fit <- Boruta(Y.form, data = data, doTrace = 1)
  sel.variables <- names(boruta.fit$finalDecision)[which(boruta.fit$finalDecision != "Rejected")]
  proxy_boruta <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_boruta, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_boruta <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_boruta$ps
  data$w.l <- W.out_boruta$weights

  fit.OR_boruta <- glm(out.formula,
                      data = data,
                      weights = W.out_boruta$weights,
                      family= binomial(link = "logit"))
  fit.RD_boruta <- glm(out.formula,
                       data = data,
                       weights = W.out_boruta$weights,
                       family = gaussian(link= "identity"))
  sum.RD_boruta <- c(summary(fit.RD_boruta)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_boruta)[2,2]))

  RD_boruta[i,] <- sum.RD_boruta
  rownames(RD_boruta)[i] <- paste0("data.", i, "_boruta")
  num.proxy_boruta <- c(num.proxy_boruta, length(proxy_boruta))
  names(num.proxy_boruta)[i] <- paste0("data.", i, "_boruta")

  proxy_boruta.i <- paste0("proxy_boruta.", i)
  assign(proxy_boruta.i, proxy_boruta)
  num.proxy_boruta.i <- paste0("num.proxy_boruta.", i)
  assign(num.proxy_boruta.i, length(proxy_boruta))
  sum.RD_boruta.i <- paste0("sum.RD_boruta.", i)
  assign(sum.RD_boruta.i, sum.RD_boruta)
}
```

```{r scenarioER: for-loop generating RD & SE results for boruta, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioER"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioER/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  boruta.fit <- Boruta(Y.form, data = data, doTrace = 1)
  sel.variables <- names(boruta.fit$finalDecision)[which(boruta.fit$finalDecision != "Rejected")]
  proxy_boruta <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_boruta, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_boruta <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_boruta$ps
  data$w.l <- W.out_boruta$weights

  fit.OR_boruta <- glm(out.formula,
                      data = data,
                      weights = W.out_boruta$weights,
                      family= binomial(link = "logit"))
  fit.RD_boruta <- glm(out.formula,
                       data = data,
                       weights = W.out_boruta$weights,
                       family = gaussian(link= "identity"))
  sum.RD_boruta <- c(summary(fit.RD_boruta)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_boruta)[2,2]))

  RD_boruta[i+a,] <- sum.RD_boruta
  rownames(RD_boruta)[i+a] <- paste0("ER.data.", i, "_boruta")
  num.proxy_boruta <- c(num.proxy_boruta, length(proxy_boruta))
  names(num.proxy_boruta)[i+a] <- paste0("ER.data.", i, "_boruta")

  proxy_boruta.i <- paste0("proxy_boruta.ER.", i)
  assign(proxy_boruta.i, proxy_boruta)
  num.proxy_boruta.i <- paste0("num.proxy_boruta.ER.", i)
  assign(num.proxy_boruta.i, length(proxy_boruta))
  sum.RD_boruta.i <- paste0("sum.RD_boruta.ER.", i)
  assign(sum.RD_boruta.i, sum.RD_boruta)
}
```

```{r scenarioOR: for-loop generating RD & SE results for boruta, warning=FALSE, cache=TRUE}
set.seed(42)

# Folder "scenarioOR"
for (i in 1:a) {
  closeAllConnections()
  url <- paste0("https://raw.githubusercontent.com/ehsanx/PlasmodeSim/main/data/hdData/data/scenarioOR/data_", 
                i, 
                ".rds")
  data <- readRDS(url(url))

  # found some id != idx
  data$idx <- data$id

  boruta.fit <- Boruta(Y.form, data = data, doTrace = 1)
  sel.variables <- names(boruta.fit$finalDecision)[which(boruta.fit$finalDecision != "Rejected")]
  proxy_boruta <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_boruta, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_boruta <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_boruta$ps
  data$w.l <- W.out_boruta$weights

  fit.OR_boruta <- glm(out.formula,
                      data = data,
                      weights = W.out_boruta$weights,
                      family= binomial(link = "logit"))
  fit.RD_boruta <- glm(out.formula,
                       data = data,
                       weights = W.out_boruta$weights,
                       family = gaussian(link= "identity"))
  sum.RD_boruta <- c(summary(fit.RD_boruta)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_boruta)[2,2]))

  RD_boruta[i+2*a,] <- sum.RD_boruta
  rownames(RD_boruta)[i+2*a] <- paste0("OR.data.", i, "_boruta")
  num.proxy_boruta <- c(num.proxy_boruta, length(proxy_boruta))
  names(num.proxy_boruta)[i+2*a] <- paste0("OR.data.", i, "_boruta")

  proxy_boruta.i <- paste0("proxy_boruta.OR.", i)
  assign(proxy_boruta.i, proxy_boruta)
  num.proxy_boruta.i <- paste0("num.proxy_boruta.OR.", i)
  assign(num.proxy_boruta.i, length(proxy_boruta))
  sum.RD_boruta.i <- paste0("sum.RD_boruta.OR.", i)
  assign(sum.RD_boruta.i, sum.RD_boruta)
}
```

```{r read RD & SE results by boruta, warning=FALSE, cache=TRUE}
RD_boruta
```

```{r check number of proxies selected, warning=FALSE, cache=TRUE}
num.proxy_boruta
mean(num.proxy_boruta[complete.cases(num.proxy_boruta)])
```

```{r check intermediate results for each data by boruta, warning=FALSE, cache=TRUE}
# check RD & SE by boruta for each data, print:
#   sum.RD_boruta.n, sum.RD_boruta.ER.n, or sum.RD_boruta.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_boruta.1
sum.RD_boruta.ER.2

# check proxy selected by boruta for each data, print:
#   proxy_boruta.n, proxy_boruta.ER.n, or proxy_boruta.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_boruta.1
proxy_boruta.ER.3

# check number of proxy selected by boruta for each data, print:
#   num.proxy_boruta.n, num.proxy_boruta.ER.n, or num.proxy_boruta.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
num.proxy_boruta.1
num.proxy_boruta.OR.3
```

### 2024-08-09 Simulation Attemps/Attempt 0/bross.R
failed simulation attemps

@@ -1,0 +1,147 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(tidyverse)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_bross <- data.frame(RD = numeric(), SE = numeric())
+num.proxy_bross <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+set.seed(42)
+
+# Folder "scenario"
+for (i in 1:a) {
+  path <- paste0("../../simData/scenario/data_", i, ".rds")
+  data <- readRDS(path)
+  
+  # found some id != idx
+  data$idx <- data$id
+  
+  # Feature Selection Method 1: Bross Formula
+  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]
+  
+  bross.list <- tryCatch({
+    get_prioritised_covariates(df = proxy.df,
+                               patientIdVarname = "idx", 
+                               exposureVector = data$exposure,
+                               outcomeVector = data$outcome,
[…]

### 2024-08-09 Simulation Attemps/Attempt 0/bross.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+#SBATCH --account=st-mekarim-1
+#SBATCH --nodes=1
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=32
+#SBATCH --mem=0
+#SBATCH --time=0-20:00:00
+#SBATCH --mail-user=leiyang1@student.ubc.ca
+#SBATCH --mail-type=ALL
+module load gcc/9.4.0
+module load r/4.4.0
+
+R CMD BATCH bross.R

### 2024-08-09 Simulation Attemps/Attempt 1/bross1.R

@@ -1,0 +1,149 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(tidyverse)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_bross <- data.frame(RD = numeric(), SE = numeric())
+num.proxy_bross <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+set.seed(42)
+
+# Folder "scenario"
+for (i in 1:a) {
+  path <- paste0("../../simData/scenario/data_", i, ".rds")
+  data <- readRDS(path)
+  
+  # found some id != idx
+  data$idx <- data$id
+  
+  # Feature Selection Method 1: Bross Formula
+  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]
+  
+  bross.list <- tryCatch({
+    get_prioritised_covariates(df = proxy.df,
+                               patientIdVarname = "idx", 
+                               exposureVector = data$exposure,
+                               outcomeVector = data$outcome,
[…]

### 2024-08-09 Simulation Attemps/Attempt 1/bross1.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+#SBATCH --account=st-mekarim-1
+#SBATCH --nodes=1
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=32
+#SBATCH --mem=0
+#SBATCH --time=0-20:00:00
+#SBATCH --mail-user=leiyang1@student.ubc.ca
+#SBATCH --mail-type=ALL
+module load gcc/9.4.0
+module load r/4.4.0
+export R_LIBS=/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4
+R CMD BATCH bross1.R

### 2024-08-09 Simulation Attemps/Attempt 2/bross2.R

@@ -1,0 +1,153 @@
+
+setwd("/home/leiyang1/hdPS_ProxySelect/simResults_scenario/1_bross")
+
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(tidyverse)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+setwd("/home/leiyang1/hdPS_ProxySelect/simResults_scenario/1_bross")
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_bross <- data.frame(RD = numeric(), SE = numeric())
+num.proxy_bross <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+set.seed(42)
+
+# Folder "scenario"
+for (i in 1:a) {
+  path <- paste0("../../simData/scenario/data_", i, ".rds")
+  data <- readRDS(path)
+  
+  # found some id != idx
+  data$idx <- data$id
+  
+  # Feature Selection Method 1: Bross Formula
+  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]
+  
+  bross.list <- tryCatch({
+    get_prioritised_covariates(df = proxy.df,
[…]

### 2024-08-09 Simulation Attemps/Attempt 2/bross2.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+#SBATCH --account=st-mekarim-1
+#SBATCH --nodes=1
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=32
+#SBATCH --mem=0
+#SBATCH --time=0-20:00:00
+#SBATCH --mail-user=leiyang1@student.ubc.ca
+#SBATCH --mail-type=ALL
+module load gcc/9.4.0
+module load r/4.4.0
+
+R CMD BATCH bross2.R

### 2024-08-09 Simulation Attemps/Attempt 3/bross3.R

@@ -1,0 +1,150 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(tidyverse)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+setwd("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenario/1_bross")
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_bross <- data.frame(RD = numeric(), SE = numeric())
+num.proxy_bross <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+set.seed(42)
+
+# Folder "scenario"
+for (i in 1:a) {
+  path <- paste0("../../simData/scenario/data_", i, ".rds")
+  data <- readRDS(path)
+  
+  # found some id != idx
+  data$idx <- data$id
+  
+  # Feature Selection Method 1: Bross Formula
+  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]
+  
+  bross.list <- tryCatch({
+    get_prioritised_covariates(df = proxy.df,
+                               patientIdVarname = "idx", 
[…]

### 2024-08-09 Simulation Attemps/Attempt 3/bross3.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+#SBATCH --account=st-mekarim-1
+#SBATCH --nodes=1
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=32
+#SBATCH --mem=0
+#SBATCH --time=0-20:00:00
+#SBATCH --mail-user=leiyang1@student.ubc.ca
+#SBATCH --mail-type=ALL
+module load gcc/9.4.0
+module load r/4.4.0
+
+R CMD BATCH bross3.R

### 2024-08-15 simResults_scenario/9_boruta/parallel_boruta.R
some simulation results (numProxy & RD & SE for method bross, hybrid, lasso, enet, [some] GA, xgboost)

@@ -1,0 +1,80 @@
+# try parallel
+library(parallel)
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+library(glmnet)
+
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+"))
+
+# ---------------------------------------------------------------
+
+n_cores <- 12  # Match this to the --ntasks value in your Slurm script
+
+proxy_select <- function(i) {
+  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
+  data <- readRDS(path)
+  
+  # found some id != idx
+  data$idx <- data$id
+  
+  boruta.fit <- Boruta(Y.form, data = data, doTrace = 1)
[…]

### 2024-08-15 simResults_scenarioER/6_ga/ga.R

@@ -1,0 +1,136 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes"
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+# function for GA
+gaOpt <- function(vars, IV.train, DV.train) {
+  varNames <- colnames(IV.train) #getting names of all variables
+  selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
+  gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars
+  
+  gaDat <- cbind(gaSolutionData,DV.train) # combining selected variables with outcome variable
+  gaMod <- glm(DV.train ~ ., family = "binomial", data = gaDat) #build model
+  gaProb <- predict(gaMod, IV.train, type = "response") # get probabilities
[…]

### 2024-08-15 simResults_scenarioOR/6_ga/ga.R

@@ -1,0 +1,135 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes"
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_1.rds")
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+# function for GA
+gaOpt <- function(vars, IV.train, DV.train) {
+  varNames <- colnames(IV.train) #getting names of all variables
+  selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
+  gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars
+  
+  gaDat <- cbind(gaSolutionData,DV.train) # combining selected variables with outcome variable
+  gaMod <- glm(DV.train ~ ., family = "binomial", data = gaDat) #build model
+  gaProb <- predict(gaMod, IV.train, type = "response") # get probabilities
[…]

### 2024-08-15 simResults_scenario/load_simResults.R
load the numProxy & RD & SE table of simulation results

@@ -1,0 +1,14 @@
+# 1_bross
+load("1_bross/bross.RData")
+
+# 2_hybrid
+load("2_hybrid/hybrid.RData")
+
+# 3_lasso
+load("3_lasso/lasso.RData")
+
+# 4_enet
+load("4_enet/enet.RData")
+
+# 7_xgboost
+load("7_xgboost/xgboost.RData")

### 2024-08-16 simResults_scenario/10.1_forward/forward.R
add results tables by method stepwise forward, stepwise backward

@@ -12,6 +12,7 @@ library(penalizedSVM)
 library(xgboost)
 library(caret)
 library(randomForest)
+library(leaps)
 # ---------------------------------------------------------------
 
 ### global information
@@ -41,9 +42,6 @@ proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+") )
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
 full.formula <- as.formula(paste0("outcome~exposure+",
                                   paste0(covarsTfull, collapse = "+"),
                                   collapse = "+"))
@@ -52,7 +50,7 @@ full.formula <- as.formula(paste0("outcome~exposure+",
 ### initialization before for-loop
 # 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
 a <- 1000
-b <- 4
+b <- 0
 
 RD_forward <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
 num.proxy_forward <- c()
@@ -69,13 +67,10 @@ for (i in (b+1):a) {
   # found some id != idx
   data$idx <- data$id
   
-  initial.model <- glm(initial.formula, data = data, family = binomial)
-  full.model <- glm(full.formula, data = data, family = binomial)
-  stepwise_forward <- stepAIC(initial.model, 
-                              scope = list(lower = initial.model, 
-                                           upper = full.model), 
-                              direction = "forward")
-  sel.variables <- all.vars(formula(stepwise_forward))[-1]
+  stepwise_forward <- regsubsets(full.formula, data = data, method = "forward", nvmax = length(proxy.list), nbest = 10)
+  summary_stepwise <- summary(stepwise_forward)
+  best_model <- which.max(summary_stepwise$adjr2)
+  sel.variables <- names(summary_stepwise$which[best_model,])[summary_stepwise$which[best_model,]]
   proxy_forward <- proxy.list[proxy.list %in% sel.variables]
   proxyform <- paste0(proxy_forward, collapse = "+")
   rhsform <- paste0(c(covform, proxyform), collapse = "+")

### 2024-08-16 simResults_scenario/10.2_backward/backward.R

@@ -12,6 +12,7 @@ library(penalizedSVM)
 library(xgboost)
 library(caret)
 library(randomForest)
+library(leaps)
 # ---------------------------------------------------------------
 
 ### global information
@@ -41,9 +42,6 @@ proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+") )
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
 full.formula <- as.formula(paste0("outcome~exposure+",
                                   paste0(covarsTfull, collapse = "+"),
                                   collapse = "+"))
@@ -68,14 +66,11 @@ for (i in (b+1):a) {
   
   # found some id != idx
   data$idx <- data$id
-  initial.model <- glm(initial.formula, data = data, family = binomial)
-  full.model <- glm(full.formula, data = data, family = binomial)
-  stepwise_backward <- stepAIC(full.model, 
-                               scope = list(lower = initial.model, 
-                                            upper = full.model), 
-                               direction = "backward")
   
-  sel.variables <- all.vars(formula(stepwise_backward))[-1]
+  stepwise_backward <- regsubsets(full.formula, data = data, method = "backward", nvmax = length(proxy.list), nbest = 10)
+  summary_stepwise <- summary(stepwise_backward)
+  best_model <- which.max(summary_stepwise$adjr2)
+  sel.variables <- names(summary_stepwise$which[best_model,])[summary_stepwise$which[best_model,]]
   proxy_backward <- proxy.list[proxy.list %in% sel.variables]
   proxyform <- paste0(proxy_backward, collapse = "+")
   rhsform <- paste0(c(covform, proxyform), collapse = "+")

### 2024-08-16 simResults_scenario/10.2_backward/parallel_backward.R

@@ -1,95 +1,0 @@
-# try parallel
-library(parallel)
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-library(glmnet)
-
-# ---------------------------------------------------------------
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes" 
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
-data1 <- readRDS(path)
-proxy.list <- names(data1[, c(grep("^rec", names(data1), value = TRUE))])
-covarsTfull <- c(investigator.specified.covariates, proxy.list)
-Y.form <- as.formula(paste0(c("outcome~ exposure", 
-                              covarsTfull), collapse = "+"))
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
-full.formula <- as.formula(paste0("outcome~exposure+",
-                                  paste0(covarsTfull, collapse = "+"),
-                                  collapse = "+"))
-# ---------------------------------------------------------------
-
-n_cores <- 12  # Match this to the --ntasks value in your Slurm script
-
-proxy_select <- function(i) {
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
-  data <- readRDS(path)
-  
-  # found some id != idx
[…]

### 2024-08-16 simResults_scenario/10.3_both/load_proxy_both.R

@@ -1,0 +1,117 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes"
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+a <- 1000
+b <- 0
+
+RD_both <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_both <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+
+for (i in (b+1):a) {
+  path_proxy <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenario/10.3_both/proxy_both.data.", i, ".RData")
+  
+  if (file.exists(path_proxy)) {
+    proxyform_name <- load(path_proxy)
+    proxyform <- get(proxyform_name)
+    proxy_both <- strsplit(proxyform, split = "\\+")[[1]]
+    
[…]

### 2024-08-16 simResults_scenario/10.3_both/load_proxy_both.sh

@@ -1,13 +1,13 @@
 #!/bin/bash
 #SBATCH --account=st-mekarim-1
 #SBATCH --nodes=1
-#SBATCH --ntasks=12
-#SBATCH --mem=10G
-#SBATCH --time=5:00:00
+#SBATCH --ntasks=1
+#SBATCH --mem=2G
+#SBATCH --time=2:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
-#SBATCH --output=output_parallel_backward.txt
-#SBATCH --error=error_parallel_backward.txt
+#SBATCH --output=output_load_proxy_both.txt
+#SBATCH --error=error_load_proxy_both.txt
 
 module load gcc/9.4.0
 module load r/4.4.0
@@ -15,4 +15,4 @@ module load r/4.4.0
 cd $SLURM_SUBMIT_DIR
 export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
 
-R CMD BATCH parallel_backward.R
+R CMD BATCH load_proxy_both.R

### 2024-08-16 simResults_scenario/10.3_both/parallel_both.R

@@ -40,8 +40,8 @@ investigator.specified.covariates <-
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
 path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
-data <- readRDS(path)
-proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+data1 <- readRDS(path)
+proxy.list <- names(data1[, c(grep("^rec", names(data1), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+"))
@@ -56,16 +56,16 @@ full.formula <- as.formula(paste0("outcome~exposure+",
 n_cores <- 12  # Match this to the --ntasks value in your Slurm script
 
 proxy_select <- function(i) {
+  browser()
   path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
-  data <- readRDS(path)
+  ds <<- readRDS(path)
   
   # found some id != idx
-  data$idx <- data$id
-  
-  data <- as.data.frame(data)
-  
-  initial.model <- glm(initial.formula, data = data, family = binomial)
-  full.model <- glm(full.formula, data = data, family = binomial)
+  ds$idx <<- ds$id
+  ds$idx <- ds$id
+
+  initial.model <- glm(initial.formula, data = ds, family = binomial)
+  full.model <- glm(full.formula, data = ds, family = binomial)
   stepwise_both <- stepAIC(initial.model, 
                            scope = list(lower = initial.model, 
                                         upper = full.model), 
@@ -75,20 +75,11 @@ proxy_select <- function(i) {
   proxyform <- paste0(proxy_both, collapse = "+")
   proxy_both.data.i <- paste0("proxy_both.data.", i)
   assign(proxy_both.data.i, proxyform)
+  return(proxyform)
   
   # Save the result to an .rds file
   save_path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenario/10.3_both/proxy_both.data.", i, ".RData")
   save(list = proxy_both.data.i, file = save_path)
-  
[…]

### 2024-08-16 simResults_scenario/10.3_both/parallel_both.sh

@@ -2,8 +2,8 @@
 #SBATCH --account=st-mekarim-1
 #SBATCH --nodes=1
 #SBATCH --ntasks=12
-#SBATCH --mem=5G
-#SBATCH --time=5:00:00
+#SBATCH --mem=10G
+#SBATCH --time=9:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
 #SBATCH --output=output_parallel_both.txt

### 2024-08-16 simResults_scenario/6_ga/parallel_ga.R

@@ -39,53 +39,64 @@ investigator.specified.covariates <-
   )
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
 data <- readRDS(path)
 proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+"))
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
-full.formula <- as.formula(paste0("outcome~exposure+",
-                                  paste0(covarsTfull, collapse = "+"),
-                                  collapse = "+"))
+gaOpt <- function(vars, IV.train, DV.train) {
+  varNames <- colnames(IV.train) #getting names of all variables
+  selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
+  gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars
+  
+  gaDat <- cbind(gaSolutionData,DV.train) # combining selected variables with outcome variable
+  gaMod <- glm(DV.train ~ ., family = "binomial", data = gaDat) #build model
+  gaProb <- predict(gaMod, IV.train, type = "response") # get probabilities
+  gaPred <- ifelse(gaProb >= .8, 1, 0) # get predicted 0s and 1s
+  
+  ari <- adjustedRandIndex(gaPred, DV.train)
+  return(ari)
+}
 # ---------------------------------------------------------------
 
 n_cores <- 12  # Match this to the --ntasks value in your Slurm script
 
 proxy_select <- function(i) {
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_", i, ".rds")
+  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
[…]

### 2024-08-16 simResults_scenario/6_ga/parallel_ga.sh

@@ -2,12 +2,12 @@
 #SBATCH --account=st-mekarim-1
 #SBATCH --nodes=1
 #SBATCH --ntasks=12
-#SBATCH --mem=5G
-#SBATCH --time=5:00:00
+#SBATCH --mem=8G
+#SBATCH --time=14:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
-#SBATCH --output=output_parallel_forward.txt
-#SBATCH --error=error_parallel_forward.txt
+#SBATCH --output=output_parallel_ga.txt
+#SBATCH --error=error_parallel_ga.txt
 
 module load gcc/9.4.0
 module load r/4.4.0
@@ -15,4 +15,4 @@ module load r/4.4.0
 cd $SLURM_SUBMIT_DIR
 export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
 
-R CMD BATCH parallel_forward.R
+R CMD BATCH parallel_ga.R

### 2024-08-16 simResults_scenario/8_rf/rf.R

@@ -46,7 +46,7 @@ Y.form <- as.formula(paste0(c("outcome~ exposure",
 ### initialization before for-loop
 # 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
 a <- 1000
-b <- 60
+b <- 323
 
 RD_rf <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
 num.proxy_rf <- c()

### 2024-08-16 simResults_scenario/8_rf/rf.sh

@@ -2,8 +2,8 @@
 #SBATCH --account=st-mekarim-1
 #SBATCH --nodes=1
 #SBATCH --ntasks=1
-#SBATCH --mem=5G
-#SBATCH --time=10:00:00
+#SBATCH --mem=10G
+#SBATCH --time=15:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
 #SBATCH --output=output_rf.txt

### 2024-08-16 simResults_scenarioER/10.1_forward/forward.R

@@ -12,6 +12,7 @@ library(penalizedSVM)
 library(xgboost)
 library(caret)
 library(randomForest)
+library(leaps)
 # ---------------------------------------------------------------
 
 ### global information
@@ -35,15 +36,12 @@ investigator.specified.covariates <-
   )
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
 data <- readRDS(path)
 proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+") )
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
 full.formula <- as.formula(paste0("outcome~exposure+",
                                   paste0(covarsTfull, collapse = "+"),
                                   collapse = "+"))
@@ -58,24 +56,21 @@ RD_forward <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a)
 num.proxy_forward <- c()
 # ---------------------------------------------------------------
 
-### scenario: for-loop generating RD & SE results
+### scenarioER: for-loop generating RD & SE results
 set.seed(42)
 
-# Folder "scenario"
+# Folder "scenarioER"
 for (i in (b+1):a) {
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
+  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_", i, ".rds")
   data <- readRDS(path)
   
   # found some id != idx
   data$idx <- data$id
   
-  initial.model <- glm(initial.formula, data = data, family = binomial)
-  full.model <- glm(full.formula, data = data, family = binomial)
-  stepwise_forward <- stepAIC(initial.model, 
-                              scope = list(lower = initial.model, 
[…]

### 2024-08-16 simResults_scenarioER/10.1_forward/forward.sh

@@ -3,7 +3,7 @@
 #SBATCH --nodes=1
 #SBATCH --ntasks=1
 #SBATCH --mem=5G
-#SBATCH --time=10:00:00
+#SBATCH --time=2:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
 #SBATCH --output=output_forward.txt

### 2024-08-16 simResults_scenarioER/10.2_backward/backward.R

@@ -12,6 +12,7 @@ library(penalizedSVM)
 library(xgboost)
 library(caret)
 library(randomForest)
+library(leaps)
 # ---------------------------------------------------------------
 
 ### global information
@@ -35,15 +36,12 @@ investigator.specified.covariates <-
   )
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
 data <- readRDS(path)
 proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+") )
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
 full.formula <- as.formula(paste0("outcome~exposure+",
                                   paste0(covarsTfull, collapse = "+"),
                                   collapse = "+"))
@@ -58,24 +56,21 @@ RD_backward <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a
 num.proxy_backward <- c()
 # ---------------------------------------------------------------
 
-### scenario: for-loop generating RD & SE results
+### scenarioER: for-loop generating RD & SE results
 set.seed(42)
 
-# Folder "scenario"
+# Folder "scenarioER"
 for (i in (b+1):a) {
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
+  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_", i, ".rds")
   data <- readRDS(path)
   
   # found some id != idx
   data$idx <- data$id
-  initial.model <- glm(initial.formula, data = data, family = binomial)
-  full.model <- glm(full.formula, data = data, family = binomial)
-  stepwise_backward <- stepAIC(full.model, 
-                               scope = list(lower = initial.model, 
[…]

### 2024-08-16 simResults_scenarioER/10.2_backward/backward.sh

@@ -3,7 +3,7 @@
 #SBATCH --nodes=1
 #SBATCH --ntasks=1
 #SBATCH --mem=5G
-#SBATCH --time=10:00:00
+#SBATCH --time=2:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
 #SBATCH --output=output_backward.txt

### 2024-08-16 simResults_scenarioER/10.2_backward/parallel_backward.R

@@ -1,95 +1,0 @@
-# try parallel
-library(parallel)
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-library(glmnet)
-
-# ---------------------------------------------------------------
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes" 
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
-data1 <- readRDS(path)
-proxy.list <- names(data1[, c(grep("^rec", names(data1), value = TRUE))])
-covarsTfull <- c(investigator.specified.covariates, proxy.list)
-Y.form <- as.formula(paste0(c("outcome~ exposure", 
-                              covarsTfull), collapse = "+"))
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
-full.formula <- as.formula(paste0("outcome~exposure+",
-                                  paste0(covarsTfull, collapse = "+"),
-                                  collapse = "+"))
-# ---------------------------------------------------------------
-
-n_cores <- 12  # Match this to the --ntasks value in your Slurm script
-
-proxy_select <- function(i) {
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_", i, ".rds")
-  data <- readRDS(path)
-  
-  # found some id != idx
[…]

### 2024-08-16 simResults_scenarioER/10.3_both/load_proxy_both.R

@@ -1,0 +1,121 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes"
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+a <- 1000
+b <- 0
+
+RD_both_ER <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_both_ER <- c()
+# ---------------------------------------------------------------
+
+### scenarioER: for-loop generating RD & SE results
+set.seed(42)
+
+for (i in (b+1):a) {
+  path_proxy <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenarioER/10.3_both/proxy_both.data.", i, ".RData")
+  
+  if (file.exists(path_proxy)) {
+    proxyform_name <- load(path_proxy)
+    proxyform <- get(proxyform_name)
[…]

### 2024-08-16 simResults_scenarioER/10.3_both/load_proxy_both.sh

@@ -1,13 +1,13 @@
 #!/bin/bash
 #SBATCH --account=st-mekarim-1
 #SBATCH --nodes=1
-#SBATCH --ntasks=12
+#SBATCH --ntasks=1
 #SBATCH --mem=10G
-#SBATCH --time=5:00:00
+#SBATCH --time=9:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
-#SBATCH --output=output_parallel_forward.txt
-#SBATCH --error=error_parallel_forward.txt
+#SBATCH --output=output_load_proxy_both.txt
+#SBATCH --error=error_load_proxy_both.txt
 
 module load gcc/9.4.0
 module load r/4.4.0
@@ -15,4 +15,4 @@ module load r/4.4.0
 cd $SLURM_SUBMIT_DIR
 export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
 
-R CMD BATCH parallel_forward.R
+R CMD BATCH load_proxy_both.R

### 2024-08-16 simResults_scenarioER/10.3_both/parallel_both.R

@@ -40,8 +40,8 @@ investigator.specified.covariates <-
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
 path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
-data <- readRDS(path)
-proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+data1 <- readRDS(path)
+proxy.list <- names(data1[, c(grep("^rec", names(data1), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+"))
@@ -56,16 +56,16 @@ full.formula <- as.formula(paste0("outcome~exposure+",
 n_cores <- 12  # Match this to the --ntasks value in your Slurm script
 
 proxy_select <- function(i) {
+  browser()
   path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_", i, ".rds")
-  data <- readRDS(path)
+  ds <<- readRDS(path)
   
   # found some id != idx
-  data$idx <- data$id
+  ds$idx <<- ds$id
+  ds$idx <- ds$id
   
-  data <- as.data.frame(data)
-  
-  initial.model <- glm(initial.formula, data = data, family = binomial)
-  full.model <- glm(full.formula, data = data, family = binomial)
+  initial.model <- glm(initial.formula, data = ds, family = binomial)
+  full.model <- glm(full.formula, data = ds, family = binomial)
   stepwise_both <- stepAIC(initial.model, 
                            scope = list(lower = initial.model, 
                                         upper = full.model), 
@@ -73,22 +73,13 @@ proxy_select <- function(i) {
   sel.variables <- all.vars(formula(stepwise_both))[-1]
   proxy_both <- proxy.list[proxy.list %in% sel.variables]
   proxyform <- paste0(proxy_both, collapse = "+")
-  proxy_both.data.i <- paste0("proxy_both.data.", i)
-  assign(proxy_both.data.i, proxyform)
+  proxy_both.data.ER.i <- paste0("proxy_both.data.ER.", i)
+  assign(proxy_both.data.ER.i, proxyform)
[…]

### 2024-08-16 simResults_scenarioER/6_ga/parallel_ga.R

@@ -39,53 +39,64 @@ investigator.specified.covariates <-
   )
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
 data <- readRDS(path)
 proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+"))
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
-full.formula <- as.formula(paste0("outcome~exposure+",
-                                  paste0(covarsTfull, collapse = "+"),
-                                  collapse = "+"))
+gaOpt <- function(vars, IV.train, DV.train) {
+  varNames <- colnames(IV.train) #getting names of all variables
+  selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
+  gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars
+  
+  gaDat <- cbind(gaSolutionData,DV.train) # combining selected variables with outcome variable
+  gaMod <- glm(DV.train ~ ., family = "binomial", data = gaDat) #build model
+  gaProb <- predict(gaMod, IV.train, type = "response") # get probabilities
+  gaPred <- ifelse(gaProb >= .8, 1, 0) # get predicted 0s and 1s
+  
+  ari <- adjustedRandIndex(gaPred, DV.train)
+  return(ari)
+}
 # ---------------------------------------------------------------
 
 n_cores <- 12  # Match this to the --ntasks value in your Slurm script
 
 proxy_select <- function(i) {
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
+  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_", i, ".rds")
[…]

### 2024-08-16 simResults_scenarioER/6_ga/parallel_ga.sh

@@ -2,12 +2,12 @@
 #SBATCH --account=st-mekarim-1
 #SBATCH --nodes=1
 #SBATCH --ntasks=12
-#SBATCH --mem=5G
-#SBATCH --time=5:00:00
+#SBATCH --mem=8G
+#SBATCH --time=14:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
-#SBATCH --output=output_parallel_backward.txt
-#SBATCH --error=error_parallel_backward.txt
+#SBATCH --output=output_parallel_ga.txt
+#SBATCH --error=error_parallel_ga.txt
 
 module load gcc/9.4.0
 module load r/4.4.0
@@ -15,4 +15,4 @@ module load r/4.4.0
 cd $SLURM_SUBMIT_DIR
 export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
 
-R CMD BATCH parallel_backward.R
+R CMD BATCH parallel_ga.R

### 2024-08-16 simResults_scenarioER/8_rf/rf.R

@@ -46,7 +46,7 @@ Y.form <- as.formula(paste0(c("outcome~ exposure",
 ### initialization before for-loop
 # 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
 a <- 1000
-b <- 0
+b <- 103
 
 RD_rf_ER <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
 num.proxy_rf <- c()

### 2024-08-16 simResults_scenarioER/8_rf/rf.sh

@@ -2,8 +2,8 @@
 #SBATCH --account=st-mekarim-1
 #SBATCH --nodes=1
 #SBATCH --ntasks=1
-#SBATCH --mem=5G
-#SBATCH --time=5:00:00
+#SBATCH --mem=10G
+#SBATCH --time=15:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
 #SBATCH --output=output_rf.txt

### 2024-08-16 simResults_scenarioER/load_simResultsER.R

@@ -1,14 +1,0 @@
-# 1_bross
-load("1_bross/bross.RData")
-
-# 2_hybrid
-load("2_hybrid/hybrid.RData")
-
-# 3_lasso
-load("3_lasso/lasso.RData")
-
-# 4_enet
-load("4_enet/enet.RData")
-
-# 7_xgboost
-load("7_xgboost/xgboost.RData")

### 2024-08-16 simResults_scenarioOR/10.1_forward/forward.R

@@ -12,6 +12,7 @@ library(penalizedSVM)
 library(xgboost)
 library(caret)
 library(randomForest)
+library(leaps)
 # ---------------------------------------------------------------
 
 ### global information
@@ -35,15 +36,12 @@ investigator.specified.covariates <-
   )
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_1.rds")
 data <- readRDS(path)
 proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+") )
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
 full.formula <- as.formula(paste0("outcome~exposure+",
                                   paste0(covarsTfull, collapse = "+"),
                                   collapse = "+"))
@@ -58,24 +56,21 @@ RD_forward <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a)
 num.proxy_forward <- c()
 # ---------------------------------------------------------------
 
-### scenario: for-loop generating RD & SE results
+### scenarioOR: for-loop generating RD & SE results
 set.seed(42)
 
-# Folder "scenario"
+# Folder "scenarioOR"
 for (i in (b+1):a) {
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
+  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_", i, ".rds")
   data <- readRDS(path)
   
   # found some id != idx
   data$idx <- data$id
   
-  initial.model <- glm(initial.formula, data = data, family = binomial)
-  full.model <- glm(full.formula, data = data, family = binomial)
-  stepwise_forward <- stepAIC(initial.model, 
[…]

### 2024-08-16 simResults_scenarioOR/10.1_forward/parallel_forward.R

@@ -1,92 +1,0 @@
-# try parallel
-library(parallel)
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-library(glmnet)
-
-# ---------------------------------------------------------------
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes" 
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_1.rds")
-data <- readRDS(path)
-proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
-covarsTfull <- c(investigator.specified.covariates, proxy.list)
-Y.form <- as.formula(paste0(c("outcome~ exposure", 
-                              covarsTfull), collapse = "+"))
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
-full.formula <- as.formula(paste0("outcome~exposure+",
-                                  paste0(covarsTfull, collapse = "+"),
-                                  collapse = "+"))
-# ---------------------------------------------------------------
-
-n_cores <- 12  # Match this to the --ntasks value in your Slurm script
-
-proxy_select <- function(i) {
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_", i, ".rds")
-  data <- readRDS(path)
-  
-  # found some id != idx
[…]

### 2024-08-16 simResults_scenarioOR/10.2_backward/backward.R

@@ -12,6 +12,7 @@ library(penalizedSVM)
 library(xgboost)
 library(caret)
 library(randomForest)
+library(leaps)
 # ---------------------------------------------------------------
 
 ### global information
@@ -35,7 +36,7 @@ investigator.specified.covariates <-
   )
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_1.rds")
 data <- readRDS(path)
 proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
@@ -58,24 +59,21 @@ RD_backward <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a
 num.proxy_backward <- c()
 # ---------------------------------------------------------------
 
-### scenario: for-loop generating RD & SE results
+### scenarioOR: for-loop generating RD & SE results
 set.seed(42)
 
-# Folder "scenario"
+# Folder "scenarioOR"
 for (i in (b+1):a) {
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
+  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_", i, ".rds")
   data <- readRDS(path)
   
   # found some id != idx
   data$idx <- data$id
-  initial.model <- glm(initial.formula, data = data, family = binomial)
-  full.model <- glm(full.formula, data = data, family = binomial)
-  stepwise_backward <- stepAIC(full.model, 
-                               scope = list(lower = initial.model, 
-                                            upper = full.model), 
-                               direction = "backward")
-  
-  sel.variables <- all.vars(formula(stepwise_backward))[-1]
+
+  stepwise_backward <- regsubsets(full.formula, data = data, method = "backward", nvmax = length(proxy.list), nbest = 10)
+  summary_stepwise <- summary(stepwise_backward)
[…]

### 2024-08-16 simResults_scenarioOR/10.3_both/load_proxy_both.R

@@ -1,0 +1,117 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes"
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_1.rds")
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+a <- 1000
+b <- 0
+
+RD_both_OR <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_both_OR <- c()
+# ---------------------------------------------------------------
+
+### scenarioOR: for-loop generating RD & SE results
+set.seed(42)
+
+for (i in (b+1):a) {
+  path_proxy <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenarioOR/10.3_both/proxy_both.data.", i, ".RData")
+  
+  if (file.exists(path_proxy)) {
+    proxyform_name <- load(path_proxy)
+    proxyform <- get(proxyform_name)
[…]

### 2024-08-16 simResults_scenarioOR/10.3_both/parallel_both.R

@@ -40,8 +40,8 @@ investigator.specified.covariates <-
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
 path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_1.rds")
-data <- readRDS(path)
-proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+data1 <- readRDS(path)
+proxy.list <- names(data1[, c(grep("^rec", names(data1), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+"))
@@ -56,16 +56,16 @@ full.formula <- as.formula(paste0("outcome~exposure+",
 n_cores <- 12  # Match this to the --ntasks value in your Slurm script
 
 proxy_select <- function(i) {
+  browser()
   path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_", i, ".rds")
-  data <- readRDS(path)
+  ds <<- readRDS(path)
   
   # found some id != idx
-  data$idx <- data$id
+  ds$idx <<- ds$id
+  ds$idx <- ds$id
   
-  data <- as.data.frame(data)
-  
-  initial.model <- glm(initial.formula, data = data, family = binomial)
-  full.model <- glm(full.formula, data = data, family = binomial)
+  initial.model <- glm(initial.formula, data = ds, family = binomial)
+  full.model <- glm(full.formula, data = ds, family = binomial)
   stepwise_both <- stepAIC(initial.model, 
                            scope = list(lower = initial.model, 
                                         upper = full.model), 
@@ -73,22 +73,13 @@ proxy_select <- function(i) {
   sel.variables <- all.vars(formula(stepwise_both))[-1]
   proxy_both <- proxy.list[proxy.list %in% sel.variables]
   proxyform <- paste0(proxy_both, collapse = "+")
-  proxy_both.data.i <- paste0("proxy_both.data.", i)
-  assign(proxy_both.data.i, proxyform)
+  proxy_both.data.OR.i <- paste0("proxy_both.data.OR.", i)
+  assign(proxy_both.data.OR.i, proxyform)
[…]

### 2024-08-16 simResults_scenarioOR/10.3_both/parallel_both.sh

@@ -3,7 +3,7 @@
 #SBATCH --nodes=1
 #SBATCH --ntasks=12
 #SBATCH --mem=10G
-#SBATCH --time=5:00:00
+#SBATCH --time=9:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
 #SBATCH --output=output_parallel_both.txt

### 2024-08-16 simResults_scenarioOR/6_ga/parallel_ga.R

@@ -40,17 +40,24 @@ investigator.specified.covariates <-
 covform <- paste0(investigator.specified.covariates, collapse = "+")
 out.formula <- as.formula(paste0("outcome", "~", "exposure"))
 path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioOR/data_1.rds")
-data1 <- readRDS(path)
-proxy.list <- names(data1[, c(grep("^rec", names(data1), value = TRUE))])
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
 covarsTfull <- c(investigator.specified.covariates, proxy.list)
 Y.form <- as.formula(paste0(c("outcome~ exposure", 
                               covarsTfull), collapse = "+"))
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
-full.formula <- as.formula(paste0("outcome~exposure+",
-                                  paste0(covarsTfull, collapse = "+"),
-                                  collapse = "+"))
+gaOpt <- function(vars, IV.train, DV.train) {
+  varNames <- colnames(IV.train) #getting names of all variables
+  selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
+  gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars
+  
+  gaDat <- cbind(gaSolutionData,DV.train) # combining selected variables with outcome variable
+  gaMod <- glm(DV.train ~ ., family = "binomial", data = gaDat) #build model
+  gaProb <- predict(gaMod, IV.train, type = "response") # get probabilities
+  gaPred <- ifelse(gaProb >= .8, 1, 0) # get predicted 0s and 1s
+  
+  ari <- adjustedRandIndex(gaPred, DV.train)
+  return(ari)
+}
 # ---------------------------------------------------------------
 
 n_cores <- 12  # Match this to the --ntasks value in your Slurm script
@@ -61,35 +68,36 @@ proxy_select <- function(i) {
   
   # found some id != idx
   data$idx <- data$id
+  covar.mat <- model.matrix(Y.form, data = data)[,-1]
   
-  data <- as.data.frame(data)
+  ga.fit <- ga(fitness = function(vars)
+    gaOpt(vars = vars, 
[…]

### 2024-08-16 simResults_scenarioOR/6_ga/parallel_ga.sh

@@ -2,12 +2,12 @@
 #SBATCH --account=st-mekarim-1
 #SBATCH --nodes=1
 #SBATCH --ntasks=12
-#SBATCH --mem=10G
-#SBATCH --time=5:00:00
+#SBATCH --mem=8G
+#SBATCH --time=14:00:00
 #SBATCH --mail-user=leiyang1@student.ubc.ca
 #SBATCH --mail-type=ALL
-#SBATCH --output=output_parallel_forward.txt
-#SBATCH --error=error_parallel_forward.txt
+#SBATCH --output=output_parallel_ga.txt
+#SBATCH --error=error_parallel_ga.txt
 
 module load gcc/9.4.0
 module load r/4.4.0
@@ -15,4 +15,4 @@ module load r/4.4.0
 cd $SLURM_SUBMIT_DIR
 export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
 
-R CMD BATCH parallel_forward.R
+R CMD BATCH parallel_ga.R

### 2024-08-16 simResults_scenarioOR/8_rf/rf.R

@@ -46,7 +46,7 @@ Y.form <- as.formula(paste0(c("outcome~ exposure",
 ### initialization before for-loop
 # 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
 a <- 1000
-b <- 0
+b <- 94
 
 RD_rf_OR <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
 num.proxy_rf <- c()

### 2024-08-16 simResults_scenario/6_ga/load_proxy_ga.R
results tables by method ga

@@ -1,0 +1,116 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes"
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+a <- 1000
+b <- 0
+
+RD_ga <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_ga <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+
+for (i in (b+1):a) {
+  path_proxy <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenario/6_ga/proxy_ga.data.", i, ".RData")
+  
+  if (file.exists(path_proxy)) {
+    proxyform_name <- load(path_proxy)
[…]

### 2024-08-16 simResults_scenario/6_ga/load_proxy_ga.sh

@@ -1,0 +1,18 @@
+#!/bin/bash
+#SBATCH --account=st-mekarim-1
+#SBATCH --nodes=1
+#SBATCH --ntasks=1
+#SBATCH --mem=2G
+#SBATCH --time=2:00:00
+#SBATCH --mail-user=leiyang1@student.ubc.ca
+#SBATCH --mail-type=ALL
+#SBATCH --output=output_load_proxy_ga.txt
+#SBATCH --error=error_load_proxy_ga.txt
+
+module load gcc/9.4.0
+module load r/4.4.0
+
+cd $SLURM_SUBMIT_DIR
+export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
+
+R CMD BATCH load_proxy_ga.R

### 2024-08-16 simResults_scenarioER/6_ga/load_proxy_ga.R

@@ -1,0 +1,116 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes"
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+a <- 1000
+b <- 0
+
+RD_ga_ER <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_ga_ER <- c()
+# ---------------------------------------------------------------
+
+### scenarioER: for-loop generating RD & SE results
+set.seed(42)
+
+for (i in (b+1):a) {
+  path_proxy <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenarioER/6_ga/proxy_ga.data.", i, ".RData")
+  
+  if (file.exists(path_proxy)) {
[…]

### 2024-08-16 simResults_scenarioOR/6_ga/load_proxy_ga.R

@@ -1,0 +1,116 @@
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes"
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenarioER/data_1.rds")
+data <- readRDS(path)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+a <- 1000
+b <- 0
+
+RD_ga_OR <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_ga_OR <- c()
+# ---------------------------------------------------------------
+
+### scenarioER: for-loop generating RD & SE results
+set.seed(42)
+
+for (i in (b+1):a) {
+  path_proxy <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenarioOR/6_ga/proxy_ga.data.", i, ".RData")
+  
+  if (file.exists(path_proxy)) {
[…]

### 2024-08-16 performance.Rmd
performance

---
title: "Summary of Performance Measures"
author: "Ehsan"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
  pdf_document:
    toc: true
    toc_depth: 2
---

## Read data

- Keep the data in the `results` folder
- make sure working directory is updated

```{r data}
library(rsimsum)
library(dplyr)
load("simResults_scenario/3_lasso/lasso.RData")
est.LASSO <- RD_lasso
est.LASSO$model <- "LASSO"

load("simResults_scenario/4_enet/enet.RData")
est.Enet <- RD_enet
est.Enet$model <- "Enet"

load("simResults_scenario/6_ga/ga.RData")
est.GA <- RD_ga
est.GA$model <- "GA"

```

## Combine data into 1 data

Make sure table provides same numbers for all model. For full analysis, all should be 1,000.

```{r bind}
est <- rbind(est.LASSO, est.Enet, est.GA) 
est$model <- as.factor(est$model)
table(est$model)
names(est)
```

## Analyze simulated data

```{r sim}
theta <- 0 # for RD or ATE; this would be 1 for OR
s1 <- simsum(data = est, estvarname = "RD", true = theta, se = "SE", 
             methodvar = "model", ref = "LASSO", x = TRUE)
ss1 <- summary(s1)
ss1
```

## Present results in a Table

change `kable(final_df, format = "html" ...` to `kable(final_df, format = "latex"` to get the latex codes.

```{r table, warning=FALSE, message=FALSE, eval=FALSE}
library(dplyr)
library(tidyr)
library(kableExtra)

extract_metric <- function(metric) {
  # Function to extract and format metric data
  metric_data <- ss1$summ[ss1$summ$stat == metric, c("model", "est", "mcse")]
  metric_data$est <- sprintf("%.4f", metric_data$est)
  metric_data$mcse <- sprintf("%.4f", metric_data$mcse)
  metric_data$formatted <- paste0(metric_data$est, " (", metric_data$mcse, ")")
  metric_data <- metric_data[, c("model", "formatted")]
  names(metric_data) <- c("model", metric)
  return(metric_data)
}

metrics <- c("bias", "empse", "mse", "modelse", "cover", "becover")
formatted_metrics <- lapply(metrics, extract_metric)
combined_df <- Reduce(function(x, y) merge(x, y, by = "model"), formatted_metrics)
final_df <- combined_df %>%
  gather(key = "metric", value = "value", -model) %>%
  spread(key = "model", value = "value")
final_df$metric <- recode(final_df$metric,
                          bias = "Bias",
                          empse = "Empirical SE",
                          mse = "MSE",
                          modelse = "Model-based SE",
                          cover = "Coverage",
                          becover = "Bias-eliminated Coverage")
final_df <- final_df %>%
  arrange(factor(metric, levels = c("Bias", "Empirical SE", "MSE", "Model-based SE", "Coverage", "Bias-eliminated Coverage"))) %>%
  rename(`Performance Measure` = metric)
names(final_df) <- c("Performance Measure", "MARS", "PS")
kable(final_df, format = "html", booktabs = TRUE, linesep = "", col.names = c("Performance Measure", "MARS", "PS"),
      caption = "Summary of Performance Measures") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)
```

## Present results in Figures

All figures also saved in the `images` folder.

```{r plots, warning=FALSE, message=FALSE}
require(ggplot2)

custom_theme <- theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "white"),  
    panel.grid.major = element_blank(),              
    panel.grid.minor = element_blank(),              
    legend.position = "bottom"                      
  )

unique(ss1$summ$stat)
autoplot(s1, type = "lolly", stats = "nsim")+ custom_theme
autoplot(s1, type = "lolly", stats = "bias")+ custom_theme  + labs(x = "Bias")
ggsave(filename = "images/bias.png")
autoplot(s1, type = "lolly", stats = "relerror")+ custom_theme  + labs(x = "Relative % error")
autoplot(s1, type = "lolly", stats = "cover")+ custom_theme  + labs(x = "95% coverage")
ggsave(filename = "images/cover.png")
autoplot(s1, type = "lolly", stats = "becover")+ custom_theme  + labs(x = "95% bias-eliminated coverage")
ggsave(filename = "images/becover.png")
autoplot(s1, type = "lolly", stats = "modelse")+ custom_theme + labs(x = "Model SE")
ggsave(filename = "images/modelse.png")
autoplot(s1, type = "lolly", stats = "empse")+ custom_theme  + labs(x = "Empirical SE")
ggsave(filename = "images/empse.png")
autoplot(s1, type = "lolly", stats = "mse")+ custom_theme + labs(x = "MSE")
autoplot(s1, type = "lolly", stats = "relprec")+ custom_theme
autoplot(s1, type = "lolly", stats = "power")+ custom_theme
zip_plot <- autoplot(s1, type = "zip", zoom = 0.5) + custom_theme
dashed_line <- geom_hline(yintercept = 0.95, linetype = "dashed", color = "blue")
zip_plot + 
  annotate("segment", x = -Inf, xend = Inf, y = 0.95, yend = 0.95, linetype = "dashed", color = "blue") +
  dashed_line
ggsave(filename = "images/zip.png")
```

## SE comparison

```{r plotSE, warning=FALSE, message=FALSE}
library(reshape2)
library(tidyr)

data <- s1$summ %>%
  filter(stat %in% c("empse", "modelse")) %>%
  select(model, stat, est) %>%
  pivot_wider(names_from = stat, values_from = est)

melted_data <- data %>%
  pivot_longer(cols = -model, names_to = "variable", values_to = "value")

ggplot(melted_data, aes(x = model, y = value, fill = factor(variable, levels = c("empse", "modelse")))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  coord_flip() + # Makes the bar plots horizontal
  labs(y = "SE", x = "model", fill = "SE") +
  scale_fill_manual(
    values = c("empse" = "lightgray", "modelse" = "darkgray"), 
    labels = c("empse" = "Empirical SE", "modelse" = "Model SE")
  ) +
  custom_theme
ggsave(filename = "images/secompare.png")
```

### 2024-08-21 simResults_scenario/8_rf/comb_results_rf.R
RD table for  rf

@@ -1,0 +1,21 @@
+a <- 1000
+b <- 0
+RD_rf <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+
+for (i in (b+1):a) {
+  path_result <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenario/8_rf/results_rf.", i, ".RData")
+  
+  if (file.exists(path_result)) {
+    result_name <- load(path_result)
+    result <- get(result_name)
+    
+    RD_rf[i,] <- result[2:4]
+    rownames(RD_rf)[i] <- result[1]
+  }
+}
+
+num.proxy_rf <- RD_rf$numProxy
+avg.num.proxy_ga <- mean(num.proxy_rf)
+
+save(RD_rf, num.proxy_rf, avg.num.proxy_rf,
+     file = "/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenario/8_rf/rf.RData")

### 2024-08-21 simResults_scenario/8_rf/comb_results_rf.sh

@@ -1,0 +1,18 @@
+#!/bin/bash
+#SBATCH --account=st-mekarim-1
+#SBATCH --nodes=1
+#SBATCH --ntasks=1
+#SBATCH --mem=2G
+#SBATCH --time=2:00:00
+#SBATCH --mail-user=leiyang1@student.ubc.ca
+#SBATCH --mail-type=ALL
+#SBATCH --output=output_comb_results_rf.txt
+#SBATCH --error=error_comb_results_rf.txt
+
+module load gcc/9.4.0
+module load r/4.4.0
+
+cd $SLURM_SUBMIT_DIR
+export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
+
+R CMD BATCH comb_results_rf.R

### 2024-08-21 simResults_scenarioER/8_rf/comb_results_rf.R

@@ -1,0 +1,21 @@
+a <- 1000
+b <- 0
+RD_rf_ER <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+
+for (i in (b+1):a) {
+  path_result <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenarioER/8_rf/results_rf.", i, ".RData")
+  
+  if (file.exists(path_result)) {
+    result_name <- load(path_result)
+    result <- get(result_name)
+    
+    RD_rf_ER[i,] <- result[2:4]
+    rownames(RD_rf_ER)[i] <- result[1]
+  }
+}
+
+num.proxy_rf_ER <- RD_rf_ER$numProxy
+avg.num.proxy_rf_ER <- mean(num.proxy_rf_ER)
+
+save(RD_rf_ER, num.proxy_rf_ER, avg.num.proxy_rf_ER,
+     file = "/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenarioER/8_rf/rf.RData")

### 2024-08-21 simResults_scenarioOR/8_rf/comb_results_rf.R

@@ -1,0 +1,21 @@
+a <- 1000
+b <- 0
+RD_rf_OR <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+
+for (i in (b+1):a) {
+  path_result <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenarioOR/8_rf/results_rf.", i, ".RData")
+  
+  if (file.exists(path_result)) {
+    result_name <- load(path_result)
+    result <- get(result_name)
+    
+    RD_rf_OR[i,] <- result[2:4]
+    rownames(RD_rf_OR)[i] <- result[1]
+  }
+}
+
+num.proxy_rf_OR <- RD_rf_OR$numProxy
+avg.num.proxy_rf_OR <- mean(num.proxy_rf_OR)
+
+save(RD_rf_OR, num.proxy_rf_OR, avg.num.proxy_rf_OR,
+     file = "/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenarioOR/8_rf/rf.RData")

### 2024-08-21 doc/performance.Rmd
performance for all 3 scenarios

---
title: "Summary of Performance Measures for Normal Scenario"
author: "Ehsan, Yang"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
  pdf_document:
    toc: true
    toc_depth: 2
---

## Read data

- Keep the data in the `results` folder
- make sure working directory is updated

```{r data}
library(rsimsum)
library(dplyr)
library(tidyr)
library(kableExtra)

load("results/scenario/bross.RData")
load("results/scenario/hybrid.RData")
load("results/scenario/lasso.RData")
load("results/scenario/enet.RData")
load("results/scenario/ga.RData")
load("results/scenario/xgboost.RData")
load("results/scenario/rf.RData")
load("results/scenario/forward.RData")
load("results/scenario/backward.RData")

ind <- which(!is.na(RD_bross[,1]))

est_bross    <- RD_bross[ind,]
est_hybird   <- RD_hybrid[ind,]
est_lasso    <- RD_lasso[ind,]
est_enet     <- RD_enet[ind,]
est_ga       <- RD_ga[ind,]
est_xgboost  <- RD_xgboost[ind,]
est_rf       <- RD_rf[ind,]
est_forward  <- RD_forward[ind,]
est_backward <- RD_backward[ind,]

est_bross$model    <- "bross"
est_hybird$model   <- "hybrid"
est_lasso$model    <- "lasso"
est_enet$model     <- "enet"
est_ga$model       <- "ga"
est_xgboost$model  <- "xgboost"
est_rf$model       <- "rf"
est_forward$model  <- "forward"
est_backward$model <- "backward"
```

## Combine data into 1 data

Make sure table provides same numbers for all model. For full analysis, all should be 766.

```{r bind}
est <- rbind(est_bross, est_hybird, est_lasso, est_enet, 
             est_ga, est_xgboost, est_rf,
             est_forward, est_backward)

est$model <- as.factor(est$model)
levels(est$model) <- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
levels <- levels(est$model)
```

## Analyze simulated data

```{r sim}
theta <- 0
s1 <- simsum(data = est, estvarname = "RD", true = theta, se = "SE", 
             methodvar = "model", ref = "bross", x = TRUE)
ss1 <- summary(s1)
ss1
```

## Present results in a Table

change `kable(final_df, format = "html" ...` to `kable(final_df, format = "latex"` to get the latex codes.

```{r table, warning=FALSE, message=FALSE, eval=FALSE}
extract_metric <- function(metric) {
  # Function to extract and format metric data
  metric_data <- ss1$summ[ss1$summ$stat == metric, c("model", "est", "mcse")]
  metric_data$est <- sprintf("%.4f", metric_data$est)
  metric_data$mcse <- sprintf("%.4f", metric_data$mcse)
  metric_data$formatted <- paste0(metric_data$est, " (", metric_data$mcse, ")")
  metric_data <- metric_data[, c("model", "formatted")]
  names(metric_data) <- c("model", metric)
  return(metric_data)
}

metrics <- c("bias", "empse", "mse", "modelse", "cover", "becover")
formatted_metrics <- lapply(metrics, extract_metric)
combined_df <- Reduce(function(x, y) merge(x, y, by = "model"), formatted_metrics)
final_df <- combined_df %>%
  gather(key = "metric", value = "value", -model) %>%
  spread(key = "model", value = "value")
final_df$metric <- recode(final_df$metric,
                          bias = "Bias",
                          empse = "Empirical SE",
                          mse = "MSE",
                          modelse = "Model-based SE",
                          cover = "Coverage",
                          becover = "Bias-eliminated Coverage")
final_df <- final_df %>%
  arrange(factor(metric, levels = c("Bias", "Empirical SE", "MSE", "Model-based SE", "Coverage", "Bias-eliminated Coverage"))) %>%
  rename(`Performance Measure` = metric)
names(final_df) <- c("Performance Measure", levels)
kable(final_df, format = "html", booktabs = TRUE, linesep = "", col.names = c("Performance Measure", levels),
      caption = "Summary of Performance Measures") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)
```

## Present results in Figures

All figures also saved in the `images` folder.

```{r plots, warning=FALSE, message=FALSE}
require(ggplot2)

custom_theme <- theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "white"),  
    panel.grid.major = element_blank(),              
    panel.grid.minor = element_blank(),              
    legend.position = "bottom"                      
  )

unique(ss1$summ$stat)
autoplot(s1, type = "lolly", stats = "nsim")+ custom_theme
autoplot(s1, type = "lolly", stats = "bias")+ custom_theme  + labs(x = "Bias")
ggsave(filename = "images/scenario/bias.png")
autoplot(s1, type = "lolly", stats = "relerror")+ custom_theme  + labs(x = "Relative % error")
autoplot(s1, type = "lolly", stats = "cover")+ custom_theme  + labs(x = "95% coverage")
ggsave(filename = "images/scenario/cover.png")
autoplot(s1, type = "lolly", stats = "becover")+ custom_theme  + labs(x = "95% bias-eliminated coverage")
ggsave(filename = "images/scenario/becover.png")
autoplot(s1, type = "lolly", stats = "modelse")+ custom_theme + labs(x = "Model SE")
ggsave(filename = "images/scenario/modelse.png")
autoplot(s1, type = "lolly", stats = "empse")+ custom_theme  + labs(x = "Empirical SE")
ggsave(filename = "images/scenario/empse.png")
autoplot(s1, type = "lolly", stats = "mse")+ custom_theme + labs(x = "MSE")
autoplot(s1, type = "lolly", stats = "relprec")+ custom_theme
autoplot(s1, type = "lolly", stats = "power")+ custom_theme
zip_plot <- autoplot(s1, type = "zip", zoom = 0.5) + custom_theme
dashed_line <- geom_hline(yintercept = 0.95, linetype = "dashed", color = "blue")
zip_plot + 
  annotate("segment", x = -Inf, xend = Inf, y = 0.95, yend = 0.95, linetype = "dashed", color = "blue") +
  dashed_line
ggsave(filename = "images/scenario/zip.png")
```

## SE comparison

```{r plotSE, warning=FALSE, message=FALSE}
library(reshape2)
library(tidyr)

data <- s1$summ %>%
  filter(stat %in% c("empse", "modelse")) %>%
  select(model, stat, est) %>%
  pivot_wider(names_from = stat, values_from = est)

melted_data <- data %>%
  pivot_longer(cols = -model, names_to = "variable", values_to = "value")

ggplot(melted_data, aes(x = model, y = value, fill = factor(variable, levels = c("empse", "modelse")))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  coord_flip() + # Makes the bar plots horizontal
  labs(y = "SE", x = "model", fill = "SE") +
  scale_fill_manual(
    values = c("empse" = "lightgray", "modelse" = "darkgray"), 
    labels = c("empse" = "Empirical SE", "modelse" = "Model SE")
  ) +
  custom_theme
ggsave(filename = "images/scenario/secompare.png")
```

### 2024-08-21 doc/performanceER.Rmd
performance for all 3 scenarios

--- 2024-08-21 doc/performance.Rmd
@@
 ---
-title: "Summary of Performance Measures for Normal Scenario"
+title: "Summary of Performance Measures for Scenario ER"
 author: "Ehsan, Yang"
@@
 
-load("results/scenario/bross.RData")
-load("results/scenario/hybrid.RData")
-load("results/scenario/lasso.RData")
-load("results/scenario/enet.RData")
-load("results/scenario/ga.RData")
-load("results/scenario/xgboost.RData")
-load("results/scenario/rf.RData")
-load("results/scenario/forward.RData")
-load("results/scenario/backward.RData")
+load("results/scenarioER/bross.RData")
+load("results/scenarioER/hybrid.RData")
+load("results/scenarioER/lasso.RData")
+load("results/scenarioER/enet.RData")
+load("results/scenarioER/ga.RData")
+load("results/scenarioER/xgboost.RData")
+load("results/scenarioER/rf.RData")
+load("results/scenarioER/forward.RData")
+load("results/scenarioER/backward.RData")
 
@@
 autoplot(s1, type = "lolly", stats = "bias")+ custom_theme  + labs(x = "Bias")
-ggsave(filename = "images/scenario/bias.png")
+ggsave(filename = "images/scenarioER/bias.png")
 autoplot(s1, type = "lolly", stats = "relerror")+ custom_theme  + labs(x = "Relative % error")
 autoplot(s1, type = "lolly", stats = "cover")+ custom_theme  + labs(x = "95% coverage")
-ggsave(filename = "images/scenario/cover.png")
+ggsave(filename = "images/scenarioER/cover.png")
 autoplot(s1, type = "lolly", stats = "becover")+ custom_theme  + labs(x = "95% bias-eliminated coverage")
-ggsave(filename = "images/scenario/becover.png")
+ggsave(filename = "images/scenarioER/becover.png")
 autoplot(s1, type = "lolly", stats = "modelse")+ custom_theme + labs(x = "Model SE")
-ggsave(filename = "images/scenario/modelse.png")
+ggsave(filename = "images/scenarioER/modelse.png")
 autoplot(s1, type = "lolly", stats = "empse")+ custom_theme  + labs(x = "Empirical SE")
-ggsave(filename = "images/scenario/empse.png")
+ggsave(filename = "images/scenarioER/empse.png")
 autoplot(s1, type = "lolly", stats = "mse")+ custom_theme + labs(x = "MSE")
@@
   dashed_line
-ggsave(filename = "images/scenario/zip.png")
+ggsave(filename = "images/scenarioER/zip.png")
 ```
@@
   custom_theme
-ggsave(filename = "images/scenario/secompare.png")
+ggsave(filename = "images/scenarioER/secompare.png")
 ```

### 2024-08-21 doc/performanceOR.Rmd
performance for all 3 scenarios

--- 2024-08-21 doc/performance.Rmd
@@
 ---
-title: "Summary of Performance Measures for Normal Scenario"
+title: "Summary of Performance Measures for Scenario OR"
 author: "Ehsan, Yang"
@@
 
-load("results/scenario/bross.RData")
-load("results/scenario/hybrid.RData")
-load("results/scenario/lasso.RData")
-load("results/scenario/enet.RData")
-load("results/scenario/ga.RData")
-load("results/scenario/xgboost.RData")
-load("results/scenario/rf.RData")
-load("results/scenario/forward.RData")
-load("results/scenario/backward.RData")
+load("results/scenarioOR/bross.RData")
+load("results/scenarioOR/hybrid.RData")
+load("results/scenarioOR/lasso.RData")
+load("results/scenarioOR/enet.RData")
+load("results/scenarioOR/ga.RData")
+load("results/scenarioOR/xgboost.RData")
+load("results/scenarioOR/rf.RData")
+load("results/scenarioOR/forward.RData")
+load("results/scenarioOR/backward.RData")
 
@@
 autoplot(s1, type = "lolly", stats = "bias")+ custom_theme  + labs(x = "Bias")
-ggsave(filename = "images/scenario/bias.png")
+ggsave(filename = "images/scenarioOR/bias.png")
 autoplot(s1, type = "lolly", stats = "relerror")+ custom_theme  + labs(x = "Relative % error")
 autoplot(s1, type = "lolly", stats = "cover")+ custom_theme  + labs(x = "95% coverage")
-ggsave(filename = "images/scenario/cover.png")
+ggsave(filename = "images/scenarioOR/cover.png")
 autoplot(s1, type = "lolly", stats = "becover")+ custom_theme  + labs(x = "95% bias-eliminated coverage")
-ggsave(filename = "images/scenario/becover.png")
+ggsave(filename = "images/scenarioOR/becover.png")
 autoplot(s1, type = "lolly", stats = "modelse")+ custom_theme + labs(x = "Model SE")
-ggsave(filename = "images/scenario/modelse.png")
+ggsave(filename = "images/scenarioOR/modelse.png")
 autoplot(s1, type = "lolly", stats = "empse")+ custom_theme  + labs(x = "Empirical SE")
-ggsave(filename = "images/scenario/empse.png")
+ggsave(filename = "images/scenarioOR/empse.png")
 autoplot(s1, type = "lolly", stats = "mse")+ custom_theme + labs(x = "MSE")
@@
   dashed_line
-ggsave(filename = "images/scenario/zip.png")
+ggsave(filename = "images/scenarioOR/zip.png")
 ```
@@
   custom_theme
-ggsave(filename = "images/scenario/secompare.png")
+ggsave(filename = "images/scenarioOR/secompare.png")
 ```

### 2024-08-21 Simulation Attemps/Attempt 0/bross.R

@@ -1,147 +1,0 @@
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(tidyverse)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-# ---------------------------------------------------------------
-
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes" 
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-# ---------------------------------------------------------------
-
-### initialization before for-loop
-# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
-a <- 1000
-
-RD_bross <- data.frame(RD = numeric(), SE = numeric())
-num.proxy_bross <- c()
-errors <- c()
-# ---------------------------------------------------------------
-
-### scenario: for-loop generating RD & SE results
-set.seed(42)
-set.seed(42)
-
-# Folder "scenario"
-for (i in 1:a) {
-  path <- paste0("../../simData/scenario/data_", i, ".rds")
-  data <- readRDS(path)
-  
-  # found some id != idx
-  data$idx <- data$id
-  
-  # Feature Selection Method 1: Bross Formula
-  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]
-  
-  bross.list <- tryCatch({
-    get_prioritised_covariates(df = proxy.df,
-                               patientIdVarname = "idx", 
-                               exposureVector = data$exposure,
-                               outcomeVector = data$outcome,
[…]

### 2024-08-21 Simulation Attemps/Attempt 0/bross.sh

@@ -1,13 +1,0 @@
-#!/bin/bash
-#SBATCH --account=st-mekarim-1
-#SBATCH --nodes=1
-#SBATCH --ntasks=1
-#SBATCH --cpus-per-task=32
-#SBATCH --mem=0
-#SBATCH --time=0-20:00:00
-#SBATCH --mail-user=leiyang1@student.ubc.ca
-#SBATCH --mail-type=ALL
-module load gcc/9.4.0
-module load r/4.4.0
-
-R CMD BATCH bross.R

### 2024-08-21 Simulation Attemps/Attempt 1/bross1.R

@@ -1,149 +1,0 @@
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(tidyverse)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-# ---------------------------------------------------------------
-
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes" 
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-# ---------------------------------------------------------------
-
-### initialization before for-loop
-# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
-a <- 1000
-
-RD_bross <- data.frame(RD = numeric(), SE = numeric())
-num.proxy_bross <- c()
-errors <- c()
-# ---------------------------------------------------------------
-
-### scenario: for-loop generating RD & SE results
-set.seed(42)
-set.seed(42)
-
-# Folder "scenario"
-for (i in 1:a) {
-  path <- paste0("../../simData/scenario/data_", i, ".rds")
-  data <- readRDS(path)
-  
-  # found some id != idx
-  data$idx <- data$id
-  
-  # Feature Selection Method 1: Bross Formula
-  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]
-  
-  bross.list <- tryCatch({
-    get_prioritised_covariates(df = proxy.df,
-                               patientIdVarname = "idx", 
-                               exposureVector = data$exposure,
-                               outcomeVector = data$outcome,
[…]

### 2024-08-21 Simulation Attemps/Attempt 1/bross1.sh

@@ -1,13 +1,0 @@
-#!/bin/bash
-#SBATCH --account=st-mekarim-1
-#SBATCH --nodes=1
-#SBATCH --ntasks=1
-#SBATCH --cpus-per-task=32
-#SBATCH --mem=0
-#SBATCH --time=0-20:00:00
-#SBATCH --mail-user=leiyang1@student.ubc.ca
-#SBATCH --mail-type=ALL
-module load gcc/9.4.0
-module load r/4.4.0
-export R_LIBS=/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4
-R CMD BATCH bross1.R

### 2024-08-21 Simulation Attemps/Attempt 2/bross2.R

@@ -1,153 +1,0 @@
-
-setwd("/home/leiyang1/hdPS_ProxySelect/simResults_scenario/1_bross")
-
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(tidyverse)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-# ---------------------------------------------------------------
-
-setwd("/home/leiyang1/hdPS_ProxySelect/simResults_scenario/1_bross")
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes" 
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-# ---------------------------------------------------------------
-
-### initialization before for-loop
-# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
-a <- 1000
-
-RD_bross <- data.frame(RD = numeric(), SE = numeric())
-num.proxy_bross <- c()
-errors <- c()
-# ---------------------------------------------------------------
-
-### scenario: for-loop generating RD & SE results
-set.seed(42)
-set.seed(42)
-
-# Folder "scenario"
-for (i in 1:a) {
-  path <- paste0("../../simData/scenario/data_", i, ".rds")
-  data <- readRDS(path)
-  
-  # found some id != idx
-  data$idx <- data$id
-  
-  # Feature Selection Method 1: Bross Formula
-  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]
-  
-  bross.list <- tryCatch({
-    get_prioritised_covariates(df = proxy.df,
[…]

### 2024-08-21 Simulation Attemps/Attempt 2/bross2.sh

@@ -1,13 +1,0 @@
-#!/bin/bash
-#SBATCH --account=st-mekarim-1
-#SBATCH --nodes=1
-#SBATCH --ntasks=1
-#SBATCH --cpus-per-task=32
-#SBATCH --mem=0
-#SBATCH --time=0-20:00:00
-#SBATCH --mail-user=leiyang1@student.ubc.ca
-#SBATCH --mail-type=ALL
-module load gcc/9.4.0
-module load r/4.4.0
-
-R CMD BATCH bross2.R

### 2024-08-21 Simulation Attemps/Attempt 3/bross3.R

@@ -1,150 +1,0 @@
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(tidyverse)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-# ---------------------------------------------------------------
-
-setwd("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenario/1_bross")
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes" 
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-# ---------------------------------------------------------------
-
-### initialization before for-loop
-# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
-a <- 1000
-
-RD_bross <- data.frame(RD = numeric(), SE = numeric())
-num.proxy_bross <- c()
-errors <- c()
-# ---------------------------------------------------------------
-
-### scenario: for-loop generating RD & SE results
-set.seed(42)
-set.seed(42)
-
-# Folder "scenario"
-for (i in 1:a) {
-  path <- paste0("../../simData/scenario/data_", i, ".rds")
-  data <- readRDS(path)
-  
-  # found some id != idx
-  data$idx <- data$id
-  
-  # Feature Selection Method 1: Bross Formula
-  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]
-  
-  bross.list <- tryCatch({
-    get_prioritised_covariates(df = proxy.df,
-                               patientIdVarname = "idx", 
[…]

### 2024-08-21 Simulation Attemps/Attempt 3/bross3.sh

@@ -1,13 +1,0 @@
-#!/bin/bash
-#SBATCH --account=st-mekarim-1
-#SBATCH --nodes=1
-#SBATCH --ntasks=1
-#SBATCH --cpus-per-task=32
-#SBATCH --mem=0
-#SBATCH --time=0-20:00:00
-#SBATCH --mail-user=leiyang1@student.ubc.ca
-#SBATCH --mail-type=ALL
-module load gcc/9.4.0
-module load r/4.4.0
-
-R CMD BATCH bross3.R

### 2024-08-22 doc/performance.Rmd
fixed some error / edit Performance.Rmd, PerformanceER.Rmd, PerformanceOR.Rmd

@@
 library(kableExtra)
+library(reshape2)
+library(ggplot2)
 
@@
 est$model <- as.factor(est$model)
-levels(est$model) <- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
-levels <- levels(est$model)
+levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
+est$model <- factor(est$model, levels = levels)
+levels(est$model)
 ```
@@
 ```{r plots, warning=FALSE, message=FALSE}
-require(ggplot2)
-
 custom_theme <- theme_minimal() + 
@@
 ```{r plotSE, warning=FALSE, message=FALSE}
-library(reshape2)
-library(tidyr)
-
 data <- s1$summ %>%

### 2024-08-22 doc/performanceER.Rmd
fixed some error / edit Performance.Rmd, PerformanceER.Rmd, PerformanceOR.Rmd

@@
 
-ind <- which(!is.na(RD_bross[,1]))
+ind <- which(!is.na(RD_bross.ER[,1]))
 
-est_bross    <- RD_bross[ind,]
-est_hybird   <- RD_hybrid[ind,]
-est_lasso    <- RD_lasso[ind,]
-est_enet     <- RD_enet[ind,]
-est_ga       <- RD_ga[ind,]
-est_xgboost  <- RD_xgboost[ind,]
-est_rf       <- RD_rf[ind,]
+est_bross    <- RD_bross.ER[ind,]
+est_hybird   <- RD_hybrid_ER[ind,]
+est_lasso    <- RD_lasso_ER[ind,]
+est_enet     <- RD_enet_ER[ind,]
+est_ga       <- RD_ga_ER[ind,]
+est_xgboost  <- RD_xgboost_ER[ind,]
+est_rf       <- RD_rf_ER[ind,]
 est_forward  <- RD_forward[ind,]

### 2024-08-22 doc/performanceOR.Rmd
fixed some error / edit Performance.Rmd, PerformanceER.Rmd, PerformanceOR.Rmd

@@
 
-ind <- which(!is.na(RD_bross[,1]))
+ind <- which(!is.na(RD_bross.OR[,1]))
 
-est_bross    <- RD_bross[ind,]
-est_hybird   <- RD_hybrid[ind,]
-est_lasso    <- RD_lasso[ind,]
-est_enet     <- RD_enet[ind,]
-est_ga       <- RD_ga[ind,]
-est_xgboost  <- RD_xgboost[ind,]
-est_rf       <- RD_rf[ind,]
+est_bross    <- RD_bross.OR[ind,]
+est_hybird   <- RD_hybrid_OR[ind,]
+est_lasso    <- RD_lasso_OR[ind,]
+est_enet     <- RD_enet_OR[ind,]
+est_ga       <- RD_ga_OR[ind,]
+est_xgboost  <- RD_xgboost_OR[ind,]
+est_rf       <- RD_rf_OR[ind,]
 est_forward  <- RD_forward[ind,]
@@
              est_forward, est_backward)
-
 est$model <- as.factor(est$model)
-levels(est$model) <- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
-levels <- levels(est$model)
+levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
+est$model <- factor(est$model, levels = levels)
+levels(est$model)
 ```

### 2024-08-22 doc/app.R

@@ -1,0 +1,47 @@
+setwd("/Users/jidianlewei/Desktop/WL_MachineLearning/hdPS/hdPS_ProxySelect/doc")
+library(shiny)
+# Define UI
+ui <- fluidPage(
+  titlePanel("Select a Scenario and Plot"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario_select", "Choose a scenario:", 
+                  choices = list("Frequent Outcome and Exposure" = "scenario",
+                                 "Rare Exposure" = "scenarioER",
+                                 "Rare Outcome" = "scenarioOR")
+      ),
+      selectInput("plot_select", "Choose a plot:", 
+                  choices = list("Bias" = "bias.png", 
+                                 "Coverage" = "cover.png", 
+                                 "Empirical SE" = "empse.png", 
+                                 "Model SE" = "modelse.png", 
+                                 "Comparison" = "secompare.png", 
+                                 "Zip" = "zip.png",
+                                 "Bias Coverage" = "becover.png")
+      )
+    ),
+    mainPanel(
+      imageOutput("selected_plot")
+    )
+  )
+)
+
+# Server logic
+server <- function(input, output) {
+  output$selected_plot <- renderImage({
+    # Get the selected scenario and plot file name
+    scenario <- input$scenario_select
+    plot_file <- input$plot_select
+    
+    # Construct the full path to the image based on the scenario
+    full_path <- file.path("images", scenario, plot_file)
+    
+    # Return a list containing the filename
+    list(src = full_path,
+         contentType = 'image/png',
+         alt = "Selected plot")
+  }, deleteFile = FALSE)
+}
+
+# Run the application 
+shinyApp(ui = ui, server = server)

### 2024-08-22 doc/app3.R

@@ -1,0 +1,166 @@
+setwd("/Users/jidianlewei/Desktop/WL_MachineLearning/hdPS/hdPS_ProxySelect/doc")
+library(shiny)
+library(ggplot2)
+library(rsimsum)
+library(knitr)
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Select a Scenario and Performance Metric"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario_select", "Choose a scenario:",
+                  choices = list("Frequent Outcome and Exposure" = "scenario",
+                                 "Rare Exposure" = "scenarioER",
+                                 "Rare Outcome" = "scenarioOR")
+      ),
+      selectInput("metric_select", "Choose a performance metric:",
+                  choices = list("Bias" = "bias", 
+                                 "Coverage" = "cover", 
+                                 "Empirical SE" = "empse", 
+                                 "Model SE" = "modelse", 
+                                 "MSE" = "mse",
+                                 "Relative Precision" = "relprec",
+                                 "Relative Error" = "relerror",
+                                 "Power" = "power",
+                                 "Bias-eliminated Coverage" = "becover")
+      )
+    ),
+    mainPanel(
+      plotOutput("selected_plot"),
+      verbatimTextOutput("numerical_values_output") 
+    )
+  )
+)
+
+# Server logic
+server <- function(input, output, session) {
+  
+  # Function to load and process the data
+  load_scenario_data <- function(scenario) {
+    base_path <- file.path("results", scenario)
+    
+    # List all .RData files in the directory
+    files <- list.files(base_path, pattern = "\\.RData$", full.names = TRUE)
+    
+    # Initialize an empty list to hold the loaded data
+    est_list <- list()
+    
+    # Loop over each file and load the corresponding data
+    for (file_path in files) {
+      load(file_path)
+      
+      # Extract the model name from the file name
+      model <- tools::file_path_sans_ext(basename(file_path))
+      
+      # Try different naming conventions
+      object_name <- paste0("RD_", model)
+      object_name_er <- paste0("RD_", model, "_ER")
+      object_name_dot_er <- paste0("RD_", model, ".ER")
+      object_name_or <- paste0("RD_", model, "_OR")
+      object_name_dot_or <- paste0("RD_", model, ".OR")
+      
+      # Check which object exists and rename it to a standard name
[…]

### 2024-08-22 simResults_scenario/10.3_both/both.R

@@ -1,123 +1,0 @@
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-# ---------------------------------------------------------------
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes"
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
-data <- readRDS(path)
-proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
-covarsTfull <- c(investigator.specified.covariates, proxy.list)
-Y.form <- as.formula(paste0(c("outcome~ exposure", 
-                              covarsTfull), collapse = "+") )
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
-full.formula <- as.formula(paste0("outcome~exposure+",
-                                  paste0(covarsTfull, collapse = "+"),
-                                  collapse = "+"))
-# ---------------------------------------------------------------
-
-### initialization before for-loop
-# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
-a <- 1000
-b <- 3
-
-RD_both <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
-num.proxy_both <- c()
-# ---------------------------------------------------------------
-
[…]

### 2024-08-22 simResults_scenario/10.3_both/both.sh

@@ -1,18 +1,0 @@
-#!/bin/bash
-#SBATCH --account=st-mekarim-1
-#SBATCH --nodes=1
-#SBATCH --ntasks=1
-#SBATCH --mem=5G
-#SBATCH --time=10:00:00
-#SBATCH --mail-user=leiyang1@student.ubc.ca
-#SBATCH --mail-type=ALL
-#SBATCH --output=output_both.txt
-#SBATCH --error=error_both.txt
-
-module load gcc/9.4.0
-module load r/4.4.0
-
-cd $SLURM_SUBMIT_DIR
-export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
-
-R CMD BATCH both.R

### 2024-08-22 simResults_scenario/10.3_both/load_proxy_both.R

@@ -1,117 +1,0 @@
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-# ---------------------------------------------------------------
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes"
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
-data <- readRDS(path)
-proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
-covarsTfull <- c(investigator.specified.covariates, proxy.list)
-Y.form <- as.formula(paste0(c("outcome~ exposure", 
-                              covarsTfull), collapse = "+") )
-
-a <- 1000
-b <- 0
-
-RD_both <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
-num.proxy_both <- c()
-# ---------------------------------------------------------------
-
-### scenario: for-loop generating RD & SE results
-set.seed(42)
-
-for (i in (b+1):a) {
-  path_proxy <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simResults_scenario/10.3_both/proxy_both.data.", i, ".RData")
-  
-  if (file.exists(path_proxy)) {
-    proxyform_name <- load(path_proxy)
-    proxyform <- get(proxyform_name)
-    proxy_both <- strsplit(proxyform, split = "\\+")[[1]]
-    
[…]

### 2024-08-22 simResults_scenario/10.3_both/load_proxy_both.sh

@@ -1,18 +1,0 @@
-#!/bin/bash
-#SBATCH --account=st-mekarim-1
-#SBATCH --nodes=1
-#SBATCH --ntasks=1
-#SBATCH --mem=2G
-#SBATCH --time=2:00:00
-#SBATCH --mail-user=leiyang1@student.ubc.ca
-#SBATCH --mail-type=ALL
-#SBATCH --output=output_load_proxy_both.txt
-#SBATCH --error=error_load_proxy_both.txt
-
-module load gcc/9.4.0
-module load r/4.4.0
-
-cd $SLURM_SUBMIT_DIR
-export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
-
-R CMD BATCH load_proxy_both.R

### 2024-08-22 simResults_scenario/10.3_both/parallel_both.R

@@ -1,85 +1,0 @@
-# try parallel
-library(parallel)
-library(autoCovariateSelection)
-library(dplyr)
-library(cobalt)
-library(WeightIt)
-library(ggplot2)
-library(lmtest)
-library(MASS)
-library(Boruta)
-library(GA)
-library(mclust)
-library(penalizedSVM)
-library(xgboost)
-library(caret)
-library(randomForest)
-library(glmnet)
-
-# ---------------------------------------------------------------
-
-### global information
-exposure <- "obese"
-outcome <- "diabetes" 
-investigator.specified.covariates <- 
-  c(# Demographic
-    "age.cat", "sex", "education", "race", 
-    "marital", "income", "born", "year",
-    
-    # health history related variables/access
-    "diabetes.family.history", "medical.access",
-    
-    # behavioral
-    "smoking", "diet.healthy", "physical.activity", "sleep",
-    
-    # Laboratory 
-    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
-    "sodium", "potassium", "globulin", "calcium.total", 
-    "systolicBP", "diastolicBP", "high.cholesterol"
-  )
-covform <- paste0(investigator.specified.covariates, collapse = "+")
-out.formula <- as.formula(paste0("outcome", "~", "exposure"))
-path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_1.rds")
-data1 <- readRDS(path)
-proxy.list <- names(data1[, c(grep("^rec", names(data1), value = TRUE))])
-covarsTfull <- c(investigator.specified.covariates, proxy.list)
-Y.form <- as.formula(paste0(c("outcome~ exposure", 
-                              covarsTfull), collapse = "+"))
-initial.formula <- as.formula(paste0("outcome~exposure+",
-                                     covform,
-                                     collapse = "+"))
-full.formula <- as.formula(paste0("outcome~exposure+",
-                                  paste0(covarsTfull, collapse = "+"),
-                                  collapse = "+"))
-# ---------------------------------------------------------------
-
-n_cores <- 12  # Match this to the --ntasks value in your Slurm script
-
-proxy_select <- function(i) {
-  browser()
-  path <- paste0("/scratch/st-mekarim-1/leiyang1/hdPS_ProxySelect/simData/scenario/data_", i, ".rds")
-  ds <<- readRDS(path)
-  
[…]

### 2024-08-22 simResults_scenario/10.3_both/parallel_both.sh

@@ -1,18 +1,0 @@
-#!/bin/bash
-#SBATCH --account=st-mekarim-1
-#SBATCH --nodes=1
-#SBATCH --ntasks=12
-#SBATCH --mem=10G
-#SBATCH --time=9:00:00
-#SBATCH --mail-user=leiyang1@student.ubc.ca
-#SBATCH --mail-type=ALL
-#SBATCH --output=output_parallel_both.txt
-#SBATCH --error=error_parallel_both.txt
-
-module load gcc/9.4.0
-module load r/4.4.0
-
-cd $SLURM_SUBMIT_DIR
-export R_LIBS=/arc/home/leiyang1/R/x86_64-pc-linux-gnu-library/4.4/
-
-R CMD BATCH parallel_both.R

### 2024-08-25 Writeup/appendix/Appendix.RMD
writeup

---
title: Supplementary Content
subtitle: Challenges of Univariate Proxy Variable Screening in High-Dimensional Propensity Score Analysis - An Argument for Multivariate Approaches
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
  html_document:
    df_print: paged
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
  word_document: default
  bookdown::html_document2:
    citation_package: natbib
    df_print: paged
    fig_caption: yes
    highlight: textmate
    keep_md: yes
    number_sections: yes
    theme: lumen
bibliography: mergedbibliography.bib
biblio-style: plainnat
always_allow_html: yes
header-includes:
- \usepackage{graphicx,longtable,booktabs,here,threeparttable}
- \usepackage{float}
- \usepackage{pdfpages}
- \usepackage{setspace}\singlespacing
- \floatplacement{figure}{H}
- \floatplacement{table}{H}
- \usepackage{xcolor,lipsum}
- \usepackage{caption}
- \captionsetup[table]{labelfont=bf}
- \usepackage[round]{natbib}
- \usepackage{pdflscape}
- \usepackage{lscape}
- \usepackage{etoolbox}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{array}
  \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
  \newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
  \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
link-citations: yes
fontsize: 10pt
geometry: margin=.8in
---
\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}

\edef\tablename{\appendixname~\tablename}
\edef\figurename{\appendixname~\figurename}

\hypertarget{X}{%
\section{X}\label{X}}

### 2024-08-25 Writeup/appendix/Appendix.tex
writeup

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  10pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=.8in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{graphicx,longtable,booktabs,here,threeparttable}
\usepackage{float}
\usepackage{pdfpages}
\usepackage{setspace}\singlespacing
\floatplacement{figure}{H}
\floatplacement{table}{H}
\usepackage{xcolor,lipsum}
\usepackage{caption}
\captionsetup[table]{labelfont=bf}
\usepackage[round]{natbib}
\usepackage{pdflscape}
\usepackage{lscape}
\usepackage{etoolbox}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{array} \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} \newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Supplementary Content},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplementary Content}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Challenges of Univariate Proxy Variable Screening in
High-Dimensional Propensity Score Analysis - An Argument for
Multivariate Approaches}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}

\edef\tablename{\appendixname~\tablename}
\edef\figurename{\appendixname~\figurename}

\hypertarget{X}{%
\section{X}\label{X}}

  \bibliography{mybibfile.bib}

\end{document}

### 2024-08-25 Writeup/manuscript.Rmd
writeup

---
# Supported options: 
#   sn-nature:       Style for submissions to Nature Portfolio journals
#   sn-basic:        Basic Springer Nature Reference Style/Chemistry Reference Style
#   sn-mathphys:     Math and Physical Sciences Reference Style
#   sn-aps:          American Physical Society (APS) Reference Style
#   sn-vancouver:    Vancouver Reference Style
#   sn-apa:          APA Reference Style 
#   sn-chicago:      Chicago-based Humanities Reference Style
#   default:         Default

classoptions: 
  - sn-vancouver      
  - Numbered      # Optional: Use numbered references instead of namedate references (only for sn-nature, sn-basic, sn-vancouver, sn-chicago, sn-mathphys or sn-nature)
  # - referee       # Optional: Use double line spacing 
  - lineno        # Optional: Add line numbers
  # - iicol         # Optional: Double column layout

title: Challenges of Univariate Proxy Variable Screening in High-Dimensional Propensity Score Analysis - An Argument for Multivariate Approaches
titlerunning: Deep Learning in Propensity Score Analysis

authors: 
  - prefix: Dr.
    firstname: Mohammad Ehsanul 
    particle: 
    lastname: Karim
    suffix: 
    naturename: 
    degrees: MSc, PhD
    email: ehsan.karim@ubc.ca
    affiliation: [1,2]
    corresponding: TRUE
    equalcont: 
  - prefix: 
    firstname: Yang
    particle: 
    lastname: Lei
    suffix: 
    naturename: 
    degrees: 
    email: 
    affiliation: [3]
    corresponding: TRUE
    equalcont: 
affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: School of Population and Public Health
      orgname: University of British Columbia
    address:
        street: 2206 East Mall
        city: Vancouver
        postcode: V6T 1Z3
        state: BC
        country: Canada
  - number: 2
    corresponding: FALSE
    info:
      orgname: St. Paul’s Hospital
    address:
        street: 588 - 1081 Burrard Street
        city: Vancouver
        postcode: V6Z 1Y6
        state: BC
        country: Canada
  - number: 3
    corresponding: FALSE
    info:
      orgdiv: Department of Statistics
      orgname: University of British Columbia
    address:
        street: Room 3182 Earth Sciences Building, 2207 Main Mall
        city: Vancouver
        postcode: V6T 1Z4
        state: BC
        country: Canada

keywords:
  - Machine learning
  - Propensity score 
  - Deep learning
  - Causal inference

pacs: 
  jel:
    - "C18"
  msc:
    - "92D30"
    - "62P10"

# Sample for structured abstract
abstract: |
  **Purpose**:

  **Methods:**

  **Results:**

  **Conclusion:**

bibliography: mergedbibliography.bib

header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \usepackage{capt-of}
  \usepackage{booktabs}
  \usepackage{amssymb}
  \usepackage{threeparttable}
  \usepackage{float}
  %\floatplacement{figure}{H}
  %\floatplacement{table}{H}
  \usepackage{lipsum,caption}
  \geometry{
    a4paper,
    left=1in,
    right=1in,
    top=1in,
    bottom=1in,
    includeheadfoot
  }
  \usepackage{setspace}
  %\usepackage{lineno}
  %\linenumbers
  \usepackage{siunitx}
  \sisetup{
    mode = match,
    propagate-math-font = true,
    reset-math-version = false,
    reset-text-family = false,
    reset-text-series = false,
    reset-text-shape = false,
    text-family-to-math = true,
    text-series-to-math = true
  }
  \doublespacing
  % Disable explicit page breaks in LaTeX
  \let\clearpage\relax
output: rticles::springer_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, # By default, hide code; set to TRUE to see code
  fig.pos = 'th', # Places figures at top or here
  out.width = '100%', dpi = 300, # Figure resolution and size
  fig.env="figure",
  out.extra = ""
) # Latex figure environment

options(knitr.table.format = "latex") # For kable tables to write LaTeX table directly
```

# Background

**Aim**:

# Methods

## Data and Simulation {-}

**Right Heart Catheterization dataset**:

**Plasmode simulation**: See Table \ref{table:scenarios} for the description of the scenarios under consideration.

\begin{table}[ht]
\centering
\caption{Simulation Scenarios for plasmode simulation.}
\label{table:scenarios}
\begin{tabular}{lcccc}
  \toprule
  \textbf{Plasmode Simulation Scenario} & \textbf{Exposure} & \textbf{Outcome} & \textbf{True} & \textbf{Sample}\\
  \textbf{} & \textbf{Prevalence} & \textbf{Prevalence} & \textbf{Odds Ratio} & \textbf{Size}\\
  \midrule
  (i) Frequent Exposure and Outcome (Base) & 30\% & 30\% & 1 & 3,500 \\
  (ii) Rare Exposure and Frequent Outcome & 5\% & 30\% & 1 & 3,500 \\
  (iii) Frequent Exposure and Rare Outcome & 30\% & 5\% & 1 & 3,500 \\
  \bottomrule
\end{tabular}
\end{table}

**True data generating mechanism used in plasmode simulation**:

**Performance measures**: From this simulation, we derived several performance metrics: (1) bias, (2) average model standard error (SE; the average of estimated SEs obtained from a model over repeated samples), (3) empirical SE (the standard deviation of estimated treatment effects across repeated samples), (4) MSE, (5) coverage probability of 95% confidence intervals, (6) bias-eliminated coverage, and (7) Zip plot [@morris2019using; @white2023check].

## Estimators under consideration {-}

# Results

# Real-world analysis

**Computing time**:

# Discussion

**Contextualizing the literature**:

**Summary of the simulation findings**:

**Data analysis findings**:

**Future Direction**:

**Conclusion**:

# List of abbreviations {-}

1. MSE - Mean Squared Error
2. SE - Standard Error
3. PS - Propensity Score
4. AE - Autoencoders
5. DL - Deep Learning
6. MARS - Multivariate Adaptive Regression Splines
7. SMD - Standardized Mean Difference
8. TMLE - Targeted Maximum Likelihood Estimation
9. RHC - Right Heart Catheterization
10. SUPPORT - Study to Understand Prognoses and Preferences for Outcomes and Risks of Treatments

# Declarations {-}

## Ethics approval and consent to participate {-}

The analysis conducted on secondary and de-identified data is exempt from research ethics approval requirements. Ethics for this study was covered by item 7.10.3 in University of British Columbia's Policy #89: Research and Other Studies Involving Human Subjects 19 and Article 2.2 in of the Tri-Council Policy Statement: Ethical Conduct for Research Involving Humans (TCPS2).

## Consent for publication {-}

## Availability of data and materials {-}

## Competing interests {-}

Over the past three years, MEK has received consulting fees from Biogen Inc. for consulting unrelated to this current work. MEK was previously supported by the Michael Smith Foundation for Health Research Scholar award.

## Funding {-}

This work was supported by MEK's Natural Sciences and Engineering Research Council of Canada (NSERC) Discovery Grants and Discovery Accelerator Supplements.

## Authors' contributions {-}

MEK: Conceptualization, Writing – Original Draft, Review & Editing
YL: Formal Analysis, Review & Editing

## Acknowledgements {-}

Not applicable.

# References {-}

### 2024-08-25 Writeup/manuscript.tex
writeup

%Version 2.1 April 2023
% See section 11 of the User Manual for version history
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[sn-vancouver,Numbered,lineno,pdflatex]{sn-jnl}

%%%% Standard Packages
%%<additional latex packages if required can be included here>

\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%
%%%%

%%%%%=============================================================================%%%%
%%%%  Remarks: This template is provided to aid authors with the preparation
%%%%  of original research articles intended for submission to journals published
%%%%  by Springer Nature. The guidance has been prepared in partnership with
%%%%  production teams to conform to Springer Nature technical requirements.
%%%%  Editorial and presentation requirements differ among journal portfolios and
%%%%  research disciplines. You may find sections in this template are irrelevant
%%%%  to your work and are empowered to omit any such section if allowed by the
%%%%  journal you intend to submit to. The submission guidelines and policies
%%%%  of the journal take precedence. A detailed User Manual is available in the
%%%%  template package for technical guidance.
%%%%%=============================================================================%%%%

\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{capt-of}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage{float}
%\floatplacement{figure}{H}
%\floatplacement{table}{H}
\usepackage{lipsum,caption}
\geometry{
  a4paper,
  left=1in,
  right=1in,
  top=1in,
  bottom=1in,
  includeheadfoot
}
\usepackage{setspace}
%\usepackage{lineno}
%\linenumbers
\usepackage{siunitx}
\sisetup{
  mode = match,
  propagate-math-font = true,
  reset-math-version = false,
  reset-text-family = false,
  reset-text-series = false,
  reset-text-shape = false,
  text-family-to-math = true,
  text-series-to-math = true
}
\doublespacing
% Disable explicit page breaks in LaTeX
\let\clearpage\relax

\raggedbottom

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\title[Deep Learning in Propensity Score Analysis]{Challenges of
Univariate Proxy Variable Screening in High-Dimensional Propensity Score
Analysis - An Argument for Multivariate Approaches}

%%=============================================================%%
%% Prefix	-> \pfx{Dr}
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% NatureName	-> \tanm{Poet Laureate} -> Title after name
%% Degrees	-> \dgr{MSc, PhD}
%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
%%=============================================================%%

\author*[1,2]{\pfx{Dr.} \fnm{Mohammad Ehsanul} \sur{Karim} \dgr{MSc,
PhD}}\email{\href{mailto:ehsan.karim@ubc.ca}{\nolinkurl{ehsan.karim@ubc.ca}}}

\author*[3]{\fnm{Yang} \sur{Lei} }

  \affil*[1]{\orgdiv{School of Population and Public
Health}, \orgname{University of British
Columbia}, \orgaddress{\city{Vancouver}, \country{Canada}, \postcode{V6T
1Z3}, \state{BC}, \street{2206 East Mall}}}
  \affil[2]{\orgname{St.~Paul's
Hospital}, \orgaddress{\city{Vancouver}, \country{Canada}, \postcode{V6Z
1Y6}, \state{BC}, \street{588 - 1081 Burrard Street}}}
  \affil[3]{\orgdiv{Department of Statistics}, \orgname{University of
British
Columbia}, \orgaddress{\city{Vancouver}, \country{Canada}, \postcode{V6T
1Z4}, \state{BC}, \street{Room 3182 Earth Sciences Building, 2207 Main
Mall}}}

\abstract{\textbf{Purpose}:

\textbf{Methods:}

\textbf{Results:}

\textbf{Conclusion:}}

\keywords{Machine learning, Propensity score, Deep learning, Causal
inference}

\pacs[JEL Classification]{C18}
\pacs[MSC Classification]{92D30, 62P10}

\maketitle

\section{Background}\label{background}

\textbf{Aim}:

\section{Methods}\label{methods}

\subsection*{Data and Simulation}\label{data-and-simulation}
\addcontentsline{toc}{subsection}{Data and Simulation}

\textbf{Right Heart Catheterization dataset}:

\textbf{Plasmode simulation}: See Table \ref{table:scenarios} for the
description of the scenarios under consideration.

\begin{table}[ht]
\centering
\caption{Simulation Scenarios for plasmode simulation based on the Right Heart Catheterization (RHC) study.}
\label{table:scenarios}
\begin{tabular}{lcccc}
  \toprule
  \textbf{Plasmode Simulation Scenario} & \textbf{Exposure} & \textbf{Outcome} & \textbf{True} & \textbf{Sample}\\
  \textbf{} & \textbf{Prevalence} & \textbf{Prevalence} & \textbf{Odds Ratio} & \textbf{Size}\\
  \midrule
  (i) Frequent Exposure and Outcome (Base) & 30\% & 30\% & 1 & 3,500 \\
  (ii) Rare Exposure and Frequent Outcome & 5\% & 30\% & 1 & 3,500 \\
  (iii) Frequent Exposure and Rare Outcome & 30\% & 5\% & 1 & 3,500 \\
  \bottomrule
\end{tabular}
\end{table}

\textbf{True data generating mechanism used in plasmode simulation}:

\textbf{Performance measures}: From this simulation, we derived several
performance metrics: (1) bias, (2) average model standard error (SE; the
average of estimated SEs obtained from a model over repeated samples),
(3) empirical SE (the standard deviation of estimated treatment effects
across repeated samples), (4) MSE, (5) coverage probability of 95\%
confidence intervals, (6) bias-eliminated coverage, and (7) Zip plot
\citep{morris2019using, white2023check}.

\subsection*{Estimators under
consideration}\label{estimators-under-consideration}
\addcontentsline{toc}{subsection}{Estimators under consideration}

\section{Results}\label{results}

\section{Real-world analysis}\label{real-world-analysis}

\textbf{Computing time}:

\section{Discussion}\label{discussion}

\textbf{Contextualizing the literature}:

\textbf{Summary of the simulation findings}:

\textbf{Data analysis findings}:

\textbf{Future Direction}:

\textbf{Conclusion}:

\section*{List of abbreviations}\label{list-of-abbreviations}
\addcontentsline{toc}{section}{List of abbreviations}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  MSE - Mean Squared Error
\item
  SE - Standard Error
\item
  PS - Propensity Score
\item
  AE - Autoencoders
\item
  DL - Deep Learning
\item
  MARS - Multivariate Adaptive Regression Splines
\item
  SMD - Standardized Mean Difference
\item
  TMLE - Targeted Maximum Likelihood Estimation
\item
  RHC - Right Heart Catheterization
\item
  SUPPORT - Study to Understand Prognoses and Preferences for Outcomes
  and Risks of Treatments
\end{enumerate}

\section*{Declarations}\label{declarations}
\addcontentsline{toc}{section}{Declarations}

\subsection*{Ethics approval and consent to
participate}\label{ethics-approval-and-consent-to-participate}
\addcontentsline{toc}{subsection}{Ethics approval and consent to
participate}

The analysis conducted on secondary and de-identified data is exempt
from research ethics approval requirements. Ethics for this study was
covered by item 7.10.3 in University of British Columbia's Policy \#89:
Research and Other Studies Involving Human Subjects 19 and Article 2.2
in of the Tri-Council Policy Statement: Ethical Conduct for Research
Involving Humans (TCPS2).

\subsection*{Consent for publication}\label{consent-for-publication}
\addcontentsline{toc}{subsection}{Consent for publication}

\subsection*{Availability of data and
materials}\label{availability-of-data-and-materials}
\addcontentsline{toc}{subsection}{Availability of data and materials}

\subsection*{Competing interests}\label{competing-interests}
\addcontentsline{toc}{subsection}{Competing interests}

Over the past three years, MEK has received consulting fees from Biogen
Inc.~for consulting unrelated to this current work. MEK was previously
supported by the Michael Smith Foundation for Health Research Scholar
award.

\subsection*{Funding}\label{funding}
\addcontentsline{toc}{subsection}{Funding}

This work was supported by MEK's Natural Sciences and Engineering
Research Council of Canada (NSERC) Discovery Grants and Discovery
Accelerator Supplements.

\subsection*{Authors' contributions}\label{authors-contributions}
\addcontentsline{toc}{subsection}{Authors' contributions}

MEK: Conceptualization, Writing -- Original Draft, Review \& Editing YL:
Formal Analysis, Review \& Editing

\subsection*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{subsection}{Acknowledgements}

Not applicable.

\renewcommand\refname{References}
\bibliography{mybibfile.bib}

\end{document}

### 2024-08-25 doc/app3.R

@@ -1,8 +1,33 @@
-setwd("/Users/jidianlewei/Desktop/WL_MachineLearning/hdPS/hdPS_ProxySelect/doc")
+#setwd("/Users/jidianlewei/Desktop/WL_MachineLearning/hdPS/hdPS_ProxySelect/doc")
+setwd("E:/GitHub/hdPS-proxy-select/doc")
 library(shiny)
 library(ggplot2)
 library(rsimsum)
 library(knitr)
+
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  relerror = "Relative Error",
+  power = "Power",
+  becover = "Bias-eliminated Coverage"
+)
+
+model_names <- c(
+  backward = "Backward Elimination",
+  bross = "Bross-based hdPS",
+  enet = "Elasticnet",
+  forward = "Forward Selection",
+  ga = "Genetic Algorithm",
+  hybrid = "Hybrid hdPS",
+  lasso = "LASSO",
+  rf = "Random Forest",
+  xgboost = "XGBoost"
+)
 
 # Define UI
 ui <- fluidPage(
@@ -28,8 +53,12 @@ ui <- fluidPage(
     ),
     mainPanel(
       plotOutput("selected_plot"),
-      verbatimTextOutput("numerical_values_output") 
+      verbatimTextOutput("numerical_values_output"),
+      downloadButton("download_png", "Download PNG"),
+      downloadButton("download_pdf", "Download PDF"),
+      downloadButton("download_jpg", "Download JPG")
     )
+    
   )
 )
 
@@ -101,6 +130,7 @@ server <- function(input, output, session) {
       stop("The data frame does not contain the required columns 'RD' and 'SE'.")
     }
     
+    est$model <- model_names[as.character(est$model)]
     est$model <- as.factor(est$model)
     return(est)
   }
@@ -144,11 +174,42 @@ server <- function(input, output, session) {
     
     metric <- input$metric_select
     
-    # Plot using autoplot with the selected metric
+    # Plot using autoplot with the selected metric and full model names
     autoplot(s1, type = "lolly", stats = metric) + 
       custom_theme + 
-      labs(x = metric)
+      labs(x = metric_names[metric])
   })
+  
+  
+  # Download handler for PNG
+  output$download_png <- downloadHandler(
+    filename = function() {
[…]

### 2024-08-25 doc/app4.R

@@ -1,0 +1,271 @@
+#setwd("/Users/jidianlewei/Desktop/WL_MachineLearning/hdPS/hdPS_ProxySelect/doc")
+setwd("E:/GitHub/hdPS-proxy-select/doc")
+library(shiny)
+library(ggplot2)
+library(rsimsum)
+library(knitr)
+
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  relerror = "Relative Error",
+  power = "Power",
+  becover = "Bias-eliminated Coverage",
+  nsim = "# of simulations"
+)
+
+model_names <- c(
+  kitchen = "Kitchen sink",
+  bross = "Bross-based hdPS",
+  hybrid = "Hybrid hdPS",
+  ga = "Genetic Algorithm",
+  xgboost = "XGBoost",
+  rf = "Random Forest",
+  forward = "Forward Selection",
+  backward = "Backward Elimination",
+  lasso = "LASSO",  
+  enet = "Elasticnet"
+)
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Select a Scenario and Performance Metric"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario_select", "Choose a scenario:",
+                  choices = list("Frequent Outcome and Exposure" = "scenario",
+                                 "Rare Exposure" = "scenarioER",
+                                 "Rare Outcome" = "scenarioOR")
+      ),
+      selectInput("metric_select", "Choose a performance metric:",
+                  choices = list("Bias" = "bias", 
+                                 "Coverage" = "cover", 
+                                 "Empirical SE" = "empse", 
+                                 "Model SE" = "modelse", 
+                                 "MSE" = "mse",
+                                 "Relative Precision" = "relprec",
+                                 "Relative Error" = "relerror",
+                                 "Power" = "power",
+                                 "Bias-eliminated Coverage" = "becover",
+                                 "Number of simulations" = "nsim")
+      )
+    ),
+    mainPanel(
+      plotOutput("selected_plot"),
+      verbatimTextOutput("numerical_values_output"),
+      downloadButton("download_png", "Download PNG"),
+      downloadButton("download_pdf", "Download PDF"),
+      downloadButton("download_jpg", "Download JPG")
+    )
+    
+  )
+)
+
+# Server logic
+server <- function(input, output, session) {
+  
+  # Function to load and process the data
[…]

### 2024-08-25 simResults_scenario/11_kitchen/kitchen.R

@@ -1,0 +1,180 @@
+path0 <- "E:/GitHub/hdPS-proxy-select/"
+
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_kitchen <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_kitchen <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+
+# Set up the directories
+save_dir_success <- paste0(path0, "simResults_scenario/11_kitchen/success/")
+save_dir_unsuccess <- paste0(path0, "simResults_scenario/11_kitchen/unsuccess/")
+
+# Ensure the "success" directory exists
+if (!file.exists(save_dir_success)) {
+  dir.create(save_dir_success, recursive = TRUE)
+}
+
+# Ensure the "unsuccess" directory exists
+if (!file.exists(save_dir_unsuccess)) {
[…]

### 2024-08-25 simResults_scenario/1_bross/bross_parallel_test.R

@@ -1,0 +1,111 @@
+# Load necessary libraries
+library(foreach)
+library(doParallel)
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(MASS)
+library(sandwich)
+
+# Set up parallel backend
+cl <- makeCluster(detectCores() - 1)  # Use all cores except one
+registerDoParallel(cl)
+
+# Global information
+path0 <- "E:/GitHub/hdPS-proxy-select/"
+exposure <- "obese"
+outcome <- "diabetes"
+investigator.specified.covariates <- 
+  c("age.cat", "sex", "education", "race", "marital", "income", "born", "year",
+    "diabetes.family.history", "medical.access",
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol")
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+
+# Initialization
+a0 <- 109
+a <- 1000
+RD_bross <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_bross <- c()
+errors <- c()
+
+# Parallel loop
+results <- foreach(i = a0:a, .combine = 'rbind', .packages = c("autoCovariateSelection", "dplyr", "cobalt", "WeightIt", "MASS", "sandwich")) %dopar% {
+  path <- paste0(path0, "simData/scenario/data_", i, ".rds")
+  data <- tryCatch(readRDS(path), error = function(e) return(NULL))
+  
+  if (is.null(data)) {
+    errors <<- c(errors, paste("Error at iteration", i, ": failed to read data"))
+    return(c(NA, NA, NA))
+  }
+  
+  data$idx <- data$id
+  proxy.df <- data[, c("idx", grep("^rec", names(data), value = TRUE))]
+  col_sums <- apply(proxy.df[,-1], 2, sum)
+  all_zero_or_one_colnames <- colnames(proxy.df)[col_sums == 0 | col_sums == nrow(proxy.df)]
+  proxy.df.filtered <- proxy.df[, !(colnames(proxy.df) %in% all_zero_or_one_colnames)]
+  
+  bross.list <- tryCatch({
[…]

### 2024-08-25 simResults_scenario/1_bross/bross_updated_test.R

@@ -1,0 +1,180 @@
+path0 <- "E:/GitHub/hdPS-proxy-select/"
+
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_bross <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_bross <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+
+# Set up the directories
+save_dir_success <- paste0(path0, "simResults_scenario/1_bross/success/")
+save_dir_unsuccess <- paste0(path0, "simResults_scenario/1_bross/unsuccess/")
+
+# Ensure the "success" directory exists
+if (!file.exists(save_dir_success)) {
+  dir.create(save_dir_success, recursive = TRUE)
+}
+
+# Ensure the "unsuccess" directory exists
+if (!file.exists(save_dir_unsuccess)) {
+  dir.create(save_dir_unsuccess, recursive = TRUE)
+}
+
+# Now you can use save_dir_success and save_dir_unsuccess in your loop for saving files
+
+
+
[…]

### 2024-08-25 simResults_scenarioER/11_kitchen/kitchen.R

@@ -1,0 +1,180 @@
+path0 <- "E:/GitHub/hdPS-proxy-select/"
+
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_kitchen <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_kitchen <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+
+# Set up the directories
+save_dir_success <- paste0(path0, "simResults_scenarioER/11_kitchen/success/")
+save_dir_unsuccess <- paste0(path0, "simResults_scenarioER/11_kitchen/unsuccess/")
+
+# Ensure the "success" directory exists
+if (!file.exists(save_dir_success)) {
+  dir.create(save_dir_success, recursive = TRUE)
+}
+
+# Ensure the "unsuccess" directory exists
+if (!file.exists(save_dir_unsuccess)) {
[…]

### 2024-08-25 simResults_scenarioOR/11_kitchen/kitchen.R

@@ -1,0 +1,180 @@
+path0 <- "E:/GitHub/hdPS-proxy-select/"
+
+library(autoCovariateSelection)
+library(dplyr)
+library(cobalt)
+library(WeightIt)
+library(ggplot2)
+library(lmtest)
+library(MASS)
+library(Boruta)
+library(GA)
+library(mclust)
+library(penalizedSVM)
+library(xgboost)
+library(caret)
+library(randomForest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_kitchen <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_kitchen <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+
+# Set up the directories
+save_dir_success <- paste0(path0, "simResults_scenarioOR/11_kitchen/success/")
+save_dir_unsuccess <- paste0(path0, "simResults_scenarioOR/11_kitchen/unsuccess/")
+
+# Ensure the "success" directory exists
+if (!file.exists(save_dir_success)) {
+  dir.create(save_dir_success, recursive = TRUE)
+}
+
+# Ensure the "unsuccess" directory exists
+if (!file.exists(save_dir_unsuccess)) {
[…]

### 2024-08-26 doc/app5.R
test 5

@@ -1,0 +1,308 @@
+#setwd("/Users/jidianlewei/Desktop/WL_MachineLearning/hdPS/hdPS_ProxySelect/doc")
+#setwd("E:/GitHub/hdPS-proxy-select/doc")
+# setwd("C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/doc")
+#setwd(normalizePath("C:\Users\Ehsan\Documents\GitHub\hdPS-proxy-select\doc"))
+
+setwd_to_script_dir <- function() {
+  if (rstudioapi::isAvailable()) {
+    script_path <- rstudioapi::getActiveDocumentContext()$path
+    if (nzchar(script_path)) {
+      script_dir <- dirname(script_path)
+      setwd(script_dir)
+      message("Working directory set to script directory: ", script_dir)
+    } else {
+      message("No active document found.")
+    }
+  } else {
+    message("rstudioapi is not available.")
+  }
+}
+setwd_to_script_dir()
+
+
+library(shiny)
+library(ggplot2)
+library(rsimsum)
+library(knitr)
+
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  relerror = "Relative Error",
+  power = "Power",
+  becover = "Bias-eliminated Coverage",
+  nsim = "# of simulations"
+)
+
+model_names <- c(
+  kitchen = "Kitchen sink",
+  bross = "Bross-based hdPS",
+  hybrid = "Hybrid hdPS",
+  ga = "Genetic Algorithm",
+  xgboost = "XGBoost",
+  rf = "Random Forest",
+  forward = "Forward Selection",
+  backward = "Backward Elimination",
+  lasso = "LASSO",  
+  enet = "Elasticnet"
+)
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Select a Scenario and Performance Metric"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario_select", "Choose a scenario:",
+                  choices = list("Frequent Outcome and Exposure" = "scenario",
+                                 "Rare Exposure" = "scenarioER",
+                                 "Rare Outcome" = "scenarioOR")
+      ),
+      selectInput("metric_select", "Choose a performance metric:",
+                  choices = list("Bias" = "bias", 
+                                 "Coverage" = "cover", 
+                                 "Empirical SE" = "empse", 
[…]

### 2024-08-26 simResults_scenario/1_bross/bross_updated_test_v2.R

@@ -1,0 +1,179 @@
+#path0 <- "E:/GitHub/hdPS-proxy-select/"
+path0 <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/"
+
+library(autoCovariateSelection)
+library(WeightIt)
+library(lmtest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+
+pathx <- paste0(path0, "simData/scenario/data_1.rds")
+data <- readRDS(pathx)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_bross <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_bross <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+
+# Set up the directories
+save_dir_success <- paste0(path0, "simResults_scenario/1_bross/success/")
+save_dir_unsuccess <- paste0(path0, "simResults_scenario/1_bross/unsuccess/")
+
+# Ensure the "success" directory exists
+if (!file.exists(save_dir_success)) {
+  dir.create(save_dir_success, recursive = TRUE)
+}
+
[…]

### 2024-08-26 simResults_scenario/1_bross/bross_updated_test_v2p.R

@@ -1,0 +1,166 @@
+library(parallel)
+library(autoCovariateSelection)
+library(WeightIt)
+library(lmtest)
+library(sandwich)
+library(dplyr)
+
+# ---------------------------------------------------------------
+
+### Global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+
+# Path
+path0 <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/"
+save_dir_success <- paste0(path0, "simResults_scenario/1_bross/success/")
+save_dir_unsuccess <- paste0(path0, "simResults_scenario/1_bross/unsuccess/")
+
+# Ensure the directories exist
+dir.create(save_dir_success, recursive = TRUE, showWarnings = FALSE)
+dir.create(save_dir_unsuccess, recursive = TRUE, showWarnings = FALSE)
+
+# ---------------------------------------------------------------
+
+### Parallel processing setup
+# Number of cores to use
+num_cores <- detectCores() - 1
+cl <- makeCluster(num_cores)
+
+# Load necessary libraries on each worker
+clusterEvalQ(cl, {
+  library(autoCovariateSelection)
+  library(WeightIt)
+  library(sandwich)
+  library(dplyr)
+  library(lmtest)
+})
+
+# Export necessary objects and functions to the cluster
+clusterExport(cl, c("covform", "out.formula", 
+                    "investigator.specified.covariates", 
+                    "save_dir_success", "save_dir_unsuccess", 
+                    "path0", "exposure", "outcome"))
+
+# ---------------------------------------------------------------
+
+### Main computation: parallelized for-loop
+a <- 40
+results <- clusterApplyLB(cl, 1:a, function(i) {
[…]

### 2024-08-26 simResults_scenario/1_bross/bross_updated_test_v3.R

@@ -1,0 +1,171 @@
+#path0 <- "E:/GitHub/hdPS-proxy-select/"
+path0 <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/"
+
+library(autoCovariateSelection)
+library(WeightIt)
+library(lmtest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+
+pathx <- paste0(path0, "simData/scenario/data_1.rds")
+data <- readRDS(pathx)
+proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(c("outcome~ exposure", 
+                              covarsTfull), collapse = "+") )
+
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_bross <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_bross <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+
+# Set up the directories
+save_dir_success <- paste0(path0, "simResults_scenario/1_bross/success/")
+save_dir_unsuccess <- paste0(path0, "simResults_scenario/1_bross/unsuccess/")
+
+# Ensure the "success" directory exists
+if (!file.exists(save_dir_success)) {
[…]

### 2024-08-26 simResults_scenario/1_bross/bross_updated_test_v4.R

@@ -1,0 +1,159 @@
+# Set the working directory
+path0 <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/"
+
+# Load necessary libraries
+library(autoCovariateSelection)
+library(WeightIt)
+library(lmtest)
+library(sandwich)
+
+# ---------------------------------------------------------------
+
+### Global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- c(
+  # Demographic
+  "age.cat", "sex", "education", "race", 
+  "marital", "income", "born", "year",
+  
+  # Health history related variables/access
+  "diabetes.family.history", "medical.access",
+  
+  # Behavioral
+  "smoking", "diet.healthy", "physical.activity", "sleep",
+  
+  # Laboratory 
+  "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+  "sodium", "potassium", "globulin", "calcium.total", 
+  "systolicBP", "diastolicBP", "high.cholesterol"
+)
+
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0(outcome, "~", exposure))
+
+# Load initial dataset
+pathx <- file.path(path0, "simData/scenario/data_1.rds")
+data <- readRDS(pathx)
+
+# Prepare proxy list and covariates
+proxy.list <- grep("^rec", names(data), value = TRUE)
+covarsTfull <- c(investigator.specified.covariates, proxy.list)
+Y.form <- as.formula(paste0(outcome, "~", exposure, "+", paste0(covarsTfull, collapse = "+")))
+
+# ---------------------------------------------------------------
+
+### Initialization before for-loop
+a <- 1000
+
+RD_bross <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_bross <- vector("numeric", a)
+errors <- vector("character")
+
+# Set up the directories
+save_dir_success <- file.path(path0, "simResults_scenario/1_bross/success/")
+save_dir_unsuccess <- file.path(path0, "simResults_scenario/1_bross/unsuccess/")
+
+# Ensure directories exist
+dir.create(save_dir_success, recursive = TRUE, showWarnings = FALSE)
+dir.create(save_dir_unsuccess, recursive = TRUE, showWarnings = FALSE)
+
+# ---------------------------------------------------------------
+
[…]

### 2024-08-26 simResults_scenario/1_bross/bross_updated_test_v5.R

@@ -1,0 +1,171 @@
+#path0 <- "E:/GitHub/hdPS-proxy-select/"
+path0 <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/"
+
+library(autoCovariateSelection)
+library(WeightIt)
+library(lmtest)
+# ---------------------------------------------------------------
+
+### global information
+exposure <- "obese"
+outcome <- "diabetes" 
+investigator.specified.covariates <- 
+  c(# Demographic
+    "age.cat", "sex", "education", "race", 
+    "marital", "income", "born", "year",
+    
+    # health history related variables/access
+    "diabetes.family.history", "medical.access",
+    
+    # behavioral
+    "smoking", "diet.healthy", "physical.activity", "sleep",
+    
+    # Laboratory 
+    "uric.acid", "protein.total", "bilirubin.total", "phosphorus",
+    "sodium", "potassium", "globulin", "calcium.total", 
+    "systolicBP", "diastolicBP", "high.cholesterol"
+  )
+covform <- paste0(investigator.specified.covariates, collapse = "+")
+out.formula <- as.formula(paste0("outcome", "~", "exposure"))
+
+# pathx <- paste0(path0, "simData/scenario/data_1.rds")
+# data <- readRDS(pathx)
+# proxy.list <- names(data[, c(grep("^rec", names(data), value = TRUE))])
+# covarsTfull <- c(investigator.specified.covariates, proxy.list)
+# Y.form <- as.formula(paste0(c("outcome~ exposure", 
+#                               covarsTfull), collapse = "+") )
+
+# ---------------------------------------------------------------
+
+### initialization before for-loop
+# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for-loop
+a <- 1000
+
+RD_bross <- data.frame(numProxy = integer(a), RD = numeric(a), SE = numeric(a))
+num.proxy_bross <- c()
+errors <- c()
+# ---------------------------------------------------------------
+
+### scenario: for-loop generating RD & SE results
+set.seed(42)
+
+# Set up the directories
+save_dir_success <- paste0(path0, "simResults_scenario/1_bross/success/")
+save_dir_unsuccess <- paste0(path0, "simResults_scenario/1_bross/unsuccess/")
+
+# Ensure the "success" directory exists
+if (!file.exists(save_dir_success)) {
[…]

### 2024-08-29 doc/performance.Rmd
new version of results tables for bross and hybrid with the edited codes

@@
 load("results/scenario/backward.RData")
+load("results/scenario/kitchen.RData")
 
@@
 est_backward <- RD_backward[ind,]
+est_kitchen  <- RD_kitchen[ind,]
 
@@
 est_backward$model <- "backward"
+est_kitchen$model  <- "kitchen"
 ```
@@
              est_ga, est_xgboost, est_rf,
-             est_forward, est_backward)
+             est_forward, est_backward, est_kitchen)
 
 est$model <- as.factor(est$model)
-levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
+levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward", "kitchen")
 est$model <- factor(est$model, levels = levels)

### 2024-08-29 doc/performanceER.Rmd
new version of results tables for bross and hybrid with the edited codes

@@
 load("results/scenarioER/backward.RData")
+load("results/scenarioER/kitchen.RData")
 

### 2024-08-29 doc/performanceOR.Rmd
new version of results tables for bross and hybrid with the edited codes

@@
 load("results/scenarioOR/backward.RData")
+load("results/scenarioOR/kitchen.RData")
 
@@
              est_ga, est_xgboost, est_rf,
-             est_forward, est_backward)
+             est_forward, est_backward, est_kitchen)
 est$model <- as.factor(est$model)
-levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward")
+levels<- c("bross", "hybrid", "lasso", "enet", "ga", "xgboost", "rf", "forward", "backward", "kitchen")
 est$model <- factor(est$model, levels = levels)

### 2024-08-29 simResults_scenario/1_bross/bross.R

@@ -93,33 +93,21 @@ for (i in 1:a) {
     save(list = results_bross.i, file = save_path)
   } else {
     proxy.df_bross <- bross.list$autoselected_covariate_df
-    hdps.data_bross <- merge(data[,c("idx",
-                                     outcome, 
-                                     exposure, 
-                                     investigator.specified.covariates)],
-                             proxy.df_bross,
-                             by = "idx")
-    hdps.data_bross$id <- hdps.data_bross$idx
-    hdps.data_bross$idx <- NULL
-    
-    hdps.data_bross$exposure <- as.numeric(I(hdps.data_bross$obese=='Yes'))
-    hdps.data_bross$outcome <- as.numeric(I(hdps.data_bross$diabetes=='Yes'))
-    
     proxy_bross <- names(proxy.df_bross[,-1])
     proxyform <- paste0(proxy_bross, collapse = "+")
     rhsformula <- paste0(c(covform, proxyform), collapse = "+")
     ps.formula <- as.formula(paste0("exposure", "~", rhsformula))
     
     W.out_bross <- weightit(ps.formula,
-                            data = hdps.data_bross, 
+                            data = data, 
                             estimand = "ATE",
                             method = "ps")
     fit.OR_bross <- glm(out.formula,
-                        data = hdps.data_bross,
+                        data = data,
                         weights = W.out_bross$weights,
                         family= binomial(link = "logit"))
     fit.RD_bross <- glm(out.formula,
-                        data= hdps.data_bross,
+                        data= data,
                         weights= W.out_bross$weights,
                         family=gaussian(link= "identity"))
     sum.RD_bross <- c(length(proxy_bross), 

### 2024-08-29 simResults_scenario/2_hybrid/hybrid.R

@@ -97,17 +97,14 @@ for (i in 1:a) {
   } else {
     proxy.df_hybrid <- hybrid.list$autoselected_covariate_df
     hdps.data_hybrid <- merge(data[,c("idx",
-                                     outcome, 
-                                     exposure, 
+                                     "outcome", 
+                                     "exposure", 
                                      investigator.specified.covariates)],
                              proxy.df_hybrid,
                              by = "idx")
     hdps.data_hybrid$id <- hdps.data_hybrid$idx
     hdps.data_hybrid$idx <- NULL
-    
-    hdps.data_hybrid$exposure <- as.numeric(I(hdps.data_hybrid$obese=='Yes'))
-    hdps.data_hybrid$outcome <- as.numeric(I(hdps.data_hybrid$diabetes=='Yes'))
-    
+
     proxy_hybrid <- names(proxy.df_hybrid[,-1])
     covarsTfull <- c(investigator.specified.covariates, proxy_hybrid)
     Y.form <- as.formula(paste0(c("outcome~ exposure", covarsTfull), 

### 2024-08-29 simResults_scenarioOR/1_bross/bross.R

@@ -94,16 +94,16 @@ for (i in 1:a) {
   } else {
     proxy.df_bross <- bross.list$autoselected_covariate_df
     hdps.data_bross <- merge(data[,c("idx",
-                                     outcome, 
-                                     exposure, 
+                                     "outcome", 
+                                     "exposure", 
                                      investigator.specified.covariates)],
                              proxy.df_bross,
                              by = "idx")
     hdps.data_bross$id <- hdps.data_bross$idx
     hdps.data_bross$idx <- NULL
     
-    hdps.data_bross$exposure <- as.numeric(I(hdps.data_bross$obese=='Yes'))
-    hdps.data_bross$outcome <- as.numeric(I(hdps.data_bross$diabetes=='Yes'))
+    #hdps.data_bross$exposure <- as.numeric(I(hdps.data_bross$obese=='Yes'))
+    #hdps.data_bross$outcome <- as.numeric(I(hdps.data_bross$diabetes=='Yes'))
     
     proxy_bross <- names(proxy.df_bross[,-1])
     proxyform <- paste0(proxy_bross, collapse = "+")

### 2024-08-29 simResults_scenarioOR/2_hybrid/hybrid.R

@@ -97,16 +97,16 @@ for (i in 1:a) {
   } else {
     proxy.df_hybrid <- hybrid.list$autoselected_covariate_df
     hdps.data_hybrid <- merge(data[,c("idx",
-                                     outcome, 
-                                     exposure, 
+                                     "outcome", 
+                                     "exposure", 
                                      investigator.specified.covariates)],
                              proxy.df_hybrid,
                              by = "idx")
     hdps.data_hybrid$id <- hdps.data_hybrid$idx
     hdps.data_hybrid$idx <- NULL
     
-    hdps.data_hybrid$exposure <- as.numeric(I(hdps.data_hybrid$obese=='Yes'))
-    hdps.data_hybrid$outcome <- as.numeric(I(hdps.data_hybrid$diabetes=='Yes'))
+    #hdps.data_hybrid$exposure <- as.numeric(I(hdps.data_hybrid$obese=='Yes'))
+    #hdps.data_hybrid$outcome <- as.numeric(I(hdps.data_hybrid$diabetes=='Yes'))
     
     proxy_hybrid <- names(proxy.df_hybrid[,-1])
     covarsTfull <- c(investigator.specified.covariates, proxy_hybrid)

### 2024-08-30 simResults_scenario/11_kitchen/kitchen.R
kitchen

@@ -1,4 +1,5 @@
-path0 <- "E:/GitHub/hdPS-proxy-select/"
+# path0 <- "E:/GitHub/hdPS-proxy-select/"
+path0 <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/"
 
 library(autoCovariateSelection)
 library(dplyr)
@@ -128,8 +129,8 @@ for (i in a0:a) {
     # hdps.data_kitchen$idx <- NULL
     
   hdps.data_kitchen <- data
-  hdps.data_kitchen$exposure <- as.numeric(I(hdps.data_kitchen$obese=='Yes'))
-  hdps.data_kitchen$outcome <- as.numeric(I(hdps.data_kitchen$diabetes=='Yes'))
+  # hdps.data_kitchen$exposure <- as.numeric(I(hdps.data_kitchen$obese=='Yes'))
+  # hdps.data_kitchen$outcome <- as.numeric(I(hdps.data_kitchen$diabetes=='Yes'))
     
   proxy_kitchen <- grep("^rec", names(data), value = TRUE)
   proxyform <- paste0(proxy_kitchen, collapse = "+")

### 2024-08-30 simResults_scenarioOR/11_kitchen/kitchen.R

@@ -1,4 +1,5 @@
-path0 <- "E:/GitHub/hdPS-proxy-select/"
+# path0 <- "E:/GitHub/hdPS-proxy-select/"
+path0 <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/"
 
 library(autoCovariateSelection)
 library(dplyr)
@@ -17,8 +18,8 @@ library(randomForest)
 # ---------------------------------------------------------------
 
 ### global information
-exposure <- "obese"
-outcome <- "diabetes" 
+# exposure <- "obese"
+# outcome <- "diabetes" 
 investigator.specified.covariates <- 
   c(# Demographic
     "age.cat", "sex", "education", "race", 
@@ -128,8 +129,8 @@ for (i in a0:a) {
     # hdps.data_kitchen$idx <- NULL
     
   hdps.data_kitchen <- data
-  hdps.data_kitchen$exposure <- as.numeric(I(hdps.data_kitchen$obese=='Yes'))
-  hdps.data_kitchen$outcome <- as.numeric(I(hdps.data_kitchen$diabetes=='Yes'))
+  # hdps.data_kitchen$exposure <- as.numeric(I(hdps.data_kitchen$obese=='Yes'))
+  # hdps.data_kitchen$outcome <- as.numeric(I(hdps.data_kitchen$diabetes=='Yes'))
     
   proxy_kitchen <- grep("^rec", names(data), value = TRUE)
   proxyform <- paste0(proxy_kitchen, collapse = "+")

### 2024-09-01 doc/app6.R
app 6

@@ -1,0 +1,656 @@
+library(shiny)
+library(ggplot2)
+library(dplyr)
+library(cowplot)
+library(rsimsum)
+library(knitr)
+library(reshape2)
+library(tidyr)
+
+# Define the models you want to work with
+model_names <- c(
+  kitchen = "Kitchen sink",
+  bross = "Bross-based hdPS",
+  hybrid = "Hybrid hdPS",
+  ga = "Genetic Algorithm",
+  xgboost = "XGBoost",
+  rf = "Random Forest",
+  forward = "Forward Selection",
+  backward = "Backward Elimination",
+  lasso = "LASSO",  
+  enet = "Elasticnet"
+)
+
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  becover = "Bias-eliminated Coverage",
+  relerror = "Relative Error",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  power = "Power",
+  nsim = "# of simulations"
+)
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Exploring the Simulation Results"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario_select", "Choose a scenario:",
+                  choices = list("Frequent Outcome and Exposure" = "scenario",
+                                 "Rare Exposure" = "scenarioER",
+                                 "Rare Outcome" = "scenarioOR")
+      ),
+      selectInput("metric_select", "Choose a performance metric:",
+                  choices = metric_names
+      ),
+      selectInput("plot_type", "Choose a plot type:",
+                  choices = c("Lolly" = "lolly",
+                              "Forest" = "forest",
+                              "Zipper" = "zip",
+                              "Heat" = "heat")),
+      sliderInput("num_indices", "Select number of simulations:",
+                  min = 100, max = 1000, value = 500, step = 50),
+      checkboxInput("show_num_indices", "Show number of simulation results aggregated", value = TRUE)  
+    ),
+    mainPanel(
+      # Display the number of simulations if the checkbox is checked
+      conditionalPanel(
+        condition = "input.show_num_indices == true",
+        textOutput("num_indices_output")  # Text output for num_indices
+      ),
+      tabsetPanel(
+        tabPanel("Plot", 
+                 tags$p("The plot represents the selected scenario and the metric."),
+                 downloadButton("download_png", "Download PNG"),
[…]

### 2024-09-01 Writeup/appendix/Appendix.RMD
appFigures

@@
 
-\hypertarget{X}{%
-\section{X}\label{X}}
+# Variables Used for Plasmode Simulation Data Generation
+
+1. Original demographic variables (8)
+
+- age, 
+- sex, 
+- education, 
+- race, 
+- marital status, 
+- income, 
+- country where born, 
+- survey cycle
+
+2. Original behaviour variables (5)
+
+- smoking, 
+- diet, 
+- high cholesterol, 
+- physical activity, 
+- sleep
+
+3. Original health history / access variables (2)
+
+- diabetes family history, 
+- medical access
+
+4.
+Transformed lab variables (6) (complex forms) based on original lab variables: uric acid, protein, bilirubin, phosphorus, sodium, potassium, globulin, calcium, systolic blood pressure, diastolic blood pressure.
+
+- Tranfored.var.1 = log(globulin)
+- Tranfored.var.2 = protein*calcium
+- Tranfored.var.3 = diastolicBP/systolicBP)^2
+- Tranfored.var.4 = sqrt(uric acid+bilirubin)/2
+- Tranfored.var.5 = phosphorus^2/(sodium*potassium)
+- Tranfored.var.6 = log(systolicBP+10)
+
+5. Count based prescription codes (1) (proxies of comorbidity)
+
+Simple count (1 variable) = sum of selected ICD-10 CM codes (converted to recurrence covariates) who had less than 0.8 or greater than 1.2 compared to the outcome = $\sum_{s=1}^{94} R_s$
+
+# True outcome model for Plasmode Simulation Data Generation
+
+Diabetes (outcome) =  Obese (exposure) + demographic/behaviour/health history variables + transformed lab variables + simple count with selected ICD-10 codes
+
+# SE comparison
+
+```{r, echo=FALSE, out.width="100%", fig.cap="Standard Error Comparison for Different Methods (Overall) when outcome and exposure are frequent.", fig.align="center", fig.label="fig:se-comparison-overall"}
+knitr::include_graphics("se_comparison_plot.png")
+```
+
+```{r, echo=FALSE, out.width="100%", fig.cap="Standard Error Comparison for Different Methods (Overall) when outcome is frequent but exposure is rare.", fig.align="center", fig.label="fig:se-comparison-overall"}
+knitr::include_graphics("se_comparison_plotER.png")
+```
+
+```{r, echo=FALSE, out.width="100%", fig.cap="Standard Error Comparison for Different Methods (Overall) when outcome is rare but exposure is frequent", fig.align="center", fig.label="fig:se-comparison-overall"}
+knitr::include_graphics("se_comparison_plotOR.png")
+```

### 2024-09-01 Writeup/appendix/Appendix.tex
appFigures

@@
 
-\hypertarget{X}{%
-\section{X}\label{X}}
+\section{Variables Used for Plasmode Simulation Data
+Generation}\label{variables-used-for-plasmode-simulation-data-generation}
 
-  \bibliography{mybibfile.bib}
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Original demographic variables (8)
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  age,
+\item
+  sex,
+\item
+  education,
+\item
+  race,
+\item
+  marital status,
+\item
+  income,
+\item
+  country where born,
+\item
+  survey cycle
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Original behaviour variables (5)
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  smoking,
+\item
+  diet,
+\item
+  high cholesterol,
+\item
+  physical activity,
+\item
+  sleep
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Original health history / access variables (2)
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  diabetes family history,
+\item
+  medical access
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
+\item
+  Transformed lab variables (6) (complex forms) based on original lab
+  variables: uric acid, protein, bilirubin, phosphorus, sodium,
+  potassium, globulin, calcium, systolic blood pressure, diastolic blood
+  pressure.
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  Tranfored.var.1 = log(globulin)
+\item
+  Tranfored.var.2 = protein*calcium
+\item
+  Tranfored.var.3 = diastolicBP/systolicBP)\^{}2
+\item
+  Tranfored.var.4 = sqrt(uric acid+bilirubin)/2
+\item
+  Tranfored.var.5 = phosphorus\^{}2/(sodium*potassium)
+\item
+  Tranfored.var.6 = log(systolicBP+10)
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{4}
+\tightlist
+\item
+  Count based prescription codes (1) (proxies of comorbidity)
+\end{enumerate}
+
+Simple count (1 variable) = sum of selected ICD-10 CM codes (converted
+to recurrence covariates) who had less than 0.8 or greater than 1.2
+compared to the outcome = \(\sum_{s=1}^{94} R_s\)
+
+\section{True outcome model for Plasmode Simulation Data
+Generation}\label{true-outcome-model-for-plasmode-simulation-data-generation}
+
+Diabetes (outcome) = Obese (exposure) + demographic/behaviour/health
+history variables + transformed lab variables + simple count with
+selected ICD-10 codes
+
+\section{SE comparison}\label{se-comparison}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{se_comparison_plot}
+
+}
+
+\caption{Standard Error Comparison for Different Methods (Overall) when outcome and exposure are frequent.}\label{fig:unnamed-chunk-1}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{se_comparison_plotER}
+
+}
+
+\caption{Standard Error Comparison for Different Methods (Overall) when outcome is frequent but exposure is rare.}\label{fig:unnamed-chunk-2}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{se_comparison_plotOR}
+
+}
+
+\caption{Standard Error Comparison for Different Methods (Overall) when outcome is rare but exposure is frequent}\label{fig:unnamed-chunk-3}
+\end{figure}
+
+  \bibliography{mergedbibliography.bib}
 

### 2024-09-01 Writeup/manuscript.Rmd
appFigures

@@
 
-title: Challenges of Univariate Proxy Variable Screening in High-Dimensional Propensity Score Analysis - An Argument for Multivariate Approaches
-titlerunning: Deep Learning in Propensity Score Analysis
+title: Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Analysis
+titlerunning: High-Dimensional Propensity Score
 
@@
     affiliation: [3]
-    corresponding: TRUE
+    corresponding: FALSE
     equalcont: 
@@
   **Purpose**: 
-
   **Methods:** 
-
   **Results:** 
-
   **Conclusion:**
@@
 header-includes: |
+  \usepackage{natbib}
   \usepackage{hyperref}
@@
 
-**Aim**:
+**Aim**: The aim of this research is to systematically evaluate and compare different proxy selection methods within the context of high-dimensional propensity score (hdPS) analysis.
+Specifically, the study focuses on assessing how these methods, including alternative variable selection approaches, perform in selecting proxy variables for confounding adjustment compared to the traditional Bross method within the hdPS framework.
+We seek to determine whether these alternative methods offer superior performance in estimating treatment effects compared to the default Bross formula.
 
@@
 
-**Right Heart Catheterization dataset**:
+**Motivating Example**: To explore the relationship between obesity and the risk of diabetes, we revisited this association using data from three cycles of the National Health and Nutrition Examination Survey (NHANES) covering the years 2013-2014, 2015-2016, and 2017-2018 [@karim2024high].
+This analysis was informed by a thorough review of the existing literature [@saydah2014trends;@liu2013association;@kabadi2012joint;@ostchega2012abdominal].
+To identify relevant covariates, we constructed a causal diagram based on established causal inference principles [@greenland1999causal].
+The covariates included in our analysis were carefully selected and categorized into Demographic, Behavioral, Health History, Access-related, and Laboratory variables [@karim2024high].
+While most of these variables were binary or categorical, the Laboratory variables were continuous.
 
-**Plasmode simulation**: See Table \ref{table:scenarios} for the description of the scenarios under consideration.
+**Plasmode simulation**: To rigorously assess the performance of the methods under consideration, we employed a plasmode simulation framework, which is particularly well-suited for reflecting real-world data structures and complexities [@franklin2014plasmode].
+This approach was modeled after the analytic dataset derived from NHANES and involved resampling from the observed covariates and exposure information (i.e., obesity) without altering them.
+By mirroring key aspects of an actual epidemiological study, this simulation framework offers a significant advantage over traditional Monte Carlo simulations, which often rely on idealized assumptions.
+
+**Simulation scenarios under consideration**: Our plasmode simulation was conducted over 500 iterations.
+For the base simulation scenario, we set the prevalence of exposure (obesity) and the event rate (diabetes) at 30%, with a true odds ratio (OR) parameter of 1, corresponding to a risk difference (RD) of 0.
+Each simulated dataset had a sample size of 3,000 participants.
+The description of other scenarios under consideration is provided in Table \ref{table:scenarios}.
 
@@
 \centering
-\caption{Simulation Scenarios for plasmode simulation.}
+\caption{Overview of Plasmode Simulation Scenarios Reflecting Varying Exposure and Outcome Prevalences Based on National Health and Nutrition Examination Survey (NHANES) Data Cycles (2013-2018)}
 \label{table:scenarios}
@@
   \midrule
-  (i) Frequent Exposure and Outcome (Base) & 30\% & 30\% & 1 & 3,500 \\
-  (ii) Rare Exposure and Frequent Outcome & 5\% & 30\% & 1 & 3,500 \\
-  (iii) Frequent Exposure and Rare Outcome & 30\% & 5\% & 1 & 3,500 \\
+  (i) Frequent Exposure and Outcome (Base) & 30\% & 30\% & 1 & 3,000 \\
+  (ii) Rare Exposure and Frequent Outcome & 5\% & 30\% & 1 & 3,000 \\
+  (iii) Frequent Exposure and Rare Outcome & 30\% & 5\% & 1 & 3,000 \\
   \bottomrule
@@
 
-**True data generating mechanism used in plasmode simulation**:
+**True Data Generating Mechanism Used in Plasmode Simulation**: The primary goal of this study is to evaluate various variable selection methods under realistic conditions.
+To achieve this, we formulated the outcome data based on a specific model specification that incorporates both exposure and covariates, including investigator-specified and proxy variables.
+The model specification consists of three key components:
 
-**Performance measures**: From this simulation, we derived several performance metrics: (1) bias, (2) average model standard error (SE; the average of estimated SEs obtained from a model over repeated samples), (3) empirical SE (the standard deviation of estimated treatment effects across repeated samples), (4) MSE, (5) coverage probability of 95% confidence intervals, (6) bias-eliminated coverage, and (7) Zip plot [@morris2019using; @white2023check].
+1. *Investigator-Specified Covariates*: We retained the original investigator-specified covariates, which were either binary or categorical, reflecting how real-world studies typically operate.
+
+2.
+*Transformation of Laboratory Variables*: In real-world studies, it is common for analysts to lack precise knowledge of the true model specification.
+To simulate this uncertainty, we transformed the continuous laboratory variables using complex functions such as logarithmic, exponential, square root, polynomial transformations, and interactions.
+This reflects the challenges analysts face in correctly specifying models when dealing with continuous data.
+
+3.
+*Inclusion of Proxy Variables*: Real-world studies often deal with unmeasured confounding, which researchers attempt to mitigate by adding proxy variables.
+However, when a large number of proxies are added, some may act as noise variables, contributing little to the analysis.
+To simulate this, we selected only those binary proxy covariates (referred to as recurrence covariates in hdPS terminology) that had a relative risk (RR) of less than 0.8 or greater than 1.2 concerning the outcome.
+Out of 143 proxy covariates, 94 met this criterion and were included in calculating a simple comorbidity burden measure.
+The remaining 49 covariates were excluded from this calculation and considered noise.
+This comorbidity burden measure was then incorporated into our model specification for generating the plasmode data.
+
+**Performance Measures**: From this simulation, we derived several performance metrics to evaluate the effectiveness of the methods under consideration: (1) bias, (2) average model standard error (SE; the average of estimated SEs obtained from a model over repeated samples), (3) empirical SE (the standard deviation of estimated treatment effects across repeated samples), (4) mean squared error (MSE), (5) coverage probability of 95% confidence intervals, (6) bias-corrected coverage, and (7) Zip plot [@morris2019using; @white2023check].
 
@@
 
+The comparison between the data generation process and the analysis process reveals two key differences: (i) The data generation used transformed laboratory variables, whereas the analysis was conducted using only the original laboratory variables.
+(ii) The data generation employed a simple sum of selected proxy variables (sum of 94 proxy covariates), while the analysis included all proxy variables (143 binary proxies), with 49 of these acting as noise variables.
+These differences help us assess how the proxy variable selection methods handle model misspecification and the presence of noise variables.
+
+1.
+**Kitchen sink model**: This is a base model for comparison, where no variable selection approaches were used.
+All investigator-selected features and all proxy variables were used to model [@karim2018can].
+
+2.
+**Bross formula**: The Bross formula is a statistical method used to calculate the bias introduced by not adjusting for a covariate [@bross1966spurious].
+In hdPS analysis, this formula was originally applied to each proxy variable to measure and rank the potential bias if the covariate were not adjusted for.
+In our analysis, the 100 proxies with the highest bias rankings are selected for further modeling [@schneeweiss2009high; @wyss2018erratum].
+
+3.
+**Least Absolute Shrinkage and Selection Operator (LASSO)**: LASSO is a variable selection technique that limits the number of variables by adding a penalty term to the regression model.
+Cross-validation (CV) is used in LASSO to identify variables with non-zero coefficients in the best model by optimizing the penalty value [@franklin2015regularized; @schneeweiss2017variable; @karim2018can].
+
+4.
+**Hybrid of hdPS and LASSO**: Instead of relying solely on LASSO for variable selection, a hybrid approach combines the Bross formula and LASSO.
+First, hdPS variables are selected using the hdPS algorithm (e.g., the top 100), and then LASSO is applied to further refine the selection [@karim2018can; @franklin2015regularized].
+
+5.
+**Elasticnet**: Elastic Net is an extension of LASSO that includes an additional penalty term to handle multicollinearity by grouping correlated features and selecting the most representative ones [@karim2018can].
+
+6.
+**Random Forest**: The Random Forest (RF) algorithm is an ensemble learning method that constructs multiple decision trees to perform classification [@breiman2001random].
+It calculates the importance of each proxy variable based on the decrease in impurity or Gini importance, providing a ranking of the proxies.
+The top 100 variables from this ranking are manually selected for further modeling [@schneeweiss2017variable].
+
+7.
+**XGBoost**: XGBoost is a gradient boosting algorithm used to optimize machine learning models [@chen2016xgboost].
+It builds decision trees that make splits based on maximum impurity reduction, and it assigns an importance score to each proxy variable by calculating the mean decrease in impurity [@xiao2024interpretable].
+
+8.
+**Stepwise**: Stepwise selection is a progressive feature selection method that can proceed in two directions—forward or backward—based on the maximum adjusted R-squared.
+We have implemented two versions: (a) Forward selection (FS) starts with an initial model (e.g., including all investigator-selected features) and adds proxies to the model one at a time.
+(b) Backward elimination (BE) starts with a full model (e.g., all investigator-selected features and all proxy variables) and removes features one at a time based on their contribution to the model.
+
+9.
+**Genetic algorithm (GA)**: GA is an evolutionary algorithm inspired by the theory of natural selection [@holland1975adaptation].
+It operates by evolving offspring from a population of the fittest individuals over several generations, evaluating and selecting the best combination of features or variables that maximize prediction accuracy.
+
 # Results
+
+```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Bias Across Different Methods in hdPS Analysis", fig.align="center", fig.label="fig:bias-comparison"}
+knitr::include_graphics("figures/metric_comparison_Bias.png")
+```
+
+```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Coverage Probability Across Different Methods in hdPS Analysis", fig.align="center", fig.label="fig:bias-comparison"}
+knitr::include_graphics("figures/metric_comparison_Coverage.png")
+```
 
@@
 
+*Here we include full data analysis (with some summary results like exposure and outcome prevalence, and sample size) and report OR and RD.
+Also mention how many proxies were chosen (add in the picture of RD and OR; side by side for each method, ordered my magnitude of RD), and how many were in common with hdPS (add table).*
+
+```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
+The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
+Methods are arranged by the number of variables used in the models.", fig.label="fig:comparison-plot", message=FALSE, warning=FALSE}
+library(ggplot2)
+library(dplyr)
+
+# Combine RD and OR data into a single data frame
+data_combined <- data.frame(
+  Method = rep(c("Bross", "Hybrid", "LASSO", "Elasticnet", "GA", "XGBoost", "RF", "FS", "BE"), 2),
+  # These are approximate values
+  Value = c(0.078, 0.078, 0.080, 0.080, 0.079, 0.080, 0.080, 0.080, 0.080, 
+            1.50, 1.53, 1.55, 1.55, 1.55, 1.53, 1.55, 1.55, 1.55),
+  LowerCI = c(0.06, 0.05, 0.06, 0.06, 0.06, 0.05, 0.06, 0.06, 0.06,
+              1.40, 1.40, 1.45, 1.45, 1.45, 1.40, 1.45, 1.45, 1.45),
+  UpperCI = c(0.09, 0.10, 0.10, 0.10, 0.10, 0.10, 0.10, 0.10, 0.10,
+              1.60, 1.65, 1.65, 1.65, 1.65, 1.65, 1.65, 1.65, 1.65),
+  Measure = rep(c("RD", "OR"), each = 9),
+  Variables = rep(c(100, 49, 60, 69, 64, 48, 100, 59, 59), 2)
+)
+
+# Create a new Method label that includes the number of variables
+data_combined <- data_combined %>%
+  mutate(MethodLabel = paste(Method, " [", Variables, "]", sep = ""))
+
+# Reorder the factor levels of MethodLabel based on the number of variables
+data_combined$MethodLabel <- factor(data_combined$MethodLabel,
+                                    levels = unique(data_combined$MethodLabel[order(data_combined$Variables)]))
+
+# Create the plot with the reordered MethodLabel
+ggplot(data_combined, aes(x = Value, y = MethodLabel)) +
+  geom_point(size = 4) +
+  geom_errorbarh(aes(xmin = LowerCI, xmax = UpperCI), height = 0.2) +
+  facet_grid(. ~ Measure, scales = "free_x") +
+  labs(x = "Value",
+       y = "Method [Chosen number of proxies]") +
+  theme_minimal() +
+  theme(strip.text = element_text(size = 12, face = "bold"))
+```
+
+Table \ref{tab:method-comparison} presents a pairwise comparison of the number of proxy features shared between different variable selection methods used in the analysis.
+Each cell in the table indicates the count of common proxy variables selected by the method in the corresponding row and column.
+The diagonal cells, where the row and column methods are the same, represent the total number of proxy variables selected exclusively by each method.
+
+\begin{table}[htbp]
+\centering
+\caption{Comparison of variable overlap of selected proxies across different methods used to evaluate the association between obesity and diabetes}
+\label{tab:method-comparison}
+\begin{tabular}{lccccccccc}
+\toprule
+ & \textbf{Bross} & \textbf{Hybrid} & \textbf{LASSO} & \textbf{Elasticnet} & \textbf{GA} & \textbf{XGBoost} & \textbf{RF} & \textbf{FS} & \textbf{BE} \\
+\midrule
+\textbf{Bross formula} & 100 & & & & & & & & \\
+\textbf{Hybrid (Bross and LASSO)} & 49 & 49 & & & & & & & \\
+\textbf{LASSO} & 47 & 47 & 60 & & & & & & \\
+\textbf{Elasticnet} & 54 & 48 & 60 & 69 & & & & & \\
+\textbf{Genetic algorithm (GA)} & 44 & 28 & 36 & 40 & 64 & & & & \\
+\textbf{XGBoost} & 38 & 24 & 28 & 30 & 25 & 48 & & & \\
+\textbf{Random Forest (RF)} & 72 & 37 & 42 & 50 & 36 & 48 & 100 & & \\
+\textbf{Forward selection (FS)} & 45 & 41 & 51 & 54 & 35 & 25 & 43 & 59 & \\
+\textbf{Backward elimination (BE)} & 45 & 41 & 51 & 54 & 35 & 25 & 43 & 59 & 59 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 **Computing time**:
+
+*Report computing time for the Real-world analysis for each method. (add ordered table)*
 

### 2024-09-01 Writeup/manuscript.tex
appFigures

@@
 
+\usepackage{natbib}
 \usepackage{hyperref}
@@
 
-\title[Deep Learning in Propensity Score Analysis]{Challenges of
-Univariate Proxy Variable Screening in High-Dimensional Propensity Score
-Analysis - An Argument for Multivariate Approaches}
+\title[High-Dimensional Propensity Score]{Understanding the role of
+different proxy selection methods in High-Dimensional Propensity Score
+Analysis}
 
@@
 
-\author*[3]{\fnm{Yang} \sur{Lei} }
+\author[3]{\fnm{Yang} \sur{Lei} }
 
@@
 
-\abstract{\textbf{Purpose}:
-
-\textbf{Methods:}
-
-\textbf{Results:}
-
+\abstract{\textbf{Purpose}: \textbf{Methods:} \textbf{Results:}
 \textbf{Conclusion:}}
@@
 
-\textbf{Aim}:
+\textbf{Aim}: The aim of this research is to systematically evaluate and
+compare different proxy selection methods within the context of
+high-dimensional propensity score (hdPS) analysis. Specifically, the
+study focuses on assessing how these methods, including alternative
+variable selection approaches, perform in selecting proxy variables for
+confounding adjustment compared to the traditional Bross method within
+the hdPS framework. We seek to determine whether these alternative
+methods offer superior performance in estimating treatment effects
+compared to the default Bross formula.
 
@@
 
-\textbf{Right Heart Catheterization dataset}:
+\textbf{Motivating Example}: To explore the relationship between obesity
+and the risk of diabetes, we revisited this association using data from
+three cycles of the National Health and Nutrition Examination Survey
+(NHANES) covering the years 2013-2014, 2015-2016, and 2017-2018
+\citep{karim2024high}. This analysis was informed by a thorough review
+of the existing literature
+\citep{saydah2014trends, liu2013association, kabadi2012joint, ostchega2012abdominal}.
+To identify relevant covariates, we constructed a causal diagram based
+on established causal inference principles \citep{greenland1999causal}.
+The covariates included in our analysis were carefully selected and
+categorized into Demographic, Behavioral, Health History,
+Access-related, and Laboratory variables \citep{karim2024high}. While
+most of these variables were binary or categorical, the Laboratory
+variables were continuous.
 
-\textbf{Plasmode simulation}: See Table \ref{table:scenarios} for the
-description of the scenarios under consideration.
+\textbf{Plasmode simulation}: To rigorously assess the performance of
+the methods under consideration, we employed a plasmode simulation
+framework, which is particularly well-suited for reflecting real-world
+data structures and complexities \citep{franklin2014plasmode}. This
+approach was modeled after the analytic dataset derived from NHANES and
+involved resampling from the observed covariates and exposure
+information (i.e., obesity) without altering them. By mirroring key
+aspects of an actual epidemiological study, this simulation framework
+offers a significant advantage over traditional Monte Carlo simulations,
+which often rely on idealized assumptions.
+
+\textbf{Simulation scenarios under consideration}: Our plasmode
+simulation was conducted over 500 iterations. For the base simulation
+scenario, we set the prevalence of exposure (obesity) and the event rate
+(diabetes) at 30\%, with a true odds ratio (OR) parameter of 1,
+corresponding to a risk difference (RD) of 0. Each simulated dataset had
+a sample size of 3,000 participants. The description of other scenarios
+under consideration is provided in Table \ref{table:scenarios}.
 
@@
 \centering
-\caption{Simulation Scenarios for plasmode simulation based on the Right Heart Catheterization (RHC) study.}
+\caption{Overview of Plasmode Simulation Scenarios Reflecting Varying Exposure and Outcome Prevalences Based on National Health and Nutrition Examination Survey (NHANES) Data Cycles (2013-2018)}
 \label{table:scenarios}
@@
 
-\textbf{True data generating mechanism used in plasmode simulation}:
+\textbf{True Data Generating Mechanism Used in Plasmode Simulation}: The
+primary goal of this study is to evaluate various variable selection
+methods under realistic conditions. To achieve this, we formulated the
+outcome data based on a specific model specification that incorporates
+both exposure and covariates, including investigator-specified and proxy
+variables. The model specification consists of three key components:
 
-\textbf{Performance measures}: From this simulation, we derived several
-performance metrics: (1) bias, (2) average model standard error (SE; the
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Investigator-Specified Covariates}: We retained the original
+  investigator-specified covariates, which were either binary or
+  categorical, reflecting how real-world studies typically operate.
+\item
+  \emph{Transformation of Laboratory Variables}: In real-world studies,
+  it is common for analysts to lack precise knowledge of the true model
+  specification. To simulate this uncertainty, we transformed the
+  continuous laboratory variables using complex functions such as
+  logarithmic, exponential, square root, polynomial transformations, and
+  interactions. This reflects the challenges analysts face in correctly
+  specifying models when dealing with continuous data.
+\item
+  \emph{Inclusion of Proxy Variables}: Real-world studies often deal
+  with unmeasured confounding, which researchers attempt to mitigate by
+  adding proxy variables. However, when a large number of proxies are
+  added, some may act as noise variables, contributing little to the
+  analysis. To simulate this, we selected only those binary proxy
+  covariates (referred to as recurrence covariates in hdPS terminology)
+  that had a relative risk (RR) of less than 0.8 or greater than 1.2
+  concerning the outcome. Out of 143 proxy covariates, 94 met this
+  criterion and were included in calculating a simple comorbidity burden
+  measure. The remaining 49 covariates were excluded from this
+  calculation and considered noise. This comorbidity burden measure was
+  then incorporated into our model specification for generating the
+  plasmode data.
+\end{enumerate}
+
+\textbf{Performance Measures}: From this simulation, we derived several
+performance metrics to evaluate the effectiveness of the methods under
+consideration: (1) bias, (2) average model standard error (SE; the
 average of estimated SEs obtained from a model over repeated samples),
 (3) empirical SE (the standard deviation of estimated treatment effects
-across repeated samples), (4) MSE, (5) coverage probability of 95\%
-confidence intervals, (6) bias-eliminated coverage, and (7) Zip plot
-\citep{morris2019using, white2023check}.
+across repeated samples), (4) mean squared error (MSE), (5) coverage
+probability of 95\% confidence intervals, (6) bias-corrected coverage,
+and (7) Zip plot \citep{morris2019using, white2023check}.
 
@@
 
+The comparison between the data generation process and the analysis
+process reveals two key differences: (i) The data generation used
+transformed laboratory variables, whereas the analysis was conducted
+using only the original laboratory variables. (ii) The data generation
+employed a simple sum of selected proxy variables (sum of 94 proxy
+covariates), while the analysis included all proxy variables (143 binary
+proxies), with 49 of these acting as noise variables. These differences
+help us assess how the proxy variable selection methods handle model
+misspecification and the presence of noise variables.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \textbf{Kitchen sink model}: This is a base model for comparison,
+  where no variable selection approaches were used. All
+  investigator-selected features and all proxy variables were used to
+  model \citep{karim2018can}.
+\item
+  \textbf{Bross formula}: The Bross formula is a statistical method used
+  to calculate the bias introduced by not adjusting for a covariate
+  \citep{bross1966spurious}. In hdPS analysis, this formula was
+  originally applied to each proxy variable to measure and rank the
+  potential bias if the covariate were not adjusted for. In our
+  analysis, the 100 proxies with the highest bias rankings are selected
+  for further modeling \citep{schneeweiss2009high, wyss2018erratum}.
+\item
+  \textbf{Least Absolute Shrinkage and Selection Operator (LASSO)}:
+  LASSO is a variable selection technique that limits the number of
+  variables by adding a penalty term to the regression model.
+  Cross-validation (CV) is used in LASSO to identify variables with
+  non-zero coefficients in the best model by optimizing the penalty
+  value
+  \citep{franklin2015regularized, schneeweiss2017variable, karim2018can}.
+\item
+  \textbf{Hybrid of hdPS and LASSO}: Instead of relying solely on LASSO
+  for variable selection, a hybrid approach combines the Bross formula
+  and LASSO. First, hdPS variables are selected using the hdPS algorithm
+  (e.g., the top 100), and then LASSO is applied to further refine the
+  selection \citep{karim2018can, franklin2015regularized}.
+\item
+  \textbf{Elasticnet}: Elastic Net is an extension of LASSO that
+  includes an additional penalty term to handle multicollinearity by
+  grouping correlated features and selecting the most representative
+  ones \citep{karim2018can}.
+\item
+  \textbf{Random Forest}: The Random Forest (RF) algorithm is an
+  ensemble learning method that constructs multiple decision trees to
+  perform classification \citep{breiman2001random}. It calculates the
+  importance of each proxy variable based on the decrease in impurity or
+  Gini importance, providing a ranking of the proxies. The top 100
+  variables from this ranking are manually selected for further modeling
+  \citep{schneeweiss2017variable}.
+\item
+  \textbf{XGBoost}: XGBoost is a gradient boosting algorithm used to
+  optimize machine learning models \citep{chen2016xgboost}. It builds
+  decision trees that make splits based on maximum impurity reduction,
+  and it assigns an importance score to each proxy variable by
+  calculating the mean decrease in impurity
+  \citep{xiao2024interpretable}.
+\item
+  \textbf{Stepwise}: Stepwise selection is a progressive feature
+  selection method that can proceed in two directions---forward or
+  backward---based on the maximum adjusted R-squared. We have
+  implemented two versions: (a) Forward selection (FS) starts with an
+  initial model (e.g., including all investigator-selected features) and
+  adds proxies to the model one at a time. (b) Backward elimination (BE)
+  starts with a full model (e.g., all investigator-selected features and
+  all proxy variables) and removes features one at a time based on their
+  contribution to the model.
+\item
+  \textbf{Genetic algorithm (GA)}: GA is an evolutionary algorithm
+  inspired by the theory of natural selection
+  \citep{holland1975adaptation}. It operates by evolving offspring from
+  a population of the fittest individuals over several generations,
+  evaluating and selecting the best combination of features or variables
+  that maximize prediction accuracy.
+\end{enumerate}
+
 \section{Results}\label{results}
+
+\begin{figure}[th]
+
+{\centering \includegraphics[width=1\linewidth,]{figures/metric_comparison_Bias}
+
+}
+
+\caption{Comparison of Bias Across Different Methods in hdPS Analysis}\label{fig:unnamed-chunk-1}
+\end{figure}
+
+\begin{figure}[th]
+
+{\centering \includegraphics[width=1\linewidth,]{figures/metric_comparison_Coverage}
+
+}
+
+\caption{Comparison of Coverage Probability Across Different Methods in hdPS Analysis}\label{fig:unnamed-chunk-2}
+\end{figure}
 
@@
 
+\emph{Here we include full data analysis (with some summary results like
+exposure and outcome prevalence, and sample size) and report OR and RD.
+Also mention how many proxies were chosen (add in the picture of RD and
+OR; side by side for each method, ordered my magnitude of RD), and how
+many were in common with hdPS (add table).}
+
+\begin{figure}[th]
+
+{\centering \includegraphics[width=1\linewidth,]{manuscript_files/figure-latex/unnamed-chunk-3-1}
+
+}
+
+\caption{Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95\% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
+The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
+Methods are arranged by the number of variables used in the models.}\label{fig:unnamed-chunk-3}
+\end{figure}
+
+Table \ref{tab:method-comparison} presents a pairwise comparison of the
+number of proxy features shared between different variable selection
+methods used in the analysis. Each cell in the table indicates the count
+of common proxy variables selected by the method in the corresponding
+row and column. The diagonal cells, where the row and column methods are
+the same, represent the total number of proxy variables selected
+exclusively by each method.
+
+\begin{table}[htbp]
+\centering
+\caption{Comparison of variable overlap of selected proxies across different methods used to evaluate the association between obesity and diabetes}
+\label{tab:method-comparison}
+\begin{tabular}{lccccccccc}
+\toprule
+ & \textbf{Bross} & \textbf{Hybrid} & \textbf{LASSO} & \textbf{Elasticnet} & \textbf{GA} & \textbf{XGBoost} & \textbf{RF} & \textbf{FS} & \textbf{BE} \\
+\midrule
+\textbf{Bross formula} & 100 & & & & & & & & \\
+\textbf{Hybrid (Bross and LASSO)} & 49 & 49 & & & & & & & \\
+\textbf{LASSO} & 47 & 47 & 60 & & & & & & \\
+\textbf{Elasticnet} & 54 & 48 & 60 & 69 & & & & & \\
+\textbf{Genetic algorithm (GA)} & 44 & 28 & 36 & 40 & 64 & & & & \\
+\textbf{XGBoost} & 38 & 24 & 28 & 30 & 25 & 48 & & & \\
+\textbf{Random Forest (RF)} & 72 & 37 & 42 & 50 & 36 & 48 & 100 & & \\
+\textbf{Forward selection (FS)} & 45 & 41 & 51 & 54 & 35 & 25 & 43 & 59 & \\
+\textbf{Backward elimination (BE)} & 45 & 41 & 51 & 54 & 35 & 25 & 43 & 59 & 59 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \textbf{Computing time}:
+
+\emph{Report computing time for the Real-world analysis for each method.
+(add ordered table)}
 
@@
 \renewcommand\refname{References}
-\bibliography{mybibfile.bib}
+\bibliography{mergedbibliography.bib}
 

### 2024-09-02 Writeup/manuscript.Rmd
app6

@@
 
-```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Bias Across Different Methods in hdPS Analysis", fig.align="center", fig.label="fig:bias-comparison"}
+The results for each method under the different scenarios are summarized below.
+See Figures \ref{fig:bias-comparison} and \ref{fig:Coverage-comparison} for an overview of the performance in terms of bias and coverage, respectively.
+
+(i) **Frequent Exposure and Outcome (base) scenario**:
+
+1.
+*Bias*: The kitchen sink model, which includes all variables without selection, exhibited the smallest bias (0.0002).
+In contrast, the Genetic Algorithm (GA) showed the highest bias (0.0287).
+Among the other methods, Bross (-0.0001), Hybrid (0.0016), and Elasticnet (0.0036) demonstrated low bias, indicating that these methods provide estimates closer to the true effect.
+XGBoost (0.0074) and Random Forest (RF) (0.0034) had slightly higher bias but remained within acceptable limits.
+
+2.
+*Coverage*: Most methods, including Hybrid, Forward, Backward, LASSO, and Elasticnet, achieved high coverage values around 98$\%$, indicating well-calibrated confidence intervals.
+However, the GA method had significantly lower coverage (83.8$\%$), suggesting that its confidence intervals might be too narrow or biased, potentially missing the true effect.
+Given the bias in the GA method's results, we also calculated bias-eliminated coverage.
+This adjustment improved GA’s coverage to 96$\%$, but it still remained lower than that of the other methods.
+
+3.
+*Mean Squared Error (MSE)*: XGBoost achieved the lowest MSE (0.0006), indicating it as the most accurate method overall.
+Conversely, the GA method had the highest MSE (0.0016), reflecting its higher bias and variability.
+The kitchen sink model (0.0009), Bross (0.0008), Hybrid (0.0008), and Elasticnet (0.0009) all had relatively similar and moderate MSE values.
+
+4.
+*Standard Error (SE)*: The lowest Empirical SE was observed with XGBoost (0.0229), indicating high precision in its estimates.
+The kitchen sink model had the highest Empirical SE (0.0305), suggesting greater variability.
+Other methods such as GA (0.0274), Hybrid (0.0278), and Bross (0.0287) exhibited moderate variability, while LASSO (0.0299) and Elasticnet (0.0294) had slightly higher variability.
+Similarly, XGBoost also showed the lowest Model-based SE (0.0268), consistent with its low Empirical SE and indicating high precision.
+The kitchen sink model had the highest Model-based SE (0.0333), suggesting less precision in its estimates.
+
+**(ii) Rare Exposure and Frequent Outcome**:
+
+1.
+*Bias*: In this scenario, the kitchen sink model showed a relatively low bias (0.0025), but the Genetic Algorithm (GA) had the highest bias (0.0408), indicating a substantial deviation from the true effect.
+XGBoost (0.0259) also exhibited higher bias compared to other methods.
+On the other hand, Bross (0.0035), Hybrid (0.0049), and Elasticnet (0.0053) demonstrated moderate bias, while Random Forest (RF) (0.0127) and Forward Selection (0.0108) had slightly higher bias but remained within an acceptable range.
+
+2.
+*Coverage*: Most methods maintained high coverage levels, with XGBoost showing the highest coverage (96.2$\%$), suggesting that its confidence intervals were well-calibrated despite the higher bias.
+The GA method, however, had slightly lower coverage (92.2$\%$), indicating that its confidence intervals might be narrower, potentially excluding the true effect.
+Other methods such as RF, Forward, Backward, and Hybrid had coverage values around 95$\%$, suggesting adequate interval calibration.
+To account for the bias in GA, bias-eliminated coverage was calculated, which improved the coverage for GA to 94.2$\%$, still slightly lower than other methods.
+
+3.
+*Mean Squared Error (MSE)*: XGBoost and Hybrid methods both demonstrated the lowest MSE (0.0032), indicating that these methods were the most accurate in this scenario.
+The GA method, with a higher MSE (0.0043), reflected its substantial bias and variability.
+The kitchen sink model had an MSE of 0.0043, similar to GA, while other methods such as Bross, RF, and Elasticnet exhibited moderate MSE values, indicating reasonable accuracy.
+
+4.
+*Standard Error (SE)*: The lowest Empirical SE was observed with XGBoost (0.0507) and GA (0.0510), reflecting the high precision of these methods despite the higher bias.
+The kitchen sink model exhibited the highest Empirical SE (0.0656), indicating greater variability.
+Methods like Hybrid (0.0564), Bross (0.0595), and RF (0.0609) showed moderate variability, while Elasticnet (0.0597) and LASSO (0.0587) had slightly higher variability.
+In terms of Model-based SE, XGBoost (0.0531) and GA (0.0533) also showed low variability, while the kitchen sink model had the highest Model-based SE (0.0623), suggesting less precision in its estimates.
+
+**(iii) Frequent Exposure and Rare Outcome**:
+
+1.
+*Bias*: In this scenario, the kitchen sink model exhibited a moderate negative bias (-0.0093), similar to the Bross method (-0.0088).
+The Genetic Algorithm (GA) showed a significantly higher bias (0.0362), indicating a substantial deviation from the true effect.
+Among other methods, XGBoost demonstrated the lowest bias (-0.0061), while methods like Hybrid (-0.0082), Forward (-0.0070), and Backward (-0.0070) had slightly higher but still moderate biases.
+Elasticnet and LASSO both had biases of -0.0079, reflecting slightly larger deviations compared to XGBoost but still within acceptable limits.
+
+2.
+*Coverage*: Most methods achieved good coverage, with XGBoost, Random Forest (RF), and Forward Selection each achieving a coverage rate of 95.4$\%$, indicating well-calibrated confidence intervals.
+The GA method, however, had slightly lower coverage (91.8$\%$), indicating that its confidence intervals might be narrower, potentially excluding the true effect.
+Bross and the kitchen sink model had slightly lower coverage values of 93.8$\%$ and 93.4$\%$, respectively.
+After accounting for bias, the bias-eliminated coverage for most methods, except GA, remained high, with values ranging from 98.4$\%$ to 99.0$\%$, indicating that most methods effectively adjusted for bias in their coverage estimates.
+GA's bias-eliminated coverage was lower at 93.4$\%$, reflecting its higher inherent bias.
+
+3.
+*Mean Squared Error (MSE)*: XGBoost exhibited the lowest MSE (0.0003), indicating it as the most accurate method overall in this scenario.
+GA had the highest MSE (0.0040), reflecting its substantial bias and variability.
+The kitchen sink model (0.0005), Bross (0.0005), and other methods like Hybrid (0.0004) and Elasticnet (0.0005) all had relatively similar MSE values, indicating moderate accuracy.
+
+4.
+*Standard Error (SE)*: The lowest Empirical SE was observed with XGBoost (0.0152), reflecting high precision in its estimates.
+The GA method exhibited the highest Empirical SE (0.0523), indicating greater variability and less precision.
+Methods like Hybrid (0.0184), Forward (0.0187), and Elasticnet (0.0203) showed moderate variability, while Bross (0.0206) and the kitchen sink model (0.0212) had slightly higher variability.
+In terms of Model-based SE, XGBoost (0.0179) again showed the lowest variability, consistent with its low Empirical SE, indicating that it provided the most stable estimates.
+The kitchen sink model had a slightly higher Model-based SE (0.0219), indicating less precision in its estimates.
+
+```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Bias Across Different Methods in hdPS Analysis\\label{fig:bias-comparison}", fig.align="center"}
 knitr::include_graphics("figures/metric_comparison_Bias.png")
@@
 
-```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Coverage Probability Across Different Methods in hdPS Analysis", fig.align="center", fig.label="fig:bias-comparison"}
+```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Coverage Probability Across Different Methods in hdPS Analysis\\label{fig:Coverage-comparison}", fig.align="center"}
 knitr::include_graphics("figures/metric_comparison_Coverage.png")
@@
 
+See Figure \ref{fig:comparison-plot} for the results from analyzing the NHANES (2013-2018) dataset.
+
 ```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
 The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
-Methods are arranged by the number of variables used in the models.", fig.label="fig:comparison-plot", message=FALSE, warning=FALSE}
+Methods are arranged by the number of variables used in the models.\\label{fig:comparison-plot}", message=FALSE, warning=FALSE}
 library(ggplot2)
@@
 
+XGBoost consistently outperformed other methods across all scenarios, demonstrating low bias, high coverage, and the lowest MSE.
+The GA, on the other hand, consistently underperformed with higher bias, lower coverage, and higher MSE, indicating less reliable estimates.
+The Bross method and the kitchen sink model generally provided moderate performance with low to moderate bias and reasonable coverage, but they were less accurate than XGBoost.
+Hybrid, Elasticnet, and LASSO methods showed competitive performance with moderate bias, good coverage, and acceptable MSE, making them reliable alternatives, though slightly less optimal than XGBoost.
+
 **Contextualizing the literature**:
@@
 
-1. MSE - Mean Squared Error
-2. SE - Standard Error
-3. PS - Propensity Score
-4. AE - Autoencoders
-5. DL - Deep Learning
-6. MARS - Multivariate Adaptive Regression Splines
-7. SMD - Standardized Mean Difference
-8. TMLE - Targeted Maximum Likelihood Estimation
-9. RHC - Right Heart Catheterization
-10. SUPPORT - Study to Understand Prognoses and Preferences for Outcomes and Risks of Treatments
+- hdPS: High-dimensional Propensity Score
+- NHANES: National Health and Nutrition Examination Survey
+- OR: Odds Ratio
+- RD: Risk Difference
+- SE: Standard Error
+- MSE: Mean Squared Error
+- LASSO: Least Absolute Shrinkage and Selection Operator
+- GA: Genetic Algorithm
+- RF: Random Forest
+- XGBoost: Extreme Gradient Boosting
+- FS: Forward Selection
+- BE: Backward Elimination
+- CV: Cross-Validation
+- RR: Relative Risk
+- Elasticnet: A regularized regression method that combines LASSO and Ridge regression
 

### 2024-09-02 Writeup/manuscript.tex
app6

@@
 
+The results for each method under the different scenarios are summarized
+below. See Figures \ref{fig:bias-comparison} and
+\ref{fig:Coverage-comparison} for an overview of the performance in
+terms of bias and coverage, respectively.
+
+\begin{enumerate}
+\def\labelenumi{(\roman{enumi})}
+\tightlist
+\item
+  \textbf{Frequent Exposure and Outcome (base) scenario}:
+\end{enumerate}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Bias}: The kitchen sink model, which includes all variables
+  without selection, exhibited the smallest bias (0.0002). In contrast,
+  the Genetic Algorithm (GA) showed the highest bias (0.0287). Among the
+  other methods, Bross (-0.0001), Hybrid (0.0016), and Elasticnet
+  (0.0036) demonstrated low bias, indicating that these methods provide
+  estimates closer to the true effect. XGBoost (0.0074) and Random
+  Forest (RF) (0.0034) had slightly higher bias but remained within
+  acceptable limits.
+\item
+  \emph{Coverage}: Most methods, including Hybrid, Forward, Backward,
+  LASSO, and Elasticnet, achieved high coverage values around 98\(\%\),
+  indicating well-calibrated confidence intervals. However, the GA
+  method had significantly lower coverage (83.8\(\%\)), suggesting that
+  its confidence intervals might be too narrow or biased, potentially
+  missing the true effect. Given the bias in the GA method's results, we
+  also calculated bias-eliminated coverage. This adjustment improved
+  GA's coverage to 96\(\%\), but it still remained lower than that of
+  the other methods.
+\item
+  \emph{Mean Squared Error (MSE)}: XGBoost achieved the lowest MSE
+  (0.0006), indicating it as the most accurate method overall.
+  Conversely, the GA method had the highest MSE (0.0016), reflecting its
+  higher bias and variability. The kitchen sink model (0.0009), Bross
+  (0.0008), Hybrid (0.0008), and Elasticnet (0.0009) all had relatively
+  similar and moderate MSE values.
+\item
+  \emph{Standard Error (SE)}: The lowest Empirical SE was observed with
+  XGBoost (0.0229), indicating high precision in its estimates. The
+  kitchen sink model had the highest Empirical SE (0.0305), suggesting
+  greater variability. Other methods such as GA (0.0274), Hybrid
+  (0.0278), and Bross (0.0287) exhibited moderate variability, while
+  LASSO (0.0299) and Elasticnet (0.0294) had slightly higher
+  variability. Similarly, XGBoost also showed the lowest Model-based SE
+  (0.0268), consistent with its low Empirical SE and indicating high
+  precision. The kitchen sink model had the highest Model-based SE
+  (0.0333), suggesting less precision in its estimates.
+\end{enumerate}
+
+\textbf{(ii) Rare Exposure and Frequent Outcome}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Bias}: In this scenario, the kitchen sink model showed a
+  relatively low bias (0.0025), but the Genetic Algorithm (GA) had the
+  highest bias (0.0408), indicating a substantial deviation from the
+  true effect. XGBoost (0.0259) also exhibited higher bias compared to
+  other methods. On the other hand, Bross (0.0035), Hybrid (0.0049), and
+  Elasticnet (0.0053) demonstrated moderate bias, while Random Forest
+  (RF) (0.0127) and Forward Selection (0.0108) had slightly higher bias
+  but remained within an acceptable range.
+\item
+  \emph{Coverage}: Most methods maintained high coverage levels, with
+  XGBoost showing the highest coverage (96.2\(\%\)), suggesting that its
+  confidence intervals were well-calibrated despite the higher bias. The
+  GA method, however, had slightly lower coverage (92.2\(\%\)),
+  indicating that its confidence intervals might be narrower,
+  potentially excluding the true effect. Other methods such as RF,
+  Forward, Backward, and Hybrid had coverage values around 95\(\%\),
+  suggesting adequate interval calibration. To account for the bias in
+  GA, bias-eliminated coverage was calculated, which improved the
+  coverage for GA to 94.2\(\%\), still slightly lower than other
+  methods.
+\item
+  \emph{Mean Squared Error (MSE)}: XGBoost and Hybrid methods both
+  demonstrated the lowest MSE (0.0032), indicating that these methods
+  were the most accurate in this scenario. The GA method, with a higher
+  MSE (0.0043), reflected its substantial bias and variability. The
+  kitchen sink model had an MSE of 0.0043, similar to GA, while other
+  methods such as Bross, RF, and Elasticnet exhibited moderate MSE
+  values, indicating reasonable accuracy.
+\item
+  \emph{Standard Error (SE)}: The lowest Empirical SE was observed with
+  XGBoost (0.0507) and GA (0.0510), reflecting the high precision of
+  these methods despite the higher bias. The kitchen sink model
+  exhibited the highest Empirical SE (0.0656), indicating greater
+  variability. Methods like Hybrid (0.0564), Bross (0.0595), and RF
+  (0.0609) showed moderate variability, while Elasticnet (0.0597) and
+  LASSO (0.0587) had slightly higher variability. In terms of
+  Model-based SE, XGBoost (0.0531) and GA (0.0533) also showed low
+  variability, while the kitchen sink model had the highest Model-based
+  SE (0.0623), suggesting less precision in its estimates.
+\end{enumerate}
+
+\textbf{(iii) Frequent Exposure and Rare Outcome}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Bias}: In this scenario, the kitchen sink model exhibited a
+  moderate negative bias (-0.0093), similar to the Bross method
+  (-0.0088). The Genetic Algorithm (GA) showed a significantly higher
+  bias (0.0362), indicating a substantial deviation from the true
+  effect. Among other methods, XGBoost demonstrated the lowest bias
+  (-0.0061), while methods like Hybrid (-0.0082), Forward (-0.0070), and
+  Backward (-0.0070) had slightly higher but still moderate biases.
+  Elasticnet and LASSO both had biases of -0.0079, reflecting slightly
+  larger deviations compared to XGBoost but still within acceptable
+  limits.
+\item
+  \emph{Coverage}: Most methods achieved good coverage, with XGBoost,
+  Random Forest (RF), and Forward Selection each achieving a coverage
+  rate of 95.4\(\%\), indicating well-calibrated confidence intervals.
+  The GA method, however, had slightly lower coverage (91.8\(\%\)),
+  indicating that its confidence intervals might be narrower,
+  potentially excluding the true effect. Bross and the kitchen sink
+  model had slightly lower coverage values of 93.8\(\%\) and 93.4\(\%\),
+  respectively. After accounting for bias, the bias-eliminated coverage
+  for most methods, except GA, remained high, with values ranging from
+  98.4\(\%\) to 99.0\(\%\), indicating that most methods effectively
+  adjusted for bias in their coverage estimates. GA's bias-eliminated
+  coverage was lower at 93.4\(\%\), reflecting its higher inherent bias.
+\item
+  \emph{Mean Squared Error (MSE)}: XGBoost exhibited the lowest MSE
+  (0.0003), indicating it as the most accurate method overall in this
+  scenario. GA had the highest MSE (0.0040), reflecting its substantial
+  bias and variability. The kitchen sink model (0.0005), Bross (0.0005),
+  and other methods like Hybrid (0.0004) and Elasticnet (0.0005) all had
+  relatively similar MSE values, indicating moderate accuracy.
+\item
+  \emph{Standard Error (SE)}: The lowest Empirical SE was observed with
+  XGBoost (0.0152), reflecting high precision in its estimates. The GA
+  method exhibited the highest Empirical SE (0.0523), indicating greater
+  variability and less precision. Methods like Hybrid (0.0184), Forward
+  (0.0187), and Elasticnet (0.0203) showed moderate variability, while
+  Bross (0.0206) and the kitchen sink model (0.0212) had slightly higher
+  variability. In terms of Model-based SE, XGBoost (0.0179) again showed
+  the lowest variability, consistent with its low Empirical SE,
+  indicating that it provided the most stable estimates. The kitchen
+  sink model had a slightly higher Model-based SE (0.0219), indicating
+  less precision in its estimates.
+\end{enumerate}
+
 \begin{figure}[th]
@@
 
-\caption{Comparison of Bias Across Different Methods in hdPS Analysis}\label{fig:unnamed-chunk-1}
+\caption{Comparison of Bias Across Different Methods in hdPS Analysis\label{fig:bias-comparison}}\label{fig:unnamed-chunk-1}
 \end{figure}
@@
 
-\caption{Comparison of Coverage Probability Across Different Methods in hdPS Analysis}\label{fig:unnamed-chunk-2}
+\caption{Comparison of Coverage Probability Across Different Methods in hdPS Analysis\label{fig:Coverage-comparison}}\label{fig:unnamed-chunk-2}
 \end{figure}
@@
 
+See Figure \ref{fig:comparison-plot} for the results from analyzing the
+NHANES (2013-2018) dataset.
+
 \begin{figure}[th]
@@
 The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
-Methods are arranged by the number of variables used in the models.}\label{fig:unnamed-chunk-3}
+Methods are arranged by the number of variables used in the models.\label{fig:comparison-plot}}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
+XGBoost consistently outperformed other methods across all scenarios,
+demonstrating low bias, high coverage, and the lowest MSE. The GA, on
+the other hand, consistently underperformed with higher bias, lower
+coverage, and higher MSE, indicating less reliable estimates. The Bross
+method and the kitchen sink model generally provided moderate
+performance with low to moderate bias and reasonable coverage, but they
+were less accurate than XGBoost. Hybrid, Elasticnet, and LASSO methods
+showed competitive performance with moderate bias, good coverage, and
+acceptable MSE, making them reliable alternatives, though slightly less
+optimal than XGBoost.
+
 \textbf{Contextualizing the literature}:
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
+\begin{itemize}
 \tightlist
 \item
-  MSE - Mean Squared Error
+  hdPS: High-dimensional Propensity Score
 \item
-  SE - Standard Error
+  NHANES: National Health and Nutrition Examination Survey
 \item
-  PS - Propensity Score
+  OR: Odds Ratio
 \item
-  AE - Autoencoders
+  RD: Risk Difference
 \item
-  DL - Deep Learning
+  SE: Standard Error
 \item
-  MARS - Multivariate Adaptive Regression Splines
+  MSE: Mean Squared Error
 \item
-  SMD - Standardized Mean Difference
+  LASSO: Least Absolute Shrinkage and Selection Operator
 \item
-  TMLE - Targeted Maximum Likelihood Estimation
+  GA: Genetic Algorithm
 \item
-  RHC - Right Heart Catheterization
+  RF: Random Forest
 \item
-  SUPPORT - Study to Understand Prognoses and Preferences for Outcomes
-  and Risks of Treatments
-\end{enumerate}
+  XGBoost: Extreme Gradient Boosting
+\item
+  FS: Forward Selection
+\item
+  BE: Backward Elimination
+\item
+  CV: Cross-Validation
+\item
+  RR: Relative Risk
+\item
+  Elasticnet: A regularized regression method that combines LASSO and
+  Ridge regression
+\end{itemize}
 

### 2024-09-02 doc/app6(stable).R

@@ -72,7 +72,6 @@ ui <- fluidPage(
         ),
         tabPanel("Chosen metric", 
                  tags$p("Numerical values correspond to the selected scenario and the metric."),
-                 checkboxInput("show_all_scenarios", "Show all scenarios side by side", value = FALSE),  # New checkbox
                  uiOutput("numerical_values_output")
         ),
         tabPanel("All metrics", 
@@ -96,8 +95,7 @@ ui <- fluidPage(
                  downloadButton("download_metric_comp_png", "Download Metric PNG"),
                  downloadButton("download_metric_comp_pdf", "Download Metric PDF"),
                  downloadButton("download_metric_comp_jpg", "Download Metric JPG"),
-                 plotOutput("metric_comparison_plot"),
-                 downloadButton("download_combined_summary", "Download Combined Summary Data")
+                 plotOutput("metric_comparison_plot")
         )
       )
     )
@@ -202,7 +200,7 @@ server <- function(input, output, session) {
     effective_num_indices(length(bross_indices))
     
     # Print the final number of rows after all models are processed
-    # print(paste("Final number of rows after filtering:", nrow(est)))
+    print(paste("Final number of rows after filtering:", nrow(est)))
     print(paste("Final effective number of simulations set to:", effective_num_indices()))
     
     return(est)
@@ -225,7 +223,7 @@ server <- function(input, output, session) {
     theta <- 0 # for RD or ATE; this would be 1 for OR
     
     simsum(data = est, estvarname = "RD", true = theta, se = "SE", 
-           methodvar = "model", x = TRUE, ref = "Kitchen sink")
+           methodvar = "model", x = TRUE)
   })
   
   # Plotting functions using the reactive data
@@ -272,55 +270,26 @@ server <- function(input, output, session) {
   
   
   output$numerical_values_output <- renderUI({
-    combined_summary <- all_scenarios_data()
-    
-    if (is.null(combined_summary)) {
-      showNotification("No data available for the selected metric.", type = "error")
-      return(NULL)
-    }
-    
+    s1 <- analysis()
+    # Ensure the correct mapping is used
     metric <- input$metric_select
     internal_metric <- names(metric_names)[metric_names == metric]
     
-    # Filter based on scenario if the checkbox is not checked
-    if (!input$show_all_scenarios) {
-      selected_scenario <- input$scenario_select
[…]

### 2024-09-03 Writeup/appendix/Appendix.RMD
writeup-update

@@
 title: Supplementary Content
-subtitle: Challenges of Univariate Proxy Variable Screening in High-Dimensional Propensity Score Analysis - An Argument for Multivariate Approaches
+subtitle: Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Framework - A Plasmode simulation study
 output:
@@
 
+\textcolor{red}{*need to have a brief description of these figures.*}
+
 ```{r, echo=FALSE, out.width="100%", fig.cap="Standard Error Comparison for Different Methods (Overall) when outcome and exposure are frequent.", fig.align="center", fig.label="fig:se-comparison-overall"}

### 2024-09-03 Writeup/appendix/Appendix.tex
writeup-update

@@
 \makeatother
-\subtitle{Challenges of Univariate Proxy Variable Screening in
-High-Dimensional Propensity Score Analysis - An Argument for
-Multivariate Approaches}
+\subtitle{Understanding the role of different proxy selection methods in
+High-Dimensional Propensity Score Framework - A Plasmode simulation
+study}
 \author{}
@@
 
+\textcolor{red}{*need to have a brief description of these figures.*}
+
 \begin{figure}

### 2024-09-03 Writeup/figures/performance_measures_tableER.tex
writeup-update

\begin{table}[!h]
\centering
\begin{tabular}{l|l|l|l|l|l|l}
\hline
  & Bias & Empirical SE & MSE & Model-based SE & Coverage & Bias-eliminated Coverage\\
\hline
\cellcolor{gray!10}{Kitchen sink} & \cellcolor{gray!10}{0.0025 (0.0029)} & \cellcolor{gray!10}{0.0656 (0.0021)} & \cellcolor{gray!10}{0.0043 (0.0005)} & \cellcolor{gray!10}{0.0623 (0.0014)} & \cellcolor{gray!10}{0.9340 (0.0111)} & \cellcolor{gray!10}{0.9320 (0.0113)}\\
\hline
Bross-based hdPS & 0.0035 (0.0027) & 0.0595 (0.0019) & 0.0035 (0.0004) & 0.0586 (0.0013) & 0.9380 (0.0108) & 0.9340 (0.0111)\\
\hline
\cellcolor{gray!10}{Hybrid hdPS} & \cellcolor{gray!10}{0.0049 (0.0025)} & \cellcolor{gray!10}{0.0564 (0.0018)} & \cellcolor{gray!10}{0.0032 (0.0003)} & \cellcolor{gray!10}{0.0564 (0.0012)} & \cellcolor{gray!10}{0.9460 (0.0101)} & \cellcolor{gray!10}{0.9340 (0.0111)}\\
\hline
Genetic Algorithm & 0.0408 (0.0023) & 0.0510 (0.0016) & 0.0043 (0.0003) & 0.0533 (0.0007) & 0.9220 (0.0120) & 0.9420 (0.0105)\\
\hline
\cellcolor{gray!10}{XGBoost} & \cellcolor{gray!10}{0.0259 (0.0023)} & \cellcolor{gray!10}{0.0507 (0.0016)} & \cellcolor{gray!10}{0.0032 (0.0003)} & \cellcolor{gray!10}{0.0531 (0.0009)} & \cellcolor{gray!10}{0.9620 (0.0086)} & \cellcolor{gray!10}{0.9400 (0.0106)}\\
\hline
Random Forest & 0.0127 (0.0027) & 0.0609 (0.0019) & 0.0039 (0.0004) & 0.0593 (0.0014) & 0.9500 (0.0097) & 0.9420 (0.0105)\\
\hline
\cellcolor{gray!10}{Forward Selection} & \cellcolor{gray!10}{0.0108 (0.0024)} & \cellcolor{gray!10}{0.0537 (0.0017)} & \cellcolor{gray!10}{0.0030 (0.0003)} & \cellcolor{gray!10}{0.0555 (0.0011)} & \cellcolor{gray!10}{0.9500 (0.0097)} & \cellcolor{gray!10}{0.9460 (0.0101)}\\
\hline
Backward Elimination & 0.0110 (0.0026) & 0.0576 (0.0018) & 0.0034 (0.0004) & 0.0578 (0.0014) & 0.9520 (0.0096) & 0.9380 (0.0108)\\
\hline
\cellcolor{gray!10}{LASSO} & \cellcolor{gray!10}{0.0060 (0.0026)} & \cellcolor{gray!10}{0.0587 (0.0019)} & \cellcolor{gray!10}{0.0035 (0.0004)} & \cellcolor{gray!10}{0.0580 (0.0014)} & \cellcolor{gray!10}{0.9420 (0.0105)} & \cellcolor{gray!10}{0.9420 (0.0105)}\\
\hline
Elasticnet & 0.0053 (0.0027) & 0.0597 (0.0019) & 0.0036 (0.0004) & 0.0584 (0.0014) & 0.9420 (0.0105) & 0.9380 (0.0108)\\
\hline
\end{tabular}
\end{table}

### 2024-09-03 Writeup/manuscript.Rmd
writeup-update

--- 2024-09-01 Writeup/manuscript.Rmd
@@
 
-title: Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Analysis
+title: Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Framework - A Plasmode simulation study
 titlerunning: High-Dimensional Propensity Score
@@
 abstract: |
-  **Purpose**: 
-  **Methods:** 
-  **Results:** 
-  **Conclusion:**
+  **Purpose**: We aims to evaluate various proxy selection methods within the context of high-dimensional propensity score (hdPS) analysis.
+The study focuses on assessing the performance of these methods, including alternative variable selection approaches, in selecting proxy variables for confounding adjustment compared to the traditional hdPS method that is rooted in Bross formula.
+The goal is to understand better the performance of these alternative methods in estimating treatment effects, and identify scenarios in which they may perform better.
+  **Methods:** Using data from three cycles of the National Health and Nutrition Examination Survey (NHANES) spanning 2013-2018, we motivated the study by examining the association between obesity and diabetes.
+A plasmode simulation framework based on this data was employed to mimic real-world data structures.
+Simulations were conducted under three scenarios: Frequent Exposure and Outcome, Rare Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome.
+The performance of a variety of proxy selection methods—including tree-based methods, LASSO-based methods, and the Genetic Algorithm (GA)—was evaluated across these scenarios using standard simulation metrics.
+  **Results:** XGBoost consistently demonstrated the lowest MSE and high coverage, making it a reliable method overall, although it did not always exhibit the lowest bias.
+In contrast, GA consistently showed the highest bias and MSE, with lower coverage and greater variability, indicating its unsuitability for accurate effect estimation.
+The kitchen sink model, Bross-based hdPS, and Hybrid hdPS methods performed moderately well, with low bias and moderate MSE, but varied in coverage across scenarios.
+Scenario-specific trends revealed that rare outcome scenarios yielded lower MSE and better precision, while rare exposure scenarios were associated with higher bias and MSE.
+  **Conclusion:** Aside from GA, the performance of most other methods in your study appears to be comparable in each scenario, though with some variations depending on specific metrics.
+The findings underscore the importance of selecting appropriate methods for hdPS analysis based on the characteristics of the data, particularly the prevalence of exposure and outcome.
+While XGBoost excelled in overall accuracy and precision, the choice of method should be tailored to the specific epidemiological goal to optimize bias, coverage, and precision in estimating treatment effects.
 
@@
 
+\textcolor{red}{*need to write what hdps is, and why alternatives are considered*}
+
 **Aim**: The aim of this research is to systematically evaluate and compare different proxy selection methods within the context of high-dimensional propensity score (hdPS) analysis.
@@
 To achieve this, we formulated the outcome data based on a specific model specification that incorporates both exposure and covariates, including investigator-specified and proxy variables.
-The model specification consists of three key components:
+The model specification consists of three key components (See Appendices \S A and B for further details):
 
@@
 ## Estimators under consideration {-}
+
+\textcolor{red}{*check if the description of the methods look okay to you. Make sure the description matches with the analysis codes.*}
 
@@
 
-```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Bias Across Different Methods in hdPS Analysis", fig.align="center", fig.label="fig:bias-comparison"}
+\textcolor{red}{*Can you check the app in the doc folder of the repo, and compare of the results description look accurate to you?*}
+
+The results for each method under the different scenarios are summarized below.
+See Figures \ref{fig:bias-comparison} and \ref{fig:Coverage-comparison} for an overview of the performance in terms of bias and coverage, respectively.
+
+(i) **Frequent Exposure and Outcome (base) scenario**:
+
+1.
+*Bias*: The kitchen sink model, which includes all variables without selection, exhibited the smallest bias (0.0002).
+GA shows the highest bias (0.0287), indicating a substantial deviation from the true effect.
+Among the other methods, Bross-based hdPS (-0.0001), Hybrid hdPS (0.0016), and Elasticnet (0.0036) demonstrated low bias.
+XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly higher bias.
+
+2.
+*Coverage*: The coverage for most methods was high, with Hybrid hdPS, Forward Selection, Backward Elimination, LASSO, and Elasticnet achieving values around 98%, indicating well-calibrated confidence intervals.
+However, GA had significantly lower coverage (83.8%), indicating that its confidence intervals might be too narrow or biased, potentially missing the true effect.
+After applying bias elimination, GA's coverage improved to 96%, which is better but still lower than other methods.
+
+3.
+*Mean Squared Error (MSE)*: XGBoost achieved the lowest MSE (0.0006), reaffirming it as the most accurate method overall.
+GA maintained the highest MSE (0.0016), reflecting its higher bias and variability.
+The kitchen sink model (0.0009), Bross-based hdPS (0.0008), Hybrid hdPS (0.0008), and Elasticnet (0.0009) all had relatively similar and moderate MSE values.
+
+4.
+*Standard Error (SE)*: XGBoost exhibited the lowest Empirical SE (0.0229), indicating high precision in its estimates.
+The kitchen sink model had the highest Empirical SE (0.0305), suggesting greater variability.
+Other methods, including GA (0.0274), Hybrid hdPS (0.0278), and Bross-based hdPS (0.0287), showed moderate variability.
+LASSO (0.0299) and Elasticnet (0.0294) had slightly higher variability.
+The Model-based SE followed a similar pattern, with XGBoost (0.0268) showing the lowest variability and the kitchen sink model (0.0333) the highest, indicating less precision in its estimates.
+See Appendix \S C for further details.
+
+**(ii) Rare Exposure and Frequent Outcome**:
+
+1.
+*Bias*: The kitchen sink model showed a relatively low bias (0.0025), while GA continued to exhibit the highest bias (0.0408), indicating a significant deviation from the true effect.
+XGBoost had a bias of 0.0259, which, while still higher than some other methods, was lower than GA.
+Other methods, such as Bross-based hdPS (0.0035), Hybrid hdPS (0.0049), and Elasticnet (0.0053), demonstrated moderate bias.
+Random Forest (RF) (0.0127) and Forward Selection (0.0108) had slightly higher bias but remained within an acceptable range.
+
+2.
+*Coverage*: Coverage levels remained high for most methods, with XGBoost achieving the highest coverage at 96.2%, indicating well-calibrated confidence intervals despite its higher bias.
+The GA method had lower coverage (92.2%), suggesting that its confidence intervals might be narrower, potentially missing the true effect.
+Other methods such as RF, Forward Selection, Backward Elimination, and Hybrid hdPS maintained coverage values around 94-95%, suggesting adequate interval calibration.
+Bias-eliminated coverage for GA improved to 94.2%, but it was still slightly lower than other methods.
+
+3.
+*Mean Squared Error (MSE)*: Hybrid hdPS and XGBoost both demonstrated the lowest MSE (0.0032), indicating that these methods were the most accurate in this scenario.
+The GA method had a higher MSE (0.0043), reflecting its substantial bias and variability.
+The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elasticnet (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.
+
+4.
+*Standard Error (SE)*: The lowest Empirical SE was observed with XGBoost (0.0507) and GA (0.0510), reflecting high precision despite their higher bias.
+The kitchen sink model had the highest Empirical SE (0.0656), indicating greater variability.
+Hybrid hdPS (0.0564), Bross-based hdPS (0.0595), and RF (0.0609) showed moderate variability.
+Forward Selection (0.0537) and Backward Elimination (0.0576) had lower variability compared to the kitchen sink model.
+In terms of Model-based SE, XGBoost (0.0531) and GA (0.0533) continued to show low variability, while the kitchen sink model had the highest Model-based SE (0.0623), indicating less precision in its estimates.
+
+**(iii) Frequent Exposure and Rare Outcome**:
+
+1.
+*Bias*: In this scenario, the kitchen sink model exhibited a moderate negative bias (-0.0093), similar to the Bross-based hdPS method (-0.0088).
+GA showed a significantly higher bias (0.0362), indicating a substantial deviation from the true effect.
+Among other methods, XGBoost demonstrated the lowest bias (-0.0061), while methods like Hybrid hdPS (-0.0082), Forward Selection (-0.0070), and Backward Elimination (-0.0070) had slightly higher but still moderate biases.
+Elasticnet and LASSO both had biases of -0.0079, reflecting slightly larger deviations compared to XGBoost but still within acceptable limits.
+
+2.
+*Coverage*: Most methods achieved good coverage, with XGBoost, RF, and Forward Selection each achieving a coverage rate of 95.4%, indicating well-calibrated confidence intervals.
+The GA method, however, had slightly lower coverage (91.8%), indicating that its confidence intervals might be narrower, potentially excluding the true effect.
+Bross-based hdPS and the kitchen sink model had slightly lower coverage values of 93.8% and 93.4%, respectively.
+After accounting for bias, the bias-eliminated coverage for most methods, except GA, remained high, with values ranging from 98.4% to 99.0%, indicating that most methods effectively adjusted for bias in their coverage estimates.
+GA's bias-eliminated coverage was lower at 93.4%, reflecting its higher inherent bias.
+
+3.
+*Mean Squared Error (MSE)*: XGBoost exhibited the lowest MSE (0.0003), indicating it as the most accurate method overall in this scenario.
+GA had the highest MSE (0.0040), reflecting its substantial bias and variability.
+The kitchen sink model (0.0005), Bross-based hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and Elasticnet (0.0005) all had relatively similar MSE values, indicating moderate accuracy.
+
+4.
+*Standard Error (SE)*: The lowest Empirical SE was observed with XGBoost (0.0152), reflecting high precision in its estimates.
+The GA method exhibited the highest Empirical SE (0.0523), indicating greater variability and less precision.
+Methods like Hybrid hdPS (0.0184), Forward Selection (0.0187), and Elasticnet (0.0203) showed moderate variability, while Bross-based hdPS (0.0206) and the kitchen sink model (0.0212) had slightly higher variability.
+In terms of Model-based SE, XGBoost (0.0179) again showed the lowest variability, consistent with its low Empirical SE, indicating that it provided the most stable estimates.
+The kitchen sink model had a slightly higher Model-based SE (0.0219), indicating less precision in its estimates.
+
+```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Bias Across Different Methods in hdPS Analysis\\label{fig:bias-comparison}", fig.align="center"}
 knitr::include_graphics("figures/metric_comparison_Bias.png")
@@
 
-*Here we include full data analysis (with some summary results like exposure and outcome prevalence, and sample size) and report OR and RD.
-Also mention how many proxies were chosen (add in the picture of RD and OR; side by side for each method, ordered my magnitude of RD), and how many were in common with hdPS (add table).*
+\textcolor{red}{*Here we include full data analysis (with some summary results like exposure and outcome prevalence, and sample size) and report OR and RD.
+Also mention how many proxies were chosen (add in the picture of RD and OR; side by side for each method, ordered my magnitude of RD), and how many were in common with hdPS (add table).*}
+
+See Figure \ref{fig:comparison-plot} for the results from analyzing the NHANES (2013-2018) dataset.
 
@@
 The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
-Methods are arranged by the number of variables used in the models.", fig.label="fig:comparison-plot", message=FALSE, warning=FALSE}
+Methods are arranged by the number of variables used in the models.\\label{fig:comparison-plot}", message=FALSE, warning=FALSE}
 library(ggplot2)
@@
 
+\textcolor{red}{*need to think about how to best present this proxy in common table.*}
+
 \begin{table}[htbp]
@@
 
-*Report computing time for the Real-world analysis for each method. (add ordered table)*
+\textcolor{red}{*Report computing time for the Real-world analysis for each method. (add ordered table or figure)*}
 
@@
 
-**Contextualizing the literature**:
+## Summary of the simulation findings
 
-**Summary of the simulation findings**:
+**Comparison of methods**:
 
-**Data analysis findings**:
+Across the three scenarios—Frequent Exposure and Outcome, Rare Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome—XGBoost consistently exhibited the lowest Mean Squared Error (MSE) and high coverage, making it one of the most reliable methods overall.
+However, XGBoost did not always have the lowest bias; in fact, methods such as the kitchen sink model, Bross-based hdPS, and Hybrid hdPS often showed lower bias.
+The GA, in contrast, consistently exhibited the highest bias and MSE, along with lower coverage and greater variability, indicating it was less reliable for accurate effect estimation.
+The kitchen sink model, while demonstrating low bias and reasonable MSE, generally had higher variability and lower precision compared to other methods like XGBoost.
+Methods such as Bross-based hdPS, Hybrid hdPS, and Elasticnet performed moderately well across all scenarios, balancing bias, coverage, and MSE, but they did not outperform XGBoost in overall accuracy and precision.
 
-**Future Direction**:
+**Comparison of scenarios**:
 
-**Conclusion**:
+Scenarios with rare exposure tended to produce higher bias, particularly for methods like GA and XGBoost, while frequent outcomes generally led to lower bias.
+Overcoverage was common in the frequent exposure and outcome scenario, while the other scenarios tended to have more balanced or slightly under-coverage.
+Frequent exposure scenarios had higher relative error, indicating more difficulty in precisely estimating effects compared to rare exposure scenarios, which had lower relative error.
+Rare outcome scenarios tended to have the lowest MSE, indicating more precise effect estimates under these conditions, whereas rare exposure scenarios had higher MSE, reflecting the challenges of estimating effects when exposure is uncommon.
+
+## Contextualizing the literature
+
+\textcolor{red}{*need to write what hdps offers in the literature; what additional selection criteria was used so far*}
+
+## Data analysis findings
+
+\textcolor{red}{*summarize real data analysis finding in 1 para*}
+
+## Future Direction
+
+\textcolor{red}{*TMLE*}
+
+## Conclusion
+
+In conclusion, this analysis highlights the importance of carefully selecting appropriate methods for hdPS analysis based on the specific characteristics of the data, particularly the prevalence of exposure and outcome.
+While XGBoost consistently demonstrated strong performance in terms of MSE and coverage, it did not always have the lowest bias, suggesting that it may be most suitable when precision is prioritized over bias minimization.
+GA, despite its potential, showed significant limitations with consistently high bias and MSE, making it less reliable for accurate effect estimation.
+The kitchen sink model, Bross-based hdPS, and Hybrid hdPS methods provided a balanced approach, often delivering low bias and moderate MSE, but with variability in coverage depending on the scenario.
+Scenario-specific trends revealed that rare outcomes generally yielded lower MSE and better precision, while rare exposures were associated with higher bias and MSE, emphasizing the challenges of accurately estimating effects in such contexts.
+Ultimately, the findings underscore the need to tailor method selection to the epidemiological scenario at hand, ensuring that the chosen approach aligns with the specific goals and challenges of the analysis.
 

### 2024-09-03 Writeup/manuscript.tex
writeup-update

--- 2024-09-01 Writeup/manuscript.tex
@@
 different proxy selection methods in High-Dimensional Propensity Score
-Analysis}
+Framework - A Plasmode simulation study}
 
@@
 
-\abstract{\textbf{Purpose}: \textbf{Methods:} \textbf{Results:}
-\textbf{Conclusion:}}
+\abstract{\textbf{Purpose}: We aims to evaluate various proxy selection
+methods within the context of high-dimensional propensity score (hdPS)
+analysis. The study focuses on assessing the performance of these
+methods, including alternative variable selection approaches, in
+selecting proxy variables for confounding adjustment compared to the
+traditional hdPS method that is rooted in Bross formula. The goal is to
+understand better the performance of these alternative methods in
+estimating treatment effects, and identify scenarios in which they may
+perform better. \textbf{Methods:} Using data from three cycles of the
+National Health and Nutrition Examination Survey (NHANES) spanning
+2013-2018, we motivated the study by examining the association between
+obesity and diabetes. A plasmode simulation framework based on this data
+was employed to mimic real-world data structures. Simulations were
+conducted under three scenarios: Frequent Exposure and Outcome, Rare
+Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome.
+The performance of a variety of proxy selection methods---including
+tree-based methods, LASSO-based methods, and the Genetic Algorithm
+(GA)---was evaluated across these scenarios using standard simulation
+metrics. \textbf{Results:} XGBoost consistently demonstrated the lowest
+MSE and high coverage, making it a reliable method overall, although it
+did not always exhibit the lowest bias. In contrast, GA consistently
+showed the highest bias and MSE, with lower coverage and greater
+variability, indicating its unsuitability for accurate effect
+estimation. The kitchen sink model, Bross-based hdPS, and Hybrid hdPS
+methods performed moderately well, with low bias and moderate MSE, but
+varied in coverage across scenarios. Scenario-specific trends revealed
+that rare outcome scenarios yielded lower MSE and better precision,
+while rare exposure scenarios were associated with higher bias and MSE.
+\textbf{Conclusion:} Aside from GA, the performance of most other
+methods in your study appears to be comparable in each scenario, though
+with some variations depending on specific metrics. The findings
+underscore the importance of selecting appropriate methods for hdPS
+analysis based on the characteristics of the data, particularly the
+prevalence of exposure and outcome. While XGBoost excelled in overall
+accuracy and precision, the choice of method should be tailored to the
+specific epidemiological goal to optimize bias, coverage, and precision
+in estimating treatment effects.}
 
@@
 \section{Background}\label{background}
+
+\textcolor{red}{*need to write what hdps is, and why alternatives are considered*}
 
@@
 both exposure and covariates, including investigator-specified and proxy
-variables. The model specification consists of three key components:
+variables. The model specification consists of three key components (See
+Appendices \S A and B for further details):
 
@@
 \addcontentsline{toc}{subsection}{Estimators under consideration}
+
+\textcolor{red}{*check if the description of the methods look okay to you. Make sure the description matches with the analysis codes.*}
 
@@
 
+\textcolor{red}{*Can you check the app in the doc folder of the repo, and compare of the results description look accurate to you?*}
+
+The results for each method under the different scenarios are summarized
+below. See Figures \ref{fig:bias-comparison} and
+\ref{fig:Coverage-comparison} for an overview of the performance in
+terms of bias and coverage, respectively.
+
+\begin{enumerate}
+\def\labelenumi{(\roman{enumi})}
+\tightlist
+\item
+  \textbf{Frequent Exposure and Outcome (base) scenario}:
+\end{enumerate}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Bias}: The kitchen sink model, which includes all variables
+  without selection, exhibited the smallest bias (0.0002). GA shows the
+  highest bias (0.0287), indicating a substantial deviation from the
+  true effect. Among the other methods, Bross-based hdPS (-0.0001),
+  Hybrid hdPS (0.0016), and Elasticnet (0.0036) demonstrated low bias.
+  XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly
+  higher bias.
+\item
+  \emph{Coverage}: The coverage for most methods was high, with Hybrid
+  hdPS, Forward Selection, Backward Elimination, LASSO, and Elasticnet
+  achieving values around 98\%, indicating well-calibrated confidence
+  intervals. However, GA had significantly lower coverage (83.8\%),
+  indicating that its confidence intervals might be too narrow or
+  biased, potentially missing the true effect. After applying bias
+  elimination, GA's coverage improved to 96\%, which is better but still
+  lower than other methods.
+\item
+  \emph{Mean Squared Error (MSE)}: XGBoost achieved the lowest MSE
+  (0.0006), reaffirming it as the most accurate method overall. GA
+  maintained the highest MSE (0.0016), reflecting its higher bias and
+  variability. The kitchen sink model (0.0009), Bross-based hdPS
+  (0.0008), Hybrid hdPS (0.0008), and Elasticnet (0.0009) all had
+  relatively similar and moderate MSE values.
+\item
+  \emph{Standard Error (SE)}: XGBoost exhibited the lowest Empirical SE
+  (0.0229), indicating high precision in its estimates. The kitchen sink
+  model had the highest Empirical SE (0.0305), suggesting greater
+  variability. Other methods, including GA (0.0274), Hybrid hdPS
+  (0.0278), and Bross-based hdPS (0.0287), showed moderate variability.
+  LASSO (0.0299) and Elasticnet (0.0294) had slightly higher
+  variability. The Model-based SE followed a similar pattern, with
+  XGBoost (0.0268) showing the lowest variability and the kitchen sink
+  model (0.0333) the highest, indicating less precision in its
+  estimates. See Appendix \S C for further details.
+\end{enumerate}
+
+\textbf{(ii) Rare Exposure and Frequent Outcome}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Bias}: The kitchen sink model showed a relatively low bias
+  (0.0025), while GA continued to exhibit the highest bias (0.0408),
+  indicating a significant deviation from the true effect. XGBoost had a
+  bias of 0.0259, which, while still higher than some other methods, was
+  lower than GA. Other methods, such as Bross-based hdPS (0.0035),
+  Hybrid hdPS (0.0049), and Elasticnet (0.0053), demonstrated moderate
+  bias. Random Forest (RF) (0.0127) and Forward Selection (0.0108) had
+  slightly higher bias but remained within an acceptable range.
+\item
+  \emph{Coverage}: Coverage levels remained high for most methods, with
+  XGBoost achieving the highest coverage at 96.2\%, indicating
+  well-calibrated confidence intervals despite its higher bias. The GA
+  method had lower coverage (92.2\%), suggesting that its confidence
+  intervals might be narrower, potentially missing the true effect.
+  Other methods such as RF, Forward Selection, Backward Elimination, and
+  Hybrid hdPS maintained coverage values around 94-95\%, suggesting
+  adequate interval calibration. Bias-eliminated coverage for GA
+  improved to 94.2\%, but it was still slightly lower than other
+  methods.
+\item
+  \emph{Mean Squared Error (MSE)}: Hybrid hdPS and XGBoost both
+  demonstrated the lowest MSE (0.0032), indicating that these methods
+  were the most accurate in this scenario. The GA method had a higher
+  MSE (0.0043), reflecting its substantial bias and variability. The
+  kitchen sink model also had an MSE of 0.0043, similar to GA, while
+  other methods like Bross-based hdPS (0.0035), RF (0.0039), and
+  Elasticnet (0.0036) exhibited moderate MSE values, indicating
+  reasonable accuracy.
+\item
+  \emph{Standard Error (SE)}: The lowest Empirical SE was observed with
+  XGBoost (0.0507) and GA (0.0510), reflecting high precision despite
+  their higher bias. The kitchen sink model had the highest Empirical SE
+  (0.0656), indicating greater variability. Hybrid hdPS (0.0564),
+  Bross-based hdPS (0.0595), and RF (0.0609) showed moderate
+  variability. Forward Selection (0.0537) and Backward Elimination
+  (0.0576) had lower variability compared to the kitchen sink model. In
+  terms of Model-based SE, XGBoost (0.0531) and GA (0.0533) continued to
+  show low variability, while the kitchen sink model had the highest
+  Model-based SE (0.0623), indicating less precision in its estimates.
+\end{enumerate}
+
+\textbf{(iii) Frequent Exposure and Rare Outcome}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Bias}: In this scenario, the kitchen sink model exhibited a
+  moderate negative bias (-0.0093), similar to the Bross-based hdPS
+  method (-0.0088). GA showed a significantly higher bias (0.0362),
+  indicating a substantial deviation from the true effect. Among other
+  methods, XGBoost demonstrated the lowest bias (-0.0061), while methods
+  like Hybrid hdPS (-0.0082), Forward Selection (-0.0070), and Backward
+  Elimination (-0.0070) had slightly higher but still moderate biases.
+  Elasticnet and LASSO both had biases of -0.0079, reflecting slightly
+  larger deviations compared to XGBoost but still within acceptable
+  limits.
+\item
+  \emph{Coverage}: Most methods achieved good coverage, with XGBoost,
+  RF, and Forward Selection each achieving a coverage rate of 95.4\%,
+  indicating well-calibrated confidence intervals. The GA method,
+  however, had slightly lower coverage (91.8\%), indicating that its
+  confidence intervals might be narrower, potentially excluding the true
+  effect. Bross-based hdPS and the kitchen sink model had slightly lower
+  coverage values of 93.8\% and 93.4\%, respectively. After accounting
+  for bias, the bias-eliminated coverage for most methods, except GA,
+  remained high, with values ranging from 98.4\% to 99.0\%, indicating
+  that most methods effectively adjusted for bias in their coverage
+  estimates. GA's bias-eliminated coverage was lower at 93.4\%,
+  reflecting its higher inherent bias.
+\item
+  \emph{Mean Squared Error (MSE)}: XGBoost exhibited the lowest MSE
+  (0.0003), indicating it as the most accurate method overall in this
+  scenario. GA had the highest MSE (0.0040), reflecting its substantial
+  bias and variability. The kitchen sink model (0.0005), Bross-based
+  hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and
+  Elasticnet (0.0005) all had relatively similar MSE values, indicating
+  moderate accuracy.
+\item
+  \emph{Standard Error (SE)}: The lowest Empirical SE was observed with
+  XGBoost (0.0152), reflecting high precision in its estimates. The GA
+  method exhibited the highest Empirical SE (0.0523), indicating greater
+  variability and less precision. Methods like Hybrid hdPS (0.0184),
+  Forward Selection (0.0187), and Elasticnet (0.0203) showed moderate
+  variability, while Bross-based hdPS (0.0206) and the kitchen sink
+  model (0.0212) had slightly higher variability. In terms of
+  Model-based SE, XGBoost (0.0179) again showed the lowest variability,
+  consistent with its low Empirical SE, indicating that it provided the
+  most stable estimates. The kitchen sink model had a slightly higher
+  Model-based SE (0.0219), indicating less precision in its estimates.
+\end{enumerate}
+
 \begin{figure}[th]
@@
 
-\emph{Here we include full data analysis (with some summary results like
-exposure and outcome prevalence, and sample size) and report OR and RD.
-Also mention how many proxies were chosen (add in the picture of RD and
-OR; side by side for each method, ordered my magnitude of RD), and how
-many were in common with hdPS (add table).}
+\textcolor{red}{*Here we include full data analysis (with some summary results like exposure and outcome prevalence, and sample size) and report OR and RD.
+Also mention how many proxies were chosen (add in the picture of RD and OR; side by side for each method, ordered my magnitude of RD), and how many were in common with hdPS (add table).*}
+
+See Figure \ref{fig:comparison-plot} for the results from analyzing the
+NHANES (2013-2018) dataset.
 
@@
 exclusively by each method.
+
+\textcolor{red}{*need to think about how to best present this proxy in common table.*}
 
@@
 
-\emph{Report computing time for the Real-world analysis for each method.
-(add ordered table)}
+\textcolor{red}{*Report computing time for the Real-world analysis for each method. (add ordered table or figure)*}
 
@@
 
-\textbf{Contextualizing the literature}:
+\subsection{Summary of the simulation
+findings}\label{summary-of-the-simulation-findings}
 
-\textbf{Summary of the simulation findings}:
+\textbf{Comparison of methods}:
 
-\textbf{Data analysis findings}:
+Across the three scenarios---Frequent Exposure and Outcome, Rare
+Exposure and Frequent Outcome, and Frequent Exposure and Rare
+Outcome---XGBoost consistently exhibited the lowest Mean Squared Error
+(MSE) and high coverage, making it one of the most reliable methods
+overall. However, XGBoost did not always have the lowest bias; in fact,
+methods such as the kitchen sink model, Bross-based hdPS, and Hybrid
+hdPS often showed lower bias. The GA, in contrast, consistently
+exhibited the highest bias and MSE, along with lower coverage and
+greater variability, indicating it was less reliable for accurate effect
+estimation. The kitchen sink model, while demonstrating low bias and
+reasonable MSE, generally had higher variability and lower precision
+compared to other methods like XGBoost. Methods such as Bross-based
+hdPS, Hybrid hdPS, and Elasticnet performed moderately well across all
+scenarios, balancing bias, coverage, and MSE, but they did not
+outperform XGBoost in overall accuracy and precision.
 
-\textbf{Future Direction}:
+\textbf{Comparison of scenarios}:
 
-\textbf{Conclusion}:
+Scenarios with rare exposure tended to produce higher bias, particularly
+for methods like GA and XGBoost, while frequent outcomes generally led
+to lower bias. Overcoverage was common in the frequent exposure and
+outcome scenario, while the other scenarios tended to have more balanced
+or slightly under-coverage. Frequent exposure scenarios had higher
+relative error, indicating more difficulty in precisely estimating
+effects compared to rare exposure scenarios, which had lower relative
+error. Rare outcome scenarios tended to have the lowest MSE, indicating
+more precise effect estimates under these conditions, whereas rare
+exposure scenarios had higher MSE, reflecting the challenges of
+estimating effects when exposure is uncommon.
+
+\subsection{Contextualizing the
+literature}\label{contextualizing-the-literature}
+
+\textcolor{red}{*need to write what hdps offers in the literature; what additional selection criteria was used so far*}
+
+\subsection{Data analysis findings}\label{data-analysis-findings}
+
+\textcolor{red}{*summarize real data analysis finding in 1 para*}
+
+\subsection{Future Direction}\label{future-direction}
+
+\textcolor{red}{*TMLE*}
+
+\subsection{Conclusion}\label{conclusion}
+
+In conclusion, this analysis highlights the importance of carefully
+selecting appropriate methods for hdPS analysis based on the specific
+characteristics of the data, particularly the prevalence of exposure and
+outcome. While XGBoost consistently demonstrated strong performance in
+terms of MSE and coverage, it did not always have the lowest bias,
+suggesting that it may be most suitable when precision is prioritized
+over bias minimization. GA, despite its potential, showed significant
+limitations with consistently high bias and MSE, making it less reliable
+for accurate effect estimation. The kitchen sink model, Bross-based
+hdPS, and Hybrid hdPS methods provided a balanced approach, often
+delivering low bias and moderate MSE, but with variability in coverage
+depending on the scenario. Scenario-specific trends revealed that rare
+outcomes generally yielded lower MSE and better precision, while rare
+exposures were associated with higher bias and MSE, emphasizing the
+challenges of accurately estimating effects in such contexts.
+Ultimately, the findings underscore the need to tailor method selection
+to the epidemiological scenario at hand, ensuring that the chosen
+approach aligns with the specific goals and challenges of the analysis.
 

### 2024-09-03 doc/backupApps/app6.R

@@ -1,0 +1,638 @@
+library(shiny)
+library(ggplot2)
+library(dplyr)
+library(cowplot)
+library(rsimsum)
+library(knitr)
+library(reshape2)
+library(tidyr)
+
+# Define the models you want to work with
+model_names <- c(
+  kitchen = "Kitchen sink",
+  bross = "Bross-based hdPS",
+  hybrid = "Hybrid hdPS",
+  ga = "Genetic Algorithm",
+  xgboost = "XGBoost",
+  rf = "Random Forest",
+  forward = "Forward Selection",
+  backward = "Backward Elimination",
+  lasso = "LASSO",  
+  enet = "Elasticnet"
+)
+
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  becover = "Bias-eliminated Coverage",
+  relerror = "Relative Error",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  power = "Power",
+  nsim = "# of simulations"
+)
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Exploring the Simulation Results"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario_select", "Choose a scenario:",
+                  choices = list("Frequent Outcome and Exposure" = "scenario",
+                                 "Rare Exposure" = "scenarioER",
+                                 "Rare Outcome" = "scenarioOR")
+      ),
+      selectInput("metric_select", "Choose a performance metric:",
+                  choices = metric_names
+      ),
+      selectInput("plot_type", "Choose a plot type:",
+                  choices = c("Lolly" = "lolly",
+                              "Forest" = "forest",
+                              "Zipper" = "zip",
+                              "Heat" = "heat")),
+      sliderInput("num_indices", "Select number of simulations:",
+                  min = 100, max = 1000, value = 500, step = 50)
+    ),
+    mainPanel(
+      # Display the number of simulations if the checkbox is checked
+      conditionalPanel(
+        condition = "input.show_num_indices == true",
+        textOutput("num_indices_output")  # Text output for num_indices
+      ),
+      tabsetPanel(
+        tabPanel("Plot", 
+                 tags$p("The plot represents the selected scenario and the metric."),
+                 downloadButton("download_png", "Download PNG"),
+                 downloadButton("download_pdf", "Download PDF"),
[…]

### 2024-09-03 doc/backupApps/app6boostV2.R

@@ -1,0 +1,471 @@
+library(shiny)
+library(ggplot2)
+library(dplyr)
+library(cowplot)
+library(rsimsum)
+library(knitr)
+library(reshape2)
+library(tidyr)
+
+# Create a mapping from scenario codes to descriptive names
+scenario_names <- c(
+  scenario = "Frequent Outcome and Exposure",
+  scenarioER = "Rare Exposure",
+  scenarioOR = "Rare Outcome"
+)
+
+# Define the models you want to work with
+model_names <- c(
+  kitchen = "Kitchen sink",
+  bross = "Bross-based hdPS",
+  hybrid = "Hybrid hdPS",
+  ga = "Genetic Algorithm",
+  xgboost = "XGBoost",
+  rf = "Random Forest",
+  forward = "Forward Selection",
+  backward = "Backward Elimination",
+  lasso = "LASSO",  
+  enet = "Elasticnet"
+)
+
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  becover = "Bias-eliminated Coverage",
+  relerror = "Relative Error",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  power = "Power",
+  nsim = "# of simulations"
+)
+
+# Define a custom theme for ggplot2
+custom_theme <- theme_minimal() + 
+  theme(
+    panel.background = element_rect(fill = "white"),  
+    panel.grid.major = element_blank(),              
+    panel.grid.minor = element_blank(),              
+    legend.position = "bottom"
+  )
+
+# Helper function to map metric names
+get_internal_metric <- function(metric) {
+  names(metric_names)[metric_names == metric]
+}
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Plasmode Simulation Results Comparing hdPS Alternatives"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario_select", "Choose a scenario:",
+                  choices = scenario_names),
+      selectInput("metric_select", "Choose a performance metric:",
+                  choices = metric_names),
+      sliderInput("num_indices", "Select number of simulations:",
+                  min = 100, max = 1000, value = 500, step = 50)
+    ),
+    mainPanel(
+      conditionalPanel(
+        condition = "input.show_num_indices == true",
+        textOutput("num_indices_output")
+      ),
+      tabsetPanel(
+        tabPanel("Plot", 
[…]

### 2024-09-03 doc/backupApps/app7.R

@@ -1,0 +1,369 @@
+library(shiny)
+library(shinyjs)
+library(ggplot2)
+library(dplyr)
+library(cowplot)
+library(rsimsum)
+library(knitr)
+library(reshape2)
+library(tidyr)
+
+# Define the models you want to work with
+model_names <- c(
+  kitchen = "Kitchen sink",
+  bross = "Bross-based hdPS",
+  hybrid = "Hybrid hdPS",
+  ga = "Genetic Algorithm",
+  xgboost = "XGBoost",
+  rf = "Random Forest",
+  forward = "Forward Selection",
+  backward = "Backward Elimination",
+  lasso = "LASSO",  
+  enet = "Elasticnet"
+)
+
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  becover = "Bias-eliminated Coverage",
+  relerror = "Relative Error",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  power = "Power",
+  nsim = "# of simulations"
+)
+
+# Define UI
+ui <- fluidPage(
+  useShinyjs(),  # Add this line to activate shinyjs
+  titlePanel("Exploring the Simulation Results"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("metric_select", "Choose a performance metric:",
+                  choices = metric_names
+      ),
+      sliderInput("num_indices", "Select number of simulations:",
+                  min = 100, max = 500, value = 500, step = 50),
+      checkboxInput("show_all_scenarios", "Show all scenarios side by side", value = FALSE),
+      selectInput("scenario_select", "Choose a scenario:",
+                  choices = list("Frequent Outcome and Exposure" = "scenario",
+                                 "Rare Exposure" = "scenarioER",
+                                 "Rare Outcome" = "scenarioOR")
+      )
+    ),
+    mainPanel(
+      tabsetPanel(
+        tabPanel("Chosen metric", 
+                 tags$p("Numerical values correspond to the selected scenario and the metric."),
+                 uiOutput("numerical_values_output")
+        ),
+        # Add the "All Scenarios" tab in the UI
+        tabPanel("All Scenarios",
+                 tags$p("Comparison of the selected metric across all scenarios (irrespective of the chosen scenario)."),
+                 checkboxInput("black_and_white", "Convert to black and white", value = FALSE),
[…]

### 2024-09-03 doc/backupApps/app8.R

@@ -1,0 +1,183 @@
+library(shiny)
+library(ggplot2)
+library(dplyr)
+library(rsimsum)
+
+# Load the combined list of scenarios
+base_path <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/doc/results"
+combined_list <- readRDS(file.path(base_path, "combined_list_filtered.rds"))
+
+# Define UI
+library(shiny)
+
+model_names <- c(
+  kitchen = "Kitchen sink",
+  bross = "Bross-based hdPS",
+  hybrid = "Hybrid hdPS",
+  ga = "Genetic Algorithm",
+  xgboost = "XGBoost",
+  rf = "Random Forest",
+  forward = "Forward Selection",
+  backward = "Backward Elimination",
+  lasso = "LASSO",  
+  enet = "Elasticnet"
+)
+
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  becover = "Bias-eliminated Coverage",
+  relerror = "Relative Error",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  power = "Power",
+  nsim = "# of simulations"
+)
+
+ui <- fluidPage(
+  titlePanel("Simulation Analysis by Performance Measure"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario", "Choose a Scenario:", choices = c("scenario", "scenarioER", "scenarioOR")),
+      selectInput("metric_select", "Choose a Performance Measure:", choices = metric_names),
+      selectInput("plot_type", "Choose a plot type:",
+                  choices = c("Lolly" = "lolly",
+                              "Forest" = "forest",
+                              "Zipper" = "zip",
+                              "Heat" = "heat")),
+      checkboxInput("show_all_measures", "Show All Measures", value = FALSE),
+      actionButton("runAnalysis", "Run Analysis")
+    ),
+    mainPanel(
+      tabsetPanel(
+        tabPanel("Summary Table", tableOutput("summaryTable")),
+        tabPanel("Plots", plotOutput("selected_plot")),
+        tabPanel("Numerical Values", uiOutput("numerical_values_output")),
+        tabPanel("Simulation Info", textOutput("num_indices_output"))
+      )
+    )
+  )
+)
+
+
+server <- function(input, output) {
[…]

### 2024-09-03 doc/backupApps/app9.R

@@ -1,0 +1,126 @@
+library(shiny)
+library(ggplot2)
+library(dplyr)
+library(rsimsum)
+
+# Define the models you want to work with
+model_names <- c(
+  kitchen = "Kitchen sink",
+  bross = "Bross-based hdPS",
+  hybrid = "Hybrid hdPS",
+  ga = "Genetic Algorithm",
+  xgboost = "XGBoost",
+  rf = "Random Forest",
+  forward = "Forward Selection",
+  backward = "Backward Elimination",
+  lasso = "LASSO",  
+  enet = "Elasticnet"
+)
+
+# Define metric names
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  becover = "Bias-eliminated Coverage",
+  relerror = "Relative Error",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  power = "Power",
+  nsim = "# of simulations"
+)
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Exploring the Simulation Results"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario_select", "Choose a scenario:",
+                  choices = list("Frequent Outcome and Exposure" = "scenario",
+                                 "Rare Exposure" = "scenarioER",
+                                 "Rare Outcome" = "scenarioOR")
+      ),
+      selectInput("metric_select", "Choose a performance metric:",
+                  choices = metric_names
+      ),
+      sliderInput("num_indices", "Select number of simulations:",
+                  min = 100, max = 1000, value = 500, step = 50)
+    ),
+    mainPanel(
+      plotOutput("selected_plot")
+    )
+  )
+)
+
+# Server logic
+server <- function(input, output, session) {
+  
+  load_all_scenarios_data <- function() {
+    base_path <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/doc/results"
+    combined_list <- readRDS(file.path(base_path, "combined_list_filtered.rds"))
+    return(combined_list)
+  }
+  
+  load_scenario_data <- function(combined_list, scenario, num_indices) {
+    selected_scenario <- combined_list[[scenario]]
+    
+    # Subset the data to the requested number of simulations
+    if (num_indices > nrow(selected_scenario)) {
+      showNotification(
+        paste("Warning: Requested number of simulations (", num_indices, 
+              ") exceeds available simulations (", nrow(selected_scenario), "). Showing available data.", sep = ""),
[…]

### 2024-09-03 doc/hdPSApp.R

@@ -1,0 +1,574 @@
+library(shiny)
+library(ggplot2)
+library(dplyr)
+library(cowplot)
+library(rsimsum)
+library(knitr)
+library(reshape2)
+library(tidyr)
+
+# Create a mapping from scenario codes to descriptive names
+scenario_names <- c(
+  scenario = "Frequent Outcome and Exposure",
+  scenarioER = "Rare Exposure",
+  scenarioOR = "Rare Outcome"
+)
+
+# Define the models you want to work with
+model_names <- c(
+  kitchen = "Kitchen sink",
+  bross = "Bross-based hdPS",
+  hybrid = "Hybrid hdPS",
+  ga = "Genetic Algorithm",
+  xgboost = "XGBoost",
+  rf = "Random Forest",
+  forward = "Forward Selection",
+  backward = "Backward Elimination",
+  lasso = "LASSO",  
+  enet = "Elasticnet"
+)
+
+metric_names <- c(
+  bias = "Bias",
+  cover = "Coverage",
+  becover = "Bias-eliminated Coverage",
+  relerror = "Relative Error",
+  empse = "Empirical SE",
+  modelse = "Model SE",
+  mse = "MSE",
+  relprec = "Relative Precision",
+  power = "Power",
+  nsim = "# of simulations"
+)
+
+# Define a custom theme for ggplot2
+custom_theme <- theme_minimal() + 
+  theme(
+    panel.background = element_rect(fill = "white"),  
+    panel.grid.major = element_blank(),              
+    panel.grid.minor = element_blank(),              
+    legend.position = "bottom"
+  )
+
+# Helper function to map metric names
+get_internal_metric <- function(metric) {
+  names(metric_names)[metric_names == metric]
+}
+
+# Helper function for download handlers
+create_download_handler <- function(extension) {
+  downloadHandler(
+    filename = function() {
+      paste("plot_", input$metric_select, ".", extension, sep = "")
+    },
+    content = function(file) {
+      ggsave(file, plot = last_plot(), device = extension, width = 8, height = 6)
+    }
+  )
+}
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Plasmode Simulation Results Comparing hdPS Alternatives"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("scenario_select", "Choose a scenario:",
+                  choices = list("Frequent Outcome and Exposure" = "scenario",
+                                 "Rare Exposure" = "scenarioER",
[…]

### 2024-09-03 doc/results/combineData.R

@@ -1,0 +1,257 @@
+# Load necessary libraries
+library(dplyr)
+
+# Define the base path where the data is stored
+base_path <- "C:/Users/Ehsan/Documents/GitHub/hdPS-proxy-select/doc/results"
+
+# Scenario 1: "scenario"
+scenario <- "scenario"
+scenario_path <- file.path(base_path, scenario)
+files <- list.files(scenario_path, pattern = "\\.RData$", full.names = TRUE)
+print(paste("Processing scenario:", scenario))
+print(paste("Files found:", files))
+
+scenario_data_list <- list()
+
+for (file_path in files) {
+  load(file_path)
+  model <- tools::file_path_sans_ext(basename(file_path))
+  print(paste("Processing file:", file_path))
+  print(paste("Model identified:", model))
+  
+  object_name <- paste0("RD_", model)
+  
+  if (exists(object_name)) {
+    print(paste("Found object:", object_name))
+    assign("current_data", get(object_name))
+  } else {
+    warning(paste("Object", object_name, "not found in", file_path))
+    next
+  }
+  
+  current_data$model <- model
+  print(head(current_data))
+  scenario_data_list[[model]] <- current_data
+}
+
+combined_scenario_data <- bind_rows(scenario_data_list)
+print(paste("Combined data for", scenario, ":", nrow(combined_scenario_data), "rows"))
+saveRDS(combined_scenario_data, file.path(base_path, paste0(scenario, "_combined.rds")))
+message(paste("Saved combined data for", scenario, "to", paste0(scenario, "_combined.rds")))
+
+# Scenario 2: "scenarioER"
+scenarioER <- "scenarioER"
+scenario_path_ER <- file.path(base_path, scenarioER)
+files_ER <- list.files(scenario_path_ER, pattern = "\\.RData$", full.names = TRUE)
+print(paste("Processing scenario:", scenarioER))
+print(paste("Files found:", files_ER))
+
+scenarioER_data_list <- list()
+
+for (file_path in files_ER) {
+  load(file_path)
+  model <- tools::file_path_sans_ext(basename(file_path))
+  print(paste("Processing file:", file_path))
+  print(paste("Model identified:", model))
+  
+  object_name <- paste0("RD_", model)
+  object_name_er <- paste0("RD_", model, "_ER")
+  object_name_dot_er <- paste0("RD_", model, ".ER")
+  
+  if (exists(object_name_er)) {
+    print(paste("Found object:", object_name_er))
[…]

### 2024-09-11 simResults_scenario/10.1_forward/forward.R
updated forward and backward stepwise simulation results

@@ -67,7 +67,11 @@ for (i in (b+1):a) {
   # found some id != idx
   data$idx <- data$id
   
-  stepwise_forward <- regsubsets(full.formula, data = data, method = "forward", nvmax = length(proxy.list), nbest = 10)
+  stepwise_forward <- regsubsets(full.formula, 
+                                 data = data, 
+                                 method = "forward", 
+                                 nvmax = length(covarsTfull)+1, 
+                                 nbest = 10)
   summary_stepwise <- summary(stepwise_forward)
   best_model <- which.max(summary_stepwise$adjr2)
   sel.variables <- names(summary_stepwise$which[best_model,])[summary_stepwise$which[best_model,]]

### 2024-09-11 simResults_scenario/10.2_backward/backward.R

@@ -67,7 +67,11 @@ for (i in (b+1):a) {
   # found some id != idx
   data$idx <- data$id
   
-  stepwise_backward <- regsubsets(full.formula, data = data, method = "backward", nvmax = length(proxy.list), nbest = 10)
+  stepwise_backward <- regsubsets(full.formula, 
+                                  data = data, 
+                                  method = "backward", 
+                                  nvmax = length(covarsTfull)+1, 
+                                  nbest = 10)
   summary_stepwise <- summary(stepwise_backward)
   best_model <- which.max(summary_stepwise$adjr2)
   sel.variables <- names(summary_stepwise$which[best_model,])[summary_stepwise$which[best_model,]]

### 2024-09-11 simResults_scenarioOR/10.2_backward/backward.R

@@ -70,7 +70,11 @@ for (i in (b+1):a) {
   # found some id != idx
   data$idx <- data$id
 
-  stepwise_backward <- regsubsets(full.formula, data = data, method = "backward", nvmax = length(proxy.list), nbest = 10)
+  stepwise_backward <- regsubsets(full.formula, 
+                                  data = data, 
+                                  method = "backward", 
+                                  nvmax = length(covarsTfull)+1, 
+                                  nbest = 10)
   summary_stepwise <- summary(stepwise_backward)
   best_model <- which.max(summary_stepwise$adjr2)
   sel.variables <- names(summary_stepwise$which[best_model,])[summary_stepwise$which[best_model,]]

### 2024-09-11 Writeup/manuscript.Rmd
add some comment to the writeup

@@
 
+\textcolor{blue}{*!!!!!!!! need to write what hdps is, and why alternatives are considered*}
+
 **Aim**: The aim of this research is to systematically evaluate and compare different proxy selection methods within the context of high-dimensional propensity score (hdPS) analysis.
@@
 The comparison between the data generation process and the analysis process reveals two key differences: (i) The data generation used transformed laboratory variables, whereas the analysis was conducted using only the original laboratory variables.
-(ii) The data generation employed a simple sum of selected proxy variables (sum of 94 proxy covariates), while the analysis included all proxy variables (143 binary proxies), with 49 of these acting as noise variables.
+(ii) The data generation employed a simple sum of selected proxy variables (sum of 94 proxy covariates), while the analysis included all proxy variables (143 \textcolor{green}{bold}{*142*} binary proxies), with 49 \textcolor{green}{bold}{*49?
+48?*} of these acting as noise variables.
 These differences help us assess how the proxy variable selection methods handle model misspecification and the presence of noise variables.

### 2024-09-12 Writeup/manuscript.Rmd
added some comment to the writeup

--- 2024-09-03 Writeup/manuscript.Rmd
@@
 
+\textcolor{blue}{\textbf{Introduction of hdPS}: The use of medico-administrative datasets in research is frequently criticized due to the potential for the lack of key confounders.
+Estimating treatment effects utilizing such data sources may be subject to residual confounding.
+To address this issue, the high-dimensional propensity score (hdPS) algorithm was introduced in 2009.
+The hdPS method systematically incorporates some information that are associated with the unmeasured or mismeasured confounders as proxies, with the goal of reducing residual confounding bias.}
+
+\textcolor{blue}{\textbf{Significance of alternatives}: Since the introduction of hdPS algorithm, numerous extensions, rooted in machine learning and semi-parametric techniques, have been developed in order to improve the selection of proxy variables.
+The study aims to compare and evaluate the hdPS methods alongside the alternative proxy selection approaches to identify the ones that provide superior confounder adjustment, reduce bias, and enhance the precision of treatment effect estimation.}
+
 **Aim**: The aim of this research is to systematically evaluate and compare different proxy selection methods within the context of high-dimensional propensity score (hdPS) analysis.
@@
 To simulate this, we selected only those binary proxy covariates (referred to as recurrence covariates in hdPS terminology) that had a relative risk (RR) of less than 0.8 or greater than 1.2 concerning the outcome.
-Out of 143 proxy covariates, 94 met this criterion and were included in calculating a simple comorbidity burden measure.
-The remaining 49 covariates were excluded from this calculation and considered noise.
+Out of 143 \textcolor{brown}{\textbf{142}} proxy covariates, 94 met this criterion and were included in calculating a simple comorbidity burden measure.
+The remaining 49 \textcolor{brown}{\textbf{49?
+or 48?}} covariates were excluded from this calculation and considered noise.
 This comorbidity burden measure was then incorporated into our model specification for generating the plasmode data.
@@
 
+\textcolor{blue}{All looks good!}
+
 The comparison between the data generation process and the analysis process reveals two key differences: (i) The data generation used transformed laboratory variables, whereas the analysis was conducted using only the original laboratory variables.
-(ii) The data generation employed a simple sum of selected proxy variables (sum of 94 proxy covariates), while the analysis included all proxy variables (143 binary proxies), with 49 of these acting as noise variables.
+(ii) The data generation employed a simple sum of selected proxy variables (sum of 94 proxy covariates), while the analysis included all proxy variables (143 \textcolor{brown}{\textbf{142}} binary proxies), with 49\textcolor{brown}{\textbf{49?
+or 48?}} of these acting as noise variables.
 These differences help us assess how the proxy variable selection methods handle model misspecification and the presence of noise variables.
@@
 5.
-**Elasticnet**: Elastic Net is an extension of LASSO that includes an additional penalty term to handle multicollinearity by grouping correlated features and selecting the most representative ones [@karim2018can].
+**Elastic Net**: Elastic Net is an extension of LASSO that includes an additional penalty term to handle multicollinearity by grouping correlated features and selecting the most representative ones [@karim2018can].
 
@@
 
+\textcolor{blue}{*Comments and edits in brown and blue color.*}
+
 The results for each method under the different scenarios are summarized below.
@@
 GA shows the highest bias (0.0287), indicating a substantial deviation from the true effect.
-Among the other methods, Bross-based hdPS (-0.0001), Hybrid hdPS (0.0016), and Elasticnet (0.0036) demonstrated low bias.
+Among the other methods, Bross-based hdPS (-0.0001), Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
 XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly higher bias.
 
+\textcolor{brown}{It seems that Bross-based hdPS (-0.0001) instead of the kitchen sink model (0.0002) exhibited the smallest bias.}
+
+\textcolor{blue}{The Bross-based hdPS model exhibited the smallest bias (-0.0001).
+GA shows the highest bias (0.0287), indicating a substantial deviation from the true effect.
+Among the other methods, the kitchen sink model (0.0002), Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
+XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly higher bias.}
+
 2.
-*Coverage*: The coverage for most methods was high, with Hybrid hdPS, Forward Selection, Backward Elimination, LASSO, and Elasticnet achieving values around 98%, indicating well-calibrated confidence intervals.
+*Coverage*: The coverage for most methods was high, with Hybrid hdPS, Forward Selection, Backward Elimination, LASSO, and Elastic Net achieving values around 98%, indicating well-calibrated confidence intervals.
 However, GA had significantly lower coverage (83.8%), indicating that its confidence intervals might be too narrow or biased, potentially missing the true effect.
@@
 GA maintained the highest MSE (0.0016), reflecting its higher bias and variability.
-The kitchen sink model (0.0009), Bross-based hdPS (0.0008), Hybrid hdPS (0.0008), and Elasticnet (0.0009) all had relatively similar and moderate MSE values.
+The kitchen sink model (0.0009), Bross-based hdPS (0.0008), Hybrid hdPS (0.0008), and Elastic Net (0.0009) all had relatively similar and moderate MSE values.
 
@@
 Other methods, including GA (0.0274), Hybrid hdPS (0.0278), and Bross-based hdPS (0.0287), showed moderate variability.
-LASSO (0.0299) and Elasticnet (0.0294) had slightly higher variability.
+LASSO (0.0299) and Elastic Net (0.0294) had slightly higher variability.
 The Model-based SE followed a similar pattern, with XGBoost (0.0268) showing the lowest variability and the kitchen sink model (0.0333) the highest, indicating less precision in its estimates.
@@
 XGBoost had a bias of 0.0259, which, while still higher than some other methods, was lower than GA.
-Other methods, such as Bross-based hdPS (0.0035), Hybrid hdPS (0.0049), and Elasticnet (0.0053), demonstrated moderate bias.
+Other methods, such as Bross-based hdPS (0.0035), Hybrid hdPS (0.0049), and Elastic Net (0.0053), demonstrated moderate bias.
 Random Forest (RF) (0.0127) and Forward Selection (0.0108) had slightly higher bias but remained within an acceptable range.
@@
 The GA method had a higher MSE (0.0043), reflecting its substantial bias and variability.
-The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elasticnet (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.
+The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.
+
+\textcolor{brown}{It seems that forward selection model instead of Hybrid hdPS and XGBoost demonstrated the lowest MSE (0.003)}
+
+\textcolor{blue}{The forward selection algorithm exhibited the lowest MSE (0.0030), indicating that this method was the most accurate in this scenario.
+In addition, the hybrid hdPS and XGBoost also demonstrated relatively low MSE (0.0032).
+The GA method had a higher MSE (0.0043), reflecting its substantial bias and variability.
+The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.}
 
@@
 Among other methods, XGBoost demonstrated the lowest bias (-0.0061), while methods like Hybrid hdPS (-0.0082), Forward Selection (-0.0070), and Backward Elimination (-0.0070) had slightly higher but still moderate biases.
-Elasticnet and LASSO both had biases of -0.0079, reflecting slightly larger deviations compared to XGBoost but still within acceptable limits.
+Elastic Net and LASSO both had biases of -0.0079, reflecting slightly larger deviations compared to XGBoost but still within acceptable limits.
 
@@
 GA had the highest MSE (0.0040), reflecting its substantial bias and variability.
-The kitchen sink model (0.0005), Bross-based hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and Elasticnet (0.0005) all had relatively similar MSE values, indicating moderate accuracy.
+The kitchen sink model (0.0005), Bross-based hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and Elastic Net (0.0005) all had relatively similar MSE values, indicating moderate accuracy.
 
@@
 The GA method exhibited the highest Empirical SE (0.0523), indicating greater variability and less precision.
-Methods like Hybrid hdPS (0.0184), Forward Selection (0.0187), and Elasticnet (0.0203) showed moderate variability, while Bross-based hdPS (0.0206) and the kitchen sink model (0.0212) had slightly higher variability.
+Methods like Hybrid hdPS (0.0184), Forward Selection (0.0187), and Elastic Net (0.0203) showed moderate variability, while Bross-based hdPS (0.0206) and the kitchen sink model (0.0212) had slightly higher variability.
 In terms of Model-based SE, XGBoost (0.0179) again showed the lowest variability, consistent with its low Empirical SE, indicating that it provided the most stable estimates.
@@
 
+\textcolor{blue}{\textbf{Summary results}: The dataset comprises 7585 individuals. Among these, the prevalence of the exposure is 0.488, while the prevalence of the outcome is 0.237.}
+
 See Figure \ref{fig:comparison-plot} for the results from analyzing the NHANES (2013-2018) dataset.
@@
 data_combined <- data.frame(
-  Method = rep(c("Bross", "Hybrid", "LASSO", "Elasticnet", "GA", "XGBoost", "RF", "FS", "BE"), 2),
+  Method = rep(c("Bross", "Hybrid", "LASSO", "ElasticNet", "GA", "XGBoost", "RF", "FS", "BE"), 2),
   # These are approximate values
@@
 
+\textcolor{brown}{I found the results in the table here is a little bit different from the value I got from the real data analysis. See the updated plot "comparison-plot-updated" and its code below:}
+
+```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
+The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
+Methods are arranged by the number of variables used in the models.\\label{fig:comparison-plot-updated}", message=FALSE, warning=FALSE}
+library(ggplot2)
+library(dplyr)
+
+# Combine RD and OR data into a single data frame
+data_combined <- data.frame(
+  Method = rep(c("KitchenSink", "Bross", "Hybrid", "LASSO", "ElasticNet", "RF", "XGBoost", "FS", "BE", "GA"), 2),
+  # These are approximate values
+  Value = c(0.075, 0.077, 0.079, 0.078, 0.075, 0.085, 0.082, 0.078, 0.078, 0.076, 
+            1.502, 1.522, 1.543, 1.531, 1.504, 1.588, 1.564, 1.533, 1.533, 1.515),
+  LowerCI = c(0.056, 0.058, 0.06, 0.059, 0.056, 0.066, 0.063, 0.059, 0.059, 0.057,
+              1.395, 1.413, 1.432, 1.421, 1.396, 1.474, 1.452, 1.423, 1.423, 1.406),
+  UpperCI = c(0.095, 0.096, 0.099, 0.098, 0.094, 0.104, 0.101, 0.097, 0.097, 0.096,
+              1.618, 1.64, 1.663, 1.65, 1.62, 1.712, 1.685, 1.653, 1.653, 1.632),
+  Measure = rep(c("RD", "OR"), each = 10),
+  Variables = rep(c(142, 100, 49, 60, 69, 100, 48, 59, 59, 64), 2)
+)
+
+# Create a new Method label that includes the number of variables
+data_combined <- data_combined %>%
+  mutate(MethodLabel = paste(Method, " [", Variables, "]", sep = ""))
+
+# Reorder the factor levels of MethodLabel based on the number of variables
+data_combined$MethodLabel <- factor(data_combined$MethodLabel,
+                                    levels = unique(data_combined$MethodLabel[order(data_combined$Variables)]))
+
+# Create the plot with the reordered MethodLabel
+ggplot(data_combined, aes(x = Value, y = MethodLabel)) +
+  geom_point(size = 4) +
+  geom_errorbarh(aes(xmin = LowerCI, xmax = UpperCI), height = 0.2) +
+  geom_text(aes(label = Value, x = Value, y = MethodLabel), 
+            vjust = -0.8, hjust = -0.5, size = 3) +
+  facet_grid(. ~ Measure, scales = "free_x") +
+  labs(x = "Value",
+       y = "Method [Chosen number of proxies]") +
+  theme_minimal() +
+  theme(strip.text = element_text(size = 12, face = "bold"))
+```
+
+\textcolor{blue}{See Figure \ref{fig:comparison-plot-updated} for the updated results from analyzing the NHANES (2013-2018) dataset.
+The methods are arranged according to the number of selected proxy variables.
+Among all variable selection algorithms, Random Forest (RF) and XGBoost demonstrate the highest odds ratios (ORs), with values of 1.588 and 1.564, respectively.
+The ORs for the remaining methods cluster around 1.523.
+Additionally, with the exception of RF and the Bross formula hdPS, a general pattern emerges where methods selecting a larger number of proxy variables yield higher ORs.
+For risk difference (RD), RF and XGBoost also exhibit the highest values, 0.085 and 0.082, respectively, while the remaining methods converge around 0.077.
+The trend observed in the OR results appears to persist in the RD analysis.}
+
 Table \ref{tab:method-comparison} presents a pairwise comparison of the number of proxy features shared between different variable selection methods used in the analysis.
@@
 \toprule
- & \textbf{Bross} & \textbf{Hybrid} & \textbf{LASSO} & \textbf{Elasticnet} & \textbf{GA} & \textbf{XGBoost} & \textbf{RF} & \textbf{FS} & \textbf{BE} \\
+ & \textbf{Bross} & \textbf{Hybrid} & \textbf{LASSO} & \textbf{ElasticNet} & \textbf{GA} & \textbf{XGBoost} & \textbf{RF} & \textbf{FS} & \textbf{BE} \\
 \midrule
@@
 \textbf{LASSO} & 47 & 47 & 60 & & & & & & \\
-\textbf{Elasticnet} & 54 & 48 & 60 & 69 & & & & & \\
+\textbf{Elastic Net} & 54 & 48 & 60 & 69 & & & & & \\
 \textbf{Genetic algorithm (GA)} & 44 & 28 & 36 & 40 & 64 & & & & \\
@@
 
+\begin{table}[htbp]
+\centering
+\caption{Computing Time for the Real-World Analysis for each Algorithm}
+\label{tab:computing-time}
+\begin{tabular}{lc}
+\toprule
+\textbf{Method} & \textbf{Computing Time}\\
+\midrule
+\textbf{Kitchen Sink} & 2.942 \\
+\textbf{Bross formula} & 2.280 \\
+\textbf{Hybrid (Bross and LASSO)} & 2.517 \\
+\textbf{LASSO} & 2.540  \\
+\textbf{Elastic Net} & 2.814 \\
+\textbf{Random Forest (RF)} & 379.485 \\
+\textbf{XGBoost} & 1.444 \\
+\textbf{Forward selection (FS)} & 7.417 \\
+\textbf{Backward elimination (BE)} & 12.794 \\
+\textbf{Genetic algorithm (GA)} & 105.697 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\textcolor{blue}{All methods, aside from RF and GA, exhibit relatively fast computing times. Although RF and GA are slower, their computational demands still remain within reasonable time limits.}
+
 # Discussion
@@
 The kitchen sink model, while demonstrating low bias and reasonable MSE, generally had higher variability and lower precision compared to other methods like XGBoost.
-Methods such as Bross-based hdPS, Hybrid hdPS, and Elasticnet performed moderately well across all scenarios, balancing bias, coverage, and MSE, but they did not outperform XGBoost in overall accuracy and precision.
+Methods such as Bross-based hdPS, Hybrid hdPS, and Elastic Net performed moderately well across all scenarios, balancing bias, coverage, and MSE, but they did not outperform XGBoost in overall accuracy and precision.
 
@@
 - RR: Relative Risk
-- Elasticnet: A regularized regression method that combines LASSO and Ridge regression
+- ElasticNet: A regularized regression method that combines LASSO and Ridge regression
 

### 2024-09-12 Writeup/manuscript.Rmd
add the common rate table and corresponding description

@@
 
-\textcolor{blue}{\textbf{Summary results}: The dataset comprises 7585 individuals. Among these, the prevalence of the exposure is 0.488, while the prevalence of the outcome is 0.237.}
+\textcolor{blue}{\textbf{Summary results}: The dataset comprises 7585 individuals.
+Among these, the prevalence of the exposure is 48.8\% or 0.488 , while the prevalence of the outcome is 23.7\% or 0.237.}
 
@@
 
-```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
+```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95\\% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
 The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
@@
 
-\textcolor{brown}{I found the results in the table here is a little bit different from the value I got from the real data analysis. See the updated plot "comparison-plot-updated" and its code below:}
+\textcolor{brown}{I found the results in the table here is a little bit different from the value I got from the real data analysis.
+Also I found the cap of the figure not printing properly on my computer.
+I have to add double backslash before the pct symbol \%.
+If on other computers the double backslash causes some error maybe deleting it would help?
+See the updated plot "comparison-plot-updated" and its code below:}
 
-```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
+\textcolor{blue}{See Figure \ref{fig:comparison-plot-updated} for the updated results from analyzing the NHANES (2013-2018) dataset.
+The methods are arranged according to the number of selected proxy variables.
+Among all variable selection algorithms, Random Forest (RF) and XGBoost demonstrate the highest odds ratios (ORs), with values of 1.588 and 1.564, respectively.
+The ORs for the remaining methods cluster around 1.523.
+Additionally, with the exception of RF and the Bross formula hdPS, a general pattern emerges where methods selecting a larger number of proxy variables yield higher ORs.
+For risk difference (RD), RF and XGBoost also exhibit the highest values, 0.085 and 0.082, respectively, while the remaining methods converge around 0.077.
+The trend observed in the OR results appears to persist in the RD analysis.}
+
+```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95\\% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
 The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
@@
 
-\textcolor{blue}{See Figure \ref{fig:comparison-plot-updated} for the updated results from analyzing the NHANES (2013-2018) dataset.
-The methods are arranged according to the number of selected proxy variables.
-Among all variable selection algorithms, Random Forest (RF) and XGBoost demonstrate the highest odds ratios (ORs), with values of 1.588 and 1.564, respectively.
-The ORs for the remaining methods cluster around 1.523.
-Additionally, with the exception of RF and the Bross formula hdPS, a general pattern emerges where methods selecting a larger number of proxy variables yield higher ORs.
-For risk difference (RD), RF and XGBoost also exhibit the highest values, 0.085 and 0.082, respectively, while the remaining methods converge around 0.077.
-The trend observed in the OR results appears to persist in the RD analysis.}
-
 Table \ref{tab:method-comparison} presents a pairwise comparison of the number of proxy features shared between different variable selection methods used in the analysis.
@@
 
+\textcolor{brown}{Updated the pairwise comparison table with adding the value for kitchen sink (ks).
+Though as the ks model contains all variables, adding the values for it would not add anything useful, I think it is weird to omit a method in the table without saying anything.
+Also here I changed the order/arrange of the methods, to match to the order/arrange of methods in the Methods section.}
+
+\textcolor{blue}{Table \ref{tab:method-comparison-updated} presents a pairwise comparison of the number of proxy features shared between different variable selection methods used in the analysis.
+Each cell in the table indicates the count of common proxy variables selected by the method in the corresponding row and column.
+The diagonal cells, where the row and column methods are the same, represent the total number of proxy variables selected exclusively by each method.
+The first column displays the number of proxy variables shared between each method and the kitchen sink (KS) model.
+Given that the KS model includes all proxy variables, the values in the first column are identical to those in the diagonal cells for each row, which also presents the total number of proxy variables selected by the method in the corresponding row.}
+
+\begin{table}[htbp]
+\centering
+\caption{Updated Comparison of variable overlap of selected proxies across different methods used to evaluate the association between obesity and diabetes}
+\label{tab:method-comparison-updated}
+\begin{tabular}{lcccccccccc}
+\toprule
+ & \textbf{KS} & \textbf{Bross} & \textbf{Hybrid} & \textbf{LASSO} & \textbf{EN} & \textbf{RF} & \textbf{XGB} & \textbf{FS} & \textbf{BE} & \textbf{GA} \\
+\midrule
+\textbf{Kitchen sink (KS)} & 142 & & & & & & & & & \\
+\textbf{Bross formula} & 100 & 100 & & & & & & & & \\
+\textbf{Hybrid (Bross and LASSO)} & 49 & 49 & 49 & & & & & & & \\
+\textbf{LASSO} & 60 & 47 & 47 & 60 & & & & & & \\
+\textbf{Elastic Net (EN)} & 69 & 54 & 48 & 60 & 69 & & & & & \\
+\textbf{Random Forest (RF)} & 100 & 71 & 38 & 46 & 52 & 100 & & & & \\  
+\textbf{XGBoost (XGB)} & 48 & 38 & 24 & 28 & 30 & 37 & 48 & & & \\
+\textbf{Forward selection (FS)} & 59 & 45 & 41 & 51 & 54 & 45 & 25 & 59 & & \\
+\textbf{Backward elimination (BE)} & 59 & 45 & 41 & 51 & 54 & 45 & 25 & 59 & 59 & \\
+\textbf{Genetic algorithm (GA)} & 64 & 44 & 28 & 36 & 40 & 49 & 25 & 35 & 35 & 64 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\textcolor{blue}{Table \ref{tab:proxy-common-pct-bross} presents the comparison of common proxy counts and rates between different methods with the bross formula hdPS.
+Column 1 indicates the number of proxy variables selected by each variable selection method.
+Column 2 shows the number of common features selected by each method and the Bross formula method.
+Column 3 demonstrates the percentage of the common features in the total number of features of each method.}
+
+\textcolor{blue}{From Table \ref{tab:proxy-common-pct-bross}, it can be observed that, with the exception of the bross hdPS and random forest (RF) models, where the number of proxies was manually set to 100, and the kitchen sink (KS) model, which inherently includes all proxies, the number of proxy variables selected by all other models ranges from 49 to 69.
+The hybird method of bross and lasso hdPS, by definition, performs lasso proxy selection on the 100 proxy variables selected by bross, resulting in an inherent common rate of 1.00.
+For the remaining methods, the common rates are clustered around 0.74, with XGBoost exhibiting the highest common rate of 0.792 and GA presenting the lowest common rate of 0.688.}
+
+\begin{table}[htbp]
+\centering
+\caption{Comparison of the count and percentage of proxy variables selected by each methods in common with that by the Bross formula hdPS}
+\label{tab:proxy-common-pct-bross}
+\begin{tabular}{lccc}
+\toprule
+\textbf{Method} & \textbf{Total Count} & \textbf{Common Count} & \textbf{Rate in Common} \\ 
+\midrule
+\textbf{Kitchen sink} & 142 & - & - \\
+\textbf{Bross formula} & 100 & - & - \\
+\textbf{Hybrid (Bross and LASSO)} & 49 & 49 & 1.000 \\
+\textbf{LASSO} & 60 & 47 & 0.783 \\
+\textbf{Elastic Net} & 69 & 54 & 0.783 \\
+\textbf{Random Forest (RF)} & 100 & 71 & 0.710 \\  
+\textbf{XGBoost} & 48 & 38 & 0.792 \\
+\textbf{Forward selection (FS)} & 59 & 45 & 0.763 \\
+\textbf{Backward elimination (BE)} & 59 & 45 & 0.763 \\
+\textbf{Genetic algorithm (GA)} & 64 & 44 & 0.688 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 **Computing time**:
@@
 
+\textcolor{blue}{Table \ref{tab:computing-time} presents the computing time for each method.
+All methods, aside from RF and GA, exhibit relatively fast computing times.
+Although RF and GA are slower, their computational demands still remain within reasonable time limits.}
+
 \begin{table}[htbp]
 \centering
-\caption{Computing Time for the Real-World Analysis for each Algorithm}
+\caption{Computing time for the real-world analysis for each algorithm}
 \label{tab:computing-time}
@@
 \end{table}
-
-\textcolor{blue}{All methods, aside from RF and GA, exhibit relatively fast computing times. Although RF and GA are slower, their computational demands still remain within reasonable time limits.}
 
@@
 - MSE: Mean Squared Error
+- \textcolor{blue}{KS: Kitchen Sink}
 - LASSO: Least Absolute Shrinkage and Selection Operator
-- GA: Genetic Algorithm
+- \textcolor{blue}{ElasticNet / EN}: A regularized regression method that combines LASSO and Ridge regression
 - RF: Random Forest
@@
 - BE: Backward Elimination
+- GA: Genetic Algorithm
 - CV: Cross-Validation
 - RR: Relative Risk
-- ElasticNet: A regularized regression method that combines LASSO and Ridge regression
 

### 2024-09-13 Writeup/manuscript.tex
updated manuscript

@@
 
+\textcolor{blue}{\textbf{Introduction of hdPS}: The use of medico-administrative datasets in research is frequently criticized due to the potential for the lack of key confounders.
+Estimating treatment effects utilizing such data sources may be subject to residual confounding.
+To address this issue, the high-dimensional propensity score (hdPS) algorithm was introduced in 2009.
+The hdPS method systematically incorporates some information that are associated with the unmeasured or mismeasured confounders as proxies, with the goal of reducing residual confounding bias.}
+
+\textcolor{blue}{\textbf{Significance of alternatives}: Since the introduction of hdPS algorithm, numerous extensions, rooted in machine learning and semi-parametric techniques, have been developed in order to improve the selection of proxy variables.
+The study aims to compare and evaluate the hdPS methods alongside the alternative proxy selection approaches to identify the ones that provide superior confounder adjustment, reduce bias, and enhance the precision of treatment effect estimation.}
+
 \textbf{Aim}: The aim of this research is to systematically evaluate and
@@
   that had a relative risk (RR) of less than 0.8 or greater than 1.2
-  concerning the outcome. Out of 143 proxy covariates, 94 met this
-  criterion and were included in calculating a simple comorbidity burden
-  measure. The remaining 49 covariates were excluded from this
-  calculation and considered noise. This comorbidity burden measure was
-  then incorporated into our model specification for generating the
+  concerning the outcome. Out of 143 \textcolor{brown}{\textbf{142}}
+  proxy covariates, 94 met this criterion and were included in
+  calculating a simple comorbidity burden measure. The remaining 49
+  \textcolor{brown}{\textbf{49? or 48?}} covariates were excluded from
+  this calculation and considered noise. This comorbidity burden measure
+  was then incorporated into our model specification for generating the
   plasmode data.
@@
 
+\textcolor{blue}{All looks good!}
+
 The comparison between the data generation process and the analysis
@@
 employed a simple sum of selected proxy variables (sum of 94 proxy
-covariates), while the analysis included all proxy variables (143 binary
-proxies), with 49 of these acting as noise variables. These differences
-help us assess how the proxy variable selection methods handle model
-misspecification and the presence of noise variables.
+covariates), while the analysis included all proxy variables (143
+\textcolor{brown}{\textbf{142}} binary proxies), with
+49\textcolor{brown}{\textbf{49? or 48?}} of these acting as noise
+variables. These differences help us assess how the proxy variable
+selection methods handle model misspecification and the presence of
+noise variables.
 
@@
 \item
-  \textbf{Elasticnet}: Elastic Net is an extension of LASSO that
+  \textbf{Elastic Net}: Elastic Net is an extension of LASSO that
   includes an additional penalty term to handle multicollinearity by
@@
 
+\textcolor{blue}{*Comments and edits in brown and blue color.*}
+
 The results for each method under the different scenarios are summarized
@@
 \def\labelenumi{\arabic{enumi}.}
+\tightlist
 \item
@@
   true effect. Among the other methods, Bross-based hdPS (-0.0001),
-  Hybrid hdPS (0.0016), and Elasticnet (0.0036) demonstrated low bias.
+  Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
   XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly
   higher bias.
+\end{enumerate}
+
+\textcolor{brown}{It seems that Bross-based hdPS (-0.0001) instead of the kitchen sink model (0.0002) exhibited the smallest bias.}
+
+\textcolor{blue}{The Bross-based hdPS model exhibited the smallest bias (-0.0001).
+GA shows the highest bias (0.0287), indicating a substantial deviation from the true effect.
+Among the other methods, the kitchen sink model (0.0002), Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
+XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly higher bias.}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
 \item
   \emph{Coverage}: The coverage for most methods was high, with Hybrid
-  hdPS, Forward Selection, Backward Elimination, LASSO, and Elasticnet
+  hdPS, Forward Selection, Backward Elimination, LASSO, and Elastic Net
   achieving values around 98\%, indicating well-calibrated confidence
@@
   variability. The kitchen sink model (0.0009), Bross-based hdPS
-  (0.0008), Hybrid hdPS (0.0008), and Elasticnet (0.0009) all had
+  (0.0008), Hybrid hdPS (0.0008), and Elastic Net (0.0009) all had
   relatively similar and moderate MSE values.
@@
   (0.0278), and Bross-based hdPS (0.0287), showed moderate variability.
-  LASSO (0.0299) and Elasticnet (0.0294) had slightly higher
+  LASSO (0.0299) and Elastic Net (0.0294) had slightly higher
   variability. The Model-based SE followed a similar pattern, with
@@
   lower than GA. Other methods, such as Bross-based hdPS (0.0035),
-  Hybrid hdPS (0.0049), and Elasticnet (0.0053), demonstrated moderate
+  Hybrid hdPS (0.0049), and Elastic Net (0.0053), demonstrated moderate
   bias. Random Forest (RF) (0.0127) and Forward Selection (0.0108) had
@@
   kitchen sink model also had an MSE of 0.0043, similar to GA, while
-  other methods like Bross-based hdPS (0.0035), RF (0.0039), and
-  Elasticnet (0.0036) exhibited moderate MSE values, indicating
-  reasonable accuracy.
+  other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elastic
+  Net (0.0036) exhibited moderate MSE values, indicating reasonable
+  accuracy.
+\end{enumerate}
+
+\textcolor{brown}{It seems that forward selection model instead of Hybrid hdPS and XGBoost demonstrated the lowest MSE (0.003)}
+
+\textcolor{blue}{The forward selection algorithm exhibited the lowest MSE (0.0030), indicating that this method was the most accurate in this scenario.
+In addition, the hybrid hdPS and XGBoost also demonstrated relatively low MSE (0.0032).
+The GA method had a higher MSE (0.0043), reflecting its substantial bias and variability.
+The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
 \item
@@
   Elimination (-0.0070) had slightly higher but still moderate biases.
-  Elasticnet and LASSO both had biases of -0.0079, reflecting slightly
+  Elastic Net and LASSO both had biases of -0.0079, reflecting slightly
   larger deviations compared to XGBoost but still within acceptable
@@
   bias and variability. The kitchen sink model (0.0005), Bross-based
-  hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and
-  Elasticnet (0.0005) all had relatively similar MSE values, indicating
+  hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and Elastic
+  Net (0.0005) all had relatively similar MSE values, indicating
   moderate accuracy.
@@
   variability and less precision. Methods like Hybrid hdPS (0.0184),
-  Forward Selection (0.0187), and Elasticnet (0.0203) showed moderate
+  Forward Selection (0.0187), and Elastic Net (0.0203) showed moderate
   variability, while Bross-based hdPS (0.0206) and the kitchen sink
@@
 
+\textcolor{blue}{\textbf{Summary results}: The dataset comprises 7585 individuals.
+Among these, the prevalence of the exposure is 48.8\% or 0.488 , while the prevalence of the outcome is 23.7\% or 0.237.}
+
 See Figure \ref{fig:comparison-plot} for the results from analyzing the
@@
 Methods are arranged by the number of variables used in the models.\label{fig:comparison-plot}}\label{fig:unnamed-chunk-3}
+\end{figure}
+
+\textcolor{brown}{I found the results in the table here is a little bit different from the value I got from the real data analysis.
+Also I found the cap of the figure not printing properly on my computer.
+I have to add double backslash before the pct symbol \%.
+If on other computers the double backslash causes some error maybe deleting it would help?
+See the updated plot "comparison-plot-updated" and its code below:}
+
+\textcolor{blue}{See Figure \ref{fig:comparison-plot-updated} for the updated results from analyzing the NHANES (2013-2018) dataset.
+The methods are arranged according to the number of selected proxy variables.
+Among all variable selection algorithms, Random Forest (RF) and XGBoost demonstrate the highest odds ratios (ORs), with values of 1.588 and 1.564, respectively.
+The ORs for the remaining methods cluster around 1.523.
+Additionally, with the exception of RF and the Bross formula hdPS, a general pattern emerges where methods selecting a larger number of proxy variables yield higher ORs.
+For risk difference (RD), RF and XGBoost also exhibit the highest values, 0.085 and 0.082, respectively, while the remaining methods converge around 0.077.
+The trend observed in the OR results appears to persist in the RD analysis.}
+
+\begin{figure}[th]
+
+{\centering \includegraphics[width=1\linewidth,]{manuscript_files/figure-latex/unnamed-chunk-4-1}
+
+}
+
+\caption{Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95\% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
+The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
+Methods are arranged by the number of variables used in the models.\label{fig:comparison-plot-updated}}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
+\textcolor{brown}{Updated the pairwise comparison table with adding the value for kitchen sink (ks).
+Though as the ks model contains all variables, adding the values for it would not add anything useful, I think it is weird to omit a method in the table without saying anything.
+Also here I changed the order/arrange of the methods, to match to the order/arrange of methods in the Methods section.}
+
+\textcolor{blue}{Table \ref{tab:method-comparison-updated} presents a pairwise comparison of the number of proxy features shared between different variable selection methods used in the analysis.
+Each cell in the table indicates the count of common proxy variables selected by the method in the corresponding row and column.
+The diagonal cells, where the row and column methods are the same, represent the total number of proxy variables selected exclusively by each method.
+The first column displays the number of proxy variables shared between each method and the kitchen sink (KS) model.
+Given that the KS model includes all proxy variables, the values in the first column are identical to those in the diagonal cells for each row, which also presents the total number of proxy variables selected by the method in the corresponding row.}
+
+\begin{table}[htbp]
+\centering
+\caption{Updated Comparison of variable overlap of selected proxies across different methods used to evaluate the association between obesity and diabetes}
+\label{tab:method-comparison-updated}
+\begin{tabular}{lcccccccccc}
+\toprule
+ & \textbf{KS} & \textbf{Bross} & \textbf{Hybrid} & \textbf{LASSO} & \textbf{EN} & \textbf{RF} & \textbf{XGB} & \textbf{FS} & \textbf{BE} & \textbf{GA} \\
+\midrule
+\textbf{Kitchen sink (KS)} & 142 & & & & & & & & & \\
+\textbf{Bross formula} & 100 & 100 & & & & & & & & \\
+\textbf{Hybrid (Bross and LASSO)} & 49 & 49 & 49 & & & & & & & \\
+\textbf{LASSO} & 60 & 47 & 47 & 60 & & & & & & \\
+\textbf{Elastic Net (EN)} & 69 & 54 & 48 & 60 & 69 & & & & & \\
+\textbf{Random Forest (RF)} & 100 & 71 & 38 & 46 & 52 & 100 & & & & \\  
+\textbf{XGBoost (XGB)} & 48 & 38 & 24 & 28 & 30 & 37 & 48 & & & \\
+\textbf{Forward selection (FS)} & 59 & 45 & 41 & 51 & 54 & 45 & 25 & 59 & & \\
+\textbf{Backward elimination (BE)} & 59 & 45 & 41 & 51 & 54 & 45 & 25 & 59 & 59 & \\
+\textbf{Genetic algorithm (GA)} & 64 & 44 & 28 & 36 & 40 & 49 & 25 & 35 & 35 & 64 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\textcolor{blue}{Table \ref{tab:proxy-common-pct-bross} presents the comparison of common proxy counts and rates between different methods with the bross formula hdPS.
+Column 1 indicates the number of proxy variables selected by each variable selection method.
+Column 2 shows the number of common features selected by each method and the Bross formula method.
+Column 3 demonstrates the percentage of the common features in the total number of features of each method.}
+
+\textcolor{blue}{From Table \ref{tab:proxy-common-pct-bross}, it can be observed that, with the exception of the bross hdPS and random forest (RF) models, where the number of proxies was manually set to 100, and the kitchen sink (KS) model, which inherently includes all proxies, the number of proxy variables selected by all other models ranges from 49 to 69.
+The hybird method of bross and lasso hdPS, by definition, performs lasso proxy selection on the 100 proxy variables selected by bross, resulting in an inherent common rate of 1.00.
+For the remaining methods, the common rates are clustered around 0.74, with XGBoost exhibiting the highest common rate of 0.792 and GA presenting the lowest common rate of 0.688.}
+
+\begin{table}[htbp]
+\centering
+\caption{Comparison of the count and percentage of proxy variables selected by each methods in common with that by the Bross formula hdPS}
+\label{tab:proxy-common-pct-bross}
+\begin{tabular}{lccc}
+\toprule
+\textbf{Method} & \textbf{Total Count} & \textbf{Common Count} & \textbf{Rate in Common} \\ 
+\midrule
+\textbf{Kitchen sink} & 142 & - & - \\
+\textbf{Bross formula} & 100 & - & - \\
+\textbf{Hybrid (Bross and LASSO)} & 49 & 49 & 1.000 \\
+\textbf{LASSO} & 60 & 47 & 0.783 \\
+\textbf{Elastic Net} & 69 & 54 & 0.783 \\
+\textbf{Random Forest (RF)} & 100 & 71 & 0.710 \\  
+\textbf{XGBoost} & 48 & 38 & 0.792 \\
+\textbf{Forward selection (FS)} & 59 & 45 & 0.763 \\
+\textbf{Backward elimination (BE)} & 59 & 45 & 0.763 \\
+\textbf{Genetic algorithm (GA)} & 64 & 44 & 0.688 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \textbf{Computing time}:
@@
 \textcolor{red}{*Report computing time for the Real-world analysis for each method. (add ordered table or figure)*}
+
+\textcolor{blue}{Table \ref{tab:computing-time} presents the computing time for each method.
+All methods, aside from RF and GA, exhibit relatively fast computing times.
+Although RF and GA are slower, their computational demands still remain within reasonable time limits.}
+
+\begin{table}[htbp]
+\centering
+\caption{Computing time for the real-world analysis for each algorithm}
+\label{tab:computing-time}
+\begin{tabular}{lc}
+\toprule
+\textbf{Method} & \textbf{Computing Time}\\
+\midrule
+\textbf{Kitchen Sink} & 2.942 \\
+\textbf{Bross formula} & 2.280 \\
+\textbf{Hybrid (Bross and LASSO)} & 2.517 \\
+\textbf{LASSO} & 2.540  \\
+\textbf{Elastic Net} & 2.814 \\
+\textbf{Random Forest (RF)} & 379.485 \\
+\textbf{XGBoost} & 1.444 \\
+\textbf{Forward selection (FS)} & 7.417 \\
+\textbf{Backward elimination (BE)} & 12.794 \\
+\textbf{Genetic algorithm (GA)} & 105.697 \\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 compared to other methods like XGBoost. Methods such as Bross-based
-hdPS, Hybrid hdPS, and Elasticnet performed moderately well across all
+hdPS, Hybrid hdPS, and Elastic Net performed moderately well across all
 scenarios, balancing bias, coverage, and MSE, but they did not
@@
 \item
+  \textcolor{blue}{KS: Kitchen Sink}
+\item
   LASSO: Least Absolute Shrinkage and Selection Operator
 \item
-  GA: Genetic Algorithm
+  \textcolor{blue}{ElasticNet / EN}: A regularized regression method
+  that combines LASSO and Ridge regression
 \item
@@
 \item
+  GA: Genetic Algorithm
+\item
   CV: Cross-Validation
@@
   RR: Relative Risk
-\item
-  Elasticnet: A regularized regression method that combines LASSO and
-  Ridge regression
 \end{itemize}

### 2024-09-13 Writeup/manuscript.Rmd
update2

@@
 
-title: Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Framework - A Plasmode simulation study
+title: Is There a Competitive Advantage to Using Multivariate Statistical or Machine Learning Methods Over the Bross Formula in the hdPS Framework for Bias and Variance Estimation?
 titlerunning: High-Dimensional Propensity Score
@@
 
-\textcolor{red}{*need to write what hdps is, and why alternatives are considered*}
+**High-dimensional Propensity Score (hdPS) Algorithm**: In epidemiology, proxy variables are commonly used as substitutes for confounders that are difficult or impossible to measure directly, such as socioeconomic status, lifestyle factors, or health behaviors [@vanderweele2019principles].
+The high-dimensional propensity score (hdPS) is a pharmacoepidemiological method designed to reduce confounding bias in large healthcare databases [@schneeweiss2009high].
+Unlike traditional propensity score models that rely on investigator-specified or manually selected covariates, hdPS automatically ranks a wide array of proxy variables from healthcare records—such as diagnosis codes, medications, and procedures—using the Bross formula [@wyss2018erratum; @bross1966spurious].
+The Bross formula ranks these variables based on their marginal associations with both exposure and outcome.
+These selected proxy variables serve as surrogates for unmeasured or poorly measured confounders, helping reduce bias in treatment effect estimates.
+The hdPS algorithm further refines the selection by prioritizing variables based on their prevalence and potential for confounding, defined by their association with both exposure and outcome [@schneeweiss2009high].
 
-\textcolor{blue}{\textbf{Introduction of hdPS}: The use of medico-administrative datasets in research is frequently criticized due to the potential for the lack of key confounders.
-Estimating treatment effects utilizing such data sources may be subject to residual confounding.
-To address this issue, the high-dimensional propensity score (hdPS) algorithm was introduced in 2009.
-The hdPS method systematically incorporates some information that are associated with the unmeasured or mismeasured confounders as proxies, with the goal of reducing residual confounding bias.}
+**Multivariate Machine Learning Extensions**: Although the Bross formula performs well in certain contexts, it has limitations in capturing complex interactions, nonlinearities, and higher-order associations between variables, especially in high-dimensional settings where it does not account for the multivariate structure of other covariates [@karim2024high; @karim2018can].
+To address these limitations, multivariate machine learning methods such as LASSO, Elastic Net, and Random Forests have been applied within the hdPS framework.
+These methods are better suited for high-dimensional data, where they can more effectively handle complex relationships and improve the selection of proxy variables, thus enhancing the precision of treatment effect estimates [@karim2018can; @schneeweiss2017variable; @franklin2015regularized].
+Simulation studies and empirical research have shown that these machine learning-based methods, or hybrid approaches combining the Bross formula with machine learning, can reduce confounding more effectively and increase efficiency compared to the Bross formula alone in certain settings [@karim2018can; @schneeweiss2017variable; @franklin2015regularized].
 
-\textcolor{blue}{\textbf{Significance of alternatives}: Since the introduction of hdPS algorithm, numerous extensions, rooted in machine learning and semi-parametric techniques, have been developed in order to improve the selection of proxy variables.
-The study aims to compare and evaluate the hdPS methods alongside the alternative proxy selection approaches to identify the ones that provide superior confounder adjustment, reduce bias, and enhance the precision of treatment effect estimation.}
+**Assessing the Simulation Performance**: Previous studies have often focused on Mean Squared Error (MSE) as a primary metric for evaluating the performance of hdPS and its machine learning extensions [@karim2018can; @franklin2015regularized].
+However, in high-dimensional settings with singly robust methods, such as hdPS and machine learning approaches like LASSO, MSE may not always be the most reliable measure.
+MSE combines both bias and variance into a single metric, which makes interpretation challenging when variance estimation is unstable—a common issue in these methods.
+In contrast, coverage, which measures the proportion of confidence intervals that capture the true treatment effect, provides a more direct and meaningful assessment of a model's reliability.
+In realistic observational studies, where model misspecification is often inevitable, coverage—along with related metrics such as bias-eliminated coverage and relative error in standard error (which compares model-based SE with empirical SE)—can reveal whether confidence intervals or SEs are too narrow (underestimating uncertainty) or too wide (overestimating uncertainty).
+This insight is crucial in determining whether the model delivers valid estimates despite misspecification.
+Even a model with poor MSE but good coverage may still be valuable, as it produces realistic confidence intervals.
+By shifting the focus to coverage, rather than relying solely on MSE, we can achieve a more comprehensive understanding of method performance, especially in cases where unstable variance estimation might distort conclusions drawn from MSE alone.
 
-**Aim**: The aim of this research is to systematically evaluate and compare different proxy selection methods within the context of high-dimensional propensity score (hdPS) analysis.
-Specifically, the study focuses on assessing how these methods, including alternative variable selection approaches, perform in selecting proxy variables for confounding adjustment compared to the traditional Bross method within the hdPS framework.
-We seek to determine whether these alternative methods offer superior performance in estimating treatment effects compared to the default Bross formula.
+**Aim**: This research aims to systematically evaluate and compare various proxy selection methods within the hdPS framework, using a diverse range of simulation performance metrics, including bias, MSE, and coverage.
+The study focuses on assessing how these alternative statistical and machine leartning methods perform in selecting proxy variables for confounding adjustment, compared to the traditional Bross formula.
 
@@
 
-**Motivating Example**: To explore the relationship between obesity and the risk of diabetes, we revisited this association using data from three cycles of the National Health and Nutrition Examination Survey (NHANES) covering the years 2013-2014, 2015-2016, and 2017-2018 [@karim2024high].
-This analysis was informed by a thorough review of the existing literature [@saydah2014trends;@liu2013association;@kabadi2012joint;@ostchega2012abdominal].
-To identify relevant covariates, we constructed a causal diagram based on established causal inference principles [@greenland1999causal].
-The covariates included in our analysis were carefully selected and categorized into Demographic, Behavioral, Health History, Access-related, and Laboratory variables [@karim2024high].
+**Motivating Example**: We revisited the association between obesity and the risk of diabetes using data from three cycles of the National Health and Nutrition Examination Survey (NHANES) covering the years 2013-2014, 2015-2016, and 2017-2018 [@karim2024high].
+To identify relevant investigator-specified covariates, we constructed a causal diagram based on literature [@saydah2014trends;@liu2013association;@kabadi2012joint;@ostchega2012abdominal] and established causal inference principles [@greenland1999causal].
+The covariates included in our analysis were carefully selected and categorized into demographic, behavioral, health history, access-related, and laboratory variables.
 While most of these variables were binary or categorical, the Laboratory variables were continuous.
@@
 This approach was modeled after the analytic dataset derived from NHANES and involved resampling from the observed covariates and exposure information (i.e., obesity) without altering them.
-By mirroring key aspects of an actual epidemiological study, this simulation framework offers a significant advantage over traditional Monte Carlo simulations, which often rely on idealized assumptions.
+By mirroring key aspects of an actual epidemiological study, this simulation framework offers a substantial advantage over traditional Monte Carlo simulations, which often rely on hypothetical assumptions.
 
@@
 
-**True Data Generating Mechanism Used in Plasmode Simulation**: The primary goal of this study is to evaluate various variable selection methods under realistic conditions.
+**True Data Generating Mechanism Used in Plasmode Simulation**: The primary goal of this plasmode simulation study is to evaluate various variable selection methods under realistic conditions.
 To achieve this, we formulated the outcome data based on a specific model specification that incorporates both exposure and covariates, including investigator-specified and proxy variables.
@@
 *Inclusion of Proxy Variables*: Real-world studies often deal with unmeasured confounding, which researchers attempt to mitigate by adding proxy variables.
-However, when a large number of proxies are added, some may act as noise variables, contributing little to the analysis.
+However, when a large number of proxies are added, some may act as noise variables, contributing little or nothing to the analysis.
 To simulate this, we selected only those binary proxy covariates (referred to as recurrence covariates in hdPS terminology) that had a relative risk (RR) of less than 0.8 or greater than 1.2 concerning the outcome.
-Out of 143 \textcolor{brown}{\textbf{142}} proxy covariates, 94 met this criterion and were included in calculating a simple comorbidity burden measure.
-The remaining 49 \textcolor{brown}{\textbf{49?
-or 48?}} covariates were excluded from this calculation and considered noise.
-This comorbidity burden measure was then incorporated into our model specification for generating the plasmode data.
+Out of 142 proxy covariates, 94 met this criterion and were included in calculating a simple comorbidity burden measure.
+The remaining 48 covariates were excluded from this calculation and considered noise.
+This comorbidity burden measure (one variable) was then incorporated into our model specification for generating the outcome data.
 
@@
 
-\textcolor{red}{*check if the description of the methods look okay to you. Make sure the description matches with the analysis codes.*}
-
-\textcolor{blue}{All looks good!}
-
 The comparison between the data generation process and the analysis process reveals two key differences: (i) The data generation used transformed laboratory variables, whereas the analysis was conducted using only the original laboratory variables.
-(ii) The data generation employed a simple sum of selected proxy variables (sum of 94 proxy covariates), while the analysis included all proxy variables (143 \textcolor{brown}{\textbf{142}} binary proxies), with 49\textcolor{brown}{\textbf{49?
-or 48?}} of these acting as noise variables.
+(ii) The data generation employed a simple sum of selected proxy variables (sum of 94 proxy covariates), while the analysis included all proxy variables (142 binary proxies), with 48 of these acting as noise variables.
 These differences help us assess how the proxy variable selection methods handle model misspecification and the presence of noise variables.

### 2024-09-13 Writeup/manuscript.tex
update2

@@
 
-\title[High-Dimensional Propensity Score]{Understanding the role of
-different proxy selection methods in High-Dimensional Propensity Score
-Framework - A Plasmode simulation study}
+\title[High-Dimensional Propensity Score]{Is There a Competitive
+Advantage to Using Multivariate Statistical or Machine Learning Methods
+Over the Bross Formula in the hdPS Framework for Bias and Variance
+Estimation?}
 
@@
 
-\textcolor{red}{*need to write what hdps is, and why alternatives are considered*}
+\textbf{High-dimensional Propensity Score (hdPS) Algorithm}: In
+epidemiology, proxy variables are commonly used as substitutes for
+confounders that are difficult or impossible to measure directly, such
+as socioeconomic status, lifestyle factors, or health behaviors
+\citep{vanderweele2019principles}. The high-dimensional propensity score
+(hdPS) is a pharmacoepidemiological method designed to reduce
+confounding bias in large healthcare databases
+\citep{schneeweiss2009high}. Unlike traditional propensity score models
+that rely on investigator-specified or manually selected covariates,
+hdPS automatically ranks a wide array of proxy variables from healthcare
+records---such as diagnosis codes, medications, and procedures---using
+the Bross formula \citep{wyss2018erratum, bross1966spurious}. The Bross
+formula ranks these variables based on their marginal associations with
+both exposure and outcome. These selected proxy variables serve as
+surrogates for unmeasured or poorly measured confounders, helping reduce
+bias in treatment effect estimates. The hdPS algorithm further refines
+the selection by prioritizing variables based on their prevalence and
+potential for confounding, defined by their association with both
+exposure and outcome \citep{schneeweiss2009high}.
 
-\textcolor{blue}{\textbf{Introduction of hdPS}: The use of medico-administrative datasets in research is frequently criticized due to the potential for the lack of key confounders.
-Estimating treatment effects utilizing such data sources may be subject to residual confounding.
-To address this issue, the high-dimensional propensity score (hdPS) algorithm was introduced in 2009.
-The hdPS method systematically incorporates some information that are associated with the unmeasured or mismeasured confounders as proxies, with the goal of reducing residual confounding bias.}
+\textbf{Multivariate Machine Learning Extensions}: Although the Bross
+formula performs well in certain contexts, it has limitations in
+capturing complex interactions, nonlinearities, and higher-order
+associations between variables, especially in high-dimensional settings
+where it does not account for the multivariate structure of other
+covariates \citep{karim2024high, karim2018can}. To address these
+limitations, multivariate machine learning methods such as LASSO,
+Elastic Net, and Random Forests have been applied within the hdPS
+framework. These methods are better suited for high-dimensional data,
+where they can more effectively handle complex relationships and improve
+the selection of proxy variables, thus enhancing the precision of
+treatment effect estimates
+\citep{karim2018can, schneeweiss2017variable, franklin2015regularized}.
+Simulation studies and empirical research have shown that these machine
+learning-based methods, or hybrid approaches combining the Bross formula
+with machine learning, can reduce confounding more effectively and
+increase efficiency compared to the Bross formula alone in certain
+settings
+\citep{karim2018can, schneeweiss2017variable, franklin2015regularized}.
 
-\textcolor{blue}{\textbf{Significance of alternatives}: Since the introduction of hdPS algorithm, numerous extensions, rooted in machine learning and semi-parametric techniques, have been developed in order to improve the selection of proxy variables.
-The study aims to compare and evaluate the hdPS methods alongside the alternative proxy selection approaches to identify the ones that provide superior confounder adjustment, reduce bias, and enhance the precision of treatment effect estimation.}
+\textbf{Assessing the Simulation Performance}: Previous studies have
+often focused on Mean Squared Error (MSE) as a primary metric for
+evaluating the performance of hdPS and its machine learning extensions
+\citep{karim2018can, franklin2015regularized}. However, in
+high-dimensional settings with singly robust methods, such as hdPS and
+machine learning approaches like LASSO, MSE may not always be the most
+reliable measure. MSE combines both bias and variance into a single
+metric, which makes interpretation challenging when variance estimation
+is unstable---a common issue in these methods. In contrast, coverage,
+which measures the proportion of confidence intervals that capture the
+true treatment effect, provides a more direct and meaningful assessment
+of a model's reliability. In realistic observational studies, where
+model misspecification is often inevitable, coverage---along with
+related metrics such as bias-eliminated coverage and relative error in
+standard error (which compares model-based SE with empirical SE)---can
+reveal whether confidence intervals or SEs are too narrow
+(underestimating uncertainty) or too wide (overestimating uncertainty).
+This insight is crucial in determining whether the model delivers valid
+estimates despite misspecification. Even a model with poor MSE but good
+coverage may still be valuable, as it produces realistic confidence
+intervals. By shifting the focus to coverage, rather than relying solely
+on MSE, we can achieve a more comprehensive understanding of method
+performance, especially in cases where unstable variance estimation
+might distort conclusions drawn from MSE alone.
 
-\textbf{Aim}: The aim of this research is to systematically evaluate and
-compare different proxy selection methods within the context of
-high-dimensional propensity score (hdPS) analysis. Specifically, the
-study focuses on assessing how these methods, including alternative
-variable selection approaches, perform in selecting proxy variables for
-confounding adjustment compared to the traditional Bross method within
-the hdPS framework. We seek to determine whether these alternative
-methods offer superior performance in estimating treatment effects
-compared to the default Bross formula.
+\textbf{Aim}: This research aims to systematically evaluate and compare
+various proxy selection methods within the hdPS framework, using a
+diverse range of simulation performance metrics, including bias, MSE,
+and coverage. The study focuses on assessing how these alternative
+statistical and machine leartning methods perform in selecting proxy
+variables for confounding adjustment, compared to the traditional Bross
+formula.
 

### 2024-09-13 Writeup/manuscript.Rmd
update3

@@
 
-**Assessing the Simulation Performance**: Previous studies have often focused on Mean Squared Error (MSE) as a primary metric for evaluating the performance of hdPS and its machine learning extensions [@karim2018can; @franklin2015regularized].
+**Assessing the Simulation Performance**: Other than bias, previous studies have primarily focused on Mean Squared Error (MSE) as a key metric for evaluating the performance of hdPS and its machine learning extensions [@franklin2015regularized; @pang2016effect; @wyss2018using; @karim2018can; @simon2023evaluating].
 However, in high-dimensional settings with singly robust methods, such as hdPS and machine learning approaches like LASSO, MSE may not always be the most reliable measure.
@@
 In contrast, coverage, which measures the proportion of confidence intervals that capture the true treatment effect, provides a more direct and meaningful assessment of a model's reliability.
-In realistic observational studies, where model misspecification is often inevitable, coverage—along with related metrics such as bias-eliminated coverage and relative error in standard error (which compares model-based SE with empirical SE)—can reveal whether confidence intervals or SEs are too narrow (underestimating uncertainty) or too wide (overestimating uncertainty).
+In realistic observational studies, where model misspecification is often inevitable, coverage—along with related metrics such as bias-eliminated coverage and relative error in standard error (SE; which compares model-based SE with empirical SE)—can reveal whether confidence intervals or SEs are too narrow (underestimating uncertainty) or too wide (overestimating uncertainty).
 This insight is crucial in determining whether the model delivers valid estimates despite misspecification.
@@
 2.
-**Bross formula**: The Bross formula is a statistical method used to calculate the bias introduced by not adjusting for a covariate [@bross1966spurious].
+**hdPS using Bross formula**: The Bross formula is a statistical method used to calculate the bias introduced by not adjusting for a covariate [@bross1966spurious].
 In hdPS analysis, this formula was originally applied to each proxy variable to measure and rank the potential bias if the covariate were not adjusted for.
@@
 
-\textcolor{red}{*Can you check the app in the doc folder of the repo, and compare of the results description look accurate to you?*}
-
-\textcolor{blue}{*Comments and edits in brown and blue color.*}
-
 The results for each method under the different scenarios are summarized below.
@@
 1.
-*Bias*: The kitchen sink model, which includes all variables without selection, exhibited the smallest bias (0.0002).
+*Bias*: Bross-based hdPS exhibited the smallest bias (-0.0001), and the kitchen sink model (0.0002) was the second.
 GA shows the highest bias (0.0287), indicating a substantial deviation from the true effect.
-Among the other methods, Bross-based hdPS (-0.0001), Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
-XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly higher bias.
-
-\textcolor{brown}{It seems that Bross-based hdPS (-0.0001) instead of the kitchen sink model (0.0002) exhibited the smallest bias.}
-
-\textcolor{blue}{The Bross-based hdPS model exhibited the smallest bias (-0.0001).
-GA shows the highest bias (0.0287), indicating a substantial deviation from the true effect.
-Among the other methods, the kitchen sink model (0.0002), Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
-XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly higher bias.}
+Among the other methods, Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
+XGBoost (0.0074) had slightly higher bias than Random Forest (RF) (0.0034).
 
@@
 *Coverage*: The coverage for most methods was high, with Hybrid hdPS, Forward Selection, Backward Elimination, LASSO, and Elastic Net achieving values around 98%, indicating well-calibrated confidence intervals.
-However, GA had significantly lower coverage (83.8%), indicating that its confidence intervals might be too narrow or biased, potentially missing the true effect.
-After applying bias elimination, GA's coverage improved to 96%, which is better but still lower than other methods.
+However, GA had noticeably lower coverage (83.8%), indicating that its confidence intervals might be too narrow or biased, potentially missing the true effect.
+After applying bias elimination (as there were substantial bias associated with this method), GA's coverage improved to 96%.
 
 3.
-*Mean Squared Error (MSE)*: XGBoost achieved the lowest MSE (0.0006), reaffirming it as the most accurate method overall.
+*Mean Squared Error (MSE)*: XGBoost achieved the lowest MSE (0.0006).
 GA maintained the highest MSE (0.0016), reflecting its higher bias and variability.
@@
 The Model-based SE followed a similar pattern, with XGBoost (0.0268) showing the lowest variability and the kitchen sink model (0.0333) the highest, indicating less precision in its estimates.
+When comparing relative error in SE estimation, XGBoost performed the worst.
 See Appendix \S C for further details.
@@
 *Bias*: The kitchen sink model showed a relatively low bias (0.0025), while GA continued to exhibit the highest bias (0.0408), indicating a significant deviation from the true effect.
-XGBoost had a bias of 0.0259, which, while still higher than some other methods, was lower than GA.
+XGBoost had a bias of 0.0259, which, while still higher than other methods, but was lower than GA.
 Other methods, such as Bross-based hdPS (0.0035), Hybrid hdPS (0.0049), and Elastic Net (0.0053), demonstrated moderate bias.
@@
 Other methods such as RF, Forward Selection, Backward Elimination, and Hybrid hdPS maintained coverage values around 94-95%, suggesting adequate interval calibration.
-Bias-eliminated coverage for GA improved to 94.2%, but it was still slightly lower than other methods.
+Bias-eliminated coverage for GA improved to 94.2%, but it was still slightly lower than other methods (e.g., forward selection).
 
 3.
-*Mean Squared Error (MSE)*: Hybrid hdPS and XGBoost both demonstrated the lowest MSE (0.0032), indicating that these methods were the most accurate in this scenario.
+*Mean Squared Error (MSE)*: Forward selection demonstrated the lowest MSE (0.0030), and then Hybrid hdPS and XGBoost.
 The GA method had a higher MSE (0.0043), reflecting its substantial bias and variability.
 The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.
-
-\textcolor{brown}{It seems that forward selection model instead of Hybrid hdPS and XGBoost demonstrated the lowest MSE (0.003)}
-
-\textcolor{blue}{The forward selection algorithm exhibited the lowest MSE (0.0030), indicating that this method was the most accurate in this scenario.
-In addition, the hybrid hdPS and XGBoost also demonstrated relatively low MSE (0.0032).
-The GA method had a higher MSE (0.0043), reflecting its substantial bias and variability.
-The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.}
 
@@
 In terms of Model-based SE, XGBoost (0.0531) and GA (0.0533) continued to show low variability, while the kitchen sink model had the highest Model-based SE (0.0623), indicating less precision in its estimates.
+When comparing relative error in SE estimation, XGBoost and kitchen sink model performed the worst (in other direction).
 
@@
 3.
-*Mean Squared Error (MSE)*: XGBoost exhibited the lowest MSE (0.0003), indicating it as the most accurate method overall in this scenario.
+*Mean Squared Error (MSE)*: XGBoost exhibited the lowest MSE (0.0003).
 GA had the highest MSE (0.0040), reflecting its substantial bias and variability.
@@
 The GA method exhibited the highest Empirical SE (0.0523), indicating greater variability and less precision.
-Methods like Hybrid hdPS (0.0184), Forward Selection (0.0187), and Elastic Net (0.0203) showed moderate variability, while Bross-based hdPS (0.0206) and the kitchen sink model (0.0212) had slightly higher variability.
+Methods such as Hybrid hdPS (0.0184), Forward Selection (0.0187), and Elastic Net (0.0203) showed moderate variability, while Bross-based hdPS (0.0206) and the kitchen sink model (0.0212) had slightly higher variability.
 In terms of Model-based SE, XGBoost (0.0179) again showed the lowest variability, consistent with its low Empirical SE, indicating that it provided the most stable estimates.
 The kitchen sink model had a slightly higher Model-based SE (0.0219), indicating less precision in its estimates.
+When comparing relative error in SE estimation, XGBoost performed the worst.
 
@@
 
-\textcolor{red}{*Here we include full data analysis (with some summary results like exposure and outcome prevalence, and sample size) and report OR and RD.
-Also mention how many proxies were chosen (add in the picture of RD and OR; side by side for each method, ordered my magnitude of RD), and how many were in common with hdPS (add table).*}
+\textbf{Summary results}: The dataset comprises 7,585 individuals. Among these, the prevalence of the exposure is 48.8\%, while the prevalence of the outcome is 23.7\%.
 
-\textcolor{blue}{\textbf{Summary results}: The dataset comprises 7585 individuals.
-Among these, the prevalence of the exposure is 48.8\% or 0.488 , while the prevalence of the outcome is 23.7\% or 0.237.}
-
-See Figure \ref{fig:comparison-plot} for the results from analyzing the NHANES (2013-2018) dataset.
-
-```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95\\% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
-The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
-Methods are arranged by the number of variables used in the models.\\label{fig:comparison-plot}", message=FALSE, warning=FALSE}
-library(ggplot2)
-library(dplyr)
-
-# Combine RD and OR data into a single data frame
-data_combined <- data.frame(
-  Method = rep(c("Bross", "Hybrid", "LASSO", "ElasticNet", "GA", "XGBoost", "RF", "FS", "BE"), 2),
-  # These are approximate values
-  Value = c(0.078, 0.078, 0.080, 0.080, 0.079, 0.080, 0.080, 0.080, 0.080, 
-            1.50, 1.53, 1.55, 1.55, 1.55, 1.53, 1.55, 1.55, 1.55),
-  LowerCI = c(0.06, 0.05, 0.06, 0.06, 0.06, 0.05, 0.06, 0.06, 0.06,
-              1.40, 1.40, 1.45, 1.45, 1.45, 1.40, 1.45, 1.45, 1.45),
-  UpperCI = c(0.09, 0.10, 0.10, 0.10, 0.10, 0.10, 0.10, 0.10, 0.10,
-              1.60, 1.65, 1.65, 1.65, 1.65, 1.65, 1.65, 1.65, 1.65),
-  Measure = rep(c("RD", "OR"), each = 9),
-  Variables = rep(c(100, 49, 60, 69, 64, 48, 100, 59, 59), 2)
-)
-
-# Create a new Method label that includes the number of variables
-data_combined <- data_combined %>%
-  mutate(MethodLabel = paste(Method, " [", Variables, "]", sep = ""))
-
-# Reorder the factor levels of MethodLabel based on the number of variables
-data_combined$MethodLabel <- factor(data_combined$MethodLabel,
-                                    levels = unique(data_combined$MethodLabel[order(data_combined$Variables)]))
-
-# Create the plot with the reordered MethodLabel
-ggplot(data_combined, aes(x = Value, y = MethodLabel)) +
-  geom_point(size = 4) +
-  geom_errorbarh(aes(xmin = LowerCI, xmax = UpperCI), height = 0.2) +
-  facet_grid(. ~ Measure, scales = "free_x") +
-  labs(x = "Value",
-       y = "Method [Chosen number of proxies]") +
-  theme_minimal() +
-  theme(strip.text = element_text(size = 12, face = "bold"))
-```
-
-\textcolor{brown}{I found the results in the table here is a little bit different from the value I got from the real data analysis.
-Also I found the cap of the figure not printing properly on my computer.
-I have to add double backslash before the pct symbol \%.
-If on other computers the double backslash causes some error maybe deleting it would help?
-See the updated plot "comparison-plot-updated" and its code below:}
-
-\textcolor{blue}{See Figure \ref{fig:comparison-plot-updated} for the updated results from analyzing the NHANES (2013-2018) dataset.
+See Figure \ref{fig:comparison-plot-updated} for the results from analyzing the NHANES (2013-2018) dataset.
 The methods are arranged according to the number of selected proxy variables.
-Among all variable selection algorithms, Random Forest (RF) and XGBoost demonstrate the highest odds ratios (ORs), with values of 1.588 and 1.564, respectively.
-The ORs for the remaining methods cluster around 1.523.
-Additionally, with the exception of RF and the Bross formula hdPS, a general pattern emerges where methods selecting a larger number of proxy variables yield higher ORs.
-For risk difference (RD), RF and XGBoost also exhibit the highest values, 0.085 and 0.082, respectively, while the remaining methods converge around 0.077.
-The trend observed in the OR results appears to persist in the RD analysis.}
+Among all variable selection algorithms, Random Forest (RF) and XGBoost demonstrate the highest odds ratios (ORs), with values of 1.59 and 1.56, respectively.
+The ORs for the remaining methods cluster around 1.52.
+Additionally, with the exception of RF and the Bross formula hdPS, a general pattern emerges where methods selecting a larger number of proxy variables yield lower ORs.
+For risk difference (RD), RF and XGBoost also exhibit the highest value 0.08, while the remaining methods converge around 0.077.
+The trend observed in the OR results appears to persist in the RD analysis.
 
@@
   # These are approximate values
-  Value = c(0.075, 0.077, 0.079, 0.078, 0.075, 0.085, 0.082, 0.078, 0.078, 0.076, 
-            1.502, 1.522, 1.543, 1.531, 1.504, 1.588, 1.564, 1.533, 1.533, 1.515),
-  LowerCI = c(0.056, 0.058, 0.06, 0.059, 0.056, 0.066, 0.063, 0.059, 0.059, 0.057,
-              1.395, 1.413, 1.432, 1.421, 1.396, 1.474, 1.452, 1.423, 1.423, 1.406),
-  UpperCI = c(0.095, 0.096, 0.099, 0.098, 0.094, 0.104, 0.101, 0.097, 0.097, 0.096,
-              1.618, 1.64, 1.663, 1.65, 1.62, 1.712, 1.685, 1.653, 1.653, 1.632),
+  Value = round(c(0.075, 0.077, 0.079, 0.078, 0.075, 0.085, 0.082, 0.078, 0.078, 0.076, 
+            1.502, 1.522, 1.543, 1.531, 1.504, 1.588, 1.564, 1.533, 1.533, 1.515),2),
+  LowerCI = round(c(0.056, 0.058, 0.06, 0.059, 0.056, 0.066, 0.063, 0.059, 0.059, 0.057,
+              1.395, 1.413, 1.432, 1.421, 1.396, 1.474, 1.452, 1.423, 1.423, 1.406),2),
+  UpperCI = round(c(0.095, 0.096, 0.099, 0.098, 0.094, 0.104, 0.101, 0.097, 0.097, 0.096,
+              1.618, 1.64, 1.663, 1.65, 1.62, 1.712, 1.685, 1.653, 1.653, 1.632),2),
   Measure = rep(c("RD", "OR"), each = 10),
@@
 
-Table \ref{tab:method-comparison} presents a pairwise comparison of the number of proxy features shared between different variable selection methods used in the analysis.
+Table \ref{tab:method-comparison-updated} presents a pairwise comparison of the number of proxy features shared between different variable selection methods used in the analysis.
 Each cell in the table indicates the count of common proxy variables selected by the method in the corresponding row and column.
 The diagonal cells, where the row and column methods are the same, represent the total number of proxy variables selected exclusively by each method.
-
-\textcolor{red}{*need to think about how to best present this proxy in common table.*}
+The first column displays the number of proxy variables shared between each method and the kitchen sink (KS) model.
+Given that the KS model includes all proxy variables, the values in the first column are identical to those in the diagonal cells for each row, which also presents the total number of proxy variables selected by the method in the corresponding row.
 
@@
 \caption{Comparison of variable overlap of selected proxies across different methods used to evaluate the association between obesity and diabetes}
-\label{tab:method-comparison}
-\begin{tabular}{lccccccccc}
-\toprule
- & \textbf{Bross} & \textbf{Hybrid} & \textbf{LASSO} & \textbf{ElasticNet} & \textbf{GA} & \textbf{XGBoost} & \textbf{RF} & \textbf{FS} & \textbf{BE} \\
-\midrule
-\textbf{Bross formula} & 100 & & & & & & & & \\
-\textbf{Hybrid (Bross and LASSO)} & 49 & 49 & & & & & & & \\
-\textbf{LASSO} & 47 & 47 & 60 & & & & & & \\
-\textbf{Elastic Net} & 54 & 48 & 60 & 69 & & & & & \\
-\textbf{Genetic algorithm (GA)} & 44 & 28 & 36 & 40 & 64 & & & & \\
-\textbf{XGBoost} & 38 & 24 & 28 & 30 & 25 & 48 & & & \\
-\textbf{Random Forest (RF)} & 72 & 37 & 42 & 50 & 36 & 48 & 100 & & \\
-\textbf{Forward selection (FS)} & 45 & 41 & 51 & 54 & 35 & 25 & 43 & 59 & \\
-\textbf{Backward elimination (BE)} & 45 & 41 & 51 & 54 & 35 & 25 & 43 & 59 & 59 \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\textcolor{brown}{Updated the pairwise comparison table with adding the value for kitchen sink (ks).
-Though as the ks model contains all variables, adding the values for it would not add anything useful, I think it is weird to omit a method in the table without saying anything.
-Also here I changed the order/arrange of the methods, to match to the order/arrange of methods in the Methods section.}
-
-\textcolor{blue}{Table \ref{tab:method-comparison-updated} presents a pairwise comparison of the number of proxy features shared between different variable selection methods used in the analysis.
-Each cell in the table indicates the count of common proxy variables selected by the method in the corresponding row and column.
-The diagonal cells, where the row and column methods are the same, represent the total number of proxy variables selected exclusively by each method.
-The first column displays the number of proxy variables shared between each method and the kitchen sink (KS) model.
-Given that the KS model includes all proxy variables, the values in the first column are identical to those in the diagonal cells for each row, which also presents the total number of proxy variables selected by the method in the corresponding row.}
-
-\begin{table}[htbp]
-\centering
-\caption{Updated Comparison of variable overlap of selected proxies across different methods used to evaluate the association between obesity and diabetes}
 \label{tab:method-comparison-updated}
@@
 
-\textcolor{blue}{Table \ref{tab:proxy-common-pct-bross} presents the comparison of common proxy counts and rates between different methods with the bross formula hdPS.
-Column 1 indicates the number of proxy variables selected by each variable selection method.
-Column 2 shows the number of common features selected by each method and the Bross formula method.
-Column 3 demonstrates the percentage of the common features in the total number of features of each method.}
+Table \ref{tab:proxy-common-pct-bross} presents a comparison of the count and percentage of common proxy variables selected by different methods in comparison with the Bross formula hdPS.
+The first column shows the total number of proxy variables selected by each method, while the second column lists the number of common features selected by both the respective method and the Bross formula.
+The third column reports the percentage of common features out of the total number of features selected by each method.
 
-\textcolor{blue}{From Table \ref{tab:proxy-common-pct-bross}, it can be observed that, with the exception of the bross hdPS and random forest (RF) models, where the number of proxies was manually set to 100, and the kitchen sink (KS) model, which inherently includes all proxies, the number of proxy variables selected by all other models ranges from 49 to 69.
-The hybird method of bross and lasso hdPS, by definition, performs lasso proxy selection on the 100 proxy variables selected by bross, resulting in an inherent common rate of 1.00.
-For the remaining methods, the common rates are clustered around 0.74, with XGBoost exhibiting the highest common rate of 0.792 and GA presenting the lowest common rate of 0.688.}
+We observe that, aside from the Bross formula hdPS and Random Forest (RF) models, where the number of proxies was manually set to 100, and the kitchen sink (KS) model, which includes all proxies by design, the number of proxy variables selected by other models ranges between 49 and 69.
+As expected, the hybrid method combining Bross and LASSO hdPS selects exactly 49 proxy variables, all of which are selected by both methods, resulting in a common feature rate of 1.00.
+For other models, the common feature percentage is generally clustered around $74\%$, with XGBoost showing the highest common percentage at $79\%$, while the Genetic Algorithm (GA) displays the lowest common percentage at $69\%$.
 
@@
 \textbf{Bross formula} & 100 & - & - \\
-\textbf{Hybrid (Bross and LASSO)} & 49 & 49 & 1.000 \\
-\textbf{LASSO} & 60 & 47 & 0.783 \\
-\textbf{Elastic Net} & 69 & 54 & 0.783 \\
-\textbf{Random Forest (RF)} & 100 & 71 & 0.710 \\  
-\textbf{XGBoost} & 48 & 38 & 0.792 \\
-\textbf{Forward selection (FS)} & 59 & 45 & 0.763 \\
-\textbf{Backward elimination (BE)} & 59 & 45 & 0.763 \\
-\textbf{Genetic algorithm (GA)} & 64 & 44 & 0.688 \\
+\textbf{Hybrid (Bross and LASSO)} & 49 & 49 & 1.00 \\
+\textbf{LASSO} & 60 & 47 & 0.78 \\
+\textbf{Elastic Net} & 69 & 54 & 0.78 \\
+\textbf{Random Forest (RF)} & 100 & 71 & 0.71 \\  
+\textbf{XGBoost} & 48 & 38 & 0.79 \\
+\textbf{Forward selection (FS)} & 59 & 45 & 0.76 \\
+\textbf{Backward elimination (BE)} & 59 & 45 & 0.76 \\
+\textbf{Genetic algorithm (GA)} & 64 & 44 & 0.69 \\
 \bottomrule
@@
 
-\textcolor{red}{*Report computing time for the Real-world analysis for each method. (add ordered table or figure)*}
+Figure \ref{fig:computing-time} presents the computing time for each method. All methods, aside from RF and GA, exhibit relatively fast computing times. RF and GA are generally much slower.
 
-\textcolor{blue}{Table \ref{tab:computing-time} presents the computing time for each method.
-All methods, aside from RF and GA, exhibit relatively fast computing times.
-Although RF and GA are slower, their computational demands still remain within reasonable time limits.}
+```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Computing time for the real-world analysis for each algorithm under consideration.
+The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.\\label{fig:computing-time}", message=FALSE, warning=FALSE}
+# Load necessary libraries
+library(ggplot2)
 
-\begin{table}[htbp]
-\centering
-\caption{Computing time for the real-world analysis for each algorithm}
-\label{tab:computing-time}
-\begin{tabular}{lc}
-\toprule
-\textbf{Method} & \textbf{Computing Time}\\
-\midrule
-\textbf{Kitchen Sink} & 2.942 \\
-\textbf{Bross formula} & 2.280 \\
-\textbf{Hybrid (Bross and LASSO)} & 2.517 \\
-\textbf{LASSO} & 2.540  \\
-\textbf{Elastic Net} & 2.814 \\
-\textbf{Random Forest (RF)} & 379.485 \\
-\textbf{XGBoost} & 1.444 \\
-\textbf{Forward selection (FS)} & 7.417 \\
-\textbf{Backward elimination (BE)} & 12.794 \\
-\textbf{Genetic algorithm (GA)} & 105.697 \\
-\bottomrule
-\end{tabular}
-\end{table}
+# Create a data frame based on the table
+computing_time_data <- data.frame(
+  Method = c("Kitchen Sink", "Bross formula", "Hybrid (Bross and LASSO)", 
+             "LASSO", "Elastic Net", "Random Forest (RF)", "XGBoost", 
+             "Forward selection (FS)", "Backward elimination (BE)", "Genetic algorithm (GA)"),
+  Computing_Time = c(2.942, 2.280, 2.517, 2.540, 2.814, 379.485, 1.444, 7.417, 12.794, 105.697)/60
+)
+
+# Plot the bar plot using ggplot2
+ggplot(computing_time_data, aes(x = reorder(Method, Computing_Time), y = Computing_Time)) +
+  geom_bar(stat = "identity", fill = "grey") + 
+  coord_flip() +  # Flips the chart for better readability
+  labs(title = "Computing Time for Each Algorithm", 
+       x = "Method", 
+       y = "Computing Time (minutes)") + 
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
 
@@
 
-Across the three scenarios—Frequent Exposure and Outcome, Rare Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome—XGBoost consistently exhibited the lowest Mean Squared Error (MSE) and high coverage, making it one of the most reliable methods overall.
-However, XGBoost did not always have the lowest bias; in fact, methods such as the kitchen sink model, Bross-based hdPS, and Hybrid hdPS often showed lower bias.
-The GA, in contrast, consistently exhibited the highest bias and MSE, along with lower coverage and greater variability, indicating it was less reliable for accurate effect estimation.
-The kitchen sink model, while demonstrating low bias and reasonable MSE, generally had higher variability and lower precision compared to other methods like XGBoost.
-Methods such as Bross-based hdPS, Hybrid hdPS, and Elastic Net performed moderately well across all scenarios, balancing bias, coverage, and MSE, but they did not outperform XGBoost in overall accuracy and precision.
+Across the three scenarios, XGBoost consistently exhibited the lowest MSE and high coverage, making it one of the most reliable methods in terms of precision.
+However, XGBoost always displayed some level of bias, particularly when compared to methods such as the kitchen sink model, Bross-based hdPS, and Hybrid hdPS, which often showed lower bias in scenarios with frequent outcomes.
+In contrast, GA consistently exhibited the highest bias and MSE, along with lower coverage and greater variability, indicating that it was the least reliable method for accurate effect estimation.
+Methods such as Bross-based hdPS, Hybrid hdPS, and Elastic Net performed moderately well across all scenarios, striking a reasonable balance between bias, coverage, and MSE.
+However, they did not outperform XGBoost in terms of overall precision, particularly with respect to MSE, though those methods often had lower bias.
+The kitchen sink model, performed competitively with Bross-based hdPS in terms of bias and coverage, but did not perform well in terms of SEs and MSE.
 
@@
 
-Scenarios with rare exposure tended to produce higher bias, particularly for methods like GA and XGBoost, while frequent outcomes generally led to lower bias.
-Overcoverage was common in the frequent exposure and outcome scenario, while the other scenarios tended to have more balanced or slightly under-coverage.
-Frequent exposure scenarios had higher relative error, indicating more difficulty in precisely estimating effects compared to rare exposure scenarios, which had lower relative error.
-Rare outcome scenarios tended to have the lowest MSE, indicating more precise effect estimates under these conditions, whereas rare exposure scenarios had higher MSE, reflecting the challenges of estimating effects when exposure is uncommon.
+Scenarios with rare exposure tended to produce higher bias, particularly for methods like GA and XGBoost, while frequent outcomes generally led to lower bias for most methods.
+Overcoverage was common in the frequent exposure and outcome scenario, with several methods producing confidence intervals that were too wide (i.e., overestimating the uncertainty), while the other scenarios showed more balanced or slightly under-coverage.
+Frequent exposure scenarios also had higher relative error in standard error estimation, indicating greater difficulty in precisely estimating effects.
+In contrast, rare exposure scenarios had higher MSE, reflecting the challenge of estimating effects when exposure is uncommon.
+The rare outcome scenarios tended to exhibit the lowest MSE across most methods (with the exception of GA), further indicating that these scenarios provided a better balance between bias and precision for most methods.
 
@@
 
-\textcolor{red}{*need to write what hdps offers in the literature; what additional selection criteria was used so far*}
+LASSO was previously shown to perform well in the contect of hdPS framework, particularly in terms of bias reduction and MSE [@karim2018can; @franklin2015regularized], with similar performance in Elastic Net [@karim2018can].
+Our findings generally support these conclusions, with both methods demonstrating moderate bias and MSE across the scenarios.
+However, the performance of these methods was not consistent across all scenarios, with these methods showing higher bias in the rare exposure scenario in previous simulation studies [@karim2018can; @franklin2015regularized].
+MSE of these methods are particularly high in rare exposure scenario.
+The hybrid method, which combines Bross-based hdPS and LASSO, also showed promising results, particularly in terms of MSE, indicating that it may be a suitable alternative to traditional hdPS methods.
+The Random Forest method also demonstrated similar performance in our study, with relatively low bias, as was also shown previously [@karim2018can].
+However, none of these works focused on coverage, and did not consider other approaches we have considered here, such as GA, XGboost, forward selection or backward elimination.
 
@@
 
-\textcolor{red}{*summarize real data analysis finding in 1 para*}
+The dataset used in the real-world analysis had frequent exposure (48.8% prevalence) and relatively moderate outcome rate (23.7%).
+RF and XGBoost demonstrated the highest ORs at 1.59 and 1.56, respectively, while the remaining methods clustered around an OR of 1.52.
+A general trend was observed where methods selecting fewer proxy variables yielded lower ORs, except for RF and the Bross formula hdPS.
+For RD, the estimates did not vary much.
+In terms of variable overlap, most methods shared around 74% of their proxy variables with the Bross formula hdPS, with XGBoost showing the highest common rate (79%) and Genetic Algorithm (GA) showing the lowest (69%).
+The computing time analysis revealed that, aside from RF and GA, most methods had relatively short computing times, with RF being the slowest by a significant margin.
+
+## Strengths
+
+Looking at the literature, almost all of the studies involving singly robust methods have focused on the performance of hdPS methods in terms of MSE [@franklin2015regularized; @pang2016effect; @wyss2018using; @karim2018can; @simon2023evaluating].
+Our study extends this work by considering a wide variety of performance metrics that allows researchers to compare the results both in terms of bias and variance estimation.
+We also provide a comprehensive comparison of the statistical and machine learning methods across different scenarios, which has not been done before.
+For example, we found that XGBoost consistently demonstrated strong performance in terms of MSE and coverage, but it did not always have the lowest bias.
+We have also seen for the first time that standard statistical variable selection methods such as forward selection or backward elimination procedures do perform very similar to the LASSO or random forest approaches across scenarios, both in terms of bias and coverage.
 
@@
 
-\textcolor{red}{*TMLE*}
+Double robust methods have been shown to be effective in achieving optimal statistical performance in hdPS analysis [@pang2016targeted; @pang2016effect; @benasseur2022comparison].
+Additionally, single robust methods include ensemble learners, such as super learners, which have been effective in other contexts, particularly in improving bias, MSE, area under the curve, and covariate balance [@guertin2016head; @wyss2018using; @ju2019propensity].
+However, despite the desirable theoretical properties of these methods, their complexity and computational burden, especially in high-dimensional settings, have limited their adoption by practitioners.
+In contrast, some of the singly robust machine learning methods we have discussed have been applied in addressing clinical questions [@hossain2023role; @basham2021post].
+Future research could explore the potential of these double robust and super learner methods in hdPS analysis, particularly in the context of rare outcomes and exposures, where the performance of traditional methods may be suboptimal.
+
+Furthermore, the impact of different hyperparameters on the performance of machine learning methods like XGBoost warrants further investigation to optimize their application in hdPS analysis.
+Lastly, conducting simulation studies to evaluate the performance of hdPS methods in terms of coverage in other epidemiological scenarios, such as time-varying exposures, could provide valuable insights into the generalizability of these findings [@neugebauer2015high].
 
@@
 - MSE: Mean Squared Error
-- \textcolor{blue}{KS: Kitchen Sink}
+- KS: Kitchen Sink
 - LASSO: Least Absolute Shrinkage and Selection Operator
-- \textcolor{blue}{ElasticNet / EN}: A regularized regression method that combines LASSO and Ridge regression
+- EN: Elastic Net; a regularized regression method that combines LASSO and Ridge regression
 - RF: Random Forest

### 2024-09-13 Writeup/manuscript.tex
update3

@@
 related metrics such as bias-eliminated coverage and relative error in
-standard error (which compares model-based SE with empirical SE)---can
-reveal whether confidence intervals or SEs are too narrow
+standard error (SE; which compares model-based SE with empirical
+SE)---can reveal whether confidence intervals or SEs are too narrow
 (underestimating uncertainty) or too wide (overestimating uncertainty).
@@
 
-\textbf{Motivating Example}: To explore the relationship between obesity
-and the risk of diabetes, we revisited this association using data from
-three cycles of the National Health and Nutrition Examination Survey
-(NHANES) covering the years 2013-2014, 2015-2016, and 2017-2018
-\citep{karim2024high}. This analysis was informed by a thorough review
-of the existing literature
-\citep{saydah2014trends, liu2013association, kabadi2012joint, ostchega2012abdominal}.
-To identify relevant covariates, we constructed a causal diagram based
-on established causal inference principles \citep{greenland1999causal}.
+\textbf{Motivating Example}: We revisited the association between
+obesity and the risk of diabetes using data from three cycles of the
+National Health and Nutrition Examination Survey (NHANES) covering the
+years 2013-2014, 2015-2016, and 2017-2018 \citep{karim2024high}. To
+identify relevant investigator-specified covariates, we constructed a
+causal diagram based on literature
+\citep{saydah2014trends, liu2013association, kabadi2012joint, ostchega2012abdominal}
+and established causal inference principles \citep{greenland1999causal}.
 The covariates included in our analysis were carefully selected and
-categorized into Demographic, Behavioral, Health History,
-Access-related, and Laboratory variables \citep{karim2024high}. While
-most of these variables were binary or categorical, the Laboratory
-variables were continuous.
+categorized into demographic, behavioral, health history,
+access-related, and laboratory variables. While most of these variables
+were binary or categorical, the Laboratory variables were continuous.
 
@@
 aspects of an actual epidemiological study, this simulation framework
-offers a significant advantage over traditional Monte Carlo simulations,
-which often rely on idealized assumptions.
+offers a substantial advantage over traditional Monte Carlo simulations,
+which often rely on hypothetical assumptions.
 
@@
 \textbf{True Data Generating Mechanism Used in Plasmode Simulation}: The
-primary goal of this study is to evaluate various variable selection
-methods under realistic conditions. To achieve this, we formulated the
-outcome data based on a specific model specification that incorporates
-both exposure and covariates, including investigator-specified and proxy
-variables. The model specification consists of three key components (See
-Appendices \S A and B for further details):
+primary goal of this plasmode simulation study is to evaluate various
+variable selection methods under realistic conditions. To achieve this,
+we formulated the outcome data based on a specific model specification
+that incorporates both exposure and covariates, including
+investigator-specified and proxy variables. The model specification
+consists of three key components (See Appendices \S A and B for further
+details):
 
@@
   adding proxy variables. However, when a large number of proxies are
-  added, some may act as noise variables, contributing little to the
-  analysis. To simulate this, we selected only those binary proxy
+  added, some may act as noise variables, contributing little or nothing
+  to the analysis. To simulate this, we selected only those binary proxy
   covariates (referred to as recurrence covariates in hdPS terminology)
   that had a relative risk (RR) of less than 0.8 or greater than 1.2
-  concerning the outcome. Out of 143 \textcolor{brown}{\textbf{142}}
-  proxy covariates, 94 met this criterion and were included in
-  calculating a simple comorbidity burden measure. The remaining 49
-  \textcolor{brown}{\textbf{49? or 48?}} covariates were excluded from
-  this calculation and considered noise. This comorbidity burden measure
-  was then incorporated into our model specification for generating the
-  plasmode data.
+  concerning the outcome. Out of 142 proxy covariates, 94 met this
+  criterion and were included in calculating a simple comorbidity burden
+  measure. The remaining 48 covariates were excluded from this
+  calculation and considered noise. This comorbidity burden measure (one
+  variable) was then incorporated into our model specification for
+  generating the outcome data.
 \end{enumerate}
@@
 
-\textcolor{red}{*check if the description of the methods look okay to you. Make sure the description matches with the analysis codes.*}
-
-\textcolor{blue}{All looks good!}
-
 The comparison between the data generation process and the analysis
@@
 employed a simple sum of selected proxy variables (sum of 94 proxy
-covariates), while the analysis included all proxy variables (143
-\textcolor{brown}{\textbf{142}} binary proxies), with
-49\textcolor{brown}{\textbf{49? or 48?}} of these acting as noise
-variables. These differences help us assess how the proxy variable
-selection methods handle model misspecification and the presence of
-noise variables.
+covariates), while the analysis included all proxy variables (142 binary
+proxies), with 48 of these acting as noise variables. These differences
+help us assess how the proxy variable selection methods handle model
+misspecification and the presence of noise variables.
 
@@
 \item
-  \textbf{Bross formula}: The Bross formula is a statistical method used
-  to calculate the bias introduced by not adjusting for a covariate
-  \citep{bross1966spurious}. In hdPS analysis, this formula was
-  originally applied to each proxy variable to measure and rank the
+  \textbf{hdPS using Bross formula}: The Bross formula is a statistical
+  method used to calculate the bias introduced by not adjusting for a
+  covariate \citep{bross1966spurious}. In hdPS analysis, this formula
+  was originally applied to each proxy variable to measure and rank the
   potential bias if the covariate were not adjusted for. In our
@@
 
-\textcolor{red}{*Can you check the app in the doc folder of the repo, and compare of the results description look accurate to you?*}
-
-\textcolor{blue}{*Comments and edits in brown and blue color.*}
-
 The results for each method under the different scenarios are summarized
@@
 \def\labelenumi{\arabic{enumi}.}
-\tightlist
 \item
-  \emph{Bias}: The kitchen sink model, which includes all variables
-  without selection, exhibited the smallest bias (0.0002). GA shows the
+  \emph{Bias}: Bross-based hdPS exhibited the smallest bias (-0.0001),
+  and the kitchen sink model (0.0002) was the second. GA shows the
   highest bias (0.0287), indicating a substantial deviation from the
-  true effect. Among the other methods, Bross-based hdPS (-0.0001),
-  Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
-  XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly
-  higher bias.
-\end{enumerate}
-
-\textcolor{brown}{It seems that Bross-based hdPS (-0.0001) instead of the kitchen sink model (0.0002) exhibited the smallest bias.}
-
-\textcolor{blue}{The Bross-based hdPS model exhibited the smallest bias (-0.0001).
-GA shows the highest bias (0.0287), indicating a substantial deviation from the true effect.
-Among the other methods, the kitchen sink model (0.0002), Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
-XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly higher bias.}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
+  true effect. Among the other methods, Hybrid hdPS (0.0016), and
+  Elastic Net (0.0036) demonstrated low bias. XGBoost (0.0074) had
+  slightly higher bias than Random Forest (RF) (0.0034).
 \item
@@
   achieving values around 98\%, indicating well-calibrated confidence
-  intervals. However, GA had significantly lower coverage (83.8\%),
+  intervals. However, GA had noticeably lower coverage (83.8\%),
   indicating that its confidence intervals might be too narrow or
   biased, potentially missing the true effect. After applying bias
-  elimination, GA's coverage improved to 96\%, which is better but still
-  lower than other methods.
+  elimination (as there were substantial bias associated with this
+  method), GA's coverage improved to 96\%.
 \item
   \emph{Mean Squared Error (MSE)}: XGBoost achieved the lowest MSE
-  (0.0006), reaffirming it as the most accurate method overall. GA
-  maintained the highest MSE (0.0016), reflecting its higher bias and
-  variability. The kitchen sink model (0.0009), Bross-based hdPS
-  (0.0008), Hybrid hdPS (0.0008), and Elastic Net (0.0009) all had
-  relatively similar and moderate MSE values.
+  (0.0006). GA maintained the highest MSE (0.0016), reflecting its
+  higher bias and variability. The kitchen sink model (0.0009),
+  Bross-based hdPS (0.0008), Hybrid hdPS (0.0008), and Elastic Net
+  (0.0009) all had relatively similar and moderate MSE values.
 \item
@@
   model (0.0333) the highest, indicating less precision in its
-  estimates. See Appendix \S C for further details.
+  estimates. When comparing relative error in SE estimation, XGBoost
+  performed the worst. See Appendix \S C for further details.
 \end{enumerate}
@@
   indicating a significant deviation from the true effect. XGBoost had a
-  bias of 0.0259, which, while still higher than some other methods, was
+  bias of 0.0259, which, while still higher than other methods, but was
   lower than GA. Other methods, such as Bross-based hdPS (0.0035),
@@
   adequate interval calibration. Bias-eliminated coverage for GA
-  improved to 94.2\%, but it was still slightly lower than other
-  methods.
+  improved to 94.2\%, but it was still slightly lower than other methods
+  (e.g., forward selection).
 \item
-  \emph{Mean Squared Error (MSE)}: Hybrid hdPS and XGBoost both
-  demonstrated the lowest MSE (0.0032), indicating that these methods
-  were the most accurate in this scenario. The GA method had a higher
-  MSE (0.0043), reflecting its substantial bias and variability. The
-  kitchen sink model also had an MSE of 0.0043, similar to GA, while
-  other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elastic
-  Net (0.0036) exhibited moderate MSE values, indicating reasonable
-  accuracy.
-\end{enumerate}
-
-\textcolor{brown}{It seems that forward selection model instead of Hybrid hdPS and XGBoost demonstrated the lowest MSE (0.003)}
-
-\textcolor{blue}{The forward selection algorithm exhibited the lowest MSE (0.0030), indicating that this method was the most accurate in this scenario.
-In addition, the hybrid hdPS and XGBoost also demonstrated relatively low MSE (0.0032).
-The GA method had a higher MSE (0.0043), reflecting its substantial bias and variability.
-The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{3}
-\tightlist
+  \emph{Mean Squared Error (MSE)}: Forward selection demonstrated the
+  lowest MSE (0.0030), and then Hybrid hdPS and XGBoost. The GA method
+  had a higher MSE (0.0043), reflecting its substantial bias and
+  variability. The kitchen sink model also had an MSE of 0.0043, similar
+  to GA, while other methods like Bross-based hdPS (0.0035), RF
+  (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values,
+  indicating reasonable accuracy.
 \item
@@
   Model-based SE (0.0623), indicating less precision in its estimates.
+  When comparing relative error in SE estimation, XGBoost and kitchen
+  sink model performed the worst (in other direction).
 \end{enumerate}
@@
   \emph{Mean Squared Error (MSE)}: XGBoost exhibited the lowest MSE
-  (0.0003), indicating it as the most accurate method overall in this
-  scenario. GA had the highest MSE (0.0040), reflecting its substantial
+  (0.0003). GA had the highest MSE (0.0040), reflecting its substantial
   bias and variability. The kitchen sink model (0.0005), Bross-based
@@
   method exhibited the highest Empirical SE (0.0523), indicating greater
-  variability and less precision. Methods like Hybrid hdPS (0.0184),
+  variability and less precision. Methods such as Hybrid hdPS (0.0184),
   Forward Selection (0.0187), and Elastic Net (0.0203) showed moderate
@@
   Model-based SE (0.0219), indicating less precision in its estimates.
+  When comparing relative error in SE estimation, XGBoost performed the
+  worst.
 \end{enumerate}
@@
 
-\textcolor{red}{*Here we include full data analysis (with some summary results like exposure and outcome prevalence, and sample size) and report OR and RD.
-Also mention how many proxies were chosen (add in the picture of RD and OR; side by side for each method, ordered my magnitude of RD), and how many were in common with hdPS (add table).*}
+\textbf{Summary results}: The dataset comprises 7,585 individuals. Among
+these, the prevalence of the exposure is 48.8\%, while the prevalence of
+the outcome is 23.7\%.
 
-\textcolor{blue}{\textbf{Summary results}: The dataset comprises 7585 individuals.
-Among these, the prevalence of the exposure is 48.8\% or 0.488 , while the prevalence of the outcome is 23.7\% or 0.237.}
-
-See Figure \ref{fig:comparison-plot} for the results from analyzing the
-NHANES (2013-2018) dataset.
+See Figure \ref{fig:comparison-plot-updated} for the results from
+analyzing the NHANES (2013-2018) dataset. The methods are arranged
+according to the number of selected proxy variables. Among all variable
+selection algorithms, Random Forest (RF) and XGBoost demonstrate the
+highest odds ratios (ORs), with values of 1.59 and 1.56, respectively.
+The ORs for the remaining methods cluster around 1.52. Additionally,
+with the exception of RF and the Bross formula hdPS, a general pattern
+emerges where methods selecting a larger number of proxy variables yield
+lower ORs. For risk difference (RD), RF and XGBoost also exhibit the
+highest value 0.08, while the remaining methods converge around 0.077.
+The trend observed in the OR results appears to persist in the RD
+analysis.
 
@@
 The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
-Methods are arranged by the number of variables used in the models.\label{fig:comparison-plot}}\label{fig:unnamed-chunk-3}
+Methods are arranged by the number of variables used in the models.\label{fig:comparison-plot-updated}}\label{fig:unnamed-chunk-3}
 \end{figure}
 
-\textcolor{brown}{I found the results in the table here is a little bit different from the value I got from the real data analysis.
-Also I found the cap of the figure not printing properly on my computer.
-I have to add double backslash before the pct symbol \%.
-If on other computers the double backslash causes some error maybe deleting it would help?
-See the updated plot "comparison-plot-updated" and its code below:}
-
-\textcolor{blue}{See Figure \ref{fig:comparison-plot-updated} for the updated results from analyzing the NHANES (2013-2018) dataset.
-The methods are arranged according to the number of selected proxy variables.
-Among all variable selection algorithms, Random Forest (RF) and XGBoost demonstrate the highest odds ratios (ORs), with values of 1.588 and 1.564, respectively.
-The ORs for the remaining methods cluster around 1.523.
-Additionally, with the exception of RF and the Bross formula hdPS, a general pattern emerges where methods selecting a larger number of proxy variables yield higher ORs.
-For risk difference (RD), RF and XGBoost also exhibit the highest values, 0.085 and 0.082, respectively, while the remaining methods converge around 0.077.
-The trend observed in the OR results appears to persist in the RD analysis.}
-
-\begin{figure}[th]
-
-{\centering \includegraphics[width=1\linewidth,]{manuscript_files/figure-latex/unnamed-chunk-4-1}
-
-}
-
-\caption{Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95\% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk.
-The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.
-Methods are arranged by the number of variables used in the models.\label{fig:comparison-plot-updated}}\label{fig:unnamed-chunk-4}
-\end{figure}
-
-Table \ref{tab:method-comparison} presents a pairwise comparison of the
-number of proxy features shared between different variable selection
-methods used in the analysis. Each cell in the table indicates the count
-of common proxy variables selected by the method in the corresponding
-row and column. The diagonal cells, where the row and column methods are
-the same, represent the total number of proxy variables selected
-exclusively by each method.
-
-\textcolor{red}{*need to think about how to best present this proxy in common table.*}
+Table \ref{tab:method-comparison-updated} presents a pairwise comparison
+of the number of proxy features shared between different variable
+selection methods used in the analysis. Each cell in the table indicates
+the count of common proxy variables selected by the method in the
+corresponding row and column. The diagonal cells, where the row and
+column methods are the same, represent the total number of proxy
+variables selected exclusively by each method. The first column displays
+the number of proxy variables shared between each method and the kitchen
+sink (KS) model. Given that the KS model includes all proxy variables,
+the values in the first column are identical to those in the diagonal
+cells for each row, which also presents the total number of proxy
+variables selected by the method in the corresponding row.
 
@@
 
-\textcolor{blue}{Table \ref{tab:proxy-common-pct-bross} presents the comparison of common proxy counts and rates between different methods with the bross formula hdPS.
-Column 1 indicates the number of proxy variables selected by each variable selection method.
-Column 2 shows the number of common features selected by each method and the Bross formula method.
-Column 3 demonstrates the percentage of the common features in the total number of features of each method.}
+Table \ref{tab:proxy-common-pct-bross} presents a comparison of the
+count and percentage of common proxy variables selected by different
+methods in comparison with the Bross formula hdPS. The first column
+shows the total number of proxy variables selected by each method, while
+the second column lists the number of common features selected by both
+the respective method and the Bross formula. The third column reports
+the percentage of common features out of the total number of features
+selected by each method.
 
-\textcolor{blue}{From Table \ref{tab:proxy-common-pct-bross}, it can be observed that, with the exception of the bross hdPS and random forest (RF) models, where the number of proxies was manually set to 100, and the kitchen sink (KS) model, which inherently includes all proxies, the number of proxy variables selected by all other models ranges from 49 to 69.
-The hybird method of bross and lasso hdPS, by definition, performs lasso proxy selection on the 100 proxy variables selected by bross, resulting in an inherent common rate of 1.00.
-For the remaining methods, the common rates are clustered around 0.74, with XGBoost exhibiting the highest common rate of 0.792 and GA presenting the lowest common rate of 0.688.}
+We observe that, aside from the Bross formula hdPS and Random Forest
+(RF) models, where the number of proxies was manually set to 100, and
+the kitchen sink (KS) model, which includes all proxies by design, the
+number of proxy variables selected by other models ranges between 49 and
+69. As expected, the hybrid method combining Bross and LASSO hdPS
+selects exactly 49 proxy variables, all of which are selected by both
+methods, resulting in a common feature rate of 1.00. For other models,
+the common feature percentage is generally clustered around \(74\%\),
+with XGBoost showing the highest common percentage at \(79\%\), while
+the Genetic Algorithm (GA) displays the lowest common percentage at
+\(69\%\).
 
@@
 
-\textcolor{red}{*Report computing time for the Real-world analysis for each method. (add ordered table or figure)*}
+Figure \ref{fig:computing-time} presents the computing time for each
+method. All methods, aside from RF and GA, exhibit relatively fast
+computing times. RF and GA are generally much slower.
 
-\textcolor{blue}{Table \ref{tab:computing-time} presents the computing time for each method.
-All methods, aside from RF and GA, exhibit relatively fast computing times.
-Although RF and GA are slower, their computational demands still remain within reasonable time limits.}
+\begin{figure}[th]
 
-\begin{table}[htbp]
-\centering
-\caption{Computing time for the real-world analysis for each algorithm}
-\label{tab:computing-time}
-\begin{tabular}{lc}
-\toprule
-\textbf{Method} & \textbf{Computing Time}\\
-\midrule
-\textbf{Kitchen Sink} & 2.942 \\
-\textbf{Bross formula} & 2.280 \\
-\textbf{Hybrid (Bross and LASSO)} & 2.517 \\
-\textbf{LASSO} & 2.540  \\
-\textbf{Elastic Net} & 2.814 \\
-\textbf{Random Forest (RF)} & 379.485 \\
-\textbf{XGBoost} & 1.444 \\
-\textbf{Forward selection (FS)} & 7.417 \\
-\textbf{Backward elimination (BE)} & 12.794 \\
-\textbf{Genetic algorithm (GA)} & 105.697 \\
-\bottomrule
-\end{tabular}
-\end{table}
+{\centering \includegraphics[width=1\linewidth,]{manuscript_files/figure-latex/unnamed-chunk-4-1}
+
+}
+
+\caption{Computing time for the real-world analysis for each algorithm under consideration.
+The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.\label{fig:computing-time}}\label{fig:unnamed-chunk-4}
+\end{figure}
 

### 2024-09-14 Writeup/BMC admin docs/tex/manuscript.tex
bmc submission

--- 2024-09-13 Writeup/manuscript.tex
@@
 
-\abstract{\textbf{Purpose}: We aims to evaluate various proxy selection
+\abstract{\textbf{Purpose}: We aim to evaluate various proxy selection
 methods within the context of high-dimensional propensity score (hdPS)
-analysis. The study focuses on assessing the performance of these
-methods, including alternative variable selection approaches, in
-selecting proxy variables for confounding adjustment compared to the
-traditional hdPS method that is rooted in Bross formula. The goal is to
-understand better the performance of these alternative methods in
-estimating treatment effects, and identify scenarios in which they may
-perform better. \textbf{Methods:} Using data from three cycles of the
-National Health and Nutrition Examination Survey (NHANES) spanning
-2013-2018, we motivated the study by examining the association between
-obesity and diabetes. A plasmode simulation framework based on this data
-was employed to mimic real-world data structures. Simulations were
-conducted under three scenarios: Frequent Exposure and Outcome, Rare
-Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome.
-The performance of a variety of proxy selection methods---including
-tree-based methods, LASSO-based methods, and the Genetic Algorithm
-(GA)---was evaluated across these scenarios using standard simulation
-metrics. \textbf{Results:} XGBoost consistently demonstrated the lowest
-MSE and high coverage, making it a reliable method overall, although it
-did not always exhibit the lowest bias. In contrast, GA consistently
-showed the highest bias and MSE, with lower coverage and greater
-variability, indicating its unsuitability for accurate effect
-estimation. The kitchen sink model, Bross-based hdPS, and Hybrid hdPS
-methods performed moderately well, with low bias and moderate MSE, but
-varied in coverage across scenarios. Scenario-specific trends revealed
-that rare outcome scenarios yielded lower MSE and better precision,
-while rare exposure scenarios were associated with higher bias and MSE.
-\textbf{Conclusion:} Aside from GA, the performance of most other
-methods in your study appears to be comparable in each scenario, though
-with some variations depending on specific metrics. The findings
-underscore the importance of selecting appropriate methods for hdPS
-analysis based on the characteristics of the data, particularly the
-prevalence of exposure and outcome. While XGBoost excelled in overall
-accuracy and precision, the choice of method should be tailored to the
-specific epidemiological goal to optimize bias, coverage, and precision
-in estimating treatment effects.}
+analysis. This study aimed to systematically evaluate and compare the
+performance of traditional statistical methods and machine learning
+approaches within the hdPS framework, focusing on key metrics such as
+bias, standard error (SE), and coverage, under various exposure and
+outcome prevalence scenarios. \textbf{Methods:} We conducted a plasmode
+simulation study using data from the National Health and Nutrition
+Examination Survey (NHANES) cycles from 2013 to 2018. We compared
+methods including the kitchen sink model, Bross-based hdPS, Hybrid hdPS,
+LASSO, Elastic Net, Random Forest, XGBoost, and Genetic Algorithm (GA).
+The performance of each method was assessed based on bias, MSE, coverage
+probability, and SE estimation across three epidemiological scenarios:
+frequent exposure and outcome, rare exposure and frequent outcome, and
+frequent exposure and rare outcome. \textbf{Results:} XGBoost
+consistently demonstrated strong performance in terms of MSE and
+coverage, making it effective for scenarios prioritizing precision.
+However, it exhibited higher bias, particularly in rare exposure
+scenarios, suggesting it is less suited when minimizing bias is
+critical. In contrast, GA showed significant limitations, with
+consistently high bias and MSE, making it the least reliable method.
+Bross-based hdPS, and Hybrid hdPS methods provided a
+balanced approach, with low bias and moderate MSE, though coverage
+varied depending on the scenario. Rare outcome scenarios generally
+resulted in lower MSE and better precision, while rare exposure
+scenarios were associated with higher bias and MSE. Notably, traditional
+statistical approaches such as forward selection and backward
+elimination performed comparably to more sophisticated machine learning
+methods in terms of bias and coverage, suggesting that these simpler
+approaches may be viable alternatives due to their computational
+efficiency. \textbf{Conclusion:} The results highlight the importance of
+selecting hdPS methods based on the specific characteristics of the
+data, such as exposure and outcome prevalence. While advanced machine
+learning methods such as XGBoost can enhance precision, simpler methods
+such as forward selection or backward elimination may offer similar
+performance in terms of bias and coverage with fewer computational
+demands. Tailoring the choice of method to the epidemiological scenario
+is essential for optimizing the balance between bias reduction and
+precision.}
 
@@
 as socioeconomic status, lifestyle factors, or health behaviors
-\citep{vanderweele2019principles}. The high-dimensional propensity score
-(hdPS) is a pharmacoepidemiological method designed to reduce
-confounding bias in large healthcare databases
+\citep{vanderweele2019principles}. The hdPS is a pharmacoepidemiological
+method designed to reduce confounding bias in large healthcare databases
 \citep{schneeweiss2009high}. Unlike traditional propensity score models
@@
 covariates \citep{karim2024high, karim2018can}. To address these
-limitations, multivariate machine learning methods such as LASSO,
-Elastic Net, and Random Forests have been applied within the hdPS
-framework. These methods are better suited for high-dimensional data,
-where they can more effectively handle complex relationships and improve
-the selection of proxy variables, thus enhancing the precision of
-treatment effect estimates
+model-specification-related limitations, multivariate machine learning
+methods such as LASSO, Elastic Net, and Random Forests have been applied
+within the hdPS framework. These methods are better suited for
+high-dimensional data, where they can more effectively handle complex
+relationships and improve the selection of proxy variables, thus
+enhancing the precision of treatment effect estimates
 \citep{karim2018can, schneeweiss2017variable, franklin2015regularized}.
@@
 
-\textbf{Assessing the Simulation Performance}: Previous studies have
-often focused on Mean Squared Error (MSE) as a primary metric for
-evaluating the performance of hdPS and its machine learning extensions
-\citep{karim2018can, franklin2015regularized}. However, in
-high-dimensional settings with singly robust methods, such as hdPS and
-machine learning approaches like LASSO, MSE may not always be the most
-reliable measure. MSE combines both bias and variance into a single
-metric, which makes interpretation challenging when variance estimation
-is unstable---a common issue in these methods. In contrast, coverage,
-which measures the proportion of confidence intervals that capture the
-true treatment effect, provides a more direct and meaningful assessment
-of a model's reliability. In realistic observational studies, where
-model misspecification is often inevitable, coverage---along with
-related metrics such as bias-eliminated coverage and relative error in
-standard error (SE; which compares model-based SE with empirical
-SE)---can reveal whether confidence intervals or SEs are too narrow
-(underestimating uncertainty) or too wide (overestimating uncertainty).
-This insight is crucial in determining whether the model delivers valid
-estimates despite misspecification. Even a model with poor MSE but good
-coverage may still be valuable, as it produces realistic confidence
-intervals. By shifting the focus to coverage, rather than relying solely
-on MSE, we can achieve a more comprehensive understanding of method
-performance, especially in cases where unstable variance estimation
-might distort conclusions drawn from MSE alone.
+\textbf{Assessing the Simulation Performance}: Other than bias, previous
+studies have primarily focused on Mean Squared Error (MSE) as a key
+metric for evaluating the performance of hdPS and its machine learning
+extensions
+\citep{franklin2015regularized, pang2016effect, wyss2018using, karim2018can, simon2023evaluating}.
+However, in high-dimensional settings with singly robust methods, such
+as hdPS and machine learning approaches such as LASSO, MSE may not
+always be the most reliable measure. MSE combines both bias and variance
+into a single metric, which makes interpretation challenging when
+variance estimation is unstable---a common issue in these methods. In
+contrast, coverage, which measures the proportion of confidence
+intervals that capture the true treatment effect, provides a more direct
+and meaningful assessment of a model's reliability. In realistic
+observational studies, where model misspecification is often inevitable,
+coverage---along with related metrics such as bias-eliminated coverage
+and relative error in standard error (SE; which compares model-based SE
+with empirical SE)---can reveal whether confidence intervals or SEs are
+too narrow (underestimating uncertainty) or too wide (overestimating
+uncertainty). This insight is crucial in determining whether the model
+delivers valid estimates despite misspecification. Even a model with
+poor MSE but good coverage may still be valuable, as it produces
+realistic confidence intervals. By shifting the focus to coverage,
+rather than relying solely on MSE, we can achieve a more comprehensive
+understanding of method performance, especially in cases where unstable
+variance estimation might distort conclusions drawn from MSE alone.
 
@@
 data structures and complexities \citep{franklin2014plasmode}. This
-approach was modeled after the analytic dataset derived from NHANES and
+approach was inspired by the analytic dataset derived from NHANES and
 involved resampling from the observed covariates and exposure
@@
 performance metrics to evaluate the effectiveness of the methods under
-consideration: (1) bias, (2) average model standard error (SE; the
-average of estimated SEs obtained from a model over repeated samples),
-(3) empirical SE (the standard deviation of estimated treatment effects
-across repeated samples), (4) mean squared error (MSE), (5) coverage
-probability of 95\% confidence intervals, (6) bias-corrected coverage,
-and (7) Zip plot \citep{morris2019using, white2023check}.
+consideration: (1) bias, (2) average model-based SE (the average of
+estimated SEs obtained from a model over repeated samples), (3)
+empirical SE (the standard deviation of estimated treatment effects
+across repeated samples), (4) MSE, (5) coverage probability of 95\%
+confidence intervals, (6) bias-corrected coverage, and (7) Zip plot
+\citep{morris2019using, white2023check}.
 
@@
   for variable selection, a hybrid approach combines the Bross formula
-  and LASSO. First, hdPS variables are selected using the hdPS algorithm
-  (e.g., the top 100), and then LASSO is applied to further refine the
-  selection \citep{karim2018can, franklin2015regularized}.
+  and LASSO. First, proxy variables are selected using the hdPS
+  algorithm (e.g., the top 100), and then LASSO is applied to further
+  refine the selection \citep{karim2018can, franklin2015regularized}.
 \item
@@
 \item
-  \textbf{Random Forest}: The Random Forest (RF) algorithm is an
-  ensemble learning method that constructs multiple decision trees to
-  perform classification \citep{breiman2001random}. It calculates the
-  importance of each proxy variable based on the decrease in impurity or
-  Gini importance, providing a ranking of the proxies. The top 100
-  variables from this ranking are manually selected for further modeling
+  \textbf{Random Forest}: The Random Forest algorithm is an ensemble
+  learning method that constructs multiple decision trees to perform
+  classification \citep{breiman2001random}. It calculates the importance
+  of each proxy variable based on the decrease in impurity or Gini
+  importance, providing a ranking of the proxies. The top 100 variables
+  from this ranking are manually selected for further modeling
   \citep{schneeweiss2017variable}.
@@
 \item
-  \textbf{Genetic algorithm (GA)}: GA is an evolutionary algorithm
-  inspired by the theory of natural selection
+  \textbf{Genetic algorithm}: Genetic algorithm is an evolutionary
+  algorithm inspired by the theory of natural selection
   \citep{holland1975adaptation}. It operates by evolving offspring from
@@
 \ref{fig:Coverage-comparison} for an overview of the performance in
-terms of bias and coverage, respectively.
-
-\begin{enumerate}
-\def\labelenumi{(\roman{enumi})}
-\tightlist
-\item
-  \textbf{Frequent Exposure and Outcome (base) scenario}:
-\end{enumerate}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  \emph{Bias}: Bross-based hdPS exhibited the smallest bias (-0.0001),
-  and the kitchen sink model (0.0002) was the second. GA shows the
-  highest bias (0.0287), indicating a substantial deviation from the
-  true effect. Among the other methods, Hybrid hdPS (0.0016), and
-  Elastic Net (0.0036) demonstrated low bias. XGBoost (0.0074) had
-  slightly higher bias than Random Forest (RF) (0.0034).
-\item
-  \emph{Coverage}: The coverage for most methods was high, with Hybrid
-  hdPS, Forward Selection, Backward Elimination, LASSO, and Elastic Net
-  achieving values around 98\%, indicating well-calibrated confidence
-  intervals. However, GA had noticeably lower coverage (83.8\%),
-  indicating that its confidence intervals might be too narrow or
-  biased, potentially missing the true effect. After applying bias
-  elimination (as there were substantial bias associated with this
-  method), GA's coverage improved to 96\%.
-\item
-  \emph{Mean Squared Error (MSE)}: XGBoost achieved the lowest MSE
-  (0.0006). GA maintained the highest MSE (0.0016), reflecting its
-  higher bias and variability. The kitchen sink model (0.0009),
-  Bross-based hdPS (0.0008), Hybrid hdPS (0.0008), and Elastic Net
-  (0.0009) all had relatively similar and moderate MSE values.
-\item
-  \emph{Standard Error (SE)}: XGBoost exhibited the lowest Empirical SE
-  (0.0229), indicating high precision in its estimates. The kitchen sink
-  model had the highest Empirical SE (0.0305), suggesting greater
-  variability. Other methods, including GA (0.0274), Hybrid hdPS
-  (0.0278), and Bross-based hdPS (0.0287), showed moderate variability.
-  LASSO (0.0299) and Elastic Net (0.0294) had slightly higher
-  variability. The Model-based SE followed a similar pattern, with
-  XGBoost (0.0268) showing the lowest variability and the kitchen sink
-  model (0.0333) the highest, indicating less precision in its
-  estimates. When comparing relative error in SE estimation, XGBoost
-  performed the worst. See Appendix \S C for further details.
-\end{enumerate}
-
-\textbf{(ii) Rare Exposure and Frequent Outcome}:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  \emph{Bias}: The kitchen sink model showed a relatively low bias
-  (0.0025), while GA continued to exhibit the highest bias (0.0408),
-  indicating a significant deviation from the true effect. XGBoost had a
-  bias of 0.0259, which, while still higher than other methods, but was
-  lower than GA. Other methods, such as Bross-based hdPS (0.0035),
-  Hybrid hdPS (0.0049), and Elastic Net (0.0053), demonstrated moderate
-  bias. Random Forest (RF) (0.0127) and Forward Selection (0.0108) had
-  slightly higher bias but remained within an acceptable range.
-\item
-  \emph{Coverage}: Coverage levels remained high for most methods, with
-  XGBoost achieving the highest coverage at 96.2\%, indicating
-  well-calibrated confidence intervals despite its higher bias. The GA
-  method had lower coverage (92.2\%), suggesting that its confidence
-  intervals might be narrower, potentially missing the true effect.
-  Other methods such as RF, Forward Selection, Backward Elimination, and
-  Hybrid hdPS maintained coverage values around 94-95\%, suggesting
-  adequate interval calibration. Bias-eliminated coverage for GA
-  improved to 94.2\%, but it was still slightly lower than other methods
-  (e.g., forward selection).
-\item
-  \emph{Mean Squared Error (MSE)}: Forward selection demonstrated the
-  lowest MSE (0.0030), and then Hybrid hdPS and XGBoost. The GA method
-  had a higher MSE (0.0043), reflecting its substantial bias and
-  variability. The kitchen sink model also had an MSE of 0.0043, similar
-  to GA, while other methods like Bross-based hdPS (0.0035), RF
-  (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values,
-  indicating reasonable accuracy.
-\item
-  \emph{Standard Error (SE)}: The lowest Empirical SE was observed with
-  XGBoost (0.0507) and GA (0.0510), reflecting high precision despite
-  their higher bias. The kitchen sink model had the highest Empirical SE
-  (0.0656), indicating greater variability. Hybrid hdPS (0.0564),
-  Bross-based hdPS (0.0595), and RF (0.0609) showed moderate
-  variability. Forward Selection (0.0537) and Backward Elimination
-  (0.0576) had lower variability compared to the kitchen sink model. In
-  terms of Model-based SE, XGBoost (0.0531) and GA (0.0533) continued to
-  show low variability, while the kitchen sink model had the highest
-  Model-based SE (0.0623), indicating less precision in its estimates.
-  When comparing relative error in SE estimation, XGBoost and kitchen
-  sink model performed the worst (in other direction).
-\end{enumerate}
-
-\textbf{(iii) Frequent Exposure and Rare Outcome}:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  \emph{Bias}: In this scenario, the kitchen sink model exhibited a
-  moderate negative bias (-0.0093), similar to the Bross-based hdPS
-  method (-0.0088). GA showed a significantly higher bias (0.0362),
-  indicating a substantial deviation from the true effect. Among other
-  methods, XGBoost demonstrated the lowest bias (-0.0061), while methods
-  like Hybrid hdPS (-0.0082), Forward Selection (-0.0070), and Backward
-  Elimination (-0.0070) had slightly higher but still moderate biases.
-  Elastic Net and LASSO both had biases of -0.0079, reflecting slightly
-  larger deviations compared to XGBoost but still within acceptable
-  limits.
-\item
-  \emph{Coverage}: Most methods achieved good coverage, with XGBoost,
-  RF, and Forward Selection each achieving a coverage rate of 95.4\%,
-  indicating well-calibrated confidence intervals. The GA method,
-  however, had slightly lower coverage (91.8\%), indicating that its
-  confidence intervals might be narrower, potentially excluding the true
-  effect. Bross-based hdPS and the kitchen sink model had slightly lower
-  coverage values of 93.8\% and 93.4\%, respectively. After accounting
-  for bias, the bias-eliminated coverage for most methods, except GA,
-  remained high, with values ranging from 98.4\% to 99.0\%, indicating
-  that most methods effectively adjusted for bias in their coverage
-  estimates. GA's bias-eliminated coverage was lower at 93.4\%,
-  reflecting its higher inherent bias.
-\item
-  \emph{Mean Squared Error (MSE)}: XGBoost exhibited the lowest MSE
-  (0.0003). GA had the highest MSE (0.0040), reflecting its substantial
-  bias and variability. The kitchen sink model (0.0005), Bross-based
-  hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and Elastic
-  Net (0.0005) all had relatively similar MSE values, indicating
-  moderate accuracy.
-\item
-  \emph{Standard Error (SE)}: The lowest Empirical SE was observed with
-  XGBoost (0.0152), reflecting high precision in its estimates. The GA
-  method exhibited the highest Empirical SE (0.0523), indicating greater
-  variability and less precision. Methods such as Hybrid hdPS (0.0184),
-  Forward Selection (0.0187), and Elastic Net (0.0203) showed moderate
-  variability, while Bross-based hdPS (0.0206) and the kitchen sink
-  model (0.0212) had slightly higher variability. In terms of
-  Model-based SE, XGBoost (0.0179) again showed the lowest variability,
-  consistent with its low Empirical SE, indicating that it provided the
-  most stable estimates. The kitchen sink model had a slightly higher
-  Model-based SE (0.0219), indicating less precision in its estimates.
-  When comparing relative error in SE estimation, XGBoost performed the
-  worst.
-\end{enumerate}
+terms of bias and coverage, respectively. All simulation results can be
+reviewed interactively through a Shiny web application available at
+\url{https://ehsanx.shinyapps.io/hdPS-Alternatives/}, providing a
+convenient platform for exploring the performance of each method across
+various scenarios.
 
@@
 
+\begin{enumerate}
+\def\labelenumi{(\roman{enumi})}
+\tightlist
+\item
+  \textbf{Frequent Exposure and Outcome (base) scenario}:
+\end{enumerate}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Bias}: Bross-based hdPS exhibited the smallest bias (-0.0001),
+  and the kitchen sink model (0.0002) was the second. Genetic algorithm
+  shows the highest bias (0.0287), indicating a substantial deviation
+  from the true effect. Among the other methods, Hybrid hdPS (0.0016),
+  and Elastic Net (0.0036) demonstrated low bias. XGBoost (0.0074) had
+  slightly higher bias than Random Forest (0.0034).
+\item
+  \emph{Coverage}: The coverage for most methods was high, with Hybrid
+  hdPS, Forward Selection, Backward Elimination, LASSO, and Elastic Net
+  achieving values around 98\%, indicating well-calibrated confidence
+  intervals. However, Genetic algorithm had noticeably lower coverage
+  (83.8\%), indicating that its confidence intervals might be too narrow
+  or biased, potentially missing the true effect. After applying bias
+  elimination (as there were substantial bias associated with this
+  method), Genetic algorithm's coverage improved to 96\%.
+\item
+  \emph{MSE}: XGBoost achieved the lowest MSE (0.0006). Genetic
+  algorithm maintained the highest MSE (0.0016), reflecting its higher
+  bias and variability. The kitchen sink model (0.0009), Bross-based
+  hdPS (0.0008), Hybrid hdPS (0.0008), and Elastic Net (0.0009) all had
+  relatively similar and moderate MSE values.
+\item
+  \emph{SE}: XGBoost exhibited the lowest Empirical SE (0.0229),
+  indicating high precision in its estimates. The kitchen sink model had
+  the highest Empirical SE (0.0305), suggesting greater variability.
+  Other methods, including Genetic algorithm (0.0274), Hybrid hdPS
+  (0.0278), and Bross-based hdPS (0.0287), showed moderate variability.
+  LASSO (0.0299) and Elastic Net (0.0294) had slightly higher
+  variability. The Model-based SE followed a similar pattern, with
+  XGBoost (0.0268) showing the lowest variability and the kitchen sink
+  model (0.0333) the highest, indicating less precision in its
+  estimates. When comparing relative error in SE estimation, XGBoost
+  performed the worst. See Appendix \S C for further details.
+\end{enumerate}
+
+\textbf{(ii) Rare Exposure and Frequent Outcome}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Bias}: The kitchen sink model showed a relatively low bias
+  (0.0025), while Genetic algorithm continued to exhibit the highest
+  bias (0.0408), indicating a significant deviation from the true
+  effect. XGBoost had a bias of 0.0259, which, while still higher than
+  other methods, but was lower than Genetic algorithm. Other methods,
+  such as Bross-based hdPS (0.0035), Hybrid hdPS (0.0049), and Elastic
+  Net (0.0053), demonstrated moderate bias. Random Forest (0.0127) and
+  Forward Selection (0.0108) had slightly higher bias but remained
+  within an acceptable range.
+\item
+  \emph{Coverage}: Coverage levels remained high for most methods, with
+  XGBoost achieving the highest coverage at 96.2\%, indicating
+  well-calibrated confidence intervals despite its higher bias. The
+  Genetic algorithm method had lower coverage (92.2\%), suggesting that
+  its confidence intervals might be narrower, potentially missing the
+  true effect. Other methods such as RF, Forward Selection, Backward
+  Elimination, and Hybrid hdPS maintained coverage values around
+  94-95\%, suggesting adequate interval calibration. Bias-eliminated
+  coverage for Genetic algorithm improved to 94.2\%, but it was still
+  slightly lower than other methods (e.g., forward selection).
+\item
+  \emph{MSE}: Forward selection demonstrated the lowest MSE (0.0030),
+  and then Hybrid hdPS and XGBoost. The Genetic algorithm method had a
+  higher MSE (0.0043), reflecting its substantial bias and variability.
+  The kitchen sink model also had an MSE of 0.0043, similar to Genetic
+  algorithm, while other methods such as Bross-based hdPS (0.0035), RF
+  (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values,
+  indicating reasonable accuracy.
+\item
+  \emph{SE}: The lowest Empirical SE was observed with XGBoost (0.0507)
+  and Genetic algorithm (0.0510), reflecting high precision despite
+  their higher bias. The kitchen sink model had the highest Empirical SE
+  (0.0656), indicating greater variability. Hybrid hdPS (0.0564),
+  Bross-based hdPS (0.0595), and RF (0.0609) showed moderate
+  variability. Forward Selection (0.0537) and Backward Elimination
+  (0.0576) had lower variability compared to the kitchen sink model. In
+  terms of Model-based SE, XGBoost (0.0531) and Genetic algorithm
+  (0.0533) continued to show low variability, while the kitchen sink
+  model had the highest Model-based SE (0.0623), indicating less
+  precision in its estimates. When comparing relative error in SE
+  estimation, XGBoost and kitchen sink model performed the worst (in
+  other direction).
+\end{enumerate}
+
+\textbf{(iii) Frequent Exposure and Rare Outcome}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \emph{Bias}: In this scenario, the kitchen sink model exhibited a
+  moderate negative bias (-0.0093), similar to the Bross-based hdPS
+  method (-0.0088). Genetic algorithm showed a significantly higher bias
+  (0.0362), indicating a substantial deviation from the true effect.
+  Among other methods, XGBoost demonstrated the lowest bias (-0.0061),
+  while methods such as Hybrid hdPS (-0.0082), Forward Selection
+  (-0.0070), and Backward Elimination (-0.0070) had slightly higher but
+  still moderate biases. Elastic Net and LASSO both had biases of
+  -0.0079, reflecting slightly larger deviations compared to XGBoost but
+  still within acceptable limits.
+\item
+  \emph{Coverage}: Most methods achieved good coverage, with XGBoost,
+  RF, and Forward Selection each achieving a coverage rate of 95.4\%,
+  indicating well-calibrated confidence intervals. The Genetic algorithm
+  method, however, had slightly lower coverage (91.8\%), indicating that
+  its confidence intervals might be narrower, potentially excluding the
+  true effect. Bross-based hdPS and the kitchen sink model had slightly
+  lower coverage values of 93.8\% and 93.4\%, respectively. After
+  accounting for bias, the bias-eliminated coverage for most methods,
+  except Genetic algorithm, remained high, with values ranging from
+  98.4\% to 99.0\%, indicating that most methods effectively adjusted
+  for bias in their coverage estimates. Genetic algorithm's
+  bias-eliminated coverage was lower at 93.4\%, reflecting its higher
+  inherent bias.
+\item
+  \emph{MSE}: XGBoost exhibited the lowest MSE (0.0003). Genetic
+  algorithm had the highest MSE (0.0040), reflecting its substantial
+  bias and variability. The kitchen sink model (0.0005), Bross-based
+  hdPS (0.0005), and other methods such as Hybrid hdPS (0.0004) and
+  Elastic Net (0.0005) all had relatively similar MSE values, indicating
+  moderate accuracy.
+\item
+  \emph{SE}: The lowest Empirical SE was observed with XGBoost (0.0152),
+  reflecting high precision in its estimates. The Genetic algorithm
+  method exhibited the highest Empirical SE (0.0523), indicating greater
+  variability and less precision. Methods such as Hybrid hdPS (0.0184),
+  Forward Selection (0.0187), and Elastic Net (0.0203) showed moderate
+  variability, while Bross-based hdPS (0.0206) and the kitchen sink
+  model (0.0212) had slightly higher variability. In terms of
+  Model-based SE, XGBoost (0.0179) again showed the lowest variability,
+  consistent with its low Empirical SE, indicating that it provided the
+  most stable estimates. The kitchen sink model had a slightly higher
+  Model-based SE (0.0219), indicating less precision in its estimates.
+  When comparing relative error in SE estimation, XGBoost performed the
+  worst.
+\end{enumerate}
+
 \section{Real-world analysis}\label{real-world-analysis}
@@
 according to the number of selected proxy variables. Among all variable
-selection algorithms, Random Forest (RF) and XGBoost demonstrate the
-highest odds ratios (ORs), with values of 1.59 and 1.56, respectively.
-The ORs for the remaining methods cluster around 1.52. Additionally,
-with the exception of RF and the Bross formula hdPS, a general pattern
-emerges where methods selecting a larger number of proxy variables yield
-lower ORs. For risk difference (RD), RF and XGBoost also exhibit the
-highest value 0.08, while the remaining methods converge around 0.077.
-The trend observed in the OR results appears to persist in the RD
-analysis.
+selection algorithms, Random Forest and XGBoost demonstrate the highest
+ORs, with values of 1.59 and 1.56, respectively. The ORs for the
+remaining methods cluster around 1.52. Additionally, with the exception
+of RF and the Bross formula hdPS, a general pattern emerges where
+methods selecting a larger number of proxy variables yield lower ORs.
+For RD, RF and XGBoost also exhibit the highest value 0.08, while the
+remaining methods converge around 0.077. The trend observed in the OR
+results appears to persist in the RD analysis.
 
@@
 
-{\centering \includegraphics[width=1\linewidth,]{manuscript_files/figure-latex/unnamed-chunk-3-1}
+{\centering \includegraphics[width=1\linewidth,]{figures/ORRD}
 
@@
 \centering
-\caption{Comparison of variable overlap of selected proxies across different methods used to evaluate the association between obesity and diabetes}
+\caption{Comparison of variable overlap of selected proxies across different methods used to evaluate the association between obesity and diabetes from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.}
 \label{tab:method-comparison-updated}
@@
 We observe that, aside from the Bross formula hdPS and Random Forest
-(RF) models, where the number of proxies was manually set to 100, and
-the kitchen sink (KS) model, which includes all proxies by design, the
+models, where the number of proxies was manually set to 100, and the
+kitchen sink (KS) model, which includes all proxies by design, the
 number of proxy variables selected by other models ranges between 49 and
@@
 \centering
-\caption{Comparison of the count and percentage of proxy variables selected by each methods in common with that by the Bross formula hdPS}
+\caption{Comparison of the count and percentage of proxy variables selected by each methods in common with that by the Bross formula-based high-dimensional propensity score to evaluate the association between obesity and diabetes from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018.}
 \label{tab:proxy-common-pct-bross}
@@
 \textbf{Elastic Net} & 69 & 54 & 0.78 \\
-\textbf{Random Forest (RF)} & 100 & 71 & 0.71 \\  
+\textbf{Random Forest} & 100 & 71 & 0.71 \\  
 \textbf{XGBoost} & 48 & 38 & 0.79 \\
-\textbf{Forward selection (FS)} & 59 & 45 & 0.76 \\
-\textbf{Backward elimination (BE)} & 59 & 45 & 0.76 \\
-\textbf{Genetic algorithm (GA)} & 64 & 44 & 0.69 \\
+\textbf{Forward selection} & 59 & 45 & 0.76 \\
+\textbf{Backward elimination} & 59 & 45 & 0.76 \\
+\textbf{Genetic algorithm} & 64 & 44 & 0.69 \\
 \bottomrule
@@
 
-{\centering \includegraphics[width=1\linewidth,]{manuscript_files/figure-latex/unnamed-chunk-4-1}
+{\centering \includegraphics[width=1\linewidth,]{figures/time}
 
@@
 
-Across the three scenarios---Frequent Exposure and Outcome, Rare
-Exposure and Frequent Outcome, and Frequent Exposure and Rare
-Outcome---XGBoost consistently exhibited the lowest Mean Squared Error
-(MSE) and high coverage, making it one of the most reliable methods
-overall. However, XGBoost did not always have the lowest bias; in fact,
-methods such as the kitchen sink model, Bross-based hdPS, and Hybrid
-hdPS often showed lower bias. The GA, in contrast, consistently
-exhibited the highest bias and MSE, along with lower coverage and
-greater variability, indicating it was less reliable for accurate effect
-estimation. The kitchen sink model, while demonstrating low bias and
-reasonable MSE, generally had higher variability and lower precision
-compared to other methods like XGBoost. Methods such as Bross-based
-hdPS, Hybrid hdPS, and Elastic Net performed moderately well across all
-scenarios, balancing bias, coverage, and MSE, but they did not
-outperform XGBoost in overall accuracy and precision.
+Across the three scenarios, XGBoost consistently achieved the lowest MSE
+and high coverage, making it one of the most reliable methods in terms
+of precision. However, it consistently exhibited some degree of bias,
+particularly when compared to methods such as the kitchen sink model,
+Bross-based hdPS, and Hybrid hdPS, which often showed lower bias in
+scenarios with frequent outcomes. In contrast, GA displayed the highest
+bias and MSE, along with lower coverage and greater variability, making
+it the least reliable method for accurate effect estimation. Methods
+such as Bross-based hdPS, Hybrid hdPS, and Elastic Net performed
+moderately well across all scenarios, balancing bias, coverage, and MSE.
+However, these methods did not outperform XGBoost in terms of overall
+precision, especially with respect to MSE, though they often resulted in
+lower bias. The kitchen sink model performed comparably to Bross-based
+hdPS in terms of bias and coverage but lagged in SE estimation and MSE.
 
@@
 
-Scenarios with rare exposure tended to produce higher bias, particularly
-for methods like GA and XGBoost, while frequent outcomes generally led
-to lower bias. Overcoverage was common in the frequent exposure and
-outcome scenario, while the other scenarios tended to have more balanced
-or slightly under-coverage. Frequent exposure scenarios had higher
-relative error, indicating more difficulty in precisely estimating
-effects compared to rare exposure scenarios, which had lower relative
-error. Rare outcome scenarios tended to have the lowest MSE, indicating
-more precise effect estimates under these conditions, whereas rare
-exposure scenarios had higher MSE, reflecting the challenges of
-estimating effects when exposure is uncommon.
+In scenarios with rare exposure, higher bias was observed, particularly
+for methods such as GA and XGBoost, whereas frequent outcomes generally
+led to lower bias across most methods. Overcoverage was more common in
+the scenario with frequent exposure and outcome, with several methods
+producing confidence intervals that were too wide, suggesting an
+overestimation of uncertainty. The other scenarios exhibited more
+balanced or slightly under-coverage. Scenarios with frequent exposure
+also displayed higher relative error in SE estimation, making it more
+difficult to precisely estimate effects. In contrast, rare exposure
+scenarios were associated with higher MSE, reflecting the challenge of
+estimating effects when the exposure is uncommon. Rare outcome scenarios
+exhibited the lowest MSE across most methods (except GA), indicating
+that these scenarios provided a better balance between bias and
+precision for most methods.
 
@@
 
-\textcolor{red}{*need to write what hdps offers in the literature; what additional selection criteria was used so far*}
+Previous studies have shown that LASSO performs well within the hdPS
+framework, particularly in terms of bias reduction and MSE
+\citep{karim2018can, franklin2015regularized}, with similar results for
+Elastic Net \citep{karim2018can}. Our findings largely support these
+conclusions, as both methods demonstrated moderate bias and MSE across
+the scenarios. However, their performance was inconsistent in some
+cases, with higher bias observed in rare exposure scenarios, as noted in
+previous studies \citep{karim2018can, franklin2015regularized}. MSE also
+increased in rare exposure scenarios. The Hybrid hdPS method, combining
+Bross-based hdPS and LASSO, showed promising results, especially in
+terms of MSE, suggesting it may serve as a suitable alternative to
+traditional hdPS methods. Random Forest also performed similarly in our
+study, yielding relatively low bias, which is consistent with previous
+findings \citep{karim2018can}. However, none of the earlier works
+emphasized coverage or examined methods such as GA, XGBoost, forward
+selection, or backward elimination, which were evaluated here.
 
@@
 
-\textcolor{red}{*summarize real data analysis finding in 1 para*}
+The real-world dataset, with frequent exposure (48.8\%) and a moderate
+outcome rate (23.7\%), produced ORs of 1.59 and 1.56 for RF and XGBoost,
+respectively, while other methods clustered around an OR of 1.52. A
+general trend emerged, showing that methods selecting fewer proxy
+variables yielded lower ORs, except for RF and the Bross formula hdPS.
+In terms of risk difference (RD), estimates were relatively stable
+across methods. Regarding variable overlap, most methods shared around
+74\% of their proxy variables with the Bross formula hdPS, with XGBoost
+showing the highest common rate (79\%) and GA the lowest (69\%).
+Computing time analysis showed that, aside from RF and GA, most methods
+had relatively fast computing times, with RF being significantly slower.
+
+\subsection{Strengths}\label{strengths}
+
+Previous studies on singly robust methods have mainly focused on hdPS
+performance using MSE as the primary evaluation metric
+\citep{franklin2015regularized, pang2016effect, wyss2018using, karim2018can, simon2023evaluating}.
+Our study extends this body of work by incorporating a broader range of
+performance metrics, allowing researchers to compare results in terms of
+both bias and variance estimation. This comprehensive comparison of
+statistical and machine learning methods across various scenarios has
+not been conducted before. For instance, we found that while XGBoost
+consistently demonstrated strong performance in terms of MSE and
+coverage, it did not always have the lowest bias. Additionally, we
+observed that traditional variable selection methods such as forward
+selection and backward elimination performed similarly to more
+sophisticated methods such as LASSO and Random Forest across scenarios,
+both in terms of bias and coverage.
+
+Our study also employed a complex plasmode simulation framework, closely
+replicating real-world data conditions. This framework not only
+accounted for model misspecification, where the true relationships
+between covariates and outcomes were unknown, but also introduced noise
+variables, addressing the challenge of dealing with irrelevant
+covariates in high-dimensional settings. By applying transformations to
+continuous variables and adding proxy variables that contributed
+minimally to the outcome, we rigorously evaluated how well each method
+handled both model uncertainty and non-informative variables, further
+strengthening the real-world relevance of our findings.
 
@@
 
-\textcolor{red}{*TMLE*}
+Double robust methods have demonstrated strong potential for achieving
+optimal statistical performance in hdPS analyses
+\citep{pang2016targeted, pang2016effect, benasseur2022comparison}. In
+addition, single robust methods, such as ensemble learners such as super
+learners, have shown promise in improving bias, MSE, area under the
+curve (AUC), and covariate balance in other contexts
+\citep{guertin2016head, wyss2018using, ju2019propensity}. Deep learning
+methods, particularly supervised architectures, offer significant
+potential for improving propensity score estimation in high-dimensional
+settings by capturing complex, non-linear relationships and performing
+well in scenarios with rare exposures, while maintaining comparable bias
+and superior variance estimation compared to traditional methods
+\citep{karim2024can}. Despite their theoretical advantages, the
+complexity and computational demands of these methods, especially in
+high-dimensional settings, have limited their adoption by practitioners.
+On the other hand, the simpler singly robust machine learning methods
+evaluated here have been applied in clinical research
+\citep{hossain2023role, basham2021post}.
+
+Future research should explore the application of double robust methods
+and super learners in hdPS analyses, particularly for handling rare
+outcomes and exposures, where the performance of traditional methods may
+be suboptimal. Additionally, investigating the impact of different
+hyperparameters on machine learning methods such as XGBoost could
+optimize their performance in hdPS analysis. Finally, future simulation
+studies should focus on evaluating coverage and other metrics in
+epidemiological scenarios such as time-varying exposures, which would
+provide valuable insights into the generalizability of our findings
+\citep{neugebauer2015high}.
 
@@
 characteristics of the data, particularly the prevalence of exposure and
-outcome. While XGBoost consistently demonstrated strong performance in
-terms of MSE and coverage, it did not always have the lowest bias,
-suggesting that it may be most suitable when precision is prioritized
-over bias minimization. GA, despite its potential, showed significant
-limitations with consistently high bias and MSE, making it less reliable
-for accurate effect estimation. The kitchen sink model, Bross-based
-hdPS, and Hybrid hdPS methods provided a balanced approach, often
-delivering low bias and moderate MSE, but with variability in coverage
-depending on the scenario. Scenario-specific trends revealed that rare
-outcomes generally yielded lower MSE and better precision, while rare
-exposures were associated with higher bias and MSE, emphasizing the
-challenges of accurately estimating effects in such contexts.
-Ultimately, the findings underscore the need to tailor method selection
-to the epidemiological scenario at hand, ensuring that the chosen
-approach aligns with the specific goals and challenges of the analysis.
+outcome. These findings also emphasize the need to tailor method
+selection to the specific epidemiological scenario, ensuring that the
+chosen method aligns with the study's goals, whether minimizing bias or
+maximizing precision.
+
+XGBoost consistently demonstrated strong performance in terms of MSE and
+coverage, making it an effective choice when precision is prioritized.
+However, it did not achieve the lowest bias, particularly in rare
+exposure scenarios, indicating that it may be less suited when
+minimizing bias is the primary objective. In contrast, the Genetic
+Algorithm (GA) exhibited significant limitations, with consistently high
+bias and MSE, making it less reliable for effect estimation.
+
+The kitchen sink, Bross-based hdPS, and Hybrid hdPS methods provided a
+more balanced approach, offering low bias and moderate MSE, though
+coverage varied depending on the scenario. The analysis also revealed
+that rare outcomes were associated with lower MSE and better precision,
+while rare exposures presented challenges, yielding higher bias and MSE.
+Interestingly, traditional statistical approaches such as forward
+selection and backward elimination performed comparably to more
+sophisticated machine learning methods across many scenarios. This
+suggests that simpler approaches can still be viable, particularly in
+terms of bias and coverage, and might be preferred due to their
+computational efficiency.
 
@@
 \item
-  \textcolor{blue}{KS: Kitchen Sink}
+  KS: Kitchen Sink
 \item
@@
 \item
-  \textcolor{blue}{ElasticNet / EN}: A regularized regression method
-  that combines LASSO and Ridge regression
+  EN: Elastic Net; a regularized regression method that combines LASSO
+  and Ridge regression
 \item
@@
 
+The National Health and Nutrition Examination Survey (NHANES), conducted
+by the U.S. Centers for Disease Control and Prevention (CDC), involves
+collecting data through direct physical examinations, laboratory
+testing, and interviews. The CDC already obtains consent from
+participants when collecting this data. When researchers use NHANES data
+for their studies, they are typically using de-identified, publicly
+available data. This means that the information cannot be linked back to
+individual participants, and therefore, additional consent from
+participants is not required for researchers to use this data.
+
 \subsection*{Availability of data and
@@
 
+NHANES data is publicly accessible and can be retrieved from the NHANES
+website. The datasets generated and/or analyzed during the current study
+are available in the NHANES repository:
+\url{https://www.cdc.gov/nchs/nhanes/index.htm}. Additionally, all
+simulation results can be interactively reviewed through a Shiny web
+application at \url{https://ehsanx.shinyapps.io/hdPS-Alternatives/}.
+
 \subsection*{Competing interests}\label{competing-interests}
@@
 
-Over the past three years, MEK has received consulting fees from Biogen
-Inc.~for consulting unrelated to this current work. MEK was previously
-supported by the Michael Smith Foundation for Health Research Scholar
-award.
+MEK is currently supported by grants from Canadian Institutes of Health
+Research and MS Canada. MEK has previously received consulting fees from
+Biogen Inc.~for consulting unrelated to this current work. MEK was also
+previously supported by the Michael Smith Foundation for Health Research
+Scholar award.
 
@@
 This work was supported by MEK's Natural Sciences and Engineering
-Research Council of Canada (NSERC) Discovery Grants and Discovery
-Accelerator Supplements.
+Research Council of Canada (NSERC) Discovery Grant (PG\#: 20R01603) and
+Discovery Launch Supplement (PG\#: 20R12709).
 

### 2024-09-14 Writeup/appendix/Appendix.RMD
update3
bmc submission

--- 2024-09-01 Writeup/appendix/Appendix.RMD
@@
 title: Supplementary Content
-subtitle: Challenges of Univariate Proxy Variable Screening in High-Dimensional Propensity Score Analysis - An Argument for Multivariate Approaches
+subtitle: Is There a Competitive Advantage to Using Multivariate Statistical or Machine Learning Methods Over the Bross Formula in the hdPS Framework for Bias and Variance Estimation?
 output:
@@
 
-# True outcome model for Plasmode Simulation Data Generation
+# True Outcome Model for Plasmode Simulation Data Generation
 
@@
 
-# SE comparison
+# Standard Error comparison
 

### 2024-09-14 Writeup/manuscript.Rmd
bmc submission

@@
 abstract: |
-  **Purpose**: We aims to evaluate various proxy selection methods within the context of high-dimensional propensity score (hdPS) analysis.
-The study focuses on assessing the performance of these methods, including alternative variable selection approaches, in selecting proxy variables for confounding adjustment compared to the traditional hdPS method that is rooted in Bross formula.
-The goal is to understand better the performance of these alternative methods in estimating treatment effects, and identify scenarios in which they may perform better.
-  **Methods:** Using data from three cycles of the National Health and Nutrition Examination Survey (NHANES) spanning 2013-2018, we motivated the study by examining the association between obesity and diabetes.
-A plasmode simulation framework based on this data was employed to mimic real-world data structures.
-Simulations were conducted under three scenarios: Frequent Exposure and Outcome, Rare Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome.
-The performance of a variety of proxy selection methods—including tree-based methods, LASSO-based methods, and the Genetic Algorithm (GA)—was evaluated across these scenarios using standard simulation metrics.
-  **Results:** XGBoost consistently demonstrated the lowest MSE and high coverage, making it a reliable method overall, although it did not always exhibit the lowest bias.
-In contrast, GA consistently showed the highest bias and MSE, with lower coverage and greater variability, indicating its unsuitability for accurate effect estimation.
-The kitchen sink model, Bross-based hdPS, and Hybrid hdPS methods performed moderately well, with low bias and moderate MSE, but varied in coverage across scenarios.
-Scenario-specific trends revealed that rare outcome scenarios yielded lower MSE and better precision, while rare exposure scenarios were associated with higher bias and MSE.
-  **Conclusion:** Aside from GA, the performance of most other methods in your study appears to be comparable in each scenario, though with some variations depending on specific metrics.
-The findings underscore the importance of selecting appropriate methods for hdPS analysis based on the characteristics of the data, particularly the prevalence of exposure and outcome.
-While XGBoost excelled in overall accuracy and precision, the choice of method should be tailored to the specific epidemiological goal to optimize bias, coverage, and precision in estimating treatment effects.
+  **Purpose**: We aim to evaluate various proxy selection methods within the context of high-dimensional propensity score (hdPS) analysis.
+This study aimed to systematically evaluate and compare the performance of traditional statistical methods and machine learning approaches within the hdPS framework, focusing on key metrics such as bias, standard error (SE), and coverage, under various exposure and outcome prevalence scenarios.
+  **Methods:** We conducted a plasmode simulation study using data from the National Health and Nutrition Examination Survey (NHANES) cycles from 2013 to 2018.
+We compared methods including the kitchen sink model, Bross-based hdPS, Hybrid hdPS, LASSO, Elastic Net, Random Forest, XGBoost, and Genetic Algorithm (GA).
+The performance of each method was assessed based on bias, MSE, coverage probability, and SE estimation across three epidemiological scenarios: frequent exposure and outcome, rare exposure and frequent outcome, and frequent exposure and rare outcome.
+  **Results:** XGBoost consistently demonstrated strong performance in terms of MSE and coverage, making it effective for scenarios prioritizing precision.
+However, it exhibited higher bias, particularly in rare exposure scenarios, suggesting it is less suited when minimizing bias is critical.
+In contrast, GA showed significant limitations, with consistently high bias and MSE, making it the least reliable method.
+Bross-based hdPS, and Hybrid hdPS methods provided a balanced approach, with low bias and moderate MSE, though coverage varied depending on the scenario.
+Rare outcome scenarios generally resulted in lower MSE and better precision, while rare exposure scenarios were associated with higher bias and MSE.
+Notably, traditional statistical approaches such as forward selection and backward elimination performed comparably to more sophisticated machine learning methods in terms of bias and coverage, suggesting that these simpler approaches may be viable alternatives due to their computational efficiency.
+  **Conclusion:** The results highlight the importance of selecting hdPS methods based on the specific characteristics of the data, such as exposure and outcome prevalence.
+While advanced machine learning methods such as XGBoost can enhance precision, simpler methods such as forward selection or backward elimination may offer similar performance in terms of bias and coverage with fewer computational demands.
+Tailoring the choice of method to the epidemiological scenario is essential for optimizing the balance between bias reduction and precision.
 
@@
 **High-dimensional Propensity Score (hdPS) Algorithm**: In epidemiology, proxy variables are commonly used as substitutes for confounders that are difficult or impossible to measure directly, such as socioeconomic status, lifestyle factors, or health behaviors [@vanderweele2019principles].
-The high-dimensional propensity score (hdPS) is a pharmacoepidemiological method designed to reduce confounding bias in large healthcare databases [@schneeweiss2009high].
+The hdPS is a pharmacoepidemiological method designed to reduce confounding bias in large healthcare databases [@schneeweiss2009high].
 Unlike traditional propensity score models that rely on investigator-specified or manually selected covariates, hdPS automatically ranks a wide array of proxy variables from healthcare records—such as diagnosis codes, medications, and procedures—using the Bross formula [@wyss2018erratum; @bross1966spurious].
@@
 **Multivariate Machine Learning Extensions**: Although the Bross formula performs well in certain contexts, it has limitations in capturing complex interactions, nonlinearities, and higher-order associations between variables, especially in high-dimensional settings where it does not account for the multivariate structure of other covariates [@karim2024high; @karim2018can].
-To address these limitations, multivariate machine learning methods such as LASSO, Elastic Net, and Random Forests have been applied within the hdPS framework.
+To address these model-specification-related limitations, multivariate machine learning methods such as LASSO, Elastic Net, and Random Forests have been applied within the hdPS framework.
 These methods are better suited for high-dimensional data, where they can more effectively handle complex relationships and improve the selection of proxy variables, thus enhancing the precision of treatment effect estimates [@karim2018can; @schneeweiss2017variable; @franklin2015regularized].
@@
 **Assessing the Simulation Performance**: Other than bias, previous studies have primarily focused on Mean Squared Error (MSE) as a key metric for evaluating the performance of hdPS and its machine learning extensions [@franklin2015regularized; @pang2016effect; @wyss2018using; @karim2018can; @simon2023evaluating].
-However, in high-dimensional settings with singly robust methods, such as hdPS and machine learning approaches like LASSO, MSE may not always be the most reliable measure.
+However, in high-dimensional settings with singly robust methods, such as hdPS and machine learning approaches such as LASSO, MSE may not always be the most reliable measure.
 MSE combines both bias and variance into a single metric, which makes interpretation challenging when variance estimation is unstable—a common issue in these methods.
@@
 **Plasmode simulation**: To rigorously assess the performance of the methods under consideration, we employed a plasmode simulation framework, which is particularly well-suited for reflecting real-world data structures and complexities [@franklin2014plasmode].
-This approach was modeled after the analytic dataset derived from NHANES and involved resampling from the observed covariates and exposure information (i.e., obesity) without altering them.
+This approach was inspired by the analytic dataset derived from NHANES and involved resampling from the observed covariates and exposure information (i.e., obesity) without altering them.
 By mirroring key aspects of an actual epidemiological study, this simulation framework offers a substantial advantage over traditional Monte Carlo simulations, which often rely on hypothetical assumptions.
@@
 
-**Performance Measures**: From this simulation, we derived several performance metrics to evaluate the effectiveness of the methods under consideration: (1) bias, (2) average model standard error (SE; the average of estimated SEs obtained from a model over repeated samples), (3) empirical SE (the standard deviation of estimated treatment effects across repeated samples), (4) mean squared error (MSE), (5) coverage probability of 95% confidence intervals, (6) bias-corrected coverage, and (7) Zip plot [@morris2019using; @white2023check].
+**Performance Measures**: From this simulation, we derived several performance metrics to evaluate the effectiveness of the methods under consideration: (1) bias, (2) average model-based SE (the average of estimated SEs obtained from a model over repeated samples), (3) empirical SE (the standard deviation of estimated treatment effects across repeated samples), (4) MSE, (5) coverage probability of 95% confidence intervals, (6) bias-corrected coverage, and (7) Zip plot [@morris2019using; @white2023check].
 
@@
 **Hybrid of hdPS and LASSO**: Instead of relying solely on LASSO for variable selection, a hybrid approach combines the Bross formula and LASSO.
-First, hdPS variables are selected using the hdPS algorithm (e.g., the top 100), and then LASSO is applied to further refine the selection [@karim2018can; @franklin2015regularized].
+First, proxy variables are selected using the hdPS algorithm (e.g., the top 100), and then LASSO is applied to further refine the selection [@karim2018can; @franklin2015regularized].
 
@@
 6.
-**Random Forest**: The Random Forest (RF) algorithm is an ensemble learning method that constructs multiple decision trees to perform classification [@breiman2001random].
+**Random Forest**: The Random Forest algorithm is an ensemble learning method that constructs multiple decision trees to perform classification [@breiman2001random].
 It calculates the importance of each proxy variable based on the decrease in impurity or Gini importance, providing a ranking of the proxies.
@@
 9.
-**Genetic algorithm (GA)**: GA is an evolutionary algorithm inspired by the theory of natural selection [@holland1975adaptation].
+**Genetic algorithm**: Genetic algorithm is an evolutionary algorithm inspired by the theory of natural selection [@holland1975adaptation].
 It operates by evolving offspring from a population of the fittest individuals over several generations, evaluating and selecting the best combination of features or variables that maximize prediction accuracy.
@@
 See Figures \ref{fig:bias-comparison} and \ref{fig:Coverage-comparison} for an overview of the performance in terms of bias and coverage, respectively.
-
-(i) **Frequent Exposure and Outcome (base) scenario**:
-
-1.
-*Bias*: Bross-based hdPS exhibited the smallest bias (-0.0001), and the kitchen sink model (0.0002) was the second.
-GA shows the highest bias (0.0287), indicating a substantial deviation from the true effect.
-Among the other methods, Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
-XGBoost (0.0074) had slightly higher bias than Random Forest (RF) (0.0034).
-
-2.
-*Coverage*: The coverage for most methods was high, with Hybrid hdPS, Forward Selection, Backward Elimination, LASSO, and Elastic Net achieving values around 98%, indicating well-calibrated confidence intervals.
-However, GA had noticeably lower coverage (83.8%), indicating that its confidence intervals might be too narrow or biased, potentially missing the true effect.
-After applying bias elimination (as there were substantial bias associated with this method), GA's coverage improved to 96%.
-
-3.
-*Mean Squared Error (MSE)*: XGBoost achieved the lowest MSE (0.0006).
-GA maintained the highest MSE (0.0016), reflecting its higher bias and variability.
-The kitchen sink model (0.0009), Bross-based hdPS (0.0008), Hybrid hdPS (0.0008), and Elastic Net (0.0009) all had relatively similar and moderate MSE values.
-
-4.
-*Standard Error (SE)*: XGBoost exhibited the lowest Empirical SE (0.0229), indicating high precision in its estimates.
-The kitchen sink model had the highest Empirical SE (0.0305), suggesting greater variability.
-Other methods, including GA (0.0274), Hybrid hdPS (0.0278), and Bross-based hdPS (0.0287), showed moderate variability.
-LASSO (0.0299) and Elastic Net (0.0294) had slightly higher variability.
-The Model-based SE followed a similar pattern, with XGBoost (0.0268) showing the lowest variability and the kitchen sink model (0.0333) the highest, indicating less precision in its estimates.
-When comparing relative error in SE estimation, XGBoost performed the worst.
-See Appendix \S C for further details.
-
-**(ii) Rare Exposure and Frequent Outcome**:
-
-1.
-*Bias*: The kitchen sink model showed a relatively low bias (0.0025), while GA continued to exhibit the highest bias (0.0408), indicating a significant deviation from the true effect.
-XGBoost had a bias of 0.0259, which, while still higher than other methods, but was lower than GA.
-Other methods, such as Bross-based hdPS (0.0035), Hybrid hdPS (0.0049), and Elastic Net (0.0053), demonstrated moderate bias.
-Random Forest (RF) (0.0127) and Forward Selection (0.0108) had slightly higher bias but remained within an acceptable range.
-
-2.
-*Coverage*: Coverage levels remained high for most methods, with XGBoost achieving the highest coverage at 96.2%, indicating well-calibrated confidence intervals despite its higher bias.
-The GA method had lower coverage (92.2%), suggesting that its confidence intervals might be narrower, potentially missing the true effect.
-Other methods such as RF, Forward Selection, Backward Elimination, and Hybrid hdPS maintained coverage values around 94-95%, suggesting adequate interval calibration.
-Bias-eliminated coverage for GA improved to 94.2%, but it was still slightly lower than other methods (e.g., forward selection).
-
-3.
-*Mean Squared Error (MSE)*: Forward selection demonstrated the lowest MSE (0.0030), and then Hybrid hdPS and XGBoost.
-The GA method had a higher MSE (0.0043), reflecting its substantial bias and variability.
-The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.
-
-4.
-*Standard Error (SE)*: The lowest Empirical SE was observed with XGBoost (0.0507) and GA (0.0510), reflecting high precision despite their higher bias.
-The kitchen sink model had the highest Empirical SE (0.0656), indicating greater variability.
-Hybrid hdPS (0.0564), Bross-based hdPS (0.0595), and RF (0.0609) showed moderate variability.
-Forward Selection (0.0537) and Backward Elimination (0.0576) had lower variability compared to the kitchen sink model.
-In terms of Model-based SE, XGBoost (0.0531) and GA (0.0533) continued to show low variability, while the kitchen sink model had the highest Model-based SE (0.0623), indicating less precision in its estimates.
-When comparing relative error in SE estimation, XGBoost and kitchen sink model performed the worst (in other direction).
-
-**(iii) Frequent Exposure and Rare Outcome**:
-
-1.
-*Bias*: In this scenario, the kitchen sink model exhibited a moderate negative bias (-0.0093), similar to the Bross-based hdPS method (-0.0088).
-GA showed a significantly higher bias (0.0362), indicating a substantial deviation from the true effect.
-Among other methods, XGBoost demonstrated the lowest bias (-0.0061), while methods like Hybrid hdPS (-0.0082), Forward Selection (-0.0070), and Backward Elimination (-0.0070) had slightly higher but still moderate biases.
-Elastic Net and LASSO both had biases of -0.0079, reflecting slightly larger deviations compared to XGBoost but still within acceptable limits.
-
-2.
-*Coverage*: Most methods achieved good coverage, with XGBoost, RF, and Forward Selection each achieving a coverage rate of 95.4%, indicating well-calibrated confidence intervals.
-The GA method, however, had slightly lower coverage (91.8%), indicating that its confidence intervals might be narrower, potentially excluding the true effect.
-Bross-based hdPS and the kitchen sink model had slightly lower coverage values of 93.8% and 93.4%, respectively.
-After accounting for bias, the bias-eliminated coverage for most methods, except GA, remained high, with values ranging from 98.4% to 99.0%, indicating that most methods effectively adjusted for bias in their coverage estimates.
-GA's bias-eliminated coverage was lower at 93.4%, reflecting its higher inherent bias.
-
-3.
-*Mean Squared Error (MSE)*: XGBoost exhibited the lowest MSE (0.0003).
-GA had the highest MSE (0.0040), reflecting its substantial bias and variability.
-The kitchen sink model (0.0005), Bross-based hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and Elastic Net (0.0005) all had relatively similar MSE values, indicating moderate accuracy.
-
-4.
-*Standard Error (SE)*: The lowest Empirical SE was observed with XGBoost (0.0152), reflecting high precision in its estimates.
-The GA method exhibited the highest Empirical SE (0.0523), indicating greater variability and less precision.
-Methods such as Hybrid hdPS (0.0184), Forward Selection (0.0187), and Elastic Net (0.0203) showed moderate variability, while Bross-based hdPS (0.0206) and the kitchen sink model (0.0212) had slightly higher variability.
-In terms of Model-based SE, XGBoost (0.0179) again showed the lowest variability, consistent with its low Empirical SE, indicating that it provided the most stable estimates.
-The kitchen sink model had a slightly higher Model-based SE (0.0219), indicating less precision in its estimates.
-When comparing relative error in SE estimation, XGBoost performed the worst.
+All simulation results can be reviewed interactively through a Shiny web application available at https://ehsanx.shinyapps.io/hdPS-Alternatives/, providing a convenient platform for exploring the performance of each method across various scenarios.
 
@@
 
+(i) **Frequent Exposure and Outcome (base) scenario**:
+
+1.
+*Bias*: Bross-based hdPS exhibited the smallest bias (-0.0001), and the kitchen sink model (0.0002) was the second.
+Genetic algorithm shows the highest bias (0.0287), indicating a substantial deviation from the true effect.
+Among the other methods, Hybrid hdPS (0.0016), and Elastic Net (0.0036) demonstrated low bias.
+XGBoost (0.0074) had slightly higher bias than Random Forest (0.0034).
+
+2.
+*Coverage*: The coverage for most methods was high, with Hybrid hdPS, Forward Selection, Backward Elimination, LASSO, and Elastic Net achieving values around 98%, indicating well-calibrated confidence intervals.
+However, Genetic algorithm had noticeably lower coverage (83.8%), indicating that its confidence intervals might be too narrow or biased, potentially missing the true effect.
+After applying bias elimination (as there were substantial bias associated with this method), Genetic algorithm's coverage improved to 96%.
+
+3.
+*MSE*: XGBoost achieved the lowest MSE (0.0006).
+Genetic algorithm maintained the highest MSE (0.0016), reflecting its higher bias and variability.
+The kitchen sink model (0.0009), Bross-based hdPS (0.0008), Hybrid hdPS (0.0008), and Elastic Net (0.0009) all had relatively similar and moderate MSE values.
+
+4.
+*SE*: XGBoost exhibited the lowest Empirical SE (0.0229), indicating high precision in its estimates.
+The kitchen sink model had the highest Empirical SE (0.0305), suggesting greater variability.
+Other methods, including Genetic algorithm (0.0274), Hybrid hdPS (0.0278), and Bross-based hdPS (0.0287), showed moderate variability.
+LASSO (0.0299) and Elastic Net (0.0294) had slightly higher variability.
+The Model-based SE followed a similar pattern, with XGBoost (0.0268) showing the lowest variability and the kitchen sink model (0.0333) the highest, indicating less precision in its estimates.
+When comparing relative error in SE estimation, XGBoost performed the worst.
+See Appendix \S C for further details.
+
+**(ii) Rare Exposure and Frequent Outcome**:
+
+1.
+*Bias*: The kitchen sink model showed a relatively low bias (0.0025), while Genetic algorithm continued to exhibit the highest bias (0.0408), indicating a significant deviation from the true effect.
+XGBoost had a bias of 0.0259, which, while still higher than other methods, but was lower than Genetic algorithm.
+Other methods, such as Bross-based hdPS (0.0035), Hybrid hdPS (0.0049), and Elastic Net (0.0053), demonstrated moderate bias.
+Random Forest (0.0127) and Forward Selection (0.0108) had slightly higher bias but remained within an acceptable range.
+
+2.
+*Coverage*: Coverage levels remained high for most methods, with XGBoost achieving the highest coverage at 96.2%, indicating well-calibrated confidence intervals despite its higher bias.
+The Genetic algorithm method had lower coverage (92.2%), suggesting that its confidence intervals might be narrower, potentially missing the true effect.
+Other methods such as RF, Forward Selection, Backward Elimination, and Hybrid hdPS maintained coverage values around 94-95%, suggesting adequate interval calibration.
+Bias-eliminated coverage for Genetic algorithm improved to 94.2%, but it was still slightly lower than other methods (e.g., forward selection).
+
+3.
+*MSE*: Forward selection demonstrated the lowest MSE (0.0030), and then Hybrid hdPS and XGBoost.
+The Genetic algorithm method had a higher MSE (0.0043), reflecting its substantial bias and variability.
+The kitchen sink model also had an MSE of 0.0043, similar to Genetic algorithm, while other methods such as Bross-based hdPS (0.0035), RF (0.0039), and Elastic Net (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.
+
+4.
+*SE*: The lowest Empirical SE was observed with XGBoost (0.0507) and Genetic algorithm (0.0510), reflecting high precision despite their higher bias.
+The kitchen sink model had the highest Empirical SE (0.0656), indicating greater variability.
+Hybrid hdPS (0.0564), Bross-based hdPS (0.0595), and RF (0.0609) showed moderate variability.
+Forward Selection (0.0537) and Backward Elimination (0.0576) had lower variability compared to the kitchen sink model.
+In terms of Model-based SE, XGBoost (0.0531) and Genetic algorithm (0.0533) continued to show low variability, while the kitchen sink model had the highest Model-based SE (0.0623), indicating less precision in its estimates.
+When comparing relative error in SE estimation, XGBoost and kitchen sink model performed the worst (in other direction).
+
+**(iii) Frequent Exposure and Rare Outcome**:
+
+1.
+*Bias*: In this scenario, the kitchen sink model exhibited a moderate negative bias (-0.0093), similar to the Bross-based hdPS method (-0.0088).
+Genetic algorithm showed a significantly higher bias (0.0362), indicating a substantial deviation from the true effect.
+Among other methods, XGBoost demonstrated the lowest bias (-0.0061), while methods such as Hybrid hdPS (-0.0082), Forward Selection (-0.0070), and Backward Elimination (-0.0070) had slightly higher but still moderate biases.
+Elastic Net and LASSO both had biases of -0.0079, reflecting slightly larger deviations compared to XGBoost but still within acceptable limits.
+
+2.
+*Coverage*: Most methods achieved good coverage, with XGBoost, RF, and Forward Selection each achieving a coverage rate of 95.4%, indicating well-calibrated confidence intervals.
+The Genetic algorithm method, however, had slightly lower coverage (91.8%), indicating that its confidence intervals might be narrower, potentially excluding the true effect.
+Bross-based hdPS and the kitchen sink model had slightly lower coverage values of 93.8% and 93.4%, respectively.
+After accounting for bias, the bias-eliminated coverage for most methods, except Genetic algorithm, remained high, with values ranging from 98.4% to 99.0%, indicating that most methods effectively adjusted for bias in their coverage estimates.
+Genetic algorithm's bias-eliminated coverage was lower at 93.4%, reflecting its higher inherent bias.
+
+3.
+*MSE*: XGBoost exhibited the lowest MSE (0.0003).
+Genetic algorithm had the highest MSE (0.0040), reflecting its substantial bias and variability.
+The kitchen sink model (0.0005), Bross-based hdPS (0.0005), and other methods such as Hybrid hdPS (0.0004) and Elastic Net (0.0005) all had relatively similar MSE values, indicating moderate accuracy.
+
+4.
+*SE*: The lowest Empirical SE was observed with XGBoost (0.0152), reflecting high precision in its estimates.
+The Genetic algorithm method exhibited the highest Empirical SE (0.0523), indicating greater variability and less precision.
+Methods such as Hybrid hdPS (0.0184), Forward Selection (0.0187), and Elastic Net (0.0203) showed moderate variability, while Bross-based hdPS (0.0206) and the kitchen sink model (0.0212) had slightly higher variability.
+In terms of Model-based SE, XGBoost (0.0179) again showed the lowest variability, consistent with its low Empirical SE, indicating that it provided the most stable estimates.
+The kitchen sink model had a slightly higher Model-based SE (0.0219), indicating less precision in its estimates.
+When comparing relative error in SE estimation, XGBoost performed the worst.
+
 # Real-world analysis
@@
 The methods are arranged according to the number of selected proxy variables.
-Among all variable selection algorithms, Random Forest (RF) and XGBoost demonstrate the highest odds ratios (ORs), with values of 1.59 and 1.56, respectively.
+Among all variable selection algorithms, Random Forest and XGBoost demonstrate the highest ORs, with values of 1.59 and 1.56, respectively.
 The ORs for the remaining methods cluster around 1.52.
 Additionally, with the exception of RF and the Bross formula hdPS, a general pattern emerges where methods selecting a larger number of proxy variables yield lower ORs.
-For risk difference (RD), RF and XGBoost also exhibit the highest value 0.08, while the remaining methods converge around 0.077.
+For RD, RF and XGBoost also exhibit the highest value 0.08, while the remaining methods converge around 0.077.
 The trend observed in the OR results appears to persist in the RD analysis.
@@
 data_combined <- data.frame(
-  Method = rep(c("KitchenSink", "Bross", "Hybrid", "LASSO", "ElasticNet", "RF", "XGBoost", "FS", "BE", "GA"), 2),
+  Method = rep(c("Kitchen Sink", "Bross", "Hybrid", "LASSO", "Elastic Net", "Random Forest", "XGBoost", "Fprward Selection", "Backward Elimination", "Genetic algorithm"), 2),
   # These are approximate values
@@
 
-We observe that, aside from the Bross formula hdPS and Random Forest (RF) models, where the number of proxies was manually set to 100, and the kitchen sink (KS) model, which includes all proxies by design, the number of proxy variables selected by other models ranges between 49 and 69.
+We observe that, aside from the Bross formula hdPS and Random Forest models, where the number of proxies was manually set to 100, and the kitchen sink (KS) model, which includes all proxies by design, the number of proxy variables selected by other models ranges between 49 and 69.
 As expected, the hybrid method combining Bross and LASSO hdPS selects exactly 49 proxy variables, all of which are selected by both methods, resulting in a common feature rate of 1.00.
@@
 
-Across the three scenarios, XGBoost consistently exhibited the lowest MSE and high coverage, making it one of the most reliable methods in terms of precision.
-However, XGBoost always displayed some level of bias, particularly when compared to methods such as the kitchen sink model, Bross-based hdPS, and Hybrid hdPS, which often showed lower bias in scenarios with frequent outcomes.
-In contrast, GA consistently exhibited the highest bias and MSE, along with lower coverage and greater variability, indicating that it was the least reliable method for accurate effect estimation.
-Methods such as Bross-based hdPS, Hybrid hdPS, and Elastic Net performed moderately well across all scenarios, striking a reasonable balance between bias, coverage, and MSE.
-However, they did not outperform XGBoost in terms of overall precision, particularly with respect to MSE, though those methods often had lower bias.
-The kitchen sink model, performed competitively with Bross-based hdPS in terms of bias and coverage, but did not perform well in terms of SEs and MSE.
+Across the three scenarios, XGBoost consistently achieved the lowest MSE and high coverage, making it one of the most reliable methods in terms of precision.
+However, it consistently exhibited some degree of bias, particularly when compared to methods such as the kitchen sink model, Bross-based hdPS, and Hybrid hdPS, which often showed lower bias in scenarios with frequent outcomes.
+In contrast, GA displayed the highest bias and MSE, along with lower coverage and greater variability, making it the least reliable method for accurate effect estimation.
+Methods such as Bross-based hdPS, Hybrid hdPS, and Elastic Net performed moderately well across all scenarios, balancing bias, coverage, and MSE.
+However, these methods did not outperform XGBoost in terms of overall precision, especially with respect to MSE, though they often resulted in lower bias.
+The kitchen sink model performed comparably to Bross-based hdPS in terms of bias and coverage but lagged in SE estimation and MSE.
 
@@
 
-Scenarios with rare exposure tended to produce higher bias, particularly for methods like GA and XGBoost, while frequent outcomes generally led to lower bias for most methods.
-Overcoverage was common in the frequent exposure and outcome scenario, with several methods producing confidence intervals that were too wide (i.e., overestimating the uncertainty), while the other scenarios showed more balanced or slightly under-coverage.
-Frequent exposure scenarios also had higher relative error in standard error estimation, indicating greater difficulty in precisely estimating effects.
-In contrast, rare exposure scenarios had higher MSE, reflecting the challenge of estimating effects when exposure is uncommon.
-The rare outcome scenarios tended to exhibit the lowest MSE across most methods (with the exception of GA), further indicating that these scenarios provided a better balance between bias and precision for most methods.
+In scenarios with rare exposure, higher bias was observed, particularly for methods such as GA and XGBoost, whereas frequent outcomes generally led to lower bias across most methods.
+Overcoverage was more common in the scenario with frequent exposure and outcome, with several methods producing confidence intervals that were too wide, suggesting an overestimation of uncertainty.
+The other scenarios exhibited more balanced or slightly under-coverage.
+Scenarios with frequent exposure also displayed higher relative error in SE estimation, making it more difficult to precisely estimate effects.
+In contrast, rare exposure scenarios were associated with higher MSE, reflecting the challenge of estimating effects when the exposure is uncommon.
+Rare outcome scenarios exhibited the lowest MSE across most methods (except GA), indicating that these scenarios provided a better balance between bias and precision for most methods.
 
@@
 
-LASSO was previously shown to perform well in the contect of hdPS framework, particularly in terms of bias reduction and MSE [@karim2018can; @franklin2015regularized], with similar performance in Elastic Net [@karim2018can].
-Our findings generally support these conclusions, with both methods demonstrating moderate bias and MSE across the scenarios.
-However, the performance of these methods was not consistent across all scenarios, with these methods showing higher bias in the rare exposure scenario in previous simulation studies [@karim2018can; @franklin2015regularized].
-MSE of these methods are particularly high in rare exposure scenario.
-The hybrid method, which combines Bross-based hdPS and LASSO, also showed promising results, particularly in terms of MSE, indicating that it may be a suitable alternative to traditional hdPS methods.
-The Random Forest method also demonstrated similar performance in our study, with relatively low bias, as was also shown previously [@karim2018can].
-However, none of these works focused on coverage, and did not consider other approaches we have considered here, such as GA, XGboost, forward selection or backward elimination.
+Previous studies have shown that LASSO performs well within the hdPS framework, particularly in terms of bias reduction and MSE [@karim2018can; @franklin2015regularized], with similar results for Elastic Net [@karim2018can].
+Our findings largely support these conclusions, as both methods demonstrated moderate bias and MSE across the scenarios.
+However, their performance was inconsistent in some cases, with higher bias observed in rare exposure scenarios, as noted in previous studies [@karim2018can; @franklin2015regularized].
+MSE also increased in rare exposure scenarios.
+The Hybrid hdPS method, combining Bross-based hdPS and LASSO, showed promising results, especially in terms of MSE, suggesting it may serve as a suitable alternative to traditional hdPS methods.
+Random Forest also performed similarly in our study, yielding relatively low bias, which is consistent with previous findings [@karim2018can].
+However, none of the earlier works emphasized coverage or examined methods such as GA, XGBoost, forward selection, or backward elimination, which were evaluated here.
 
@@
 
-The dataset used in the real-world analysis had frequent exposure (48.8% prevalence) and relatively moderate outcome rate (23.7%).
-RF and XGBoost demonstrated the highest ORs at 1.59 and 1.56, respectively, while the remaining methods clustered around an OR of 1.52.
-A general trend was observed where methods selecting fewer proxy variables yielded lower ORs, except for RF and the Bross formula hdPS.
-For RD, the estimates did not vary much.
-In terms of variable overlap, most methods shared around 74% of their proxy variables with the Bross formula hdPS, with XGBoost showing the highest common rate (79%) and Genetic Algorithm (GA) showing the lowest (69%).
-The computing time analysis revealed that, aside from RF and GA, most methods had relatively short computing times, with RF being the slowest by a significant margin.
+The real-world dataset, with frequent exposure (48.8%) and a moderate outcome rate (23.7%), produced ORs of 1.59 and 1.56 for RF and XGBoost, respectively, while other methods clustered around an OR of 1.52.
+A general trend emerged, showing that methods selecting fewer proxy variables yielded lower ORs, except for RF and the Bross formula hdPS.
+In terms of risk difference (RD), estimates were relatively stable across methods.
+Regarding variable overlap, most methods shared around 74% of their proxy variables with the Bross formula hdPS, with XGBoost showing the highest common rate (79%) and GA the lowest (69%).
+Computing time analysis showed that, aside from RF and GA, most methods had relatively fast computing times, with RF being significantly slower.
 
@@
 
-Looking at the literature, almost all of the studies involving singly robust methods have focused on the performance of hdPS methods in terms of MSE [@franklin2015regularized; @pang2016effect; @wyss2018using; @karim2018can; @simon2023evaluating].
-Our study extends this work by considering a wide variety of performance metrics that allows researchers to compare the results both in terms of bias and variance estimation.
-We also provide a comprehensive comparison of the statistical and machine learning methods across different scenarios, which has not been done before.
-For example, we found that XGBoost consistently demonstrated strong performance in terms of MSE and coverage, but it did not always have the lowest bias.
-We have also seen for the first time that standard statistical variable selection methods such as forward selection or backward elimination procedures do perform very similar to the LASSO or random forest approaches across scenarios, both in terms of bias and coverage.
+Previous studies on singly robust methods have mainly focused on hdPS performance using MSE as the primary evaluation metric [@franklin2015regularized; @pang2016effect; @wyss2018using; @karim2018can; @simon2023evaluating].
+Our study extends this body of work by incorporating a broader range of performance metrics, allowing researchers to compare results in terms of both bias and variance estimation.
+This comprehensive comparison of statistical and machine learning methods across various scenarios has not been conducted before.
+For instance, we found that while XGBoost consistently demonstrated strong performance in terms of MSE and coverage, it did not always have the lowest bias.
+Additionally, we observed that traditional variable selection methods such as forward selection and backward elimination performed similarly to more sophisticated methods such as LASSO and Random Forest across scenarios, both in terms of bias and coverage.
+
+Our study also employed a complex plasmode simulation framework, closely replicating real-world data conditions.
+This framework not only accounted for model misspecification, where the true relationships between covariates and outcomes were unknown, but also introduced noise variables, addressing the challenge of dealing with irrelevant covariates in high-dimensional settings.
+By applying transformations to continuous variables and adding proxy variables that contributed minimally to the outcome, we rigorously evaluated how well each method handled both model uncertainty and non-informative variables, further strengthening the real-world relevance of our findings.
 
@@
 
-Double robust methods have been shown to be effective in achieving optimal statistical performance in hdPS analysis [@pang2016targeted; @pang2016effect; @benasseur2022comparison].
-Additionally, single robust methods include ensemble learners, such as super learners, which have been effective in other contexts, particularly in improving bias, MSE, area under the curve, and covariate balance [@guertin2016head; @wyss2018using; @ju2019propensity].
-However, despite the desirable theoretical properties of these methods, their complexity and computational burden, especially in high-dimensional settings, have limited their adoption by practitioners.
-In contrast, some of the singly robust machine learning methods we have discussed have been applied in addressing clinical questions [@hossain2023role; @basham2021post].
-Future research could explore the potential of these double robust and super learner methods in hdPS analysis, particularly in the context of rare outcomes and exposures, where the performance of traditional methods may be suboptimal.
+Double robust methods have demonstrated strong potential for achieving optimal statistical performance in hdPS analyses [@pang2016targeted; @pang2016effect; @benasseur2022comparison].
+In addition, single robust methods, such as ensemble learners such as super learners, have shown promise in improving bias, MSE, area under the curve (AUC), and covariate balance in other contexts [@guertin2016head; @wyss2018using; @ju2019propensity].
+Deep learning methods, particularly supervised architectures, offer significant potential for improving propensity score estimation in high-dimensional settings by capturing complex, non-linear relationships and performing well in scenarios with rare exposures, while maintaining comparable bias and superior variance estimation compared to traditional methods [@karim2024can].
+Despite their theoretical advantages, the complexity and computational demands of these methods, especially in high-dimensional settings, have limited their adoption by practitioners.
+On the other hand, the simpler singly robust machine learning methods evaluated here have been applied in clinical research [@hossain2023role; @basham2021post].
 
-Furthermore, the impact of different hyperparameters on the performance of machine learning methods like XGBoost warrants further investigation to optimize their application in hdPS analysis.
-Lastly, conducting simulation studies to evaluate the performance of hdPS methods in terms of coverage in other epidemiological scenarios, such as time-varying exposures, could provide valuable insights into the generalizability of these findings [@neugebauer2015high].
+Future research should explore the application of double robust methods and super learners in hdPS analyses, particularly for handling rare outcomes and exposures, where the performance of traditional methods may be suboptimal.
+Additionally, investigating the impact of different hyperparameters on machine learning methods such as XGBoost could optimize their performance in hdPS analysis.
+Finally, future simulation studies should focus on evaluating coverage and other metrics in epidemiological scenarios such as time-varying exposures, which would provide valuable insights into the generalizability of our findings [@neugebauer2015high].
 
@@
 In conclusion, this analysis highlights the importance of carefully selecting appropriate methods for hdPS analysis based on the specific characteristics of the data, particularly the prevalence of exposure and outcome.
-While XGBoost consistently demonstrated strong performance in terms of MSE and coverage, it did not always have the lowest bias, suggesting that it may be most suitable when precision is prioritized over bias minimization.
-GA, despite its potential, showed significant limitations with consistently high bias and MSE, making it less reliable for accurate effect estimation.
-The kitchen sink model, Bross-based hdPS, and Hybrid hdPS methods provided a balanced approach, often delivering low bias and moderate MSE, but with variability in coverage depending on the scenario.
-Scenario-specific trends revealed that rare outcomes generally yielded lower MSE and better precision, while rare exposures were associated with higher bias and MSE, emphasizing the challenges of accurately estimating effects in such contexts.
-Ultimately, the findings underscore the need to tailor method selection to the epidemiological scenario at hand, ensuring that the chosen approach aligns with the specific goals and challenges of the analysis.
+These findings also emphasize the need to tailor method selection to the specific epidemiological scenario, ensuring that the chosen method aligns with the study's goals, whether minimizing bias or maximizing precision.
+
+XGBoost consistently demonstrated strong performance in terms of MSE and coverage, making it an effective choice when precision is prioritized.
+However, it did not achieve the lowest bias, particularly in rare exposure scenarios, indicating that it may be less suited when minimizing bias is the primary objective.
+In contrast, the Genetic Algorithm (GA) exhibited significant limitations, with consistently high bias and MSE, making it less reliable for effect estimation.
+
+The kitchen sink, Bross-based hdPS, and Hybrid hdPS methods provided a more balanced approach, offering low bias and moderate MSE, though coverage varied depending on the scenario.
+The analysis also revealed that rare outcomes were associated with lower MSE and better precision, while rare exposures presented challenges, yielding higher bias and MSE.
+Interestingly, traditional statistical approaches such as forward selection and backward elimination performed comparably to more sophisticated machine learning methods across many scenarios.
+This suggests that simpler approaches can still be viable, particularly in terms of bias and coverage, and might be preferred due to their computational efficiency.
 
@@
 
+The National Health and Nutrition Examination Survey (NHANES), conducted by the U.S.
+Centers for Disease Control and Prevention (CDC), involves collecting data through direct physical examinations, laboratory testing, and interviews.
+The CDC already obtains consent from participants when collecting this data.
+When researchers use NHANES data for their studies, they are typically using de-identified, publicly available data.
+This means that the information cannot be linked back to individual participants, and therefore, additional consent from participants is not required for researchers to use this data.
+
 ## Availability of data and materials {-}
+
+NHANES data is publicly accessible and can be retrieved from the NHANES website.
+The datasets generated and/or analyzed during the current study are available in the NHANES repository: https://www.cdc.gov/nchs/nhanes/index.htm.
+Additionally, all simulation results can be interactively reviewed through a Shiny web application at https://ehsanx.shinyapps.io/hdPS-Alternatives/.
 
@@
 
-Over the past three years, MEK has received consulting fees from Biogen Inc.
+MEK is currently supported by grants from Canadian Institutes of Health Research and MS Canada.
+MEK has previously received consulting fees from Biogen Inc.
 for consulting unrelated to this current work.
-MEK was previously supported by the Michael Smith Foundation for Health Research Scholar award.
+MEK was also previously supported by the Michael Smith Foundation for Health Research Scholar award.
 
@@
 
-This work was supported by MEK's Natural Sciences and Engineering Research Council of Canada (NSERC) Discovery Grants and Discovery Accelerator Supplements.
+This work was supported by MEK’s Natural Sciences and Engineering Research Council of Canada (NSERC) Discovery Grant (PG#: 20R01603) and Discovery Launch Supplement (PG#: 20R12709).
 

### 2024-09-24 Writeup/manuscript.tex
bmc correct

@@
 
-\abstract{\textbf{Purpose}: We aims to evaluate various proxy selection
+\abstract{\textbf{Purpose}: We aim to evaluate various proxy selection
 methods within the context of high-dimensional propensity score (hdPS)
-analysis. The study focuses on assessing the performance of these
-methods, including alternative variable selection approaches, in
-selecting proxy variables for confounding adjustment compared to the
-traditional hdPS method that is rooted in Bross formula. The goal is to
-understand better the performance of these alternative methods in
-estimating treatment effects, and identify scenarios in which they may
-perform better. \textbf{Methods:} Using data from three cycles of the
-National Health and Nutrition Examination Survey (NHANES) spanning
-2013-2018, we motivated the study by examining the association between
-obesity and diabetes. A plasmode simulation framework based on this data
-was employed to mimic real-world data structures. Simulations were
-conducted under three scenarios: Frequent Exposure and Outcome, Rare
-Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome.
-The performance of a variety of proxy selection methods---including
-tree-based methods, LASSO-based methods, and the Genetic Algorithm
-(GA)---was evaluated across these scenarios using standard simulation
-metrics. \textbf{Results:} XGBoost consistently demonstrated the lowest
-MSE and high coverage, making it a reliable method overall, although it
-did not always exhibit the lowest bias. In contrast, GA consistently
-showed the highest bias and MSE, with lower coverage and greater
-variability, indicating its unsuitability for accurate effect
-estimation. The kitchen sink model, Bross-based hdPS, and Hybrid hdPS
-methods performed moderately well, with low bias and moderate MSE, but
-varied in coverage across scenarios. Scenario-specific trends revealed
-that rare outcome scenarios yielded lower MSE and better precision,
-while rare exposure scenarios were associated with higher bias and MSE.
-\textbf{Conclusion:} Aside from GA, the performance of most other
-methods in your study appears to be comparable in each scenario, though
-with some variations depending on specific metrics. The findings
-underscore the importance of selecting appropriate methods for hdPS
-analysis based on the characteristics of the data, particularly the
-prevalence of exposure and outcome. While XGBoost excelled in overall
-accuracy and precision, the choice of method should be tailored to the
-specific epidemiological goal to optimize bias, coverage, and precision
-in estimating treatment effects.}
+analysis. This study aimed to systematically evaluate and compare the
+performance of traditional statistical methods and machine learning
+approaches within the hdPS framework, focusing on key metrics such as
+bias, standard error (SE), and coverage, under various exposure and
+outcome prevalence scenarios. \textbf{Methods:} We conducted a plasmode
+simulation study using data from the National Health and Nutrition
+Examination Survey (NHANES) cycles from 2013 to 2018. We compared
+methods including the kitchen sink model, Bross-based hdPS, Hybrid hdPS,
+LASSO, Elastic Net, Random Forest, XGBoost, and Genetic Algorithm (GA).
+The performance of each method was assessed based on bias, MSE, coverage
+probability, and SE estimation across three epidemiological scenarios:
+frequent exposure and outcome, rare exposure and frequent outcome, and
+frequent exposure and rare outcome. \textbf{Results:} XGBoost
+consistently demonstrated strong performance in terms of MSE and
+coverage, making it effective for scenarios prioritizing precision.
+However, it exhibited higher bias, particularly in rare exposure
+scenarios, suggesting it is less suited when minimizing bias is
+critical. In contrast, GA showed significant limitations, with
+consistently high bias and MSE, making it the least reliable method.
+Bross-based hdPS, and Hybrid hdPS methods provided a balanced approach,
+with low bias and moderate MSE, though coverage varied depending on the
+scenario. Rare outcome scenarios generally resulted in lower MSE and
+better precision, while rare exposure scenarios were associated with
+higher bias and MSE. Notably, traditional statistical approaches such as
+forward selection and backward elimination performed comparably to more
+sophisticated machine learning methods in terms of bias and coverage,
+suggesting that these simpler approaches may be viable alternatives due
+to their computational efficiency. \textbf{Conclusion:} The results
+highlight the importance of selecting hdPS methods based on the specific
+characteristics of the data, such as exposure and outcome prevalence.
+While advanced machine learning methods such as XGBoost can enhance
+precision, simpler methods such as forward selection or backward
+elimination may offer similar performance in terms of bias and coverage
+with fewer computational demands. Tailoring the choice of method to the
+epidemiological scenario is essential for optimizing the balance between
+bias reduction and precision.}
 
@@
 
+NHANES data is publicly accessible and can be retrieved from the NHANES
+website. The datasets generated and/or analyzed during the current study
+are available in the NHANES repository:
+\url{https://www.cdc.gov/nchs/nhanes/index.htm}. Additionally, all
+simulation results can be interactively reviewed through a Shiny web
+application at \url{https://ehsanx.shinyapps.io/hdPS-Alternatives/}.
+
+\subsection*{Clinical trial number}\label{clinical-trial-number}
+\addcontentsline{toc}{subsection}{Clinical trial number}
+
+Not applicable.
+
 \subsection*{Competing interests}\label{competing-interests}

### 2025-01-04 Writeup/bmc/figures/performance_measures_table.tex
plos1submission

\begin{table}[!h]
\centering
\begin{tabular}{l|l|l|l|l|l|l}
\hline
  & Bias & Empirical SE & MSE & Model-based SE & Coverage & Bias-eliminated Coverage\\
\hline
\cellcolor{gray!10}{Kitchen sink} & \cellcolor{gray!10}{0.0002 (0.0014)} & \cellcolor{gray!10}{0.0305 (0.0010)} & \cellcolor{gray!10}{0.0009 (0.0001)} & \cellcolor{gray!10}{0.0333 (0.0007)} & \cellcolor{gray!10}{0.9720 (0.0074)} & \cellcolor{gray!10}{0.9720 (0.0074)}\\
\hline
Bross-based hdPS & -0.0001 (0.0013) & 0.0287 (0.0009) & 0.0008 (0.0001) & 0.0318 (0.0006) & 0.9780 (0.0066) & 0.9760 (0.0068)\\
\hline
\cellcolor{gray!10}{Hybrid hdPS} & \cellcolor{gray!10}{0.0016 (0.0012)} & \cellcolor{gray!10}{0.0278 (0.0009)} & \cellcolor{gray!10}{0.0008 (0.0001)} & \cellcolor{gray!10}{0.0306 (0.0007)} & \cellcolor{gray!10}{0.9820 (0.0059)} & \cellcolor{gray!10}{0.9800 (0.0063)}\\
\hline
Genetic Algorithm & 0.0287 (0.0012) & 0.0274 (0.0009) & 0.0016 (0.0001) & 0.0285 (0.0003) & 0.8380 (0.0165) & 0.9600 (0.0088)\\
\hline
\cellcolor{gray!10}{XGBoost} & \cellcolor{gray!10}{0.0074 (0.0010)} & \cellcolor{gray!10}{0.0229 (0.0007)} & \cellcolor{gray!10}{0.0006 (0.0000)} & \cellcolor{gray!10}{0.0268 (0.0002)} & \cellcolor{gray!10}{0.9740 (0.0071)} & \cellcolor{gray!10}{0.9760 (0.0068)}\\
\hline
Random Forest & 0.0034 (0.0012) & 0.0278 (0.0009) & 0.0008 (0.0001) & 0.0303 (0.0005) & 0.9780 (0.0066) & 0.9700 (0.0076)\\
\hline
\cellcolor{gray!10}{Forward Selection} & \cellcolor{gray!10}{0.0059 (0.0012)} & \cellcolor{gray!10}{0.0271 (0.0009)} & \cellcolor{gray!10}{0.0008 (0.0001)} & \cellcolor{gray!10}{0.0304 (0.0008)} & \cellcolor{gray!10}{0.9800 (0.0063)} & \cellcolor{gray!10}{0.9760 (0.0068)}\\
\hline
Backward Elimination & 0.0063 (0.0013) & 0.0288 (0.0009) & 0.0009 (0.0001) & 0.0309 (0.0009) & 0.9820 (0.0059) & 0.9800 (0.0063)\\
\hline
\cellcolor{gray!10}{LASSO} & \cellcolor{gray!10}{0.0043 (0.0013)} & \cellcolor{gray!10}{0.0299 (0.0009)} & \cellcolor{gray!10}{0.0009 (0.0001)} & \cellcolor{gray!10}{0.0319 (0.0010)} & \cellcolor{gray!10}{0.9820 (0.0059)} & \cellcolor{gray!10}{0.9780 (0.0066)}\\
\hline
Elasticnet & 0.0036 (0.0013) & 0.0294 (0.0009) & 0.0009 (0.0001) & 0.0319 (0.0009) & 0.9800 (0.0063) & 0.9760 (0.0068)\\
\hline
\end{tabular}
\end{table}

### 2025-01-04 Writeup/bmc/figures/performance_measures_tableOR.tex
plos1submission

\begin{table}[!h]
\centering
\begin{tabular}{l|l|l|l|l|l|l}
\hline
  & Bias & Empirical SE & MSE & Model-based SE & Coverage & Bias-eliminated Coverage\\
\hline
\cellcolor{gray!10}{Kitchen sink} & \cellcolor{gray!10}{-0.0093 (0.0009)} & \cellcolor{gray!10}{0.0212 (0.0007)} & \cellcolor{gray!10}{0.0005 (0.0001)} & \cellcolor{gray!10}{0.0219 (0.0009)} & \cellcolor{gray!10}{0.9340 (0.0111)} & \cellcolor{gray!10}{0.9880 (0.0049)}\\
\hline
Bross-based hdPS & -0.0088 (0.0009) & 0.0206 (0.0007) & 0.0005 (0.0001) & 0.0215 (0.0011) & 0.9380 (0.0108) & 0.9900 (0.0044)\\
\hline
\cellcolor{gray!10}{Hybrid hdPS} & \cellcolor{gray!10}{-0.0082 (0.0008)} & \cellcolor{gray!10}{0.0184 (0.0006)} & \cellcolor{gray!10}{0.0004 (0.0000)} & \cellcolor{gray!10}{0.0198 (0.0007)} & \cellcolor{gray!10}{0.9360 (0.0109)} & \cellcolor{gray!10}{0.9880 (0.0049)}\\
\hline
Genetic Algorithm & 0.0362 (0.0023) & 0.0523 (0.0017) & 0.0040 (0.0003) & 0.0521 (0.0007) & 0.9180 (0.0123) & 0.9340 (0.0111)\\
\hline
\cellcolor{gray!10}{XGBoost} & \cellcolor{gray!10}{-0.0061 (0.0007)} & \cellcolor{gray!10}{0.0152 (0.0005)} & \cellcolor{gray!10}{0.0003 (0.0000)} & \cellcolor{gray!10}{0.0179 (0.0003)} & \cellcolor{gray!10}{0.9540 (0.0094)} & \cellcolor{gray!10}{0.9860 (0.0053)}\\
\hline
Random Forest & -0.0067 (0.0009) & 0.0206 (0.0007) & 0.0005 (0.0001) & 0.0203 (0.0009) & 0.9540 (0.0094) & 0.9840 (0.0056)\\
\hline
\cellcolor{gray!10}{Forward Selection} & \cellcolor{gray!10}{-0.0070 (0.0008)} & \cellcolor{gray!10}{0.0187 (0.0006)} & \cellcolor{gray!10}{0.0004 (0.0000)} & \cellcolor{gray!10}{0.0200 (0.0008)} & \cellcolor{gray!10}{0.9520 (0.0096)} & \cellcolor{gray!10}{0.9840 (0.0056)}\\
\hline
Backward Elimination & -0.0070 (0.0009) & 0.0206 (0.0007) & 0.0005 (0.0001) & 0.0209 (0.0014) & 0.9400 (0.0106) & 0.9840 (0.0056)\\
\hline
\cellcolor{gray!10}{LASSO} & \cellcolor{gray!10}{-0.0079 (0.0009)} & \cellcolor{gray!10}{0.0204 (0.0006)} & \cellcolor{gray!10}{0.0005 (0.0001)} & \cellcolor{gray!10}{0.0205 (0.0012)} & \cellcolor{gray!10}{0.9400 (0.0106)} & \cellcolor{gray!10}{0.9880 (0.0049)}\\
\hline
Elasticnet & -0.0079 (0.0009) & 0.0203 (0.0006) & 0.0005 (0.0001) & 0.0206 (0.0012) & 0.9360 (0.0109) & 0.9880 (0.0049)\\
\hline
\end{tabular}
\end{table}

### 2025-01-04 Writeup/plos/appendix/Appendix.tex
plos1submission

--- 2024-09-01 Writeup/appendix/Appendix.tex
@@
 \makeatother
-\subtitle{Challenges of Univariate Proxy Variable Screening in
-High-Dimensional Propensity Score Analysis - An Argument for
-Multivariate Approaches}
+\subtitle{Is There a Competitive Advantage to Using Multivariate
+Statistical or Machine Learning Methods Over the Bross Formula in the
+hdPS Framework for Bias and Variance Estimation?}
 \author{}
@@
 
-\section{True outcome model for Plasmode Simulation Data
+\section{True Outcome Model for Plasmode Simulation Data
 Generation}\label{true-outcome-model-for-plasmode-simulation-data-generation}
@@
 
-\section{SE comparison}\label{se-comparison}
+\section{Standard Error comparison}\label{standard-error-comparison}
 
